### 2017-12-18 article/ms.tex

\documentclass[a4paper,fleqn,usenatbib]{mnras}

\usepackage{newtxtext,newtxmath}
% Depending on your LaTeX fonts installation, you might get better results with one of these:
%\usepackage{mathptmx}
%\usepackage{txfonts}

\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}

\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[Short title, max. 45 characters]{MNRAS \LaTeXe\ template -- title goes here}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[K. T. Smith et al.]{
Keith T. Smith,$^{1}$\thanks{E-mail: mn@ras.org.uk (KTS)}
A. N. Other,$^{2}$
Third Author$^{2,3}$
and Fourth Author$^{3}$
\\
% List of institutions
$^{1}$Royal Astronomical Society, Burlington House, Piccadilly, London W1J 0BQ, UK\\
$^{2}$Department, Institution, Street Address, City Postal Code, Country\\
$^{3}$Another Department, Different Institution, Street Address, City Postal Code, Country
}

\date{Accepted XXX. Received YYY; in original form ZZZ}

\pubyear{2015}

\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle

\begin{abstract}
This is a simple template for authors to write new MNRAS papers.
The abstract should briefly describe the aims, methods, and main results of the paper.
It should be a single paragraph not more than 250 words (200 words for Letters).
No references should appear in the abstract.
\end{abstract}

\begin{keywords}
keyword1 -- keyword2 -- keyword3
\end{keywords}

\section{Introduction}

This is a simple template for authors to write new MNRAS papers.
See \texttt{mnras\_sample.tex} for a more complex example, and \texttt{mnras\_guide.tex}
for a full user guide.

All papers should start with an Introduction section, which sets the work
in context, cites relevant earlier studies in the field by \citet{Others2013},
and describes the problem the authors aim to solve \citep[e.g.][]{Author2012}.

\section{Methods, Observations, Simulations etc.}

Normally the next section describes the techniques the authors used.
It is frequently split into subsections, such as Section~\ref{sec:maths} below.

\subsection{Maths}
\label{sec:maths}

Simple mathematics can be inserted into the flow of the text e.g. $2\times3=6$
or $v=220$\,km\,s$^{-1}$, but more complicated expressions should be entered
as a numbered equation:

\begin{equation}
    x=\frac{-b\pm\sqrt{b^2-4ac}}{2a}.
	\label{eq:quadratic}
\end{equation}

Refer back to them as e.g. equation~(\ref{eq:quadratic}).

\subsection{Figures and tables}

Figures and tables should be placed at logical positions in the text. Don't
worry about the exact layout, which will be handled by the publishers.

Figures are referred to as e.g. Fig.~\ref{fig:example_figure}, and tables as
e.g. Table~\ref{tab:example_table}.

\begin{figure}
	% To include a figure from a file named example.*
	% Allowable file formats are eps or ps if compiling using latex
	% or pdf, png, jpg if compiling using pdflatex
	\includegraphics[width=\columnwidth]{example}
    \caption{This is an example figure. Captions appear below each figure.
	Give enough detail for the reader to understand what they're looking at,
	but leave detailed discussion to the main body of the text.}
    \label{fig:example_figure}
\end{figure}

\begin{table}
	\centering
	\caption{This is an example table. Captions appear above each table.
	Remember to define the quantities, symbols and units used.}
	\label{tab:example_table}
	\begin{tabular}{lccr} % four columns, alignment for each
		\hline
		A & B & C & D\\
		\hline
		1 & 2 & 3 & 4\\
		2 & 4 & 6 & 8\\
		3 & 5 & 7 & 9\\
		\hline
	\end{tabular}
\end{table}

\section{Conclusions}

The last numbered section should briefly summarise what has been done, and describe
the final conclusions which the authors draw from their work.

\section*{Acknowledgements}

The Acknowledgements section is not numbered. Here you can thank helpful
colleagues, acknowledge funding agencies, telescopes and facilities used etc.
Try to keep it short.

% The best way to enter references is to use BibTeX:

%\bibliographystyle{mnras}
%\bibliography{example} % if your bibtex file is called example.bib

\begin{thebibliography}{99}
\bibitem[\protect\citeauthoryear{Author}{2012}]{Author2012}
Author A.~N., 2013, Journal of Improbable Astronomy, 1, 1
\bibitem[\protect\citeauthoryear{Others}{2013}]{Others2013}
Others S., 2012, Journal of Interesting Stuff, 17, 198
\end{thebibliography}

\appendix

\section{Some extra material}

If you want to present additional material which would interrupt the flow of the main paper,
it can be placed in an Appendix which appears after the list of references.

% Don't change these lines
\bsp	% typesetting comment
\label{lastpage}
\end{document}

### 2018-01-10 Tc_process.py
Tc and Na check

@@ -1,0 +1,241 @@
+import numpy as np
+import os
+import matplotlib.pyplot as plt
+from astropy.table import Table
+
+import lamost
+import utils
+import pandas as pd
+
+plt.ioff()
+catalog = lamost.load_catalog()
+wavelengths = lamost.common_wavelengths
+N, P = (len(catalog), wavelengths.size)
+
+# Open the data arrays
+all_observed_flux = np.memmap(
+    os.path.join(lamost.LAMOST_PATH, "observed_flux.memmap"),
+    mode="r", dtype='float32', shape=(N, P))
+
+all_observed_ivar = np.memmap(
+    os.path.join(lamost.LAMOST_PATH, "observed_ivar.memmap"),
+    mode="r", dtype='float32', shape=(N, P))
+
+all_model_flux = np.memmap(
+    os.path.join(lamost.LAMOST_PATH, "model_flux.memmap"),
+    mode="r", dtype="float32", shape=(N, P))
+
+d = Table.read("Tc_catalog.fits")
+d.write("Tc_catalog.csv",overwrite=True)
+
+data=pd.read_csv('Tc_catalog.csv')
+
+csv=np.array(data)
+#Barium
+Ba4554_wavelength = csv[:,29] #
+Ba4554_amp = csv[:,13]
+Ba4554_amperr = csv[:,14]
+#Strontium
+St4077_wavelength = csv[:,31] #
+St4077_amp = csv[:,15]
+St4077_amperr = csv[:,16]
+
+#Technetium
+Tc4049_wavelength = csv[:,33] #
+Tc4049_amp = csv[:,17]
+Tc4049_amperr = csv[:,18]
+
+Tc4238_wavelength = csv[:,35] #
+Tc4238_amp = csv[:,19]
+Tc4238_amperr = csv[:,20]
+
+Tc4262_wavelength = csv[:,37] #
+Tc4262_amp = csv[:,21]
+Tc4262_amperr = csv[:,22]
+
+Tc4297_wavelength = csv[:,39] #
+Tc4297_amp = csv[:,23]
+Tc4297_amperr = csv[:,24]
+
+Tc5924_wavelength = csv[:,41] #
+Tc5924_amp = csv[:,25]
+Tc5924_amperr = csv[:,26]
+
+
+#Sodium
+Na5889_wavelength = csv[:,43] #
+Na5889_amp = csv[:,27]
[…]

### 2018-01-12 article/ms.tex
paper

@@
 
+\makeatletter
+\newcommand{\rmnum}[1]{\romannumeral #1}
+\newcommand{\Rmnum}[1]{\expandafter\@slowromancap\romannumeral #1@}
+\makeatother
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 % Keep the title short and informative.
-\title[Short title, max. 45 characters]{MNRAS \LaTeXe\ template -- title goes here}
+\title[Short title, max. 45 characters]{Mans not hot, Man can never be hot}
 
@@
 % If you need two or more lines of authors, add an extra line using \newauthor
-\author[K. T. Smith et al.]{
-Keith T. Smith,$^{1}$\thanks{E-mail: mn@ras.org.uk (KTS)}
+\author[B. J. Norfolk et al.]{
+Brodie J. Norfolk,$^{1}$\thanks{E-mail: bjee7@student.monash.edu (MU)}
 A. N. Other,$^{2}$
@@
 
-\pubyear{2015}
+\pubyear{2018}
 
@@
 
-This is a simple template for authors to write new MNRAS papers.
-See \texttt{mnras\_sample.tex} for a more complex example, and \texttt{mnras\_guide.tex}
-for a full user guide.
+Barium stars as first recognized by \citet{Bidelman1951}, are chemically unique red giants that exhibit envelopes with an overabundance of both carbon, and heavy elements (Z > 30) in comparison to the Sun.
+The red giants studied here display especially strong s-process enhancement for Ba\Rmnum{2} and Sr\Rmnum{2} at lines 4554\AA \hspace{0.2mm} and 4077\AA, respectively.
+(thinking I should extend this sentence with a little on the Carbon, maybe I should search for carbon in my figures ?).
+The slow newtron capture process (s-process), occuring in the interior of AGB (asymptotic giant branch) stars, synthesizes roughly half of all elements heavier than iron \citep[e.g.][]{busso1999,travaglio2001,
+herwig2005,romano2010,kobayashi2011,prantzos2012,bisterzo2014,
+karakas12016}.
+Late in the AGB phase, during the thermally pulsing-AGB (TP-AGB) phase, thermal instabilities occur in the He shell every $10^5$ years or so, depending on the H-exhausted core mass, and will drive a convective zone that sweeps the entire region lying between the core mass and He-shell mixing the products of nucleosynthesis within these regions.
+The energy from the thermal pulses force the star to expand, pushing the H-shell out to cooler regions and allowing the convective envelope to move inwards to regions previously mixed by the thermal pulse driven convective zones.
+This expansion and resultsing inward movement is classified as the third dredge up (TDU), and is theorized to occur after each thermal pulse.
+During the TP-AGB phase, enrichent on the surface in $^{12}$C and heavy elements produced by the s-process is a result of the repeated downwash extensions of TDU \citep[e.g.][]{busso2001}.
+Post TDU, the star contracts and reignites the H-shell producing the majority of the surface lumiosity for the next interpulse period.
+The interpulse, thermal pulse, and dredge up cycle may occur numerous times and is dependent on the intitial mass, composition and mass-loss rate of the star.
+\\
+mass ranges
+\\
+According to the mass-transfer hypothesis, extrinsic Barium stars are a consequence of stellar wind accretion \citep{boffin1988,jorissen1992} or Roche-lobe overflow \citep{webbink1986}, in a binary system containing a previous AGB companion star (intrinsic Barium star) in its final phase as a white dwarf \citep{bohm1980,bohm1984}.
+In fact, \citet{mcclure1983} determines 85\% of all Barium stars are in binary systems and those that appear singular are actually pole-on, or highly eccentric binaries with significant radial velocity variations only occuring in a small phase range as detailed by \citet{pourbaix2004}.
+\\
+In this paper ...
 
-All papers should start with an Introduction section, which sets the work
-in context, cites relevant earlier studies in the field by \citet{Others2013},
-and describes the problem the authors aim to solve \citep[e.g.][]{Author2012}.
+\section{Observations}
 
-\section{Methods, Observations, Simulations etc.}
+\section{Analysis and Results}
+
+\section{Discussion}
+
+\section{Conclusions}
+
+The last numbered section should briefly summarise what has been done, and describe
+the final conclusions which the authors draw from their work.
+
+\section*{Acknowledgements}
+
+The Acknowledgements section is not numbered. Here you can thank helpful
+colleagues, acknowledge funding agencies, telescopes and facilities used etc.
+Try to keep it short.
+
+\section{Examples}
 
@@
 
-\section{Conclusions}
-
-The last numbered section should briefly summarise what has been done, and describe
-the final conclusions which the authors draw from their work.
-
-\section*{Acknowledgements}
-
-The Acknowledgements section is not numbered. Here you can thank helpful
-colleagues, acknowledge funding agencies, telescopes and facilities used etc.
-Try to keep it short.
-
 % The best way to enter references is to use BibTeX:
 
-%\bibliographystyle{mnras}
-%\bibliography{example} % if your bibtex file is called example.bib
+\bibliographystyle{mnras}
+\bibliography{example} % if your bibtex file is called example.bib
 
@@
 Others S., 2012, Journal of Interesting Stuff, 17, 198
+
+\bibitem[\protect\citeauthoryear{Bidelman \& Keenan}{1951}]{Bidelman1951}
+Bidelman, W.~P. \& Keenan, P.~C. , 1951, ApJ, 114, 473
+\bibitem[\protect\citeauthoryear{Busso et al.}{1999}]{busso1999}
+Busso, M., Gallino, R., \& Wasserburg, P.~C. 1999, 
+ARA\& A, 37, 239
+\bibitem[\protect\citeauthoryear{Travaglio et al.}{2001}]{travaglio2001}
+Travaglio, C., et al. 2001, 
+ApJ, 549, 346
+\bibitem[\protect\citeauthoryear{Herwig}{2005}]{herwig2005}
+Herwig, F. 2005, 
+ARA\& A, 43, 435
+\bibitem[\protect\citeauthoryear{Romano et al.}{2010}]{romano2010}
+Romano, D., et al. 2010, 
+A\& A, 522, A32
+\bibitem[\protect\citeauthoryear{Kobayashi et al.}{2011}]{kobayashi2011}
+Kobayashi, C., Karakas, A., \& Umeda, H. 2011, 
+MNRAS, 414, 3231
+\bibitem[\protect\citeauthoryear{Prantzos}{2012}]{prantzos2012}
+Prantzos, N. 2012, 
+A\& A, 542, A67
+\bibitem[\protect\citeauthoryear{Bisterzo et al.}{2014}]{bisterzo2014}
+Bisterzo, S., et al. 2014, 
+ApJ, 787, 10
+\bibitem[\protect\citeauthoryear{Karakas}{2016}]{karakas12016}
+Karakas, A. 2016, 
+SAIt, 87, 229
+\bibitem[\protect\citeauthoryear{Busso et al.}{2001}]{busso2001}
+Busso, M., Gallino, R., Lambert, D.~L., Travaglio, C.\& Smith, V.~V. 2001, 
+ApJ, 557, 802
+\bibitem[\protect\citeauthoryear{McClure}{1983}]{mcclure1983}
+McClure, R.~D. 1983, 
+ApJ, 268, 264
+\bibitem[\protect\citeauthoryear{Pourbaix et al.}{2004}]{pourbaix2004}
+Pourbaix, D., Tokovinin, A.~A., Batten, A.~H., Fekel, F.~C., Hartkopf, W.~I. et al. 2001, 
+A\& A, 424, 727
+\bibitem[\protect\citeauthoryear{B\"ohm-Vitense}{1980}]{bohm1980}
+B\"ohm-Vitense, E. 1980, 
+ApJ, 239, L79
+\bibitem[\protect\citeauthoryear{B\"ohm-Vitense et al.}{1984}]{bohm1984}
+B\"ohm-Vitense, E., Nemec, J., Proffitt, C. 1984, 
+ApJ, 278, 726
+\bibitem[\protect\citeauthoryear{Boffin \& Jorissen}{1988}]{boffin1988}
+Boffin H, M.~J., Jorissen, A. 1988, 
+A\& A, 205, 155
+\bibitem[\protect\citeauthoryear{Jorissen \& Boffin}{1992}]{jorissen1992}
+Jorissen, A., Boffin H, M.~J., 1992, 
+Evidences for interaction among wide binary systems: To Ba or not to Ba? In: Duquennoy, A., Mayor, M.,(eds.) Binaries as tracers of stellar formation. Cambridge Univ. Press., p.185
+\bibitem[\protect\citeauthoryear{Webbink}{1986}]{webbink1986}
+Webbink, R.~F. 1986, 
+In: Leung, K.~C., Zhai, D.~S.(eds.) Critical Observations versus Physical Models for Close Binary Systems. Gordon and Breach, New York, p.403
+
 \end{thebibliography}

### 2018-01-15 article/ms.tex
introduction review

--- 2017-12-18 article/ms.tex
@@
 
-This is a simple template for authors to write new MNRAS papers.
-See \texttt{mnras\_sample.tex} for a more complex example, and \texttt{mnras\_guide.tex}
-for a full user guide.
+Barium stars as first recognized by \citet{Bidelman1951}, are chemically unique red giants that exhibit envelopes with an overabundance of both carbon, and heavy elements (Z > 30) in comparison to the Sun.
+The red giants studied here display especially strong s-process enhancement for Ba\Rmnum{2} and Sr\Rmnum{2} at lines 4554\AA \hspace{0.2mm} and 4077\AA, respectively.
+(thinking I should extend this sentence with a little on the Carbon, maybe I should search for carbon in my figures ?).
+The slow neutron capture process (s-process), occuring in the interior of AGB (asymptotic giant branch) stars, synthesizes roughly half of all elements heavier than iron \citep[e.g.][]{busso1999,travaglio2001,
+herwig2005,romano2010,kobayashi2011,prantzos2012,bisterzo2014,
+karakas12016}.
+Late in the AGB phase, during the thermally pulsing-AGB (TP-AGB) phase, thermal instabilities occur in the He shell every $10^5$ years or so, depending on the H-exhausted core mass, and will drive a convective zone that sweeps the entire region lying between the core mass and He-shell; mixing the products of nucleosynthesis within these regions.
+The energy from the thermal pulses force the star to expand, pushing the H-shell out to cooler regions and allowing the convective envelope to move inwards to regions previously mixed by the thermal pulse driven convective zones.
+This expansion and resultsing inward movement is classified as the third dredge up (TDU), and is theorized to occur after each thermal pulse.
+During the TP-AGB phase, enrichent on the surface in $^{12}$C and heavy elements produced by the s-process is a result of the repeated downwash extensions of TDU \citep[e.g.][]{busso2001}.
+Post TDU, the star contracts and reignites the H-shell producing the majority of the surface luminosity for the next interpulse period.
+The interpulse, thermal pulse, and dredge up cycle may occur numerous times and is dependent on the intitial mass, composition and mass-loss rate of the star.
 
-All papers should start with an Introduction section, which sets the work
-in context, cites relevant earlier studies in the field by \citet{Others2013},
-and describes the problem the authors aim to solve \citep[e.g.][]{Author2012}.
+Barium giants form within a metallicity dependent initial mass range (approximately 0.8 - 8$M_{\odot}$), with the minimum mass for core helium and carbon burning decreasing as metalicity decreases.
+The age of these stars vary considerably, with observable stars in metal-poor globular clusters hosting populations of $\approx$12Gyr.
+In contrast, metal rich, young observable stars reaching the upper limit may only reach $\approx$100Myr, this includes stars that are at the core carbon burning limit or very close to it \citep[e.g.][]{whitelock2013}.
 
-\section{Methods, Observations, Simulations etc.}
+According to the mass-transfer hypothesis, extrinsic Barium stars are a consequence of stellar wind accretion \citep{boffin1988,jorissen1992} or Roche-lobe overflow \citep{webbink1986}, and are within a binary system containing a previous AGB companion star (intrinsic Barium star) in its final phase as a white dwarf \citep{bohm1980,bohm1984}.
+In fact, \citet{mcclure1983} determines 85\% of all Barium stars are in binary systems and those that appear singular are actually pole-on, or highly eccentric binaries with significant radial velocity variations only occuring in a small phase range as detailed by \citet{pourbaix2004}.
 
-Normally the next section describes the techniques the authors used.
-It is frequently split into subsections, such as Section~\ref{sec:maths} below.
+Barium stars currently have only been discovered in the disk and halo of the Galaxy according to \citet{gomez1997} and \citet{mennessier1997}.
+Both studies show the stellar populations of Barium stars can be seperated into two groups when divided according to luminosity, kinematic and spatial parameters.
+Barium stars populating the halo have already been investigated \citep[e.g.][]{junqueira2001,drake2008,pereira2009,allen2006} and their relationship with metal-poor, yellow, symbiotic halo stars has been established by \citet{jorissen2005} and \citet{pereira2009}.
+Additionally, \citet{pereira2011} concludes metal-rich barium stars share similar kinematics to other metal-rich and super metal-rich stars already analysed, demonstrating they do not belong to the bulge population.
+Furthermore, it is neccessary to establish known abundances of s-process elements in a greater sample of Barium stars to conclude the percentage population of said stars in the Galaxy, and compare with their theoratical birthrate \citep{han1995}
 
-\subsection{Maths}
-\label{sec:maths}
+In this paper we analysis the \textit{Cannon} fitted LAMOST spectra \citep{ho2017} to obtain a sample set of s-process enriched Barium stars and investigate atmospheric parameters including, the distributions of temperature, surface gravity and metalicity.
+Additionally, the abundances of elements not produced in the s-process such as sodium and technetium (Na and Tc) are examined to determine  if the sample Barium stars share similar abundance to field giants with equal metallicities.
+Moreover, the stellar sample is cross matched with GAIA, producing (not sure exactly what gaia gave us) neccessary to determine the kinematics of our Barium samples.
 
-Simple mathematics can be inserted into the flow of the text e.g. $2\times3=6$
-or $v=220$\,km\,s$^{-1}$, but more complicated expressions should be entered
-as a numbered equation:
+In our research we analysed 272 Barium canidates amoung the 454,180 stellar sample produced by \citet{ho2017} and with GAIA determined the galactic motions for 21 out the 272 canidates.
 
-\begin{equation}
-    x=\frac{-b\pm\sqrt{b^2-4ac}}{2a}.
-	\label{eq:quadratic}
-\end{equation}
+\section{Observations, Target Selection}
+The low-resolution spectra of our stars were obtained from the \textit{Cannon} fits predictive model implemented by \citet{ho2017} on the LAMOST (Large Sky Area Multi-Object Fibre Spectroscopic Telescope) DR2 release \citep{luo2015}.
+The resulting 454,180 stellar data set contains infered $T_{eff}$, $log g$, $[Fe/H]$, and [$\alpha/M$] values.
 
-Refer back to them as e.g. equation~(\ref{eq:quadratic}).
+\section{Analysis and Results}
+\subsection{Line Selection}
+\subsection{Technetium Lines}
+\subsection{Abundance Analysis}
+\subsection{Abundance Uncertainties}
 
-\subsection{Figures and tables}
-
-Figures and tables should be placed at logical positions in the text. Don't
-worry about the exact layout, which will be handled by the publishers.
-
-Figures are referred to as e.g. Fig.~\ref{fig:example_figure}, and tables as
-e.g. Table~\ref{tab:example_table}.
-
-\begin{figure}
-	% To include a figure from a file named example.*
-	% Allowable file formats are eps or ps if compiling using latex
-	% or pdf, png, jpg if compiling using pdflatex
-	\includegraphics[width=\columnwidth]{example}
-    \caption{This is an example figure. Captions appear below each figure.
-	Give enough detail for the reader to understand what they're looking at,
-	but leave detailed discussion to the main body of the text.}
-    \label{fig:example_figure}
-\end{figure}
-
-\begin{table}
-	\centering
-	\caption{This is an example table. Captions appear above each table.
-	Remember to define the quantities, symbols and units used.}
-	\label{tab:example_table}
-	\begin{tabular}{lccr} % four columns, alignment for each
-		\hline
-		A & B & C & D\\
-		\hline
-		1 & 2 & 3 & 4\\
-		2 & 4 & 6 & 8\\
-		3 & 5 & 7 & 9\\
-		\hline
-	\end{tabular}
-\end{table}
+\section{Discussion}
 
@@
 
+%\section{Examples}
+%
+%Normally the next section describes the techniques the authors used.
+%It is frequently split into subsections, such as Section~\ref{sec:maths} below.
+%
+%\subsection{Maths}
+%\label{sec:maths} 
+%
+%Simple mathematics can be inserted into the flow of the text e.g. $2\times3=6$
+%or $v=220$\,km\,s$^{-1}$, but more complicated expressions should be entered
+%as a numbered equation:
+%
+%\begin{equation}
+%    x=\frac{-b\pm\sqrt{b^2-4ac}}{2a}.
+%	\label{eq:quadratic}
+%\end{equation}
+%
+%Refer back to them as e.g. equation~(\ref{eq:quadratic}).
+%
+%\subsection{Figures and tables}
+%
+%Figures and tables should be placed at logical positions in the text. Don't
+%worry about the exact layout, which will be handled by the publishers.
+%
+%Figures are referred to as e.g. Fig.~\ref{fig:example_figure}, and tables as
+%e.g. Table~\ref{tab:example_table}.
+%
+%\begin{figure}
+%	% To include a figure from a file named example.*
+%	% Allowable file formats are eps or ps if compiling using latex
+%	% or pdf, png, jpg if compiling using pdflatex
+%	\includegraphics[width=\columnwidth]{example}
+%    \caption{This is an example figure. Captions appear below each figure.
+%	Give enough detail for the reader to understand what they're looking at,
+%	but leave detailed discussion to the main body of the text.}
+%    \label{fig:example_figure}
+%\end{figure}
+%
+%
+%\begin{table}
+%	\centering
+%	\caption{This is an example table. Captions appear above each table.
+%	Remember to define the quantities, symbols and units used.}
+%	\label{tab:example_table}
+%	\begin{tabular}{lccr} % four columns, alignment for each
+%		\hline
+%		A & B & C & D\\
+%		\hline
+%		1 & 2 & 3 & 4\\
+%		2 & 4 & 6 & 8\\
+%		3 & 5 & 7 & 9\\
+%		\hline
+%	\end{tabular}
+%\end{table}
+
 % The best way to enter references is to use BibTeX:
 
-%\bibliographystyle{mnras}
-%\bibliography{example} % if your bibtex file is called example.bib
+\bibliographystyle{mnras}
+\bibliography{example} % if your bibtex file is called example.bib
 
@@
 Others S., 2012, Journal of Interesting Stuff, 17, 198
+
+\bibitem[\protect\citeauthoryear{Bidelman \& Keenan}{1951}]{Bidelman1951}
+Bidelman, W.~P. \& Keenan, P.~C. , 1951, ApJ, 114, 473
+\bibitem[\protect\citeauthoryear{Busso et al.}{1999}]{busso1999}
+Busso, M., Gallino, R., \& Wasserburg, P.~C. 1999, 
+ARA$\&$A, 37, 239
+\bibitem[\protect\citeauthoryear{Travaglio et al.}{2001}]{travaglio2001}
+Travaglio, C., et al. 2001, 
+ApJ, 549, 346
+\bibitem[\protect\citeauthoryear{Herwig}{2005}]{herwig2005}
+Herwig, F. 2005, 
+ARA$\&$A, 43, 435
+\bibitem[\protect\citeauthoryear{Romano et al.}{2010}]{romano2010}
+Romano, D., et al. 2010, 
+A$\&$A, 522, A32
+\bibitem[\protect\citeauthoryear{Kobayashi et al.}{2011}]{kobayashi2011}
+Kobayashi, C., Karakas, A., \& Umeda, H. 2011, 
+MNRAS, 414, 3231
+\bibitem[\protect\citeauthoryear{Prantzos}{2012}]{prantzos2012}
+Prantzos, N. 2012, 
+A$\&$A, 542, A67
+\bibitem[\protect\citeauthoryear{Bisterzo et al.}{2014}]{bisterzo2014}
+Bisterzo, S., et al. 2014, 
+ApJ, 787, 10
+\bibitem[\protect\citeauthoryear{Karakas}{2016}]{karakas12016}
+Karakas, A. 2016, 
+SAIt, 87, 229
+\bibitem[\protect\citeauthoryear{Busso et al.}{2001}]{busso2001}
+Busso, M., Gallino, R., Lambert, D.~L., Travaglio, C.\& Smith, V.~V. 2001, 
+ApJ, 557, 802
+\bibitem[\protect\citeauthoryear{McClure}{1983}]{mcclure1983}
+McClure, R.~D. 1983, 
+ApJ, 268, 264
+\bibitem[\protect\citeauthoryear{Pourbaix et al.}{2004}]{pourbaix2004}
+Pourbaix, D., Tokovinin, A.~A., Batten, A.~H., Fekel, F.~C., Hartkopf, W.~I. et al. 2001, 
+A$\&$A, 424, 727
+\bibitem[\protect\citeauthoryear{B\"ohm-Vitense}{1980}]{bohm1980}
+B\"ohm-Vitense, E. 1980, 
+ApJ, 239, L79
+\bibitem[\protect\citeauthoryear{B\"ohm-Vitense et al.}{1984}]{bohm1984}
+B\"ohm-Vitense, E., Nemec, J.,\& Proffitt, C. 1984, 
+ApJ, 278, 726
+\bibitem[\protect\citeauthoryear{Boffin \& Jorissen}{1988}]{boffin1988}
+Boffin H, M.~J.,\& Jorissen, A. 1988, 
+A$\&$A, 205, 155
+\bibitem[\protect\citeauthoryear{Jorissen \& Boffin}{1992}]{jorissen1992}
+Jorissen, A.,\& Boffin H, M.~J., 1992, 
+Evidences for interaction among wide binary systems: To Ba or not to Ba? In: Duquennoy, A., Mayor, M.,(eds.) Binaries as tracers of stellar formation. Cambridge Univ. Press., p.185
+\bibitem[\protect\citeauthoryear{Webbink}{1986}]{webbink1986}
+Webbink, R.~F. 1986, 
+In: Leung, K.~C., Zhai, D.~S.(eds.) Critical Observations versus Physical Models for Close Binary Systems. Gordon and Breach, New York, p.403
+\bibitem[\protect\citeauthoryear{Whitelock et al.}{2013}]{whitelock2013}
+Whitelock, P.~A., et al. 2013, 
+MNRAS, 428, 2216
+\bibitem[\protect\citeauthoryear{Gomez et al.}{1997}]{gomez1997}
+Gomez, A.~E., Luri, X., Grenier, S., et al. 1997, 
+A$\&$A, 319, 881
+\bibitem[\protect\citeauthoryear{Mennessier et al.}{1997}]{mennessier1997}
+Mennessier, M.~O., Luri, X., Figueras, F., et al. 1997, 
+A$\&$A, 326, 722
+\bibitem[\protect\citeauthoryear{Junqueira \& Pereira}{2001}]{junqueira2001}
+Junqueira S.,\& Pereira, C.~B. 2001, 
+AJ, 122, 360
+\bibitem[\protect\citeauthoryear{Drake \& Pereira}{2008}]{drake2008}
+Drake N.,~A.,\& Pereira, C.~B. 2008, 
+AJ, 135, 1070
+\bibitem[\protect\citeauthoryear{Pereira \& Drake}{2009}]{pereira2009}
+Pereira, C.~B.,\& Drake N.,~A. 2009, 
+A$\&$A, 496, 791
+\bibitem[\protect\citeauthoryear{Allen \& Barbuy}{2006}]{allen2006}
+Allen, D.~M.,\& Barbuy B. 2006, 
+A$\&$A, 454, 917
+\bibitem[\protect\citeauthoryear{Jorissen et al.}{2005}]{jorissen2005}
+Jorissen, A., Za$\check{c}$, L., Udry, S., Lindgren, H.,\& Musaev, F.~A. 2005, 
+A$\&$A, 441, 1135
+\bibitem[\protect\citeauthoryear{Han et al.}{1995}]{han1995}
+Han, Z., Eggleton, P.~P., Podsiadlowski, P.,\& Tout, C.~A. 1995, 
+MNRAS, 277, 1443
+\bibitem[\protect\citeauthoryear{Pereira et al.}{2011}]{pereira2011}
+Pereira, C.~B., Sales Silva, J.,~A., Chavero, C., Roig, F.,\& Jilinski E. 2011, 
+A$\&$A, 533, A51
+\bibitem[\protect\citeauthoryear{Ho et al.}{2017}]{ho2017}
+Ho, A.~Y.~Q., Ness, M.~K., Hogg, D.~W. Rix, H.-W. Liu, C. Yang, F. Zhang, Y. Hou,\& Y. Wang, Y. 2017, 
+ApJ, 836, 5
+\bibitem[\protect\citeauthoryear{Luo A.L., Bai Z.R. et al}{(2015)}]{luo2015}
+Luo, A.~L., Bai, Z.~R., et al. 2015, 
+RAA, in press
+
 \end{thebibliography}

### 2018-01-16 article/ms.tex
observ/target section

@@
 
-In our research we analysed 272 Barium canidates amoung the 454,180 stellar sample produced by \citet{ho2017} and with GAIA determined the galactic motions for 21 out the 272 canidates.
+In our research we analysed 273 Barium canidates amoung the 454,180 stellar sample produced by \citet{ho2017} and with GAIA determined the galactic motions for 21 out the 273 canidates.
 
-\section{Observations, Target Selection}
-The low-resolution spectra of our stars were obtained from the \textit{Cannon} fits predictive model implemented by \citet{ho2017} on the LAMOST (Large Sky Area Multi-Object Fibre Spectroscopic Telescope) DR2 release \citep{luo2015}.
-The resulting 454,180 stellar data set contains infered $T_{eff}$, $log g$, $[Fe/H]$, and [$\alpha/M$] values.
+\section{Observations and Target Selection}
+The spectral data of our stars were obtained from the \textit{Cannon} fits predictive model implemented by \citet{ho2017} on the LAMOST (Large Sky Area Multi-Object Fibre Spectroscopic Telescope) DR2 release \citep{luo2015}.
+The LAMOST spectral resolving power of R = 1800, a wavelength coverage from 3700$\AA$ to 9000$\AA$, and a nominal S/N ratio of 100.
+\citet{ho2017} cross-matches 9,952 stars between the low resolution spectra of LAMOST and the high resolution spectra from the APOGEE survey, and through a data driven spectral model.
+produces a 454,180 stellar data set.
+For this stellar data set the \textit{Cannon} predictive model infers $T_{eff}$, $log g$, $[Fe/H]$, and [$\alpha/M$] values.
+
+The Barium stars analysed in this research were obtained by filtering for significant flux residuals, taken as, a disparity between the normalised LAMOST flux and the data driven model derived by \citet{ho2017}.
+A negative residual as shown in (I know I shoould expand here on the psoter child)figure \ref{fig:figure1} illustrates an enhancement in Ba\Rmnum{2} and Sr\Rmnum{2} at lines 4554\AA \hspace{0.2mm} and 4077\AA, respectively.
+(thinking a sentence on why these lines are the strongest ?).
+The filter process had five requirements that each spectra for both enhancement lines had to meet to be considered a Barium star canidate, these included:
+
+\renewcommand\labelenumi{(\roman{enumi})}
+\renewcommand\theenumi\labelenumi
+
+\begin{enumerate} 
+\item Profile amplitude for both enhancement lines must exceed A$\leq$-0.05.
+\item Both amplittudes must be measured within 3$\sigma$ $(|A|/\sigma _A \geq 3)$.
+\item The wavelength at each absorption line must be within $2$\AA \hspace{0.2mm}$(\lambda \leq 2)$.
+\item The chi must be less then 3 (not sure on math wrting for this).
+\item And, the spectra must have a signal-to-noise ratio of S/N $\geq 30$.
+\end{enumerate}
+In addition, a visual observation of the accuracy between each normalised LAMOST flux and its accompanying data driven model was undertaken to exclude any results containing, false positives, candidates exhibiting data reduction issues, apparent absorption finer then the spectral resolution, and overly noisy normalised LAMOST spectra.
+This combined method generated the 273 Barium star candidates as listed in Table \ref{table:table1}.
 
 \section{Analysis and Results}
+
 \subsection{Line Selection}

### 2018-01-16 article/ms.tex
comments

@@
 % If you need two or more lines of authors, add an extra line using \newauthor
-\author[B. J. Norfolk et al.]{
-Brodie J. Norfolk,$^{1}$\thanks{E-mail: bjee7@student.monash.edu (MU)}
-A. N. Other,$^{2}$
-Third Author$^{2,3}$
-and Fourth Author$^{3}$
+\author[B. J. Norfolk et al.]{Brodie J. Norfolk,$^{1}$\thanks{E-mail: bjee7@student.monash.edu (MU)}
+Andrew R. Casey,$^{1,2}$
+Ernie? Kemp? Karakas? Lattanzio? \newauthor
+Schlaufman? others?
 \\
 % List of institutions
-$^{1}$Royal Astronomical Society, Burlington House, Piccadilly, London W1J 0BQ, UK\\
-$^{2}$Department, Institution, Street Address, City Postal Code, Country\\
-$^{3}$Another Department, Different Institution, Street Address, City Postal Code, Country
+$^{1}$School of Physics \& Astronomy, Monash University, Clayton 3800, Victoria, Australia\\
+$^{2}$Faculty of Information Technology, Monash University, Clayton 3800, Victoria, Australia\\
 }
@@
 \section{Introduction}
+
+% What's a barium star (as observed)? What is the s-process
+
+% What causes a barium star? (extrinsic/intrinsic?)
+
+% AGB stars and the s-process.
+
+% Comparisons to expectations of theoretical birth rate
+% Binary fraction at different metallicities
+% Mass differentials of binary stars
+% Yields of AGB stars at different masses and metallicities.
 

### 2018-01-16 article/ms.tex
fixed serious issue with title /cc @bjnorfolk
suggested edits to agb and s-process paragraph

@@
 
+\usepackage{color}
+\newcommand{\todo}[1]{\textcolor{red}{#1}}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 % Keep the title short and informative.
-\title[Short title, max. 45 characters]{Mans not hot, Man can never be hot}
+\title[Short title, max. 45 characters]{Man's not hot, Man can never be hot}
 
@@
 
-% What's a barium star (as observed)? What is the s-process
+% What's a barium star (as observed)?% What causes a barium star? (extrinsic/intrinsic?)
 
-% What causes a barium star? (extrinsic/intrinsic?)
+Barium stars are chemically unusual red giants with an overabundance of carbon and heavy elements ($Z > 30$) relative to the Sun \citep{Bidelman1951}.
+\todo{Explain why this chemical signature is unusual: because this signature can really only be produced by TP-AGB stars, but we see barium stars that have not evolved to the AGB stars.
+Introduce extrinsic/intrinsic.
+Barium stars are considered to have been polluted by a binary TP-AGB star, or they are TP-AGB stars themselves.}
 
 % AGB stars and the s-process.
+
+About half of all heavy elements are produced by the slow neutron-capture process ($s$-process) inside asymptotic giant branch (AGB) stars \citep[e.g.][]{busso1999,travaglio2001,
+herwig2005,romano2010,kobayashi2011,prantzos2012,bisterzo2014,
+karakas12016}. 
+\todo{This is very good, but the sentence needs splitting up: Late in the AGB phase, during the thermally pulsing-AGB (TP-AGB) phase, thermal instabilities occur in the He shell every $10^5$ years or so, depending on the H-exhausted core mass, and will drive a convective zone that sweeps the entire region lying between the core mass and He-shell; mixing the products of nucleosynthesis within these regions.} The energy from each thermal pulse forces the star to expand, pushing the H-shell out to cooler regions and allowing the convective envelope to move inwards to regions previously mixed by the thermally-driven convective zone.
+This expansion and resulting inward movement is described as the third dredge up (TDU), and is theorised to occur after every thermal pulse.
+The repeated downwash extensions of TDU cause enhancement of surface $^{12}$C abundance and of other heavy elements produced by the s-process \citep[e.g.,][]{busso2001}.
+The star contracts after \todo{PDU} and reignites the H-shell, producing the majority of the surface luminosity for the next interpulse period.
+The interpulse, thermal pulse, and dredge up cycle may occur numerous times and is dependent on the initial mass, composition, and mass-loss rate of the star.
+
+Barium giants form within a metallicity dependent initial mass range (approximately 0.8 - 8$M_{\odot}$), with the minimum mass for core helium and carbon burning decreasing as metalicity decreases.
+The age of these stars vary considerably, with observable stars in metal-poor globular clusters hosting populations of $\approx$12Gyr.
+In contrast, metal rich, young observable stars reaching the upper limit may only reach $\approx$100Myr, this includes stars that are at the core carbon burning limit or very close to it \citep[e.g.][]{whitelock2013}.
 
@@
 % Yields of AGB stars at different masses and metallicities.
-
-Barium stars as first recognized by \citet{Bidelman1951}, are chemically unique red giants that exhibit envelopes with an overabundance of both carbon, and heavy elements (Z > 30) in comparison to the Sun.
-The red giants studied here display especially strong s-process enhancement for Ba\Rmnum{2} and Sr\Rmnum{2} at lines 4554\AA \hspace{0.2mm} and 4077\AA, respectively.
-(thinking I should extend this sentence with a little on the Carbon, maybe I should search for carbon in my figures ?).
-The slow neutron capture process (s-process), occuring in the interior of AGB (asymptotic giant branch) stars, synthesizes roughly half of all elements heavier than iron \citep[e.g.][]{busso1999,travaglio2001,
-herwig2005,romano2010,kobayashi2011,prantzos2012,bisterzo2014,
-karakas12016}.
-Late in the AGB phase, during the thermally pulsing-AGB (TP-AGB) phase, thermal instabilities occur in the He shell every $10^5$ years or so, depending on the H-exhausted core mass, and will drive a convective zone that sweeps the entire region lying between the core mass and He-shell; mixing the products of nucleosynthesis within these regions.
-The energy from the thermal pulses force the star to expand, pushing the H-shell out to cooler regions and allowing the convective envelope to move inwards to regions previously mixed by the thermal pulse driven convective zones.
-This expansion and resultsing inward movement is classified as the third dredge up (TDU), and is theorized to occur after each thermal pulse.
-During the TP-AGB phase, enrichent on the surface in $^{12}$C and heavy elements produced by the s-process is a result of the repeated downwash extensions of TDU \citep[e.g.][]{busso2001}.
-Post TDU, the star contracts and reignites the H-shell producing the majority of the surface luminosity for the next interpulse period.
-The interpulse, thermal pulse, and dredge up cycle may occur numerous times and is dependent on the intitial mass, composition and mass-loss rate of the star.
-
-Barium giants form within a metallicity dependent initial mass range (approximately 0.8 - 8$M_{\odot}$), with the minimum mass for core helium and carbon burning decreasing as metalicity decreases.
-The age of these stars vary considerably, with observable stars in metal-poor globular clusters hosting populations of $\approx$12Gyr.
-In contrast, metal rich, young observable stars reaching the upper limit may only reach $\approx$100Myr, this includes stars that are at the core carbon burning limit or very close to it \citep[e.g.][]{whitelock2013}.
 
@@
 Furthermore, it is neccessary to establish known abundances of s-process elements in a greater sample of Barium stars to conclude the percentage population of said stars in the Galaxy, and compare with their theoratical birthrate \citep{han1995}
+
+\todo{The red giants studied here display especially strong s-process enhancement for \ion{Ba}{II} and \ion{Sr}{II} at lines 4554\AA\ and 4077\AA, respectively.
+(thinking I should extend this sentence with a little on the Carbon, maybe I should search for carbon in my figures ?).
+}
 

### 2018-01-16 article/ms.tex
intro edits

@@
 Andrew R. Casey,$^{1,2}$
-Ernie? Kemp? Karakas? Lattanzio? \newauthor
+Ernie? Kemp? Karakas? Lattanzio? Ho?\newauthor
 Schlaufman? others?
@@
 
-Barium stars are chemically unusual red giants with an overabundance of carbon and heavy elements ($Z > 30$) relative to the Sun \citep{Bidelman1951}.
+Barium stars are red giants with an unusual overabundance of carbon and heavy elements ($Z > 30$) relative to the Sun \citep{Bidelman1951}.
 \todo{Explain why this chemical signature is unusual: because this signature can really only be produced by TP-AGB stars, but we see barium stars that have not evolved to the AGB stars.
@@
 Barium stars are considered to have been polluted by a binary TP-AGB star, or they are TP-AGB stars themselves.}
+For these reasons, the properties and occurrence rate of barium stars are informative of the theoretical birth rate of AGB stars, the binary star fraction as a function of metallicity, the mass ratio of binary stars, as well as AGB yields across different masses and metallicities.
 
@@
 
-About half of all heavy elements are produced by the slow neutron-capture process ($s$-process) inside asymptotic giant branch (AGB) stars \citep[e.g.][]{busso1999,travaglio2001,
+About half of all heavy elements are produced by the slow neutron-capture process (s-process) inside asymptotic giant branch (AGB) stars \citep[e.g.][]{busso1999,travaglio2001,
 herwig2005,romano2010,kobayashi2011,prantzos2012,bisterzo2014,
@@
 
-Barium giants form within a metallicity dependent initial mass range (approximately 0.8 - 8$M_{\odot}$), with the minimum mass for core helium and carbon burning decreasing as metalicity decreases.
+% Link AGB stars and barium stars.
+
+According to the mass-transfer hypothesis, extrinsic Barium stars are a consequence of stellar wind accretion \citep{boffin1988,jorissen1992} or Roche-lobe overflow \citep{webbink1986}, and are within a binary system containing a previous AGB companion star (intrinsic Barium star) in its final phase as a white dwarf \citep{bohm1980,bohm1984}.
+In fact, \citet{mcclure1983} determines 85\% of all Barium stars are in binary systems and those that appear singular are actually pole-on, or highly eccentric binaries with significant radial velocity variations only occurring in a small phase range as detailed by \citet{pourbaix2004}.
+
+% Properties of barium stars.
+
+Barium giants form within a metallicity dependent initial mass range (approximately 0.8 - 8$M_{\odot}$), with the minimum mass for core helium and carbon burning decreasing as metallicity decreases.
 The age of these stars vary considerably, with observable stars in metal-poor globular clusters hosting populations of $\approx$12Gyr.
@@
 
-According to the mass-transfer hypothesis, extrinsic Barium stars are a consequence of stellar wind accretion \citep{boffin1988,jorissen1992} or Roche-lobe overflow \citep{webbink1986}, and are within a binary system containing a previous AGB companion star (intrinsic Barium star) in its final phase as a white dwarf \citep{bohm1980,bohm1984}.
-In fact, \citet{mcclure1983} determines 85\% of all Barium stars are in binary systems and those that appear singular are actually pole-on, or highly eccentric binaries with significant radial velocity variations only occuring in a small phase range as detailed by \citet{pourbaix2004}.
+Many barium stars have been discovered in the disk and halo of the Milky Way \citep{gomez1997,mennessier1997}.
+Both studies show that the stellar populations of Barium stars can be separated into two groups when considering their \todo{absolute?} luminosity, kinematic, and spatial properties.
+Barium stars populating the halo have already been investigated \citep[e.g.][]{junqueira2001,drake2008,pereira2009,allen2006} and their relationship with metal-poor, yellow, symbiotic halo stars has been established by \citet{jorissen2005} and \citet{pereira2009}.
+Additionally, \citet{pereira2011} concludes metal-rich barium stars share similar kinematics to other metal-rich and super metal-rich stars already analysed, suggesting that they do not belong to the bulge population.
+Furthermore, it is necessary to establish known abundances of s-process elements in a greater sample of Barium stars in order to compare their birth rate to theoretical expectations   \citep{han1995}, explore the binary fraction at different metallicities, and infer AGB star yields at different masses and metallicities.
 
-Barium stars currently have only been discovered in the disk and halo of the Galaxy according to \citet{gomez1997} and \citet{mennessier1997}.
-Both studies show the stellar populations of Barium stars can be seperated into two groups when divided according to luminosity, kinematic and spatial parameters.
-Barium stars populating the halo have already been investigated \citep[e.g.][]{junqueira2001,drake2008,pereira2009,allen2006} and their relationship with metal-poor, yellow, symbiotic halo stars has been established by \citet{jorissen2005} and \citet{pereira2009}.
-Additionally, \citet{pereira2011} concludes metal-rich barium stars share similar kinematics to other metal-rich and super metal-rich stars already analysed, demonstrating they do not belong to the bulge population.
-Furthermore, it is neccessary to establish known abundances of s-process elements in a greater sample of Barium stars to conclude the percentage population of said stars in the Galaxy, and compare with their theoratical birthrate \citep{han1995}
+In this paper we analysis 454,180 giant stars from LAMOST data release (DR) 2 to identify and examine 273 Barium star candidates that show enhancements of s-process elements.
+In Section \ref{sec:observations} we describe the observations and candidate selection, as well as the analysis follow up our follow-up observing campaign.
+In Section \ref{sec:discussion} we discuss the properties of our Barium stars in context of existing literature.
+We provide concluding remarks in Section \ref{sec:conclusion}
 
-\todo{The red giants studied here display especially strong s-process enhancement for \ion{Ba}{II} and \ion{Sr}{II} at lines 4554\AA\ and 4077\AA, respectively.
-(thinking I should extend this sentence with a little on the Carbon, maybe I should search for carbon in my figures ?).
-}
-
-In this paper we analysis the \textit{Cannon} fitted LAMOST spectra \citep{ho2017} to obtain a sample set of s-process enriched Barium stars and investigate atmospheric parameters including, the distributions of temperature, surface gravity and metalicity.
+%and investigate atmospheric parameters including, the distributions of temperature, surface gravity and metalicity.
 Additionally, the abundances of elements not produced in the s-process such as sodium and technetium (Na and Tc) are examined to determine  if the sample Barium stars share similar abundance to field giants with equal metallicities.
@@
 
-In our research we analysed 273 Barium canidates amoung the 454,180 stellar sample produced by \citet{ho2017} and with GAIA determined the galactic motions for 21 out the 273 canidates.
+% move to observations and target selection:
+%In our research we analysed 273 Barium canidates amoung the 454,180 stellar sample produced by \citet{ho2017} and with GAIA determined the galactic motions for 21 out the 273 canidates.
+
+\todo{move or remove: The red giants studied here display especially strong s-process enhancement for \ion{Ba}{II} and \ion{Sr}{II} at lines 4554\AA\ and 4077\AA, respectively.
+(thinking I should extend this sentence with a little on the Carbon, maybe I should search for carbon in my figures ?).
+}
 

### 2018-01-16 article/ms.tex

@@
 The spectral data of our stars were obtained from the \textit{Cannon} fits predictive model implemented by \citet{ho2017} on the LAMOST (Large Sky Area Multi-Object Fibre Spectroscopic Telescope) DR2 release \citep{luo2015}.
-The LAMOST spectral resolving power of R = 1800, a wavelength coverage from 3700$\AA$ to 9000$\AA$, and a nominal S/N ratio of 100.
-\citet{ho2017} cross-matches 9,952 stars between the low resolution spectra of LAMOST and the high resolution spectra from the APOGEE survey, and through a data driven spectral model.
-produces a 454,180 stellar data set.
-For this stellar data set the \textit{Cannon} predictive model infers $T_{eff}$, $log g$, $[Fe/H]$, and [$\alpha/M$] values.
+The LAMOST spectral resolving power of R = 1800, a wavelength coverage from 3700\AA\ to 9000\AA, and \todo{a nominal S/N ratio of 100 (is this true?)}.
+Stellar parameters ($T_{\rm eff}$, $\log{g}$, [M/H], [$\alpha$/M]) were derived using a data-driven model constructed using high fidelity APOGEE labels of 9,952 stars in common between LAMOST and the APOGEE survey.
 
@@
 A negative residual as shown in (I know I shoould expand here on the psoter child)figure \ref{fig:figure1} illustrates an enhancement in Ba\Rmnum{2} and Sr\Rmnum{2} at lines 4554\AA \hspace{0.2mm} and 4077\AA, respectively.
+\todo{These \ion{Ba}{II} and \ion{Sr}{II} resonance lines are very strong, allowing us to identify stars enhanced in neutron-capture elements given a well-fit model for the data}.
  (thinking a sentence on why these lines are the strongest ?).
-The filter process had five requirements that each spectra for both enhancement lines had to meet to be considered a Barium star canidate, these included:
+\todo{We used five filters that...} requirements that each spectra for both enhancement lines had to meet to be considered a Barium star candidate, these included:
 

### 2018-01-18 article/ms.tex
changes applied

@@
 \usepackage{ae,aecompl}
+\usepackage{booktabs}
 
@@
 \usepackage{amssymb}	% Extra maths symbols
+\usepackage{color}
+\newcommand{\todo}[1]{\textcolor{red}{#1}}
+\newcommand{\countertodo}[1]{\textcolor{green}{#1}}
 
@@
 \makeatother
-
-\usepackage{color}
-\newcommand{\todo}[1]{\textcolor{red}{#1}}
 
@@
 % Keep the title short and informative.
-\title[Short title, max. 45 characters]{Man's not hot, Man can never be hot}
+\title[Barium Stars in the Disk]{S-process Enhancement in Barium Disk Stars}
 
@@
 % If you need two or more lines of authors, add an extra line using \newauthor
-\author[B. J. Norfolk et al.]{Brodie J. Norfolk,$^{1}$\thanks{E-mail: bjee7@student.monash.edu (MU)}
+\author[B. J. Norfolk et al.]{
+Brodie J. Norfolk,$^{1}$\thanks{E-mail: bjee7@student.monash.edu (MU)}
 Andrew R. Casey,$^{1,2}$
-Ernie? Kemp? Karakas? Lattanzio? Ho?\newauthor
-Schlaufman? others?
+Mathew T. Miles,$^{1}$
+Alex J. Kemp,$^{1}$ \newauthor
+Karakas ? Lattanzio ? Schlaufman ? and others ?
 \\
-% List of institutions
 $^{1}$School of Physics \& Astronomy, Monash University, Clayton 3800, Victoria, Australia\\
@@
 }
-
 \date{Accepted XXX. Received YYY; in original form ZZZ}
@@
 \begin{abstract}
-This is a simple template for authors to write new MNRAS papers.
-The abstract should briefly describe the aims, methods, and main results of the paper.
-It should be a single paragraph not more than 250 words (200 words for Letters).
-No references should appear in the abstract.
+In this paper we present the analysis of 454,180 giant stars from LAMOST data release (DR) 2 to identify and examine 257 Barium star candidates that show enhancements of s-process elements.
+Barium stars exist as either intrinsic TP-AGB stars, producing enhancements in s-process elements via cyclic thermal pulses.
+Or, extrinsic giants still on the main sequence with enhancements in s-process element the results of polluton from a binary TP-AGB star.
+Enhancements in \ion{Ba}{II} and \ion{Sr}{II} resonance lines are very strong, allowing us to identify stars enhanced in neutron-capture elements through a data-driven analysis given a well-fitted model.
+We determined ...
+
 \end{abstract}
@@
 
-\section{Introduction}
-
-% What's a barium star (as observed)?% What causes a barium star? (extrinsic/intrinsic?)
-
-Barium stars are red giants with an unusual overabundance of carbon and heavy elements ($Z > 30$) relative to the Sun \citep{Bidelman1951}.
-\todo{Explain why this chemical signature is unusual: because this signature can really only be produced by TP-AGB stars, but we see barium stars that have not evolved to the AGB stars.
-Introduce extrinsic/intrinsic.
-Barium stars are considered to have been polluted by a binary TP-AGB star, or they are TP-AGB stars themselves.}
-For these reasons, the properties and occurrence rate of barium stars are informative of the theoretical birth rate of AGB stars, the binary star fraction as a function of metallicity, the mass ratio of binary stars, as well as AGB yields across different masses and metallicities.
-
 % AGB stars and the s-process.
-
-About half of all heavy elements are produced by the slow neutron-capture process (s-process) inside asymptotic giant branch (AGB) stars \citep[e.g.][]{busso1999,travaglio2001,
-herwig2005,romano2010,kobayashi2011,prantzos2012,bisterzo2014,
-karakas12016}. 
-\todo{This is very good, but the sentence needs splitting up: Late in the AGB phase, during the thermally pulsing-AGB (TP-AGB) phase, thermal instabilities occur in the He shell every $10^5$ years or so, depending on the H-exhausted core mass, and will drive a convective zone that sweeps the entire region lying between the core mass and He-shell; mixing the products of nucleosynthesis within these regions.} The energy from each thermal pulse forces the star to expand, pushing the H-shell out to cooler regions and allowing the convective envelope to move inwards to regions previously mixed by the thermally-driven convective zone.
-This expansion and resulting inward movement is described as the third dredge up (TDU), and is theorised to occur after every thermal pulse.
-The repeated downwash extensions of TDU cause enhancement of surface $^{12}$C abundance and of other heavy elements produced by the s-process \citep[e.g.,][]{busso2001}.
-The star contracts after \todo{PDU} and reignites the H-shell, producing the majority of the surface luminosity for the next interpulse period.
-The interpulse, thermal pulse, and dredge up cycle may occur numerous times and is dependent on the initial mass, composition, and mass-loss rate of the star.
-
-% Link AGB stars and barium stars.
-
-According to the mass-transfer hypothesis, extrinsic Barium stars are a consequence of stellar wind accretion \citep{boffin1988,jorissen1992} or Roche-lobe overflow \citep{webbink1986}, and are within a binary system containing a previous AGB companion star (intrinsic Barium star) in its final phase as a white dwarf \citep{bohm1980,bohm1984}.
-In fact, \citet{mcclure1983} determines 85\% of all Barium stars are in binary systems and those that appear singular are actually pole-on, or highly eccentric binaries with significant radial velocity variations only occurring in a small phase range as detailed by \citet{pourbaix2004}.
-
-% Properties of barium stars.
-
-Barium giants form within a metallicity dependent initial mass range (approximately 0.8 - 8$M_{\odot}$), with the minimum mass for core helium and carbon burning decreasing as metallicity decreases.
-The age of these stars vary considerably, with observable stars in metal-poor globular clusters hosting populations of $\approx$12Gyr.
-In contrast, metal rich, young observable stars reaching the upper limit may only reach $\approx$100Myr, this includes stars that are at the core carbon burning limit or very close to it \citep[e.g.][]{whitelock2013}.
 
@@
 % Yields of AGB stars at different masses and metallicities.
+
+\section{Introduction}
+
+Barium stars as first recognized by \citet{Bidelman1951}, are chemically unique objects that exhibit envelopes with an overabundance of both carbon, and heavy elements (Z > 30) in comparison to the Sun.
+Barium stars exist as either intrinsic or extrinsic objects; intrinsic barium stars are in the TP-AGB (thermally pulsing-asymptotic giant branch) phase, the overabundance of both carbon and heavy elements are produced through the s-process and exist on the surface as the result of a thermal pulsing cycle.
+According to the mass-transfer hypothesis, extrinsic Barium stars are a consequence of stellar wind accretion \citep{boffin1988,jorissen1992} or Roche-lobe overflow \citep{webbink1986}, and are within a binary system containing a previous TP-AGB companion star (intrinsic Barium star) in its final phase as a white dwarf \citep{bohm1980,bohm1984}.
+In fact, \citet{mcclure1983} determines 85\% of all Barium stars are in binary systems and those that appear singular are actually pole-on, or highly eccentric binaries with significant radial velocity variations only occuring in a small phase range as detailed by \citet{pourbaix2004}.
+For these reasons, the properties and occurrence rate of barium stars are informative of the theoretical birth rate of AGB stars, the binary star fraction as a function of metallicity, the mass ratio of binary stars, as well as AGB yields across different masses and metallicities.
+
+The slow neutron capture process (s-process), occuring in the interior of AGB stars, synthesizes roughly half of all elements heavier than iron \citep[e.g.][]{busso1999,travaglio2001,herwig2005,romano2010,kobayashi2011,prantzos2012,bisterzo2014,karakas12016}.
+Late in the AGB phase, during the thermally pulsing-AGB (TP-AGB) phase, thermal instabilities occur in the He shell every $10^5$ years or so, depending on the H-exhausted core mass.
+These energy bursts drive a convective zone that sweeps the entire region lying between the core mass and He-shell; mixing the products of nucleosynthesis within these regions.
+The energy from the thermal pulses force the star to expand, pushing the H-shell out to cooler regions and allowing the convective envelope to move inwards to regions previously mixed by the thermal pulse driven convective zones.
+This expansion and resultsing inward movement is classified as the third dredge up (TDU), and is theorized to occur after each thermal pulse.
+During the TP-AGB phase, enrichent on the surface in $^{12}$C and heavy elements produced by the s-process is a result of the repeated downwash extensions of TDU \citep[e.g.][]{busso2001}.
+The star contracts PDU and reignites the H-shell producing the majority of the surface luminosity for the next interpulse period.
+The interpulse, thermal pulse, and dredge up cycle may occur numerous times and is dependent on the intitial mass, composition and mass-loss rate of the star.
+
+Barium giants form within a metallicity dependent initial mass range (approximately 0.8 - 8$M_{\odot}$), with the minimum mass for core helium and carbon burning decreasing as metalicity decreases.
+The age of these stars vary considerably, with observable stars in metal-poor globular clusters hosting populations of $\approx$12Gyr.
+In contrast, metal rich, young observable stars reaching the upper limit may only reach $\approx$100Myr, this includes stars that are at the core carbon burning limit or very close to it \citep[e.g.][]{whitelock2013}.
 
@@
 
-In this paper we analysis 454,180 giant stars from LAMOST data release (DR) 2 to identify and examine 273 Barium star candidates that show enhancements of s-process elements.
-In Section \ref{sec:observations} we describe the observations and candidate selection, as well as the analysis follow up our follow-up observing campaign.
-In Section \ref{sec:discussion} we discuss the properties of our Barium stars in context of existing literature.
-We provide concluding remarks in Section \ref{sec:conclusion}
+In this paper we analysis 454,180 giant stars from LAMOST data release (DR) 2 to identify and examine 257 Barium star candidates that show enhancements of s-process elements.
+Specifcally, the giants studied here display especially molecular band absorption for CH, CN, and C$_2$ molecular bands, and strong s-process enhancement for \ion{Ba}{II} and \ion{Sr}{II} at lines 4554\AA \hspace{0.2mm} and 4077\AA, respectively.
+In Section \ref{sec:obs} we describe the observations and candidate selection, as well as the analysis follow up our follow-up observing campaign in Section \ref{sec:an}.
+In Section \ref{sec:dis} we discuss the properties of our Barium stars in context of existing literature.
+We provide concluding remarks in Section \ref{sec:con}
 
-%and investigate atmospheric parameters including, the distributions of temperature, surface gravity and metalicity.
-Additionally, the abundances of elements not produced in the s-process such as sodium and technetium (Na and Tc) are examined to determine  if the sample Barium stars share similar abundance to field giants with equal metallicities.
-Moreover, the stellar sample is cross matched with GAIA, producing (not sure exactly what gaia gave us) neccessary to determine the kinematics of our Barium samples.
-
-% move to observations and target selection:
-%In our research we analysed 273 Barium canidates amoung the 454,180 stellar sample produced by \citet{ho2017} and with GAIA determined the galactic motions for 21 out the 273 canidates.
-
-\todo{move or remove: The red giants studied here display especially strong s-process enhancement for \ion{Ba}{II} and \ion{Sr}{II} at lines 4554\AA\ and 4077\AA, respectively.
-(thinking I should extend this sentence with a little on the Carbon, maybe I should search for carbon in my figures ?).
-}
-
-\section{Observations and Target Selection}
+\section{Observations and Target Selection} \label{sec:obs}
 The spectral data of our stars were obtained from the \textit{Cannon} fits predictive model implemented by \citet{ho2017} on the LAMOST (Large Sky Area Multi-Object Fibre Spectroscopic Telescope) DR2 release \citep{luo2015}.
-The LAMOST spectral resolving power of R = 1800, a wavelength coverage from 3700\AA\ to 9000\AA, and \todo{a nominal S/N ratio of 100 (is this true?)}.
+The LAMOST spectral resolving power of R = 1800, a wavelength coverage from 3700\AA\ to 9000\AA, and \todo{a nominal S/N ratio of 100 (is this true?)}\countertodo{I read it in a paper somewhere, is it not true ?}.
 Stellar parameters ($T_{\rm eff}$, $\log{g}$, [M/H], [$\alpha$/M]) were derived using a data-driven model constructed using high fidelity APOGEE labels of 9,952 stars in common between LAMOST and the APOGEE survey.
@@
 The Barium stars analysed in this research were obtained by filtering for significant flux residuals, taken as, a disparity between the normalised LAMOST flux and the data driven model derived by \citet{ho2017}.
-A negative residual as shown in (I know I shoould expand here on the psoter child)figure \ref{fig:figure1} illustrates an enhancement in Ba\Rmnum{2} and Sr\Rmnum{2} at lines 4554\AA \hspace{0.2mm} and 4077\AA, respectively.
-\todo{These \ion{Ba}{II} and \ion{Sr}{II} resonance lines are very strong, allowing us to identify stars enhanced in neutron-capture elements given a well-fit model for the data}.
- (thinking a sentence on why these lines are the strongest ?).
-\todo{We used five filters that...} requirements that each spectra for both enhancement lines had to meet to be considered a Barium star candidate, these included:
+A negative residual as shown in the poster child figure \ref{fig:figure1} illustrates an enhancement in \ion{Ba}{II} and \ion{Sr}{II} at lines 4554\AA \hspace{0.2mm} and 4077\AA, respectively.
+These \ion{Ba}{II} and \ion{Sr}{II} resonance lines are very strong, allowing us to identify stars enhanced in neutron-capture elements given a well-fit model for the data.
+We used five filters that each spectra for both enhancement lines had to meet to be considered a Barium star candidate, these included:
 
@@
 \item The wavelength at each absorption line must be within $2$\AA \hspace{0.2mm}$(\lambda \leq 2)$.
-\item The chi must be less then 3 (not sure on math wrting for this).
+\item $\chi^2 \leq 3$.
 \item And, the spectra must have a signal-to-noise ratio of S/N $\geq 30$.
@@
 In addition, a visual observation of the accuracy between each normalised LAMOST flux and its accompanying data driven model was undertaken to exclude any results containing, false positives, candidates exhibiting data reduction issues, apparent absorption finer then the spectral resolution, and overly noisy normalised LAMOST spectra.
-This combined method generated the 273 Barium star candidates as listed in Table \ref{table:table1}.
+This combined method generated the 257 Barium star candidates as listed in Table \ref{table:table1}.
 
-\section{Analysis and Results}
+\begin{figure}
+	% To include a figure from a file named example.*
+	% Allowable file formats are eps or ps if compiling using latex
+	% or pdf, png, jpg if compiling using pdflatex
+	\includegraphics[width=\columnwidth]{posterchild.png}
+    \caption{Posterchild}
+    \label{fig:figure1}
+\end{figure}
 
-\subsection{Line Selection}
+\begin{table}[]
+\centering
+\caption{Available online in its entirety. Here we show a portion to demonstrate its style and content}
+\label{table:table1}
+\begin{tabular}{@{}|l|l|l|l|l|l|l|l|l|l|@{}}
+\toprule
+2MASSID             & RA (hms         & DEC (hms)        & Vr (km/s) & S/N & Teff (K) & Log g & {[}Fe/H{]} & {[}$\alpha$/H{]} & $\chi^2$  \\ \midrule
+J000134.95+490743.2 & 00:01:34.96 & +49:07:43.2 & -42.27    & 72  & 5044 & 3.11  & -0.54      & 0.11      & 0.79 \\ \midrule
+J000403.80+160257.1 & 00:04:03.80 & +16:02:57.2 & -35.38    & 42  & 5200 & 3.40  & -0.41      & 0.09      & 0.33 \\ \midrule
+J000908.48+421615.4 & 00:09:08.49 & +42:16:15.5 & -34.78    & 36  & 4825 & 3.02  & -0.46      & 0.16      & 0.25 \\ \midrule
+J001754.17+394140.0 & 00:17:54.17 & +39:41:40.0 & -42.87    & 39  & 5008 & 3.16  & -0.64      & 0.12      & 0.23 \\ \midrule
+J001841.57+040533.7 & 00:18:41.57 & +04:05:33.8 & -20.69    & 141 & 4840 & 3.68  & -0.52      & 0.06      & 0.93 \\ \midrule
+J002107.60+361533.0 & 00:21:07.60 & +36:15:33.1 & -53.06    & 44  & 4854 & 2.87  & 0.01       & 0.06      & 0.54 \\ \midrule
+J002537.59+411123.7 & 00:25:37.59 & +41:11:23.8 & -12.59    & 36  & 5075 & 3.30  & -0.32      & 0.10      & 0.33 \\ \midrule
+J003755.55+571706.8 & 00:37:55.55 & +57:17:06.9 & -5.70     & 49  & 4046 & 1.14  & -0.09      & -0.01     & 0.83 \\ \midrule
+J003813.23+423025.9 & 00:38:13.23 & +42:30:25.9 & -40.17    & 36  & 4475 & 2.12  & 0.14       & 0.00      & 0.51 \\ \midrule
+J003959.14+394614.6 & 00:39:59.14 & +39:46:14.6 & 5.10      & 35  & 4955 & 3.23  & -0.40      & 0.11      & 0.28 \\ \midrule
+J004119.68+324627.8 & 00:41:19.68 & +32:46:27.9 & 4.50      & 122 & 4861 & 2.59  & -0.31      & 0.08      & 1.67 \\ \midrule
+J004156.56+390945.6 & 00:41:56.57 & +39:09:45.6 & -254.52   & 44  & 4771 & 2.34  & -0.74      & 0.16      & 0.57 \\ \midrule
+J004743.01+433358.1 & 00:47:43.02 & +43:33:58.2 & -62.66    & 65  & 4834 & 2.64  & -0.60      & 0.17      & 1.06 \\ \midrule
+J005101.98+314045.6 & 00:51:01.98 & +31:40:45.7 & -23.68    & 98  & 5202 & 3.32  & -0.53      & 0.10      & 0.67 \\ \midrule
+J005254.69+203554.7 & 00:52:54.69 & +20:35:54.7 & 35.68     & 113 & 5026 & 3.17  & -0.82      & 0.20      & 1.01 \\ \midrule
+J010836.26+444435.9 & 01:08:36.26 & +44:44:35.9 & 12.59     & 49  & 5189 & 3.19  & -0.56      & 0.10      & 0.98 \\ \midrule
+J011919.20+195227.0 & 01:19:19.21 & +19:52:27.0 & -35.38    & 31  & 4897 & 2.77  & -0.54      & 0.11      & 0.29 \\ \midrule
+J011930.90-015027.3 & 01:19:30.91 & -01:50:27.4 & -143.30   & 44  & 5040 & 3.22  & -0.91      & 0.20      & 0.48 \\ \midrule
+J020316.40+462211.1 & 02:03:16.41 & +46:22:11.1 & 11.09     & 37  & 4897 & 2.89  & -0.39      & 0.11      & 0.51 \\ \bottomrule
+\end{tabular}
+\end{table}
+
+\section{Analysis and Results}  \label{sec:an}
+\begin{figure}
+	% To include a figure from a file named example.*
+	% Allowable file formats are eps or ps if compiling using latex
+	% or pdf, png, jpg if compiling using pdflatex
+	\includegraphics[width=\columnwidth]{HRdummy.png}
+    \caption{HR Diagram}
+    \label{fig:figure2}
+\end{figure}
+
+\begin{figure}
+	% To include a figure from a file named example.*
+	% Allowable file formats are eps or ps if compiling using latex
+	% or pdf, png, jpg if compiling using pdflatex
+	\includegraphics[width=\columnwidth]{ECCdummy.png}
+    \caption{Eccentricity}
+    \label{fig:figure3}
+\end{figure}
+
+\subsection{Line Selection and Atmospheric Parameters}
+
 \subsection{Technetium Lines}
+
 \subsection{Abundance Analysis}
@@
 
-\section{Discussion}
+\section{Discussion} \label{sec:dis}
 
-\section{Conclusions}
+\subsection{HR Diagram}
+
+\subsection{Abundances}
+\subsubsection{Rejected Stars}
+\subsubsection{Sodium Abundance}
+\subsubsection{Heavy Element Abundance}
+\subsection{Kinematics}
+
+\section{Conclusions} \label{sec:con}
 
@@
 
-The Acknowledgements section is not numbered. Here you can thank helpful
-colleagues, acknowledge funding agencies, telescopes and facilities used etc.
-Try to keep it short.
+I thank Andrew R. Casey for finally re-hiring me.
 

### 2018-01-19 Tc_process.py
old code don't rip my skills

@@ -143,6 +143,17 @@ N_Bariumstars = N_St4077*N_Ba4554
 N_Tc = N_St4077*N_Ba4554*N_Tc4049*N_Tc4238*N_Tc4262*N_Tc4297*N_Tc5924
 N_TcAll = N_Tc4049*N_Tc4238*N_Tc4262*N_Tc4297*N_Tc5924
 N_Na = N_St4077*N_Ba4554*N_Na5889
+N_Tc3ormore = (N_St4077 * N_Ba4554) * ((N_Tc4049 + N_Tc4238 + N_Tc4262 + N_Tc4297 + N_Tc5924) >= 3)
+N_Tc2ormore = (N_St4077 * N_Ba4554) * ((N_Tc4049 + N_Tc4238 + N_Tc4262 + N_Tc4297 + N_Tc5924) >= 2)
+N_Tc1ormore = (N_Bariumstars) * ((N_Tc4049 + N_Tc4238 + N_Tc4262 + N_Tc4297 + N_Tc5924) >= 1)
+N_Tc4049s=N_Tc4049*N_Bariumstars
+N_Tc4238s=N_Tc4238*N_Bariumstars
+N_Tc4262s=N_Tc4262*N_Bariumstars
+N_Tc4297s=N_Tc4297*N_Bariumstars
+N_Tc5924s=N_Tc5924*N_Bariumstars
+
+
+
 
 print("Barium stars: {}".format(sum(N_Bariumstars)))
 print("Sodium 5889: {}".format(sum(N_Na5889)))
@@ -154,6 +165,11 @@ print("Technetium 5924: {}".format(sum(N_Tc5924)))
 print("Technetium all: {}".format(sum(N_TcAll)))
 print("Barium star Tc Matches: {}".format(sum(N_Tc)))
 print("Barium star Na Matches: {}".format(sum(N_Na)))
+print("Technetium 3: {}".format(sum(N_Tc3ormore)))
+print("Technetium 2: {}".format(sum(N_Tc2ormore)))
+print("Technetium 1: {}".format(sum(N_Tc1ormore)))
+
+
 
 
 """
@@ -193,9 +209,10 @@ for index, star in enumerate(csv):
 
     del fig
     print(index)
-
+"""
+"""
 for index, star in enumerate(csv):
-    if not N_Tc[index]: continue
+    if not N_Na[index]: continue
 
     observed_flux = all_observed_flux[index]
     observed_ivar = all_observed_ivar[index]
[…]

### 2018-01-19 article/ms.tex
Put Out Work Evening Riter

@@
 We determined ...
+Sodium enrichment was present in 5 of our barium star candidates and could be attributed to the NeNa cycle in more evolved stars.
 
@@
 In this paper we analysis 454,180 giant stars from LAMOST data release (DR) 2 to identify and examine 257 Barium star candidates that show enhancements of s-process elements.
-Specifcally, the giants studied here display especially molecular band absorption for CH, CN, and C$_2$ molecular bands, and strong s-process enhancement for \ion{Ba}{II} and \ion{Sr}{II} at lines 4554\AA \hspace{0.2mm} and 4077\AA, respectively.
-In Section \ref{sec:obs} we describe the observations and candidate selection, as well as the analysis follow up our follow-up observing campaign in Section \ref{sec:an}.
+Specifcally, the giants studied here display especially strong s-process enhancement for \ion{Ba}{II} and \ion{Sr}{II} at lines 4554\AA \hspace{0.2mm} and 4077\AA, respectively.
+Additionally, molecular band absorption for G Band, CH bands is observed.
+In Section \ref{sec:methods} we describe the observations and candidate selection, as well as the analysis follow up our follow-up observing campaign with MAGGELLAN.
 In Section \ref{sec:dis} we discuss the properties of our Barium stars in context of existing literature.
@@
 
-\section{Observations and Target Selection} \label{sec:obs}
+\section{Methods} \label{sec:methods}
+\subsection{LAMOST Analysis}
+\subsubsection{Data-driven Analysis}
 The spectral data of our stars were obtained from the \textit{Cannon} fits predictive model implemented by \citet{ho2017} on the LAMOST (Large Sky Area Multi-Object Fibre Spectroscopic Telescope) DR2 release \citep{luo2015}.
@@
 
+\subsubsection{Candidate Selection} \label{sec:cand}
 The Barium stars analysed in this research were obtained by filtering for significant flux residuals, taken as, a disparity between the normalised LAMOST flux and the data driven model derived by \citet{ho2017}.
@@
 These \ion{Ba}{II} and \ion{Sr}{II} resonance lines are very strong, allowing us to identify stars enhanced in neutron-capture elements given a well-fit model for the data.
-We used five filters that each spectra for both enhancement lines had to meet to be considered a Barium star candidate, these included:
+We used five filters that each spectra, for both enhancement lines, had to meet to be considered a Barium star candidate; these included:
 
@@
 
-\section{Analysis and Results}  \label{sec:an}
-\begin{figure}
-	% To include a figure from a file named example.*
-	% Allowable file formats are eps or ps if compiling using latex
-	% or pdf, png, jpg if compiling using pdflatex
-	\includegraphics[width=\columnwidth]{HRdummy.png}
-    \caption{HR Diagram}
-    \label{fig:figure2}
-\end{figure}
+\subsubsection{Technetium Lines}
+
+Enhancement of technetium lines in our sample would indicate the presence of high luminosity Tc-self-enriched AGB S stars \citep{jorissen1993} and, suggest our candidates are infact intrinsic Barium stars.
+We undertook an identical analysis to the process described in Section \ref{sec:cand}, negative residuals for Tc enhancement lines 4049\AA, 4238.19\AA, 4262.27\AA, 4297\AA, and 5924.47\AA\hspace{0.2mm} were filtered for.
+In agreement with previous findings \citep[e.g.][]{little1987,smith1984,smith1983}, the results indicate that none of the evolved barium stars in our sample exhibited the presence of Tc enhancement.
+It is noted, \todo{51} of our barium candidates were enhanced in Tc lines, although, this is attributed to \todo{something} and is disregarded.
+
+\subsubsection{Carbon Bands}
+
+\subsubsection{Sodium Doublet}
+
+According to \citet{el1995}, sodium overabundance observed in the atmospheres of A-F supergiant stars is synthesized in the convective core of main-sequence stars in the NeNa reaction chain.
+Sodium is transported to the surface of these supergiants via mixing of CNO cycle products during the first dredge-up, this constrains sodium enhancement to supergiants and giants only.
+\citet{antipova2004} discovered a sodium enhancement in a number of their barium star candidates, they relate this to the dredge-up of nuclear-burning material produced by convection during the red-giant phase.
+Moreover, they suggest [Na/Fe] values do not exhibit variations in metallicity, but [Na/Fe] ratios exhibit systematically higher values for giants with lower log g values.
+Similarily, \citet{decastro2016} highlights the possible weak, but statistically significant anti-correlation between [Na/Fe] ratio and log g, and illustrates this trend in previous studies\citep[e.g.][]{boyarchuk2002,mishenina2006,luck2007,takeda2008}.
+
+Through an identical analysis to the process described in Section \ref{sec:cand}, we filtered for negative residuals in the enhanced sodium doublet lines 5889.950\AA\hspace{0.2mm} and 5895.924\AA.
+Our analysis produced 5 matches with our barium star candidates, this suggests sodium-rich material from the TP-AGB star polluted the barium star.
+Although, it's important to note a star with a minimum 1.5$M_\odot$ can exhibit sodium abundance through the NeNc cycle \citep{denissenkov1987}.
+During the giant phase synthesized sodium is brought to the surface via the first dredge-up, therefore, these candidates may display sodium enhancement without mass transfer from a TP-AGB star.
+
+\subsection{MAGELLAN Analysis}
+
+\subsubsection{Observations}
+
+\subsubsection{Abundance Analysis}
+
+\subsubsection{Abundance Uncertainties}
+
+\subsection{Dynamics}
+The dynamical analysis of our barium star candidates was accomplished by crossing matching the sample with GAIA \todo{ref gaia}, producing 21 matches, and then using gala Python package to intergrate the galactic dynamics.
+The Milky Way potential model was used to integrate the orbits of our candidates back a \todo{number} years, and compute distributions of orbital properties including orbital period, orbital energy, apocenter, eccentricity, and angular momentum in z.
 
@@
 
-\subsection{Line Selection and Atmospheric Parameters}
-
-\subsection{Technetium Lines}
-
-\subsection{Abundance Analysis}
-\subsection{Abundance Uncertainties}
+\begin{figure}
+	% To include a figure from a file named example.*
+	% Allowable file formats are eps or ps if compiling using latex
+	% or pdf, png, jpg if compiling using pdflatex
+	\includegraphics[width=\columnwidth]{energy_angmomz.png}
+    \caption{Energy Vs. Angular Momentum in Z}
+    \label{fig:figure3}
+\end{figure}
 
@@
 \subsection{HR Diagram}
-
-\subsection{Abundances}
-\subsubsection{Rejected Stars}
-\subsubsection{Sodium Abundance}
-\subsubsection{Heavy Element Abundance}
-\subsection{Kinematics}
+\begin{figure}
+	% To include a figure from a file named example.*
+	% Allowable file formats are eps or ps if compiling using latex
+	% or pdf, png, jpg if compiling using pdflatex
+	\includegraphics[width=\columnwidth]{HRdummy.png}
+    \caption{HR Diagram}
+    \label{fig:figure2}
+\end{figure}
 
@@
 
-I thank Andrew R. Casey for finally re-hiring me.
+To John Power, hold in there buddy
 
@@
 \bibitem[\protect\citeauthoryear{Ho et al.}{2017}]{ho2017}
-Ho, A.~Y.~Q., Ness, M.~K., Hogg, D.~W. Rix, H.-W. Liu, C. Yang, F. Zhang, Y. Hou,\& Y. Wang, Y. 2017, 
+Ho, A.~Y.~Q., Ness, M.~K., Hogg, D.~W., Rix, H.-W. Liu, C., Yang, F., Zhang, Y., Hou, Y.,\& Wang, Y. 2017, 
 ApJ, 836, 5
-\bibitem[\protect\citeauthoryear{Luo A.L., Bai Z.R. et al}{(2015)}]{luo2015}
+\bibitem[\protect\citeauthoryear{Luo A.L., Bai Z.R. et al}{2015}]{luo2015}
 Luo, A.~L., Bai, Z.~R., et al. 2015, 
 RAA, in press
+\bibitem[\protect\citeauthoryear{Jorissen et al.}{1993}]{jorissen1993}
+Jorissen, A., Frayer, D.~T., Johnson, H.~W., Mayor, M.,\& Smith, V.~V. 1993, 
+A$\&$A, 271, 463
+\bibitem[\protect\citeauthoryear{Little-Marenin \& Little}{1987}]{little1987}
+Little-Marenin, I.~R.,\& Little, S.~J. 1987, 
+AJ, 93, 1539
+\bibitem[\protect\citeauthoryear{Smith}{1984}]{smith1984}
+Smith, V.~V. 1984, 
+A$\&$A, 132, 326
+\bibitem[\protect\citeauthoryear{Smith \& Wallerstein}{1983}]{smith1983}
+Smith, V.~V.,\& Wallerstein, G. 1983, 
+ApJ, 273, 742
+\bibitem[\protect\citeauthoryear{El Eid \& Champagne}{1995}]{el1995}
+El Eid, M.~F.,\& Champagne, A.~E. 1995, 
+ApJ, 451, 298
+\bibitem[\protect\citeauthoryear{Antipova et al.}{2004}]{antipova2004}
+Antipova, L.~I., Boyarchuk, A.~A., Pakhomov, Yu.~V.,\& Panchuk, V.~E. 2004, 
+ARep, 48, 597
+\bibitem[\protect\citeauthoryear{Boyarchuk et al.}{2002}]{boyarchuk2002}
+Boyarchuk, A.~A., Pakhomov, Y.~V., Antipova, L.~I.,\& Boyarchuk, M.~E. 2002, 
+ARep, 46, 819
+\bibitem[\protect\citeauthoryear{Takeda et al.}{2008}]{takeda2008}
+Takeda, Y., Sato, B.~V.,\& Murata, D. 2008, 
+AJ, 60, 781
+\bibitem[\protect\citeauthoryear{Mishenina et al.}{2006}]{mishenina2006}
+Mishenina, T.~V., Bienaym\' e, O., Gorbaneva, T.~I.,\& Charbonnel, C. 2006, 
+A$\&$A, 456, 1109
+\bibitem[\protect\citeauthoryear{Luck \& Heiter}{2007}]{luck2007}
+Luck R.~E.,\& Heiter, U. 2007, 
+AJ, 133, 2464
+\bibitem[\protect\citeauthoryear{Denissenkov \& Ivanov}{1987}]{denissenkov1987}
+Denissenkov P.~A.,\& Ivanov, V.~V. 1987, 
+SvAL, 13, 214
+\bibitem[\protect\citeauthoryear{de Castro et al.}{2016}]{decastro2016}
+de Castro, D.~B., Pereira, C.~B., Roig, F., Jilinski, E., Drake, N.~A., Chavero, C.,\& Sales Silva, J.~V. 2016, 
+MNRAS, 459, 4299
 

### 2018-01-21 article/ms.tex
analy

@@
 
-\section{Introduction}
+\section{Introduction} \label{sec:intro}
 
@@
 
+Barium stars are optimal sites for investigating the relationship between the neutron-capture elements and other species that may be
+depleted or enhanced, because they act as neutron seeds during the operation of the s-process.
+In the ABG phase the abundance of carbon is a product of helium fusion, specifically the triple-alpha process within a star.
+In an identical mechanism to the presence of s-process elelment enhancement, carbon enhanced stars exist intrinsically or extrinsically.
+Giants and supergiants become enhanced in carbon through TDU process discussed in Section \ref{sec:intro}, and extrinsic carbon enhancement occurs via mass transfer from a binary AGB star.
+In our sample of barium star candidates we discovered enhancement in both CH and the G band for 178 of our total 257 stars.
+\todo{maybe put a list of the stars ?}
+
 \subsubsection{Sodium Doublet}
@@
 During the giant phase synthesized sodium is brought to the surface via the first dredge-up, therefore, these candidates may display sodium enhancement without mass transfer from a TP-AGB star.
+\todo{maybe put a list of the stars ?}
 
@@
 
-To John Power, hold in there buddy
+Fired Status: yes
 

### 2018-01-22 article/ms.tex
reorganise abstract

@@
 % Keep the title short and informative.
-\title[Barium Stars in the Disk]{S-process Enhancement in Barium Disk Stars}
+\title[Barium stars in LAMOST]{Discovery of barium stars in the LAMOST survey}
 
@@
 % If you need two or more lines of authors, add an extra line using \newauthor
-\author[B. J. Norfolk et al.]{
-Brodie J. Norfolk,$^{1}$\thanks{E-mail: bjee7@student.monash.edu (MU)}
+\author[B. J. Norfolk et al.]{Brodie J. Norfolk,$^{1}$\thanks{E-mail: bjee7@student.monash.edu (MU)}
 Andrew R. Casey,$^{1,2}$
 Mathew T. Miles,$^{1}$
-Alex J. Kemp,$^{1}$ \newauthor
+Alexander J. Kemp,$^{1}$ \newauthor
 Karakas ? Lattanzio ? Schlaufman ? and others ?
@@
 \begin{abstract}
-In this paper we present the analysis of 454,180 giant stars from LAMOST data release (DR) 2 to identify and examine 257 Barium star candidates that show enhancements of s-process elements.
-Barium stars exist as either intrinsic TP-AGB stars, producing enhancements in s-process elements via cyclic thermal pulses.
+Stars with peculiar enhancements of carbon and heavy elements ($Z > 30$) are historically referred to as Barium stars.
+While this chemical abundance pattern can be explained by thermally pulsing asymptotic giant branch (AGB) stars, many barium stars have not evolved through the red giant (or main-sequence) phase and therefore cannot be an AGB star.
+These stars are generally thought to have accreted mass from a more evolved companion.
+For this reason the frequency and properties of less-evolved barium stars is uniquely informative on the binary fraction, AGB yields, mass transfer, and stellar evolution.
+Here we present the discovery of 257 barium stars from 454,180 giant stars observed by LAMOST.
+This sample constitutes the largest sample of barium stars discovered to date, and the most comprehensive search for barium stars in the Milky Way.
+\todo{Nearly all} of our barium stars are disk stars, and we find an \todo{steady/increasing/decreasing} fraction of barium stars with stellar metallicity, as \todo{expected} from AGB yields and stellar evolution theory.
+% Technitium?
+\todo{Most (178/257) of our sample show strong carbon enhancement.}
+Despite previous claims indicating that barium stars are preferentially enhanced in sodium due to the NeNa nucleosynthesis cycle occurring in \todo{massive} AGB stars, only 5 ($<2$\,\%) of our Barium stars show any evidence of enhancement in sodium.
+\todo{This implies ....}
+ %Barium stars exist as either intrinsic TP-AGB stars, producing enhancements in s-process elements via cyclic thermal pulses.
 Or, extrinsic giants still on the main sequence with enhancements in s-process element the results of polluton from a binary TP-AGB star.
 Enhancements in \ion{Ba}{II} and \ion{Sr}{II} resonance lines are very strong, allowing us to identify stars enhanced in neutron-capture elements through a data-driven analysis given a well-fitted model.
-We determined ...
-Sodium enrichment was present in 5 of our barium star candidates and could be attributed to the NeNa cycle in more evolved stars.
-
+% We determined ... Sodium enrichment was present in 5 of our barium star candidates and could be attributed to the NeNa cycle in more evolved stars.
 \end{abstract}

### 2018-01-22 article/ms.tex
add comments etc

@@
 \subsubsection{Data-driven Analysis}
-The spectral data of our stars were obtained from the \textit{Cannon} fits predictive model implemented by \citet{ho2017} on the LAMOST (Large Sky Area Multi-Object Fibre Spectroscopic Telescope) DR2 release \citep{luo2015}.
-The LAMOST spectral resolving power of R = 1800, a wavelength coverage from 3700\AA\ to 9000\AA, and \todo{a nominal S/N ratio of 100 (is this true?)}\countertodo{I read it in a paper somewhere, is it not true ?}.
+The LAMOST (Large sky Area Multi-Object Fibre Spectrographic) survey released low-resolution ($\mathcal{R} \approx 1800$) optical spectra (3700\,\AA\ to 9000\,\AA) for over two million stars in their second data release \citep{luo2015}.
 Stellar parameters ($T_{\rm eff}$, $\log{g}$, [M/H], [$\alpha$/M]) were derived using a data-driven model constructed using high fidelity APOGEE labels of 9,952 stars in common between LAMOST and the APOGEE survey.
+\todo{Write more about this: the precision in parameters, how giants were selected from dwarfs, and then talk about how many giant spectra we used}.
 
@@
 \item $\chi^2 \leq 3$.
-\item And, the spectra must have a signal-to-noise ratio of S/N $\geq 30$.
+\item And, the spectra must have a signal-to-noise ratio of S/N $\geq 30$ per pixel.
 \end{enumerate}
@@
 
-\subsubsection{Technetium Lines}
-
-Enhancement of technetium lines in our sample would indicate the presence of high luminosity Tc-self-enriched AGB S stars \citep{jorissen1993} and, suggest our candidates are infact intrinsic Barium stars.
-We undertook an identical analysis to the process described in Section \ref{sec:cand}, negative residuals for Tc enhancement lines 4049\AA, 4238.19\AA, 4262.27\AA, 4297\AA, and 5924.47\AA\hspace{0.2mm} were filtered for.
-In agreement with previous findings \citep[e.g.][]{little1987,smith1984,smith1983}, the results indicate that none of the evolved barium stars in our sample exhibited the presence of Tc enhancement.
-It is noted, \todo{51} of our barium candidates were enhanced in Tc lines, although, this is attributed to \todo{something} and is disregarded.
-
 \subsubsection{Carbon Bands}
@@
 \todo{maybe put a list of the stars ?}
+
+\subsubsection{Technetium Lines}
+
+Enhancement of technetium lines in our sample would indicate the presence of high luminosity Tc-self-enriched AGB S stars \citep{jorissen1993} and, suggest our candidates are infact intrinsic Barium stars.
+We undertook an identical analysis to the process described in Section \ref{sec:cand}, negative residuals for Tc enhancement lines 4049\AA, 4238.19\AA, 4262.27\AA, 4297\AA, and 5924.47\AA\hspace{0.2mm} were filtered for.
+In agreement with previous findings \citep[e.g.][]{little1987,smith1984,smith1983}, the results indicate that none of the evolved barium stars in our sample exhibited the presence of Tc enhancement.
+It is noted, \todo{51} of our barium candidates were enhanced in Tc lines, although, this is attributed to \todo{something} and is disregarded.
 
@@
 
-\subsection{MAGELLAN Analysis}
+\subsection{Follow-up observations with Magellan/MIKE}
 
 \subsubsection{Observations}
+On the night of \todo{X} January 2018 we performed follow-up observations of \todo{X} barium star candidates using the MIKE spectrograph on the Magellan Clay telescope at Las Campanas Observatory, Chile.
+Candidates for follow-up observations were chosen based on observability constraints and ranked by their apparent visual magnitude.
+We observed \todo{X} stars in good seeing using the 0.7 arcsecond slit and 2x2 spatial on-chip binning, which provides a spectral resolution of ($\mathcal{R} \approx \todo{22,000}$).
+Exposure times were set to achieve a S/N ratio of 30 per pixel at 4500\,\AA.
+We acquired calibration (biases, milky, quartz, and Th-Ar arc lamp) frames in the afternoon.
+
+We reduced the data using the \texttt{CarPy} Python package \citep{kels03,kels14}.
+We used spline functions to continuum-normalise individual echelle orders, and resampled the normalised spectra onto a uniform-sized wavelength map.
+We used a rest-frame normalised template of a FGK-type star to place the observed spectra in the rest frame.
 
 \subsubsection{Abundance Analysis}
+We adopted the stellar parameters ($T_{\rm eff}$, $\log_{10}g$, [Fe/H]) provided from the data-driven analysis of \citep{Ho_2017}.
+Following the procedure outlined in \citep{Casey_2014}, we measured the strength of atomic absorption lines by fitting Gaussian profiles to the continuum-normalised spectra.
+Most elemental abundances were derived directly from these line measurements, except for elements that show significant hyperfine splitting \todo{(e.g., )} or blending \todo{(e.g., X)}.
+In these situations, we adopted a spectral synthesis approach.
+\todo{citations for line lists}
 
-\subsubsection{Abundance Uncertainties}
+\todo{Some sentences for andy to add regarding abundance analysis and verification of stellar parameters from LAMOST}
+
+\todo{Were ant of the stars observed with Magellan/MIKE the stars enhanced in Na? C?}
+
+%\subsubsection{Abundance Uncertainties}
 
 \subsection{Dynamics}
+\todo{rewrite this with more detail: see Casey \& Schlaufman (2017) to see how much detail you should give for dynamics analysis...}
 The dynamical analysis of our barium star candidates was accomplished by crossing matching the sample with GAIA \todo{ref gaia}, producing 21 matches, and then using gala Python package to intergrate the galactic dynamics.

### 2018-01-24 article/ms.tex
draft

@@
 \usepackage{color}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%
+\usepackage{float}
 \newcommand{\todo}[1]{\textcolor{red}{#1}}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%
-
 % Please keep new commands to a minimum, and use \newcommand not \def to avoid
@@
 
-% Title of the paper, and the short title which is used in the headers.
-% Keep the title short and informative.
-\title[Barium stars in LAMOST]{Discovery of barium stars in the LAMOST survey}
+\title[S-process stars in LAMOST]{Discovery of s-process stars in the LAMOST survey}
 
@@
 For this reason the frequency and properties of less-evolved barium stars is uniquely informative on the binary fraction, AGB yields, mass transfer, and stellar evolution.
-Here we present the discovery of 257 barium stars from 454,180 giant stars observed by LAMOST.
+Here we present the discovery of 967 s-process candidates including; 257 barium stars, 49 barium doublet stars, and 661 strontium doublet stars from 454,180 giant stars observed by LAMOST.
 This sample constitutes the largest sample of barium stars discovered to date, and the most comprehensive search for barium stars in the Milky Way.
@@
 \todo{This implies ....}
- %Barium stars exist as either intrinsic TP-AGB stars, producing enhancements in s-process elements via cyclic thermal pulses.
-Or, extrinsic giants still on the main sequence with enhancements in s-process element the results of polluton from a binary TP-AGB star.
-Enhancements in \ion{Ba}{II} and \ion{Sr}{II} resonance lines are very strong, allowing us to identify stars enhanced in neutron-capture elements through a data-driven analysis given a well-fitted model.
-% We determined ... Sodium enrichment was present in 5 of our barium star candidates and could be attributed to the NeNa cycle in more evolved stars.
 \end{abstract}
@@
 \end{keywords}
-
-% AGB stars and the s-process.
-
-% Comparisons to expectations of theoretical birth rate
-% Binary fraction at different metallicities
-% Mass differentials of binary stars
-% Yields of AGB stars at different masses and metallicities.
 
@@
 
-In this paper we analysis 454,180 giant stars from LAMOST data release (DR) 2 to identify and examine 257 Barium star candidates that show enhancements of s-process elements.
-Specifcally, the giants studied here display especially strong s-process enhancement for \ion{Ba}{II} and \ion{Sr}{II} at lines 4554\AA \hspace{0.2mm} and 4077\AA, respectively.
-Additionally, molecular band absorption for G Band, CH bands is observed.
+In this paper we analysis 454,180 giant stars from LAMOST data release (DR) 2 to identify and examine 967 s-process candidates including barium stars, barium doublet stars and strontium doublet stars.
+Specifcally, the barium star giants studied here display especially strong s-process enhancement for \ion{Ba}{II} and \ion{Sr}{II} at lines 4554\AA \hspace{0.2mm} and 4077\AA, respectively.
+Our doublet candidates show s-process enhancement in 4554\AA \hspace{0.2mm} and 4934\AA for barium enhancement, and, 4554\AA \hspace{0.2mm} and 4215\AA for strontium enhancement.
 In Section \ref{sec:methods} we describe the observations and candidate selection, as well as the analysis follow up our follow-up observing campaign with MAGGELLAN.
@@
 The LAMOST (Large sky Area Multi-Object Fibre Spectrographic) survey released low-resolution ($\mathcal{R} \approx 1800$) optical spectra (3700\,\AA\ to 9000\,\AA) for over two million stars in their second data release \citep{luo2015}.
-Stellar parameters ($T_{\rm eff}$, $\log{g}$, [M/H], [$\alpha$/M]) were derived using a data-driven model constructed using high fidelity APOGEE labels of 9,952 stars in common between LAMOST and the APOGEE survey.
+Stellar parameters ($T_{\rm eff}$, $\log{g}$, [M/H], [$\alpha$/M]) were derived using a data-driven model constructed using high fidelity APOGEE labels of 9,952 giant stars in common between LAMOST and the APOGEE survey.
+The cross-validation of the model with S/N > 50, yielded typical uncertainties of 70K in $T_eff$, 0.1 in log g, 0.1 in [Fe/H], and 0.04 in [$\alpha$/M].
+These uncertainties are broadly comparable to the conservative APOGEE DR12 uncertainties.
+\todo{not sure how the dwalfs come into play}
+
 \todo{Write more about this: the precision in parameters, how giants were selected from dwarfs, and then talk about how many giant spectra we used}.
@@
 These \ion{Ba}{II} and \ion{Sr}{II} resonance lines are very strong, allowing us to identify stars enhanced in neutron-capture elements given a well-fit model for the data.
-We used five filters that each spectra, for both enhancement lines, had to meet to be considered a Barium star candidate; these included:
+We used five filters that each spectra, for both enhancement lines, had to meet to be considered a s-process candidate; these included:
 
@@
 In addition, a visual observation of the accuracy between each normalised LAMOST flux and its accompanying data driven model was undertaken to exclude any results containing, false positives, candidates exhibiting data reduction issues, apparent absorption finer then the spectral resolution, and overly noisy normalised LAMOST spectra.
-This combined method generated the 257 Barium star candidates as listed in Table \ref{table:table1}.
+This combined method generated 967 s-process candidates including; 257 barium stars, 49 barium doublet stars, and 661 strontium doublet stars, as listed in Table \ref{table:table1}.
 
@@
 
-\begin{table}[]
+\begin{table*}
 \centering
@@
 \end{tabular}
-\end{table}
+\end{table*}
 
@@
 In our sample of barium star candidates we discovered enhancement in both CH and the G band for 178 of our total 257 stars.
-\todo{maybe put a list of the stars ?}
 
@@
 
-According to \citet{el1995}, sodium overabundance observed in the atmospheres of A-F supergiant stars is synthesized in the convective core of main-sequence stars in the NeNa reaction chain.
-Sodium is transported to the surface of these supergiants via mixing of CNO cycle products during the first dredge-up, this constrains sodium enhancement to supergiants and giants only.
-\citet{antipova2004} discovered a sodium enhancement in a number of their barium star candidates, they relate this to the dredge-up of nuclear-burning material produced by convection during the red-giant phase.
-Moreover, they suggest [Na/Fe] values do not exhibit variations in metallicity, but [Na/Fe] ratios exhibit systematically higher values for giants with lower log g values.
-Similarily, \citet{decastro2016} highlights the possible weak, but statistically significant anti-correlation between [Na/Fe] ratio and log g, and illustrates this trend in previous studies\citep[e.g.][]{boyarchuk2002,mishenina2006,luck2007,takeda2008}.
-
 Through an identical analysis to the process described in Section \ref{sec:cand}, we filtered for negative residuals in the enhanced sodium doublet lines 5889.950\AA\hspace{0.2mm} and 5895.924\AA.
 Our analysis produced 5 matches with our barium star candidates, this suggests sodium-rich material from the TP-AGB star polluted the barium star.
-Although, it's important to note a star with a minimum 1.5$M_\odot$ can exhibit sodium abundance through the NeNc cycle \citep{denissenkov1987}.
-During the giant phase synthesized sodium is brought to the surface via the first dredge-up, therefore, these candidates may display sodium enhancement without mass transfer from a TP-AGB star.
-\todo{maybe put a list of the stars ?}
 
@@
 \subsection{Dynamics}
-\todo{rewrite this with more detail: see Casey \& Schlaufman (2017) to see how much detail you should give for dynamics analysis...}
-The dynamical analysis of our barium star candidates was accomplished by crossing matching the sample with GAIA \todo{ref gaia}, producing 21 matches, and then using gala Python package to intergrate the galactic dynamics.
-The Milky Way potential model was used to integrate the orbits of our candidates back a \todo{number} years, and compute distributions of orbital properties including orbital period, orbital energy, apocenter, eccentricity, and angular momentum in z.
+The dynamical analysis of our barium star candidates was accomplished by crossing matching the sample with GAIA \todo{ref gaia}, to produce 21 matches with proper motions, parallax, and galactic positions.
+We then, using the gala Python package, intergrated our data to calculate the orbits of our 21 candidates with a Milky Way Potential model.
+The parameters of the mass model are determined by least-squares fitting the enclosed mass profile of a pre-defined potential form to recent measurements compiled from the literature.
+These measurements are provided with the documentation of gala \citep{price2017}.
+The Milky Way potential implemented was constructed using a four component potential model consisting of a \citet{hernquist1990} bulge and nucleus, a \citet{miyamoto1975} disk, and an \citet{nfw1997} halo.
+In this potential, parameters of the disk and bulge were adjuted to be consistent with previous work \citep{bovy2015} and vary the scale mass and scale radius of the nucleus and halo, respectively.
+This potential model was used to integrate the orbits of our candidates back a \todo{number} years, and compute distributions of orbital properties including orbital period, orbital energy, apocenter, eccentricity, and angular momentum in z.
+\subsubsection{Galactic Positioning}
+The galactic position of our GAIA matched candidates was determined through observation of the relationship between orbital energy and angular momentum in z.
+For this relationship a comparison between for 1,000 random normal-looking LAMOST stars and our barum star candidates was made.
+Both samples followed an identical trend and given the fact that most LAMOST stars are disk stars, it was concluded that our barium star candidates existed in the disk of the Milky Way.
 
@@
 
-\subsection{HR Diagram}
 \begin{figure}
@@
 \end{figure}
+
+\subsection{Sodium Enhancment}
+According to \citet{el1995}, sodium overabundance observed in the atmospheres of A-F supergiant stars is synthesized in the convective core of main-sequence stars in the NeNa reaction chain.
+Sodium is transported to the surface of these supergiants via mixing of CNO cycle products during the first dredge-up, this constrains sodium enhancement to supergiants and giants only.
+\citet{antipova2004} discovered a sodium enhancement in a number of their barium star candidates, they relate this to the dredge-up of nuclear-burning material produced by convection during the red-giant phase.
+Moreover, they suggest [Na/Fe] values do not exhibit variations in metallicity, but [Na/Fe] ratios exhibit systematically higher values for giants with lower log g values.
+Similarily, \citet{decastro2016} highlights the possible weak, but statistically significant anti-correlation between [Na/Fe] ratio and log g, and illustrates this trend in previous studies\citep[e.g.][]{boyarchuk2002,mishenina2006,luck2007,takeda2008}.
+
+Although, it's important to note a star with a minimum 1.5$M_\odot$ can exhibit sodium abundance through the NeNc cycle \citep{denissenkov1987}.
+During the giant phase synthesized sodium is brought to the surface via the first dredge-up, therefore, these candidates may display sodium enhancement without mass transfer from a TP-AGB star.
+Lastly, it is important to note studies including \citet{decastro2016} conclude sodium enhancement is ubiquitous throughout barium stars yet in contradiction, our sample only exhibits only a $<2$\,\% sodium presence.
 
@@
 \bibliographystyle{mnras}
-\bibliography{example} % if your bibtex file is called example.bib
+%\bibliography{example} % if your bibtex file is called example.bib
 
 \begin{thebibliography}{99}
-\bibitem[\protect\citeauthoryear{Author}{2012}]{Author2012}
-Author A.~N., 2013, Journal of Improbable Astronomy, 1, 1
-\bibitem[\protect\citeauthoryear{Others}{2013}]{Others2013}
-Others S., 2012, Journal of Interesting Stuff, 17, 198
-
+\bibitem[\protect\citeauthoryear{Allen \& Barbuy}{2006}]{allen2006}
+Allen, D.~M.,\& Barbuy B. 2006, 
+A$\&$A, 454, 917
+\bibitem[\protect\citeauthoryear{Antipova et al.}{2004}]{antipova2004}
+Antipova, L.~I., Boyarchuk, A.~A., Pakhomov, Yu.~V.,\& Panchuk, V.~E. 2004, 
+ARep, 48, 597
 \bibitem[\protect\citeauthoryear{Bidelman \& Keenan}{1951}]{Bidelman1951}
 Bidelman, W.~P. \& Keenan, P.~C. , 1951, ApJ, 114, 473
-\bibitem[\protect\citeauthoryear{Busso et al.}{1999}]{busso1999}
-Busso, M., Gallino, R., \& Wasserburg, P.~C. 1999, 
-ARA$\&$A, 37, 239
-\bibitem[\protect\citeauthoryear{Travaglio et al.}{2001}]{travaglio2001}
-Travaglio, C., et al. 2001, 
-ApJ, 549, 346
-\bibitem[\protect\citeauthoryear{Herwig}{2005}]{herwig2005}
-Herwig, F. 2005, 
-ARA$\&$A, 43, 435
-\bibitem[\protect\citeauthoryear{Romano et al.}{2010}]{romano2010}
-Romano, D., et al. 2010, 
-A$\&$A, 522, A32
-\bibitem[\protect\citeauthoryear{Kobayashi et al.}{2011}]{kobayashi2011}
-Kobayashi, C., Karakas, A., \& Umeda, H. 2011, 
-MNRAS, 414, 3231
-\bibitem[\protect\citeauthoryear{Prantzos}{2012}]{prantzos2012}
-Prantzos, N. 2012, 
-A$\&$A, 542, A67
 \bibitem[\protect\citeauthoryear{Bisterzo et al.}{2014}]{bisterzo2014}
@@
 ApJ, 787, 10
-\bibitem[\protect\citeauthoryear{Karakas}{2016}]{karakas12016}
-Karakas, A. 2016, 
-SAIt, 87, 229
-\bibitem[\protect\citeauthoryear{Busso et al.}{2001}]{busso2001}
-Busso, M., Gallino, R., Lambert, D.~L., Travaglio, C.\& Smith, V.~V. 2001, 
-ApJ, 557, 802
-\bibitem[\protect\citeauthoryear{McClure}{1983}]{mcclure1983}
-McClure, R.~D. 1983, 
-ApJ, 268, 264
-\bibitem[\protect\citeauthoryear{Pourbaix et al.}{2004}]{pourbaix2004}
-Pourbaix, D., Tokovinin, A.~A., Batten, A.~H., Fekel, F.~C., Hartkopf, W.~I. et al. 2001, 
 A$\&$A, 424, 727
+\bibitem[\protect\citeauthoryear{Boffin \& Jorissen}{1988}]{boffin1988}
+Boffin H, M.~J.,\& Jorissen, A. 1988, 
+A$\&$A, 205, 155
 \bibitem[\protect\citeauthoryear{B\"ohm-Vitense}{1980}]{bohm1980}
@@
 ApJ, 278, 726
-\bibitem[\protect\citeauthoryear{Boffin \& Jorissen}{1988}]{boffin1988}
-Boffin H, M.~J.,\& Jorissen, A. 1988, 
-A$\&$A, 205, 155
+\bibitem[\protect\citeauthoryear{Bovy}{2015}]{bovy2015}
+Bovy, J. 2015, 
+ApJ, 216, 29
+\bibitem[\protect\citeauthoryear{Boyarchuk et al.}{2002}]{boyarchuk2002}
+Boyarchuk, A.~A., Pakhomov, Y.~V., Antipova, L.~I.,\& Boyarchuk, M.~E. 2002, 
+ARep, 46, 819
+\bibitem[\protect\citeauthoryear{Busso et al.}{1999}]{busso1999}
+Busso, M., Gallino, R., \& Wasserburg, P.~C. 1999, 
+ARA$\&$A, 37, 239
+\bibitem[\protect\citeauthoryear{Busso et al.}{2001}]{busso2001}
+Busso, M., Gallino, R., Lambert, D.~L., Travaglio, C.\& Smith, V.~V. 2001, 
+ApJ, 557, 802
+\bibitem[\protect\citeauthoryear{deCastro et al.}{2016}]{decastro2016}
+deCastro, D.~B., Pereira, C.~B., Roig, F., Jilinski, E., Drake, N.~A., Chavero, C.,\& Sales Silva, J.~V. 2016, 
+MNRAS, 459, 4299
+\bibitem[\protect\citeauthoryear{Denissenkov \& Ivanov}{1987}]{denissenkov1987}
+Denissenkov P.~A.,\& Ivanov, V.~V. 1987, 
+SvAL, 13, 214
+\bibitem[\protect\citeauthoryear{Drake \& Pereira}{2008}]{drake2008}
+Drake N.,~A.,\& Pereira, C.~B. 2008, 
+AJ, 135, 1070
+\bibitem[\protect\citeauthoryear{El Eid \& Champagne}{1995}]{el1995}
+El Eid, M.~F.,\& Champagne, A.~E. 1995, 
+ApJ, 451, 298
+\bibitem[\protect\citeauthoryear{Gomez et al.}{1997}]{gomez1997}
+Gomez, A.~E., Luri, X., Grenier, S., et al. 1997, 
+A$\&$A, 319, 881
+\bibitem[\protect\citeauthoryear{Han et al.}{1995}]{han1995}
+Han, Z., Eggleton, P.~P., Podsiadlowski, P.,\& Tout, C.~A. 1995, 
+MNRAS, 277, 1443
+\bibitem[\protect\citeauthoryear{Hernquist}{1990}]{hernquist1990}
+Hernquist, L. 1990, 
+ApJ, 356, 359
+\bibitem[\protect\citeauthoryear{Herwig}{2005}]{herwig2005}
+Herwig, F. 2005, 
+ARA$\&$A, 43, 435
+\bibitem[\protect\citeauthoryear{Ho et al.}{2017}]{ho2017}
+Ho, A.~Y.~Q., Ness, M.~K., Hogg, D.~W., Rix, H.-W. Liu, C., Yang, F., Zhang, Y., Hou, Y.,\& Wang, Y. 2017, 
+ApJ, 836, 5
 \bibitem[\protect\citeauthoryear{Jorissen \& Boffin}{1992}]{jorissen1992}
@@
 Evidences for interaction among wide binary systems: To Ba or not to Ba? In: Duquennoy, A., Mayor, M.,(eds.) Binaries as tracers of stellar formation. Cambridge Univ. Press., p.185
+\bibitem[\protect\citeauthoryear{Jorissen et al.}{1993}]{jorissen1993}
+Jorissen, A., Frayer, D.~T., Johnson, H.~W., Mayor, M.,\& Smith, V.~V. 1993, 
+A$\&$A, 271, 463
+\bibitem[\protect\citeauthoryear{Jorissen et al.}{2005}]{jorissen2005}
+Jorissen, A., Za$\check{c}$, L., Udry, S., Lindgren, H.,\& Musaev, F.~A. 2005, 
+A$\&$A, 441, 1135
+\bibitem[\protect\citeauthoryear{Junqueira \& Pereira}{2001}]{junqueira2001}
+Junqueira S.,\& Pereira, C.~B. 2001, 
+AJ, 122, 360
+\bibitem[\protect\citeauthoryear{Karakas}{2016}]{karakas12016}
+Karakas, A. 2016, 
+SAIt, 87, 229
+\bibitem[\protect\citeauthoryear{Kobayashi et al.}{2011}]{kobayashi2011}
+Kobayashi, C., Karakas, A., \& Umeda, H. 2011, 
+MNRAS, 414, 3231
+\bibitem[\protect\citeauthoryear{Little-Marenin \& Little}{1987}]{little1987}
+Little-Marenin, I.~R.,\& Little, S.~J. 1987, 
+AJ, 93, 1539
+\bibitem[\protect\citeauthoryear{Luck \& Heiter}{2007}]{luck2007}
+Luck R.~E.,\& Heiter, U. 2007, 
+AJ, 133, 2464
+\bibitem[\protect\citeauthoryear{Luo A.L., Bai Z.R. et al}{2015}]{luo2015}
+Luo, A.~L., Bai, Z.~R., et al. 2015, 
+RAA, in press
+\bibitem[\protect\citeauthoryear{McClure}{1983}]{mcclure1983}
+McClure, R.~D. 1983, 
+ApJ, 268, 264
+\bibitem[\protect\citeauthoryear{Mennessier et al.}{1997}]{mennessier1997}
+Mennessier, M.~O., Luri, X., Figueras, F., et al. 1997, 
+A$\&$A, 326, 722
+\bibitem[\protect\citeauthoryear{Mishenina et al.}{2006}]{mishenina2006}
+Mishenina, T.~V., Bienaym\' e, O., Gorbaneva, T.~I.,\& Charbonnel, C. 2006, 
+A$\&$A, 456, 1109
+\bibitem[\protect\citeauthoryear{Miyamoto-Nagai}{1975}]{miyamoto1975}
+Miyamoto, M,\& Nagai, R. 1975, 
+PASJ, 27, 533
+\bibitem[\protect\citeauthoryear{NFW}{1997}]{nfw1997}
+Navarro, J.~F., Frenk, C.~S.,\& White, S.~D.~M. 1997, 
+ApJ, 490, 493
+\bibitem[\protect\citeauthoryear{Pereira \& Drake}{2009}]{pereira2009}
+Pereira, C.~B.,\& Drake N.,~A. 2009, 
+A$\&$A, 496, 791
+\bibitem[\protect\citeauthoryear{Pereira et al.}{2011}]{pereira2011}
+Pereira, C.~B., Sales Silva, J.,~A., Chavero, C., Roig, F.,\& Jilinski E. 2011, 
+A$\&$A, 533, A51
+\bibitem[\protect\citeauthoryear{Pourbaix et al.}{2004}]{pourbaix2004}
+Pourbaix, D., Tokovinin, A.~A., Batten, A.~H., Fekel, F.~C., Hartkopf, W.~I. et al. 2001, 
+\bibitem[\protect\citeauthoryear{Prantzos}{2012}]{prantzos2012}
+Prantzos, N. 2012, 
+A$\&$A, 542, A67
+\bibitem[\protect\citeauthoryear{Price-Whelan}{2017}]{price2017}
+Price-Whelan, A.~M. 2017, 
+The Journal of Open Source Software, 2, 388
+\bibitem[\protect\citeauthoryear{Romano et al.}{2010}]{romano2010}
+Romano, D., et al. 2010, 
+A$\&$A, 522, A32
+\bibitem[\protect\citeauthoryear{Smith \& Wallerstein}{1983}]{smith1983}
+Smith, V.~V.,\& Wallerstein, G. 1983, 
+ApJ, 273, 742
+\bibitem[\protect\citeauthoryear{Smith}{1984}]{smith1984}
+Smith, V.~V. 1984, 
+A$\&$A, 132, 326
+\bibitem[\protect\citeauthoryear{Takeda et al.}{2008}]{takeda2008}
+Takeda, Y., Sato, B.~V.,\& Murata, D. 2008, 
+AJ, 60, 781
+\bibitem[\protect\citeauthoryear{Travaglio et al.}{2001}]{travaglio2001}
+Travaglio, C., et al. 2001, 
+ApJ, 549, 346
 \bibitem[\protect\citeauthoryear{Webbink}{1986}]{webbink1986}
@@
 MNRAS, 428, 2216
-\bibitem[\protect\citeauthoryear{Gomez et al.}{1997}]{gomez1997}
-Gomez, A.~E., Luri, X., Grenier, S., et al. 1997, 
-A$\&$A, 319, 881
-\bibitem[\protect\citeauthoryear{Mennessier et al.}{1997}]{mennessier1997}
-Mennessier, M.~O., Luri, X., Figueras, F., et al. 1997, 
-A$\&$A, 326, 722
-\bibitem[\protect\citeauthoryear{Junqueira \& Pereira}{2001}]{junqueira2001}
-Junqueira S.,\& Pereira, C.~B. 2001, 
-AJ, 122, 360
-\bibitem[\protect\citeauthoryear{Drake \& Pereira}{2008}]{drake2008}
-Drake N.,~A.,\& Pereira, C.~B. 2008, 
-AJ, 135, 1070
-\bibitem[\protect\citeauthoryear{Pereira \& Drake}{2009}]{pereira2009}
-Pereira, C.~B.,\& Drake N.,~A. 2009, 
-A$\&$A, 496, 791
-\bibitem[\protect\citeauthoryear{Allen \& Barbuy}{2006}]{allen2006}
-Allen, D.~M.,\& Barbuy B. 2006, 
-A$\&$A, 454, 917
-\bibitem[\protect\citeauthoryear{Jorissen et al.}{2005}]{jorissen2005}
-Jorissen, A., Za$\check{c}$, L., Udry, S., Lindgren, H.,\& Musaev, F.~A. 2005, 
-A$\&$A, 441, 1135
-\bibitem[\protect\citeauthoryear{Han et al.}{1995}]{han1995}
-Han, Z., Eggleton, P.~P., Podsiadlowski, P.,\& Tout, C.~A. 1995, 
-MNRAS, 277, 1443
-\bibitem[\protect\citeauthoryear{Pereira et al.}{2011}]{pereira2011}
-Pereira, C.~B., Sales Silva, J.,~A., Chavero, C., Roig, F.,\& Jilinski E. 2011, 
-A$\&$A, 533, A51
-\bibitem[\protect\citeauthoryear{Ho et al.}{2017}]{ho2017}
-Ho, A.~Y.~Q., Ness, M.~K., Hogg, D.~W., Rix, H.-W. Liu, C., Yang, F., Zhang, Y., Hou, Y.,\& Wang, Y. 2017, 
-ApJ, 836, 5
-\bibitem[\protect\citeauthoryear{Luo A.L., Bai Z.R. et al}{2015}]{luo2015}
-Luo, A.~L., Bai, Z.~R., et al. 2015, 
-RAA, in press
-\bibitem[\protect\citeauthoryear{Jorissen et al.}{1993}]{jorissen1993}
-Jorissen, A., Frayer, D.~T., Johnson, H.~W., Mayor, M.,\& Smith, V.~V. 1993, 
-A$\&$A, 271, 463
-\bibitem[\protect\citeauthoryear{Little-Marenin \& Little}{1987}]{little1987}
-Little-Marenin, I.~R.,\& Little, S.~J. 1987, 
-AJ, 93, 1539
-\bibitem[\protect\citeauthoryear{Smith}{1984}]{smith1984}
-Smith, V.~V. 1984, 
-A$\&$A, 132, 326
-\bibitem[\protect\citeauthoryear{Smith \& Wallerstein}{1983}]{smith1983}
-Smith, V.~V.,\& Wallerstein, G. 1983, 
-ApJ, 273, 742
-\bibitem[\protect\citeauthoryear{El Eid \& Champagne}{1995}]{el1995}
-El Eid, M.~F.,\& Champagne, A.~E. 1995, 
-ApJ, 451, 298
-\bibitem[\protect\citeauthoryear{Antipova et al.}{2004}]{antipova2004}
-Antipova, L.~I., Boyarchuk, A.~A., Pakhomov, Yu.~V.,\& Panchuk, V.~E. 2004, 
-ARep, 48, 597
-\bibitem[\protect\citeauthoryear{Boyarchuk et al.}{2002}]{boyarchuk2002}
-Boyarchuk, A.~A., Pakhomov, Y.~V., Antipova, L.~I.,\& Boyarchuk, M.~E. 2002, 
-ARep, 46, 819
-\bibitem[\protect\citeauthoryear{Takeda et al.}{2008}]{takeda2008}
-Takeda, Y., Sato, B.~V.,\& Murata, D. 2008, 
-AJ, 60, 781
-\bibitem[\protect\citeauthoryear{Mishenina et al.}{2006}]{mishenina2006}
-Mishenina, T.~V., Bienaym\' e, O., Gorbaneva, T.~I.,\& Charbonnel, C. 2006, 
-A$\&$A, 456, 1109
-\bibitem[\protect\citeauthoryear{Luck \& Heiter}{2007}]{luck2007}
-Luck R.~E.,\& Heiter, U. 2007, 
-AJ, 133, 2464
-\bibitem[\protect\citeauthoryear{Denissenkov \& Ivanov}{1987}]{denissenkov1987}
-Denissenkov P.~A.,\& Ivanov, V.~V. 1987, 
-SvAL, 13, 214
-\bibitem[\protect\citeauthoryear{de Castro et al.}{2016}]{decastro2016}
-de Castro, D.~B., Pereira, C.~B., Roig, F., Jilinski, E., Drake, N.~A., Chavero, C.,\& Sales Silva, J.~V. 2016, 
-MNRAS, 459, 4299
 

### 2018-01-24 article/ms.tex
be gentle

@@
 % If you need two or more lines of authors, add an extra line using \newauthor
-\author[B. J. Norfolk et al.]{Brodie J. Norfolk,$^{1}$\thanks{E-mail: bjee7@student.monash.edu (MU)}
-Andrew R. Casey,$^{1,2}$
-Mathew T. Miles,$^{1}$
-Alexander J. Kemp,$^{1}$ \newauthor
-Karakas ? Lattanzio ? Schlaufman ? and others ?
+\author[B.J. Norfolk et al.]{B.J. Norfolk,$^{1}$\thanks{E-mail: bjee7@student.monash.edu (MU)}
+A.R. Casey,$^{1,2}$
+M.T. Miles,$^{1}$
+A.J. Kemp,$^{1}$ 
+A.I. Karakas,$^{1}$ \newauthor
+J.C. Lattanzio,$^{1}$
+and K.C. Schlaufman 
 \\
@@
 Stars with peculiar enhancements of carbon and heavy elements ($Z > 30$) are historically referred to as Barium stars.
-While this chemical abundance pattern can be explained by thermally pulsing asymptotic giant branch (AGB) stars, many barium stars have not evolved through the red giant (or main-sequence) phase and therefore cannot be an AGB star.
-These stars are generally thought to have accreted mass from a more evolved companion.
-For this reason the frequency and properties of less-evolved barium stars is uniquely informative on the binary fraction, AGB yields, mass transfer, and stellar evolution.
-Here we present the discovery of 967 s-process candidates including; 257 barium stars, 49 barium doublet stars, and 661 strontium doublet stars from 454,180 giant stars observed by LAMOST.
-This sample constitutes the largest sample of barium stars discovered to date, and the most comprehensive search for barium stars in the Milky Way.
-\todo{Nearly all} of our barium stars are disk stars, and we find an \todo{steady/increasing/decreasing} fraction of barium stars with stellar metallicity, as \todo{expected} from AGB yields and stellar evolution theory.
-% Technitium?
-\todo{Most (178/257) of our sample show strong carbon enhancement.}
-Despite previous claims indicating that barium stars are preferentially enhanced in sodium due to the NeNa nucleosynthesis cycle occurring in \todo{massive} AGB stars, only 5 ($<2$\,\%) of our Barium stars show any evidence of enhancement in sodium.
+While this chemical abundance pattern can be explained by thermally pulsing asymptotic giant branch (AGB) stars, many Barium stars have not evolved through the red giant phase and therefore cannot be AGB stars.
+These stars are generally thought to have accreted mass from a more evolved AGB companion.
+For this reason the frequency and properties of less-evolved Barium stars is uniquely informative on the binary fraction, AGB yields, mass transfer, and stellar evolution.
+Here we present the discovery of 967 s-process candidates including; 257 Barium stars, 49 stars exhibiting exclusively barium enhancement, and 661 exhibiting exclusively strontium enhancement from 454,180 giant stars observed by LAMOST.
+This sample constitutes the largest sample of s-process enhanced stars discovered to date, and the most comprehensive search for Barium stars in the Milky Way.
+\todo{Nearly all} of our Barium stars are disk stars, and we find an \todo{steady/increasing/decreasing} fraction of Barium stars with stellar metallicity, as \todo{expected} from AGB yields and stellar evolution theory.
+51 Barium stars exhibited tecnetium enhancement in a single Tc emission line suggesting the exsistence of AGB stars in our sample.
+Most (178/257) of our sample show strong carbon enhancement consistent with the literature.
+Despite previous claims indicating that Barium stars are preferentially enhanced in sodium due to the NeNa nucleosynthesis cycle occurring in \todo{massive} AGB stars, only 5 ($<2$\,\%) of our Barium stars show any evidence of enhancement in sodium.
 \todo{This implies ....}
@@
 
-Barium stars as first recognized by \citet{Bidelman1951}, are chemically unique objects that exhibit envelopes with an overabundance of both carbon, and heavy elements (Z > 30) in comparison to the Sun.
-Barium stars exist as either intrinsic or extrinsic objects; intrinsic barium stars are in the TP-AGB (thermally pulsing-asymptotic giant branch) phase, the overabundance of both carbon and heavy elements are produced through the s-process and exist on the surface as the result of a thermal pulsing cycle.
+Barium stars as first recognized by \citet{Bidelman1951}, are chemically unique objects that exhibit envelopes with an overabundance of carbon and heavy elements (Z > 30) in comparison to the Sun.
+Barium stars exist as either intrinsic or extrinsic objects; intrinsic Barium stars are in the TP-AGB (thermally pulsing-asymptotic giant branch) phase, where the overabundance of both carbon and heavy elements are produced through the s-process and exist on the surface as the result of a thermal pulsing cycle.
 According to the mass-transfer hypothesis, extrinsic Barium stars are a consequence of stellar wind accretion \citep{boffin1988,jorissen1992} or Roche-lobe overflow \citep{webbink1986}, and are within a binary system containing a previous TP-AGB companion star (intrinsic Barium star) in its final phase as a white dwarf \citep{bohm1980,bohm1984}.
-In fact, \citet{mcclure1983} determines 85\% of all Barium stars are in binary systems and those that appear singular are actually pole-on, or highly eccentric binaries with significant radial velocity variations only occuring in a small phase range as detailed by \citet{pourbaix2004}.
-For these reasons, the properties and occurrence rate of barium stars are informative of the theoretical birth rate of AGB stars, the binary star fraction as a function of metallicity, the mass ratio of binary stars, as well as AGB yields across different masses and metallicities.
+In fact, \citet{mcclure1983} determines 85\% of all Barium stars are in binary systems and claims that those that appear singular are actually pole-on, or highly eccentric binaries with significant radial velocity variations only occuring in a small phase range as detailed by \citet{pourbaix2004}.
+For these reasons, the properties and occurrence rate of Barium stars are informative of the theoretical birth rate of AGB stars, the binary star fraction as a function of metallicity, the mass ratio of binary stars, as well as AGB yields across different masses and metallicities.
 
@@
 The energy from the thermal pulses force the star to expand, pushing the H-shell out to cooler regions and allowing the convective envelope to move inwards to regions previously mixed by the thermal pulse driven convective zones.
-This expansion and resultsing inward movement is classified as the third dredge up (TDU), and is theorized to occur after each thermal pulse.
+This expansion and resultsing inward movement is classified as the third dredge up (TDU), and is theorised to occur after each thermal pulse.
 During the TP-AGB phase, enrichent on the surface in $^{12}$C and heavy elements produced by the s-process is a result of the repeated downwash extensions of TDU \citep[e.g.][]{busso2001}.
 The star contracts PDU and reignites the H-shell producing the majority of the surface luminosity for the next interpulse period.
-The interpulse, thermal pulse, and dredge up cycle may occur numerous times and is dependent on the intitial mass, composition and mass-loss rate of the star.
+The interpulse, thermal pulse, and dredge up cycle may occur numerous times and is dependent on the intitial mass, composition, and mass-loss rate of the star.
 
-Barium giants form within a metallicity dependent initial mass range (approximately 0.8 - 8$M_{\odot}$), with the minimum mass for core helium and carbon burning decreasing as metalicity decreases.
+Barium giants form within a metallicity-dependent initial mass range (approximately 0.8 - 8$M_{\odot}$), with the minimum mass for core helium and carbon burning decreasing as metallicity decreases.
 The age of these stars vary considerably, with observable stars in metal-poor globular clusters hosting populations of $\approx$12Gyr.
-In contrast, metal rich, young observable stars reaching the upper limit may only reach $\approx$100Myr, this includes stars that are at the core carbon burning limit or very close to it \citep[e.g.][]{whitelock2013}.
+In contrast, metal rich, young observable stars may only reach $\approx$100Myr, this includes stars that are at the core carbon burning limit or very close to it \citep[e.g.][]{whitelock2013}.
 
-Many barium stars have been discovered in the disk and halo of the Milky Way \citep{gomez1997,mennessier1997}.
-Both studies show that the stellar populations of Barium stars can be separated into two groups when considering their \todo{absolute?} luminosity, kinematic, and spatial properties.
+Many Barium stars have been discovered in the disk and halo of the Milky Way \citep{gomez1997,mennessier1997}.
+These studies show that the stellar populations of Barium stars can be separated into two groups when considering their absolute luminosity, kinematic, and spatial properties.
 Barium stars populating the halo have already been investigated \citep[e.g.][]{junqueira2001,drake2008,pereira2009,allen2006} and their relationship with metal-poor, yellow, symbiotic halo stars has been established by \citet{jorissen2005} and \citet{pereira2009}.
-Additionally, \citet{pereira2011} concludes metal-rich barium stars share similar kinematics to other metal-rich and super metal-rich stars already analysed, suggesting that they do not belong to the bulge population.
-Furthermore, it is necessary to establish known abundances of s-process elements in a greater sample of Barium stars in order to compare their birth rate to theoretical expectations \citep{han1995}, explore the binary fraction at different metallicities, and infer AGB star yields at different masses and metallicities.
+Additionally, \citet{pereira2011} concludes that metal-rich Barium stars share similar kinematics to other metal-rich and super metal-rich stars already analysed, suggesting that they do not belong to the bulge population.
+Furthermore, it is necessary to establish known abundances of s-process elements in a greater sample of Barium stars in order to compare their birth rate to theoretical expectations \citep{han1995}, explore the binary fraction at different metallicities, and compare to AGB star yields at different masses and metallicities.
 
-In this paper we analysis 454,180 giant stars from LAMOST data release (DR) 2 to identify and examine 967 s-process candidates including barium stars, barium doublet stars and strontium doublet stars.
-Specifcally, the barium star giants studied here display especially strong s-process enhancement for \ion{Ba}{II} and \ion{Sr}{II} at lines 4554\AA \hspace{0.2mm} and 4077\AA, respectively.
-Our doublet candidates show s-process enhancement in 4554\AA \hspace{0.2mm} and 4934\AA for barium enhancement, and, 4554\AA \hspace{0.2mm} and 4215\AA for strontium enhancement.
-In Section \ref{sec:methods} we describe the observations and candidate selection, as well as the analysis follow up our follow-up observing campaign with MAGGELLAN.
+In this paper we analyse 454,180 giant stars from LAMOST data release (DR) 2 to identify and examine 967 s-process candidates including Barium stars, and exclusvely enhanced barium and strontium stars, respectively.
+Specifcally, the Barium star giants studied here display especially strong s-process enhancement for \ion{Ba}{II} and \ion{Sr}{II} at lines 4554\AA \hspace{0.2mm} and 4077\AA, respectively.
+Our exclusive barium and strontium candidates show s-process enhancement in 4554\AA \hspace{0.2mm} and 4934\AA for barium enhancement, and, 4554\AA \hspace{0.2mm} and 4215\AA for strontium enhancement.
+In Section \ref{sec:methods} we describe the observations and candidate selection, as well as the analysis follow up our follow-up observing campaign with Magellan.
 In Section \ref{sec:dis} we discuss the properties of our Barium stars in context of existing literature.
@@
 \section{Methods} \label{sec:methods}
-\subsection{LAMOST Analysis}
-\subsubsection{Data-driven Analysis}
+\subsection{LAMOST analysis}
+\subsubsection{Data-driven analysis}
 The LAMOST (Large sky Area Multi-Object Fibre Spectrographic) survey released low-resolution ($\mathcal{R} \approx 1800$) optical spectra (3700\,\AA\ to 9000\,\AA) for over two million stars in their second data release \citep{luo2015}.
 Stellar parameters ($T_{\rm eff}$, $\log{g}$, [M/H], [$\alpha$/M]) were derived using a data-driven model constructed using high fidelity APOGEE labels of 9,952 giant stars in common between LAMOST and the APOGEE survey.
-The cross-validation of the model with S/N > 50, yielded typical uncertainties of 70K in $T_eff$, 0.1 in log g, 0.1 in [Fe/H], and 0.04 in [$\alpha$/M].
-These uncertainties are broadly comparable to the conservative APOGEE DR12 uncertainties.
-\todo{not sure how the dwalfs come into play}
+It is important to note, this sample is exclusive to giant stars presenting the possibility that this research missed dwarf s-process enhanced stars.
+Cross-validation experience shows that the typical uncertainties are 70K in effective temperature $T_{eff}$, 0.1 dex in surface gravity log g, 0.1 dex in metallicity [Fe/H], and 0.04 dex in the alpha abundance relative to iron [$\alpha$/M].
+These uncertainties are approximately comparable to the conservative APOGEE DR12 uncertainties.
 
-\todo{Write more about this: the precision in parameters, how giants were selected from dwarfs, and then talk about how many giant spectra we used}.
-
-\subsubsection{Candidate Selection} \label{sec:cand}
+\subsubsection{Candidate selection} \label{sec:cand}
 The Barium stars analysed in this research were obtained by filtering for significant flux residuals, taken as, a disparity between the normalised LAMOST flux and the data driven model derived by \citet{ho2017}.
-A negative residual as shown in the poster child figure \ref{fig:figure1} illustrates an enhancement in \ion{Ba}{II} and \ion{Sr}{II} at lines 4554\AA \hspace{0.2mm} and 4077\AA, respectively.
+A negative residual as shown in the randomly selected Figure \ref{fig:figure1}, illustrates an enhancement in \ion{Ba}{II} and \ion{Sr}{II} at lines 4554\AA \hspace{0.2mm}, 4077\AA.
 These \ion{Ba}{II} and \ion{Sr}{II} resonance lines are very strong, allowing us to identify stars enhanced in neutron-capture elements given a well-fit model for the data.
-We used five filters that each spectra, for both enhancement lines, had to meet to be considered a s-process candidate; these included:
+We used five filters that each spectrum, for both enhancement lines, had to meet in order to be considered a s-process candidate; these included:
 
@@
 \begin{enumerate} 
-\item Profile amplitude for both enhancement lines must exceed A$\leq$-0.05.
-\item Both amplittudes must be measured within 3$\sigma$ $(|A|/\sigma _A \geq 3)$.
-\item The wavelength at each absorption line must be within $2$\AA \hspace{0.2mm}$(\lambda \leq 2)$.
-\item $\chi^2 \leq 3$.
-\item And, the spectra must have a signal-to-noise ratio of S/N $\geq 30$ per pixel.
+\item Profile amplitude for both enhancement lines must exceed A < -0.05.
+\item Both amplittudes must be measured within 3$\sigma$ ($|A|/\sigma _A$ < 3).
+\item The wavelength at each absorption line must be within $2$\AA \hspace{0.2mm}($\lambda$ < 2).
+\item Reduced $\chi^2$ from The Cannon must be < 3.
+\item And, the LAMOST spectra must have a signal-to-noise ratio of S/N > 30 per pixel.
 \end{enumerate}
-In addition, a visual observation of the accuracy between each normalised LAMOST flux and its accompanying data driven model was undertaken to exclude any results containing, false positives, candidates exhibiting data reduction issues, apparent absorption finer then the spectral resolution, and overly noisy normalised LAMOST spectra.
-This combined method generated 967 s-process candidates including; 257 barium stars, 49 barium doublet stars, and 661 strontium doublet stars, as listed in Table \ref{table:table1}.
+In addition, a visual inspection was undertaken to exclude any results containing, false positives, candidates exhibiting data reduction issues, apparent absorption finer then the spectral resolution, and overly noisy normalised LAMOST spectra.
+This combined method generated 967 s-process candidates including; 257 Barium stars, 49 stars exhibiting exclusively barium enhancement, and 661 exhibiting exclusively strontium enhancement, as listed in Table \ref{table:table1}.
 
@@
 	\includegraphics[width=\columnwidth]{posterchild.png}
-    \caption{Posterchild}
+    \caption{Random Barium Star Spectrum}
     \label{fig:figure1}
@@
 
-\subsubsection{Carbon Bands}
-
-Barium stars are optimal sites for investigating the relationship between the neutron-capture elements and other species that may be
-depleted or enhanced, because they act as neutron seeds during the operation of the s-process.
-In the ABG phase the abundance of carbon is a product of helium fusion, specifically the triple-alpha process within a star.
-In an identical mechanism to the presence of s-process elelment enhancement, carbon enhanced stars exist intrinsically or extrinsically.
-Giants and supergiants become enhanced in carbon through TDU process discussed in Section \ref{sec:intro}, and extrinsic carbon enhancement occurs via mass transfer from a binary AGB star.
-In our sample of barium star candidates we discovered enhancement in both CH and the G band for 178 of our total 257 stars.
-
-\subsubsection{Technetium Lines}
-
-Enhancement of technetium lines in our sample would indicate the presence of high luminosity Tc-self-enriched AGB S stars \citep{jorissen1993} and, suggest our candidates are infact intrinsic Barium stars.
-We undertook an identical analysis to the process described in Section \ref{sec:cand}, negative residuals for Tc enhancement lines 4049\AA, 4238.19\AA, 4262.27\AA, 4297\AA, and 5924.47\AA\hspace{0.2mm} were filtered for.
-In agreement with previous findings \citep[e.g.][]{little1987,smith1984,smith1983}, the results indicate that none of the evolved barium stars in our sample exhibited the presence of Tc enhancement.
-It is noted, \todo{51} of our barium candidates were enhanced in Tc lines, although, this is attributed to \todo{something} and is disregarded.
-
-\subsubsection{Sodium Doublet}
-
-Through an identical analysis to the process described in Section \ref{sec:cand}, we filtered for negative residuals in the enhanced sodium doublet lines 5889.950\AA\hspace{0.2mm} and 5895.924\AA.
-Our analysis produced 5 matches with our barium star candidates, this suggests sodium-rich material from the TP-AGB star polluted the barium star.
+\subsubsection{Further enhancements}
+We undertook an identical analysis to the process described in Section \ref{sec:cand} for sodium, technetium, and carbon enhancement.
+We filtered for negative residuals in the enhanced sodium doublet lines 5889.950\AA\hspace{0.2mm} and 5895.924\AA.
+Our analysis produced 5 matches with our Barium star candidates.
+51 canditdates were discovered to be enhanced in a single technetium line.
+And, for the CH and G band region at approximately 4300\AA\hspace{0.2mm} we matched 178 enhanced stars out of our total 257 stars.
 
@@
 \subsubsection{Observations}
-On the night of \todo{X} January 2018 we performed follow-up observations of \todo{X} barium star candidates using the MIKE spectrograph on the Magellan Clay telescope at Las Campanas Observatory, Chile.
+On the night of \todo{X} January 2018 we performed follow-up observations of \todo{X} Barium star candidates using the MIKE spectrograph on the Magellan Clay telescope at Las Campanas Observatory, Chile.
 Candidates for follow-up observations were chosen based on observability constraints and ranked by their apparent visual magnitude.
@@
 
-We reduced the data using the \texttt{CarPy} Python package \citep{kels03,kels14}.
+We reduced the data using the \texttt{CarPy} Python package \citep{kelson2000,kelson2003}.
 We used spline functions to continuum-normalise individual echelle orders, and resampled the normalised spectra onto a uniform-sized wavelength map.
@@
 
-\subsubsection{Abundance Analysis}
-We adopted the stellar parameters ($T_{\rm eff}$, $\log_{10}g$, [Fe/H]) provided from the data-driven analysis of \citep{Ho_2017}.
-Following the procedure outlined in \citep{Casey_2014}, we measured the strength of atomic absorption lines by fitting Gaussian profiles to the continuum-normalised spectra.
+\subsubsection{Abundance analysis}
+We adopted the stellar parameters ($T_{\rm eff}$, $\log_{10}g$, [Fe/H]) provided from the data-driven analysis of \citep{ho2017}.
+Following the procedure outlined in \citep{casey2014}, we measured the strength of atomic absorption lines by fitting Gaussian profiles to the continuum-normalised spectra.
 Most elemental abundances were derived directly from these line measurements, except for elements that show significant hyperfine splitting \todo{(e.g., )} or blending \todo{(e.g., X)}.
@@
 
-\todo{Some sentences for andy to add regarding abundance analysis and verification of stellar parameters from LAMOST}
-
-\todo{Were ant of the stars observed with Magellan/MIKE the stars enhanced in Na? C?}
+\todo{Some sentences for our fearless leader to add regarding abundance analysis and verification of stellar parameters from LAMOST}
 
@@
 \subsection{Dynamics}
-The dynamical analysis of our barium star candidates was accomplished by crossing matching the sample with GAIA \todo{ref gaia}, to produce 21 matches with proper motions, parallax, and galactic positions.
-We then, using the gala Python package, intergrated our data to calculate the orbits of our 21 candidates with a Milky Way Potential model.
-The parameters of the mass model are determined by least-squares fitting the enclosed mass profile of a pre-defined potential form to recent measurements compiled from the literature.
-These measurements are provided with the documentation of gala \citep{price2017}.
-The Milky Way potential implemented was constructed using a four component potential model consisting of a \citet{hernquist1990} bulge and nucleus, a \citet{miyamoto1975} disk, and an \citet{nfw1997} halo.
-In this potential, parameters of the disk and bulge were adjuted to be consistent with previous work \citep{bovy2015} and vary the scale mass and scale radius of the nucleus and halo, respectively.
-This potential model was used to integrate the orbits of our candidates back a \todo{number} years, and compute distributions of orbital properties including orbital period, orbital energy, apocenter, eccentricity, and angular momentum in z.
-\subsubsection{Galactic Positioning}
-The galactic position of our GAIA matched candidates was determined through observation of the relationship between orbital energy and angular momentum in z.
-For this relationship a comparison between for 1,000 random normal-looking LAMOST stars and our barum star candidates was made.
-Both samples followed an identical trend and given the fact that most LAMOST stars are disk stars, it was concluded that our barium star candidates existed in the disk of the Milky Way.
-
-\begin{figure}
-	% To include a figure from a file named example.*
-	% Allowable file formats are eps or ps if compiling using latex
-	% or pdf, png, jpg if compiling using pdflatex
-	\includegraphics[width=\columnwidth]{ECCdummy.png}
-    \caption{Eccentricity}
-    \label{fig:figure3}
-\end{figure}
-
-\begin{figure}
-	% To include a figure from a file named example.*
-	% Allowable file formats are eps or ps if compiling using latex
-	% or pdf, png, jpg if compiling using pdflatex
-	\includegraphics[width=\columnwidth]{energy_angmomz.png}
-    \caption{Energy Vs. Angular Momentum in Z}
-    \label{fig:figure3}
-\end{figure}
+The dynamical analysis undertaken for our Barium star candidates was accomplished by crossing matching the sample with Gaia \citep{gaia2016a,gaia2016b} to produce 21 matches with proper motions, parallax, and galactic positions.
+We then, using the gala Python package, integrated our data to calculate the orbits of our 21 candidates with a Milky Way Potential model.
+The Milky Way potential implemented was constructed using a four component potential model built from a \citet{hernquist1990} bulge and nucleus, a \citet{miyamoto1975} disk, and the \citet{nfw1997} halo.
+In this potential, the disk and bulge parameters were adjusted to be consistent with previous work \citep{bovy2015}, and to vary the scale mass and radius, of the nucleus and halo, respectively.
+This potential model was used to integrate the orbits of our candidates back half a billion years, and compute distributions of orbital properties including orbital period, orbital energy, apocenter, eccentricity, and angular momentum in z.
+All stars are shown to have orbits consistent with being disk stars.
 
 \section{Discussion}  \label{sec:dis}
+
+\subsection{Sodium enhancment}
+According to \citet{el1995}, sodium overabundance observed in the atmospheres of supergiants is synthesized by the NeNa reaction chain in the convective core of main-sequence stars.
+Sodium is transported to the surface of these supergiants via mixing of CNO cycle products during the first dredge-up, although, it is important to note sodium enhancement is not constrained to supergiant stars.
+Stars with a  minimum 1.5$M_\odot$ can exhibit sodium abundance similarily through the NeNa cycle \citep{denissenkov1987}.
+\citet{antipova2004} discovered a sodium enhancement in 16 of their Barium star candidates, they relate this to the dredge-up of nuclear-burning material produced by convection during the red-giant phase.
+Moreover, they suggest [Na/Fe] ratios exhibit systematically higher values for giants with lower log g values, but do not exhibit variations in metallicity.
+Similarily, \citet{decastro2016} highlights the possible weak, anti-correlation between [Na/Fe] ratio and log g, and illustrates this trend in previous studies\citep[e.g.][]{boyarchuk2002,mishenina2006,luck2007,takeda2008}.
+
+It's important to highlight our research only discovered $<2$\,\% sodium presence in our 257 Barium candidates, contrary to previous studies \citep[e.g.][]{decastro2016}.
+Also, synonymous to our s-process candidates, synthesized sodium is brought to the surface of giants via the first dredge-up, therefore, these candidates may display sodium enhancement without mass transfer from a TP-AGB star.
+And, in juxtaposition to the literature, our 5 sodium enhanced stars exhibit a surface gravity range between 2.98 and 3, showing no correlation between higher [Na/Fe] values and lower log g values.
+These considerations suggest sodium-rich material from the TP-AGB star polluted our 5 Barium candidates, but also, sodium enhancement is not unbiquitous in Barium Stars.
+
+\subsection{Technetium enhancement}
+Technetium has a half life of approximately 211,000 years and as a result cannot be present in an extrinsic Barium star, enhancemnt in this element in our sample would indicate the presence of AGB stars \citep{jorissen1993}, and suggest some of our candidates are intrinsic Barium stars.
+Our analyse discovered 51 single Tc line matches within our 257 Barium star candidate sample.
+However, for Tc to be present in  a star the enhancement lines must be considerably strong, and given that all 51 matches were at single lines it is concluded that these results are data artifacts.
+In agreement with previous findings \citep[e.g.][]{little1987,smith1984,smith1983}, the results indicate that none of the evolved Barium stars in our sample exhibited the presence of Tc enhancement, and it can be concluded our Barium star sample is extrinsic.
+It is noted, Tc enhancement is a very difficult line to analyse and that this conclusion is not concrete.
+
+\subsection{Carbon bands}
+Barium stars are excellent candidates for investigating the relationship between neutron-capture elements and other species that may be depleted or enhanced, since they act as neutron seeds during the operation of the s-process.
+In the AGB phase the abundance of carbon is a product of helium fusion, specifically the triple-alpha process within a star.
+In an identical mechanism to the presence of s-process element enhancement, carbon enhanced stars exist intrinsically or extrinsically.
+Giants and supergiants become enhanced in carbon through TDU process discussed in Section \ref{sec:intro}, and extrinsic carbon enhancement occurs via mass transfer from a binary AGB star.
+
+Our analsyse produced 178 CH and G band enhanced stars out of the total 257 Barium candidates.
+Similar to the s-process enhancement, this suggests our candidates are either intrinsic or extrinsic Barium stars.
+
+\subsection{Extrinsic and intrinsic Barium stars}
+Barium stars exist as either intrinsic or extrinsic objects.
+Intrinsic Barium stars must be massive enough to reach the TP-AGB phase, and extrinsic Barium stars must be in a binary with a previosuly polluting TP-AGB star companion.
+Figure \ref{fig:figure2} demonstrates the majority of our Barium star sample has a surface gravity greater then 2, highlighting that our sample is primarily not massive enough to have reach the TP-AGB phase and therefore, must be extrinsic Barium stars.
 
@@
 
-\subsection{Sodium Enhancment}
-According to \citet{el1995}, sodium overabundance observed in the atmospheres of A-F supergiant stars is synthesized in the convective core of main-sequence stars in the NeNa reaction chain.
-Sodium is transported to the surface of these supergiants via mixing of CNO cycle products during the first dredge-up, this constrains sodium enhancement to supergiants and giants only.
-\citet{antipova2004} discovered a sodium enhancement in a number of their barium star candidates, they relate this to the dredge-up of nuclear-burning material produced by convection during the red-giant phase.
-Moreover, they suggest [Na/Fe] values do not exhibit variations in metallicity, but [Na/Fe] ratios exhibit systematically higher values for giants with lower log g values.
-Similarily, \citet{decastro2016} highlights the possible weak, but statistically significant anti-correlation between [Na/Fe] ratio and log g, and illustrates this trend in previous studies\citep[e.g.][]{boyarchuk2002,mishenina2006,luck2007,takeda2008}.
-
-Although, it's important to note a star with a minimum 1.5$M_\odot$ can exhibit sodium abundance through the NeNc cycle \citep{denissenkov1987}.
-During the giant phase synthesized sodium is brought to the surface via the first dredge-up, therefore, these candidates may display sodium enhancement without mass transfer from a TP-AGB star.
-Lastly, it is important to note studies including \citet{decastro2016} conclude sodium enhancement is ubiquitous throughout barium stars yet in contradiction, our sample only exhibits only a $<2$\,\% sodium presence.
+\subsection{AGB yields comparison}
 
@@
 
-The last numbered section should briefly summarise what has been done, and describe
-the final conclusions which the authors draw from their work.
+Our research discovered 967 s-process candidates including; 257 Barium stars, 49 stars exhibiting exclusively barium enhancement, and 661 exhibiting exclusively strontium enhancement from 454,180 giant stars observed by LAMOST.
+This is the largest sample of s-process enhanced stars to date.
+Nearly all of our Barium candidates are disk stars, 178 exhibit CH and G band enhancement, no plausible technetium enhancement is discovered, and it is shown sodium ehancement is not ubiquitous in s-process stars as previously claimed.
+We highlight that the majority of our Barium stars have a surface gravity greater then 2, this suggests that these are extrinsic Barium stars
 
@@
 Fired Status: yes
-
-%\section{Examples}
-%
-%Normally the next section describes the techniques the authors used.
-%It is frequently split into subsections, such as Section~\ref{sec:maths} below.
-%
-%\subsection{Maths}
-%\label{sec:maths} 
-%
-%Simple mathematics can be inserted into the flow of the text e.g. $2\times3=6$
-%or $v=220$\,km\,s$^{-1}$, but more complicated expressions should be entered
-%as a numbered equation:
-%
-%\begin{equation}
-%    x=\frac{-b\pm\sqrt{b^2-4ac}}{2a}.
-%	\label{eq:quadratic}
-%\end{equation}
-%
-%Refer back to them as e.g. equation~(\ref{eq:quadratic}).
-%
-%\subsection{Figures and tables}
-%
-%Figures and tables should be placed at logical positions in the text. Don't
-%worry about the exact layout, which will be handled by the publishers.
-%
-%Figures are referred to as e.g. Fig.~\ref{fig:example_figure}, and tables as
-%e.g. Table~\ref{tab:example_table}.
-%
-%\begin{figure}
-%	% To include a figure from a file named example.*
-%	% Allowable file formats are eps or ps if compiling using latex
-%	% or pdf, png, jpg if compiling using pdflatex
-%	\includegraphics[width=\columnwidth]{example}
-%    \caption{This is an example figure. Captions appear below each figure.
-%	Give enough detail for the reader to understand what they're looking at,
-%	but leave detailed discussion to the main body of the text.}
-%    \label{fig:example_figure}
-%\end{figure}
-%
-%
-%\begin{table}
-%	\centering
-%	\caption{This is an example table. Captions appear above each table.
-%	Remember to define the quantities, symbols and units used.}
-%	\label{tab:example_table}
-%	\begin{tabular}{lccr} % four columns, alignment for each
-%		\hline
-%		A & B & C & D\\
-%		\hline
-%		1 & 2 & 3 & 4\\
-%		2 & 4 & 6 & 8\\
-%		3 & 5 & 7 & 9\\
-%		\hline
-%	\end{tabular}
-%\end{table}
-
-% The best way to enter references is to use BibTeX:
 
@@
 ApJ, 451, 298
+\bibitem[\protect\citeauthoryear{Gaia Collaboration et al.}{2016a}]{gaia2016a}
+Gaia Collaboration, Brown, A.~G.~A., Vallenari, A., Prusti, T., de Bruijne, J.~H.~J., Mignard, F., Drimmel, R., Babusiaux, C., Bailer-Jones, C.~A.~L.,\& Bastian, U., et al. 2016, 
+A$\&$A, 595, A2
+\bibitem[\protect\citeauthoryear{Gaia Collaboration et al.}{2016b}]{gaia2016b}
+Gaia Collaboration, Prusti, T., de Bruijne, J.~H.~J., Brown, A.~G.~A., Vallenari, A., Babusiaux, C., Bailer-Jones, C.~A.~L., Bastian, U., Biermann, M.,\& Evans, D.~W. et al. 2016, 
+A$\&$A, 595, A1
 \bibitem[\protect\citeauthoryear{Gomez et al.}{1997}]{gomez1997}
@@
 SAIt, 87, 229
+\bibitem[\protect\citeauthoryear{Kelson et al.}{2000}]{kelson2000}
+Kelson, D.~D., Illingworth, G.~D., van Dokkum, P.~G.,\& Franx, M. 2000, ApJ, 531, 159
+\bibitem[\protect\citeauthoryear{Kelson}{2003}]{kelson2003}
+Kelson, D.~D. 2003, 
+PASP, 115, 688
 \bibitem[\protect\citeauthoryear{Kobayashi et al.}{2011}]{kobayashi2011}
@@
 AJ, 133, 2464
-\bibitem[\protect\citeauthoryear{Luo A.L., Bai Z.R. et al}{2015}]{luo2015}
+\bibitem[\protect\citeauthoryear{Luo et al}{2015}]{luo2015}
 Luo, A.~L., Bai, Z.~R., et al. 2015, 
@@
 
-\appendix
-
-\section{Some extra material}
-
-If you want to present additional material which would interrupt the flow of the main paper,
-it can be placed in an Appendix which appears after the list of references.
-
 % Don't change these lines

### 2018-01-24 article/ms.tex
be gentle

@@
 It's important to highlight our research only discovered $<2$\,\% sodium presence in our 257 Barium candidates, contrary to previous studies \citep[e.g.][]{decastro2016}.
+This suggests systematic differences in the analyse undertaken by said previous studies.
 Also, synonymous to our s-process candidates, synthesized sodium is brought to the surface of giants via the first dredge-up, therefore, these candidates may display sodium enhancement without mass transfer from a TP-AGB star.
@@
 \subsection{Technetium enhancement}
-Technetium has a half life of approximately 211,000 years and as a result cannot be present in an extrinsic Barium star, enhancemnt in this element in our sample would indicate the presence of AGB stars \citep{jorissen1993}, and suggest some of our candidates are intrinsic Barium stars.
+Technetium has a half life of approximately 211,000 years and as a result cannot be present in an extrinsic Barium star.
+Enhancemnt in Tc would indicate the presence of AGB stars \citep{jorissen1993}, and suggest some of our candidates are intrinsic Barium stars.
 Our analyse discovered 51 single Tc line matches within our 257 Barium star candidate sample.
@@
 Figure \ref{fig:figure2} demonstrates the majority of our Barium star sample has a surface gravity greater then 2, highlighting that our sample is primarily not massive enough to have reach the TP-AGB phase and therefore, must be extrinsic Barium stars.
+Furthermore, this suggests other enhancements including our 5 sodium and 178 carbon enhanced Barium stars exist through TP-AGB companion pollution.
 
@@
 Nearly all of our Barium candidates are disk stars, 178 exhibit CH and G band enhancement, no plausible technetium enhancement is discovered, and it is shown sodium ehancement is not ubiquitous in s-process stars as previously claimed.
-We highlight that the majority of our Barium stars have a surface gravity greater then 2, this suggests that these are extrinsic Barium stars
+We highlight that the majority of our Barium stars have a surface gravity greater then 2, this suggests that these are extrinsic Barium stars.
 
@@
 
+\bibitem[\protect\citeauthoryear{Casey}{2014}]{casey2014}
+Casey, A.~R. 2014, 
+PhDT, 394
+\todo{format Andy's ref properly}
+%@PHDTHESIS{2014PhDT.......394C,
+%   author = {{Casey}, A.~R.},
+%    title = "{A Tale of Tidal Tales in the Milky Way}",
+% keywords = {Astronomy, Astrophysics, Stellar streams},
+%   school = {Australian National University},
+%     year = 2014,
+%    month = May,
+%      doi = {10.5281/zenodo.49493},
+%   adsurl = {http://adsabs.harvard.edu/abs/2014PhDT.......394C},
+%  adsnote = {Provided by the SAO/NASA Astrophysics Data System}
+%}
+
 \end{thebibliography}

### 2018-01-24 article/ms.tex
add schlauf affil and spacing for author initials

@@
 
-% Please keep new commands to a minimum, and use \newcommand not \def to avoid
-% overwriting existing commands. Example:
-%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \title[S-process stars in LAMOST]{Discovery of s-process stars in the LAMOST survey}
 
-% The list of authors, and the short list which is used in the headers.
-% If you need two or more lines of authors, add an extra line using \newauthor
-\author[B.J. Norfolk et al.]{B.J. Norfolk,$^{1}$\thanks{E-mail: bjee7@student.monash.edu (MU)}
-A.R. Casey,$^{1,2}$
-M.T. Miles,$^{1}$
-A.J. Kemp,$^{1}$ 
-A.I. Karakas,$^{1}$ \newauthor
-J.C. Lattanzio,$^{1}$
-and K.C. Schlaufman 
+\author[B.~J. Norfolk et al.]{B.~J. Norfolk,$^{1}$\thanks{E-mail: bjee7@student.monash.edu (MU)}
+A.~R. Casey,$^{1,2}$
+M.~T. Miles,$^{1}$
+A.~J. Kemp,$^{1}$ 
+A.~I. Karakas,$^{1}$ \newauthor
+J.~C. Lattanzio,$^{1}$
+and K.~C. Schlaufman$^{3}$
 \\
@@
 $^{2}$Faculty of Information Technology, Monash University, Clayton 3800, Victoria, Australia\\
+$^{3}$Department of Physics and Astronomy, Johns Hopkins University, 3400 N Charles St., Baltimore, MD 21218, USA
 }

### 2018-01-24 article/ms.tex
abstract edits and minor spelling

@@
 \begin{abstract}
-Stars with peculiar enhancements of carbon and heavy elements ($Z > 30$) are historically referred to as Barium stars.
-While this chemical abundance pattern can be explained by thermally pulsing asymptotic giant branch (AGB) stars, many Barium stars have not evolved through the red giant phase and therefore cannot be AGB stars.
-These stars are generally thought to have accreted mass from a more evolved AGB companion.
-For this reason the frequency and properties of less-evolved Barium stars is uniquely informative on the binary fraction, AGB yields, mass transfer, and stellar evolution.
-Here we present the discovery of 967 s-process candidates including; 257 Barium stars, 49 stars exhibiting exclusively barium enhancement, and 661 exhibiting exclusively strontium enhancement from 454,180 giant stars observed by LAMOST.
-This sample constitutes the largest sample of s-process enhanced stars discovered to date, and the most comprehensive search for Barium stars in the Milky Way.
-\todo{Nearly all} of our Barium stars are disk stars, and we find an \todo{steady/increasing/decreasing} fraction of Barium stars with stellar metallicity, as \todo{expected} from AGB yields and stellar evolution theory.
-51 Barium stars exhibited tecnetium enhancement in a single Tc emission line suggesting the exsistence of AGB stars in our sample.
-Most (178/257) of our sample show strong carbon enhancement consistent with the literature.
-Despite previous claims indicating that Barium stars are preferentially enhanced in sodium due to the NeNa nucleosynthesis cycle occurring in \todo{massive} AGB stars, only 5 ($<2$\,\%) of our Barium stars show any evidence of enhancement in sodium.
-\todo{This implies ....}
+Stars with peculiar enhancements of carbon and heavy elements ($Z > 30$) are historically referred to as `Barium stars'.
+While this chemical abundance pattern can be explained by thermally pulsing asymptotic giant branch (AGB) stars, many so-called Barium stars have not evolved through the red giant phase and therefore cannot be AGB stars.
+These less-evolved stars are generally thought to have accreted mass from a more-evolved AGB companion.
+For this reason the frequency and properties of less-evolved Barium stars are uniquely informative on the binary fraction, AGB yields, mass transfer, and stellar evolution.
+Here we present the discovery of 967 s-process candidates from 454,180 giant stars observed by LAMOST.
+Our sample includes; 257 Barium stars, 49 stars exhibiting only significant barium enhancement, and 661 exhibiting only strontium enhancement.
+This sample constitutes the largest number of s-process enhanced stars ever discovered, and represents the most comprehensive search for Barium stars in the Milky Way.
+All of our Barium stars are consistent with membership in the Milky Way disk, and we find an \todo{steady/increasing/decreasing} fraction of Barium stars with stellar metallicity, as \todo{expected} from AGB yields and stellar evolution theory.
+We find 51 Barium stars exhibit some evidence of technetium, \todo{suggesting the existence of AGB stars in our sample}.
+Most (178/257) Barium stars in our sample show strong carbon enhancement, consistent with the literature.
+However, despite previous claims indicating that Barium stars are preferentially enhanced in sodium due to the NeNa nucleosynthesis cycle occurring in massive AGB stars, only 5 ($<2$\,\%) of our Barium stars show any evidence of enhancement in sodium.
+\todo{A sentence about AGB yield comparison.} When binary properties become available from end-of-mission Gaia astrometry, this sample of s-process stars will be critical in explaining mass transfer in binary systems and refining AGB yields across a range of masses and metallicities.
 \end{abstract}
@@
 
-Barium stars as first recognized by \citet{Bidelman1951}, are chemically unique objects that exhibit envelopes with an overabundance of carbon and heavy elements (Z > 30) in comparison to the Sun.
+Barium stars as first recognised by \citet{Bidelman1951}, are chemically unique objects that exhibit envelopes with an overabundance of carbon and heavy elements (Z > 30) in comparison to the Sun.
 Barium stars exist as either intrinsic or extrinsic objects; intrinsic Barium stars are in the TP-AGB (thermally pulsing-asymptotic giant branch) phase, where the overabundance of both carbon and heavy elements are produced through the s-process and exist on the surface as the result of a thermal pulsing cycle.
 According to the mass-transfer hypothesis, extrinsic Barium stars are a consequence of stellar wind accretion \citep{boffin1988,jorissen1992} or Roche-lobe overflow \citep{webbink1986}, and are within a binary system containing a previous TP-AGB companion star (intrinsic Barium star) in its final phase as a white dwarf \citep{bohm1980,bohm1984}.
-In fact, \citet{mcclure1983} determines 85\% of all Barium stars are in binary systems and claims that those that appear singular are actually pole-on, or highly eccentric binaries with significant radial velocity variations only occuring in a small phase range as detailed by \citet{pourbaix2004}.
+In fact, \citet{mcclure1983} determines 85\% of all Barium stars are in binary systems and claims that those that appear singular are actually pole-on, or highly eccentric binaries with significant radial velocity variations only occurring in a small phase range as detailed by \citet{pourbaix2004}.
 For these reasons, the properties and occurrence rate of Barium stars are informative of the theoretical birth rate of AGB stars, the binary star fraction as a function of metallicity, the mass ratio of binary stars, as well as AGB yields across different masses and metallicities.

### 2018-01-24 article/ms.tex
spelling

@@
 
-The slow neutron capture process (s-process), occuring in the interior of AGB stars, synthesizes roughly half of all elements heavier than iron \citep[e.g.][]{busso1999,travaglio2001,herwig2005,romano2010,kobayashi2011,prantzos2012,bisterzo2014,karakas12016}.
+The slow neutron capture process (s-process), occurring in the interior of AGB stars, synthesises roughly half of all elements heavier than iron \citep[e.g.][]{busso1999,travaglio2001,herwig2005,romano2010,kobayashi2011,prantzos2012,bisterzo2014,karakas12016}.
 Late in the AGB phase, during the thermally pulsing-AGB (TP-AGB) phase, thermal instabilities occur in the He shell every $10^5$ years or so, depending on the H-exhausted core mass.
@@
 The energy from the thermal pulses force the star to expand, pushing the H-shell out to cooler regions and allowing the convective envelope to move inwards to regions previously mixed by the thermal pulse driven convective zones.
-This expansion and resultsing inward movement is classified as the third dredge up (TDU), and is theorised to occur after each thermal pulse.
-During the TP-AGB phase, enrichent on the surface in $^{12}$C and heavy elements produced by the s-process is a result of the repeated downwash extensions of TDU \citep[e.g.][]{busso2001}.
+This expansion and resulting inward movement is described as the third dredge up (TDU), and is theorised to occur after each thermal pulse.
+During the TP-AGB phase, enrichment on the surface in $^{12}$C and heavy elements produced by the s-process is a result of the repeated downwash extensions of TDU \citep[e.g.][]{busso2001}.
 The star contracts PDU and reignites the H-shell producing the majority of the surface luminosity for the next interpulse period.
-The interpulse, thermal pulse, and dredge up cycle may occur numerous times and is dependent on the intitial mass, composition, and mass-loss rate of the star.
+The interpulse, thermal pulse, and dredge up cycle may occur numerous times and is dependent on the initial mass, composition, and mass-loss rate of the star.
 

### 2018-01-24 article/ms.tex
updates to methods

@@
 
-Barium giants form within a metallicity-dependent initial mass range (approximately 0.8 - 8$M_{\odot}$), with the minimum mass for core helium and carbon burning decreasing as metallicity decreases.
+Barium giants form within a metallicity-dependent initial mass range (approximately $0.8 - 8\,M_{\odot}$), with the minimum mass for core helium and carbon burning decreasing as metallicity decreases.
 The age of these stars vary considerably, with observable stars in metal-poor globular clusters hosting populations of $\approx$12Gyr.
@@
 
-In this paper we analyse 454,180 giant stars from LAMOST data release (DR) 2 to identify and examine 967 s-process candidates including Barium stars, and exclusvely enhanced barium and strontium stars, respectively.
-Specifcally, the Barium star giants studied here display especially strong s-process enhancement for \ion{Ba}{II} and \ion{Sr}{II} at lines 4554\AA \hspace{0.2mm} and 4077\AA, respectively.
-Our exclusive barium and strontium candidates show s-process enhancement in 4554\AA \hspace{0.2mm} and 4934\AA for barium enhancement, and, 4554\AA \hspace{0.2mm} and 4215\AA for strontium enhancement.
-In Section \ref{sec:methods} we describe the observations and candidate selection, as well as the analysis follow up our follow-up observing campaign with Magellan.
+In this paper we analyse 454,180 giant stars from the second LAMOST data release (DR) to identify and examine 967 s-process candidates including Barium stars, and exclusively enhanced barium and strontium stars, respectively.
+In Section \ref{sec:methods} we describe the observations and candidate selection, as well as the analysis of high-resolution follow-up observations obtained for a few candidates.
 In Section \ref{sec:dis} we discuss the properties of our Barium stars in context of existing literature.
@@
 The Barium stars analysed in this research were obtained by filtering for significant flux residuals, taken as, a disparity between the normalised LAMOST flux and the data driven model derived by \citet{ho2017}.
-A negative residual as shown in the randomly selected Figure \ref{fig:figure1}, illustrates an enhancement in \ion{Ba}{II} and \ion{Sr}{II} at lines 4554\AA \hspace{0.2mm}, 4077\AA.
+Specifically, we identified Barium stars by searching for \ion{Ba}{II} and \ion{Sr}{II} enhancement at the 4554\,\AA\ and 4077\,\AA, respectively.
+A negative residual, as shown in a candidate Barium star in Figure \ref{fig:figure1}, illustrates an enhancement in \ion{Ba}{II} and \ion{Sr}{II} at lines 4554\,\AA\, 4077\,\AA.
 These \ion{Ba}{II} and \ion{Sr}{II} resonance lines are very strong, allowing us to identify stars enhanced in neutron-capture elements given a well-fit model for the data.
-We used five filters that each spectrum, for both enhancement lines, had to meet in order to be considered a s-process candidate; these included:
+Stars identified to just show high levels of barium required enhancement at both the 4554\,\AA\ and 4934\,\AA\ resonance lines, and for stars just enhanced in strontium we looked for significant residuals at the 4554\,\AA\ and 4215\,\AA\ absorption lines.
+
+We used five filters that each spectrum, for each set of absorption lines, had to meet in order to be considered a s-process candidate; these included:
 
@@
 \begin{enumerate} 
-\item Profile amplitude for both enhancement lines must exceed A < -0.05.
-\item Both amplittudes must be measured within 3$\sigma$ ($|A|/\sigma _A$ < 3).
-\item The wavelength at each absorption line must be within $2$\AA \hspace{0.2mm}($\lambda$ < 2).
-\item Reduced $\chi^2$ from The Cannon must be < 3.
-\item And, the LAMOST spectra must have a signal-to-noise ratio of S/N > 30 per pixel.
+\item Profile amplitude for both enhancement lines must be $A < -0.05$.
+\item Both amplitudes must be measured within 3$\sigma$ ($|A|/\sigma _A$ < 3).
+\item The wavelength at each absorption line must be within 2\,\AA\ ($\lambda$ < 2).
+\item The reduced $\chi^2$ from \emph{The Cannon} must be $\chi_r^2 < 3$.
+\item And finally, the LAMOST spectra must have a signal-to-noise ratio of $S/N > 30\,\textrm{pixel}^{-1}$.
 \end{enumerate}

### 2018-01-25 article/ms.tex
update abstract

@@
 All of our Barium stars are consistent with membership in the Milky Way disk, and we find an \todo{steady/increasing/decreasing} fraction of Barium stars with stellar metallicity, as \todo{expected} from AGB yields and stellar evolution theory.
-We find 51 Barium stars exhibit some evidence of technetium, \todo{suggesting the existence of AGB stars in our sample}.
+We find up to 51 Barium stars exhibit some evidence of technetium from LAMOST spectra, and most (46/51) have $\log{g} > 2$, which suggests they cannot be AGB stars and may indicate a recent ($100\,\textrm{Myr}$) mass accretion event.
 Most (178/257) Barium stars in our sample show strong carbon enhancement, consistent with the literature.

### 2018-01-25 article/ms.tex
methods

@@
 
-\subsubsection{Further enhancements}
-We undertook an identical analysis to the process described in Section \ref{sec:cand} for sodium, technetium, and carbon enhancement.
-We filtered for negative residuals in the enhanced sodium doublet lines 5889.950\AA\hspace{0.2mm} and 5895.924\AA.
-Our analysis produced 5 matches with our Barium star candidates.
-51 canditdates were discovered to be enhanced in a single technetium line.
-And, for the CH and G band region at approximately 4300\AA\hspace{0.2mm} we matched 178 enhanced stars out of our total 257 stars.
+\subsubsection{Enhancements due to sodium, technetium, and carbon}
+We performed an identical analysis to the process described in Section \ref{sec:cand} in order to identify sodium, technetium, or carbon enhancement in our sample of 257 Barium stars.
+We used the sodium doublet lines at 5889\,\AA\ and 5895\,\AA\ to select Barium stars enhanced in sodium, and required significant absorption in both features.
+Only 5/257 Barium stars met this criteria,  \todo{however something about the dust for those stars}.
+For technetium enhancement we searched for significant residual deviations at the 4049\,\AA, 4238\,\AA, 4262\,\AA, 4297\,\AA, and 5924\,\AA.
+These absorption lines are extremely weak, and would require a substantial amount of technetium before it would be visible in a high S/N LAMOST spectrum.
+We found 51 Barium stars exhibited some level of significant enhancement (based on the filters above) at a single technetium line, yet none showed enhancement at more than one technetium line.
+We note that the single enhancement near technetium for these 51 stars may be the consequence of data reduction/calibration artefacts, but we include details of which stars matched on technetium in Table \ref{tab:table} nonetheless.
+Finally, for carbon enhancement we searched for significant deviations at the CH and G band near 4300\,\AA.
+We found 178/257 stars to show significant carbon enhancement (e.g., $[\textrm{C/M}] \gtrsim 0.5$).
 

### 2018-01-25 article/ms.tex
stuff on sodium enhancement

@@
 \subsection{Dynamics}
-The dynamical analysis undertaken for our Barium star candidates was accomplished by crossing matching the sample with Gaia \citep{gaia2016a,gaia2016b} to produce 21 matches with proper motions, parallax, and galactic positions.
-We then, using the gala Python package, integrated our data to calculate the orbits of our 21 candidates with a Milky Way Potential model.
-The Milky Way potential implemented was constructed using a four component potential model built from a \citet{hernquist1990} bulge and nucleus, a \citet{miyamoto1975} disk, and the \citet{nfw1997} halo.
+We integrated galactic orbits for 21 Barium stars using recent astrometry from Gaia/TGAS \citep{gaia2016a,gaia2016b}.
+Using the \texttt{gala} Python package, we integrated each star backwards for $0.5\,\textrm{Gyr}$ in a Milky Way-like potential that consists of four components: a \citet{hernquist1990} bulge and nucleus, a \citet{miyamoto1975} disk, and the \citet{nfw1997} halo.
 In this potential, the disk and bulge parameters were adjusted to be consistent with previous work \citep{bovy2015}, and to vary the scale mass and radius, of the nucleus and halo, respectively.
-This potential model was used to integrate the orbits of our candidates back half a billion years, and compute distributions of orbital properties including orbital period, orbital energy, apocenter, eccentricity, and angular momentum in z.
-All stars are shown to have orbits consistent with being disk stars.
+We computed orbital periods, energy, apocenters, pericenters, eccentricities, and angular momentum in the $z$-direction.
+All 21 stars showed prograde orbits that were consistent with membership in the Milky Way disk.
 
@@
 
+\subsection{Extrinsic and intrinsic Barium stars}
+Barium stars exist as either intrinsic or extrinsic objects.
+Intrinsic Barium stars must be massive enough to reach the TP-AGB phase, and extrinsic Barium stars must be in a binary with a previously polluting TP-AGB star companion.
+Figure \ref{fig:figure2} shows that the majority of our Barium stars have $\log{g} > 2$, highlighting that most stars in our sample are not massive enough to have already reached the TP-AGB phase and therefore, must be extrinsic Barium stars.
+The classification for Barium stars with $\log{g} < 2$ is uncertain: these stars could be intrinsic or extrinsic.
+From here on when we refer to extrinsic Barium stars, we specifically refer to those with $\log{g} > 2$.
+
 \subsection{Sodium enhancment}
-According to \citet{el1995}, sodium overabundance observed in the atmospheres of supergiants is synthesized by the NeNa reaction chain in the convective core of main-sequence stars.
+According to \citet{el1995}, sodium overabundances observed in the atmospheres of supergiants is synthesised by the NeNa reaction chain in the convective core of main-sequence stars.
 Sodium is transported to the surface of these supergiants via mixing of CNO cycle products during the first dredge-up, although, it is important to note sodium enhancement is not constrained to supergiant stars.
-Stars with a  minimum 1.5$M_\odot$ can exhibit sodium abundance similarily through the NeNa cycle \citep{denissenkov1987}.
-\citet{antipova2004} discovered a sodium enhancement in 16 of their Barium star candidates, they relate this to the dredge-up of nuclear-burning material produced by convection during the red-giant phase.
-Moreover, they suggest [Na/Fe] ratios exhibit systematically higher values for giants with lower log g values, but do not exhibit variations in metallicity.
-Similarily, \citet{decastro2016} highlights the possible weak, anti-correlation between [Na/Fe] ratio and log g, and illustrates this trend in previous studies\citep[e.g.][]{boyarchuk2002,mishenina2006,luck2007,takeda2008}.
+Stars with a  minimum mass of $1.5\,M_\odot$ can also exhibit enhanced sodium abundances through the NeNa cycle \citep{denissenkov1987}.
+\citet{antipova2004} reported sodium enhancements in 16\todo{/??} of their Barium star candidates, and they relate this to the dredge-up of nuclear-burning material produced by convection during the red-giant phase.
+Moreover, they suggest [Na/Fe] ratios exhibit systematically higher values for giants with lower $\log{g}$ values, but do not exhibit variations in metallicity.
+Similarly, \citet{decastro2016} highlights the possible weak anti-correlation between [Na/Fe] ratio and $\log{g}$, and highlights that this trend in previous studies \citep[e.g.][]{boyarchuk2002,mishenina2006,luck2007,takeda2008}.
 
-It's important to highlight our research only discovered $<2$\,\% sodium presence in our 257 Barium candidates, contrary to previous studies \citep[e.g.][]{decastro2016}.
-This suggests systematic differences in the analyse undertaken by said previous studies.
-Also, synonymous to our s-process candidates, synthesized sodium is brought to the surface of giants via the first dredge-up, therefore, these candidates may display sodium enhancement without mass transfer from a TP-AGB star.
-And, in juxtaposition to the literature, our 5 sodium enhanced stars exhibit a surface gravity range between 2.98 and 3, showing no correlation between higher [Na/Fe] values and lower log g values.
-These considerations suggest sodium-rich material from the TP-AGB star polluted our 5 Barium candidates, but also, sodium enhancement is not unbiquitous in Barium Stars.
+We find only $<2$\,\% of our Barium stars show sodium enhancement, contrary to previous studies \citep[e.g.][]{decastro2016}.
+We also note that the 5 sodium-enhanced Barium stars all have $\log{g} \approx 3$, not at lower $\log{g}$ values as might be expected if low $\log{g}$ values systematically contributed to higher [Na/Fe] abundance ratios.
+These results suggest that sodium-rich material from a companion TP-AGB star has polluted these 5 Barium candidates, but importantly, sodium enhancement is by no means ubiquitous in Barium stars.
+The comparisons made in \citep{decastro2016} made use of multiple literature comparisons, and therefore it is possible that there are systematic differences (biases) between Milky Way studies of normal FGK-type stars and those focussed on Barium stars, leading to unresolved differences in the reported [Na/Fe] abundance ratio.
+These same systematic effects could contribute to the observed correlation between [Na/Fe] and $\log{g}$, which we do not observe in our sample.
+
+% Could be removed:
+%Also, synonymous to our s-process candidates, synthesised sodium is brought to the surface of giants via the first dredge-up, therefore, these candidates may display sodium enhancement without mass transfer from a TP-AGB star.
+
+%Furthermore, this suggests other enhancements including our 5 sodium and 178 carbon enhanced Barium stars exist through TP-AGB companion pollution.
 
@@
 Similar to the s-process enhancement, this suggests our candidates are either intrinsic or extrinsic Barium stars.
-
-\subsection{Extrinsic and intrinsic Barium stars}
-Barium stars exist as either intrinsic or extrinsic objects.
-Intrinsic Barium stars must be massive enough to reach the TP-AGB phase, and extrinsic Barium stars must be in a binary with a previosuly polluting TP-AGB star companion.
-Figure \ref{fig:figure2} demonstrates the majority of our Barium star sample has a surface gravity greater then 2, highlighting that our sample is primarily not massive enough to have reach the TP-AGB phase and therefore, must be extrinsic Barium stars.
-Furthermore, this suggests other enhancements including our 5 sodium and 178 carbon enhanced Barium stars exist through TP-AGB companion pollution.
 

### 2018-01-25 article/ms.tex
minor things on concl

@@
 All of our Barium stars are consistent with membership in the Milky Way disk, and we find an \todo{steady/increasing/decreasing} fraction of Barium stars with stellar metallicity, as \todo{expected} from AGB yields and stellar evolution theory.
-We find up to 51 Barium stars exhibit some evidence of technetium from LAMOST spectra, and most (46/51) have $\log{g} > 2$, which suggests they cannot be AGB stars and may indicate a recent ($100\,\textrm{Myr}$) mass accretion event.
+We find up to 51 Barium stars exhibit some evidence of technetium from LAMOST spectra, and most (46/51) have $\log{g} > 2$, which suggests they cannot be AGB stars and may indicate a recent ($<1\,\textrm{Myr}$) mass accretion event.
 Most (178/257) Barium stars in our sample show strong carbon enhancement, consistent with the literature.
@@
 \subsection{Technetium enhancement}
-Technetium has a half life of approximately 211,000 years and as a result cannot be present in an extrinsic Barium star.
+\todo{Technetium has a half life of approximately 211,000 years and as a result cannot be present in an extrinsic Barium star.
 Enhancemnt in Tc would indicate the presence of AGB stars \citep{jorissen1993}, and suggest some of our candidates are intrinsic Barium stars.
@@
 In agreement with previous findings \citep[e.g.][]{little1987,smith1984,smith1983}, the results indicate that none of the evolved Barium stars in our sample exhibited the presence of Tc enhancement, and it can be concluded our Barium star sample is extrinsic.
-It is noted, Tc enhancement is a very difficult line to analyse and that this conclusion is not concrete.
+It is noted, Tc enhancement is a very difficult line to analyse and that this conclusion is not concrete.}
 
@@
 \begin{figure}
-	% To include a figure from a file named example.*
-	% Allowable file formats are eps or ps if compiling using latex
-	% or pdf, png, jpg if compiling using pdflatex
 	\includegraphics[width=\columnwidth]{HRdummy.png}
@@
 Our research discovered 967 s-process candidates including; 257 Barium stars, 49 stars exhibiting exclusively barium enhancement, and 661 exhibiting exclusively strontium enhancement from 454,180 giant stars observed by LAMOST.
-This is the largest sample of s-process enhanced stars to date.
-Nearly all of our Barium candidates are disk stars, 178 exhibit CH and G band enhancement, no plausible technetium enhancement is discovered, and it is shown sodium ehancement is not ubiquitous in s-process stars as previously claimed.
-We highlight that the majority of our Barium stars have a surface gravity greater then 2, this suggests that these are extrinsic Barium stars.
-
+This is the largest sample of s-process enhanced stars to date \todo{by a factor of how many?
+what's the next largest size sample?}.
+Nearly all of our Barium candidates are disk stars, 178 exhibit CH and G band enhancement, no plausible technetium enhancement is discovered, and it is shown sodium enhancement is not ubiquitous in s-process stars as previously claimed.
+\todo{AGB yields comparison.
+Something about binary eccentricities.}
 \section*{Acknowledgements}

### 2018-01-25 article/ms.tex
foo
merge

--- 2018-01-25 article/ms.tex
@@
 
+% Please keep new commands to a minimum, and use \newcommand not \def to avoid
+% overwriting existing commands. Example:
+%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \title[S-process stars in LAMOST]{Discovery of s-process stars in the LAMOST survey}
 
-\author[B.~J. Norfolk et al.]{B.~J. Norfolk,$^{1}$\thanks{E-mail: bjee7@student.monash.edu (MU)}
-A.~R. Casey,$^{1,2}$
-M.~T. Miles,$^{1}$
-A.~J. Kemp,$^{1}$ 
-A.~I. Karakas,$^{1}$ \newauthor
-J.~C. Lattanzio,$^{1}$
-and K.~C. Schlaufman$^{3}$
+% The list of authors, and the short list which is used in the headers.
+% If you need two or more lines of authors, add an extra line using \newauthor
+\author[B.J. Norfolk et al.]{B.J. Norfolk,$^{1}$\thanks{E-mail: bjee7@student.monash.edu (MU)}
+A.R. Casey,$^{1,2}$
+M.T. Miles,$^{1}$
+A.J. Kemp,$^{1}$ 
+A.I. Karakas,$^{1}$ \newauthor
+J.C. Lattanzio,$^{1}$
+and K.C. Schlaufman 
 \\
@@
 $^{2}$Faculty of Information Technology, Monash University, Clayton 3800, Victoria, Australia\\
-$^{3}$Department of Physics and Astronomy, Johns Hopkins University, 3400 N Charles St., Baltimore, MD 21218, USA
 }
@@
 \begin{abstract}
-Stars with peculiar enhancements of carbon and heavy elements ($Z > 30$) are historically referred to as `Barium stars'.
-While this chemical abundance pattern can be explained by thermally pulsing asymptotic giant branch (AGB) stars, many so-called Barium stars have not evolved through the red giant phase and therefore cannot be AGB stars.
-These less-evolved stars are generally thought to have accreted mass from a more-evolved AGB companion.
-For this reason the frequency and properties of less-evolved Barium stars are uniquely informative on the binary fraction, AGB yields, mass transfer, and stellar evolution.
-Here we present the discovery of 967 s-process candidates from 454,180 giant stars observed by LAMOST.
-Our sample includes; 257 Barium stars, 49 stars exhibiting only significant barium enhancement, and 661 exhibiting only strontium enhancement.
-This sample constitutes the largest number of s-process enhanced stars ever discovered, and represents the most comprehensive search for Barium stars in the Milky Way.
-All of our Barium stars are consistent with membership in the Milky Way disk, and we find an \todo{steady/increasing/decreasing} fraction of Barium stars with stellar metallicity, as \todo{expected} from AGB yields and stellar evolution theory.
-We find up to 51 Barium stars exhibit some evidence of technetium from LAMOST spectra, and most (46/51) have $\log{g} > 2$, which suggests they cannot be AGB stars and may indicate a recent ($100\,\textrm{Myr}$) mass accretion event.
-Most (178/257) Barium stars in our sample show strong carbon enhancement, consistent with the literature.
-However, despite previous claims indicating that Barium stars are preferentially enhanced in sodium due to the NeNa nucleosynthesis cycle occurring in massive AGB stars, only 5 ($<2$\,\%) of our Barium stars show any evidence of enhancement in sodium.
-\todo{A sentence about AGB yield comparison.} When binary properties become available from end-of-mission Gaia astrometry, this sample of s-process stars will be critical in explaining mass transfer in binary systems and refining AGB yields across a range of masses and metallicities.
+Stars with peculiar enhancements of carbon and heavy elements ($Z > 30$) are historically referred to as Barium stars.
+While this chemical abundance pattern can be explained by thermally pulsing asymptotic giant branch (AGB) stars, many Barium stars have not evolved through the red giant phase and therefore cannot be AGB stars.
+These stars are generally thought to have accreted mass from a more evolved AGB companion.
+For this reason the frequency and properties of less-evolved Barium stars is uniquely informative on the binary fraction, AGB yields, mass transfer, and stellar evolution.
+Here we present the discovery of 967 s-process candidates including; 257 Barium stars, 49 stars exhibiting exclusively barium enhancement, and 661 exhibiting exclusively strontium enhancement from 454,180 giant stars observed by LAMOST.
+This sample constitutes the largest sample of s-process enhanced stars discovered to date, and the most comprehensive search for Barium stars in the Milky Way.
+\todo{Nearly all} of our Barium stars are disk stars, and we find an \todo{steady/increasing/decreasing} fraction of Barium stars with stellar metallicity, as \todo{expected} from AGB yields and stellar evolution theory.
+51 Barium stars exhibited tecnetium enhancement in a single Tc emission line suggesting the exsistence of AGB stars in our sample.
+Most (178/257) of our sample show strong carbon enhancement consistent with the literature.
+Despite previous claims indicating that Barium stars are preferentially enhanced in sodium due to the NeNa nucleosynthesis cycle occurring in \todo{massive} AGB stars, only 5 ($<2$\,\%) of our Barium stars show any evidence of enhancement in sodium.
+\todo{This implies ....}
 \end{abstract}
@@
 
-Barium stars as first recognised by \citet{Bidelman1951}, are chemically unique objects that exhibit envelopes with an overabundance of carbon and heavy elements (Z > 30) in comparison to the Sun.
+Barium stars as first recognized by \citet{Bidelman1951}, are chemically unique objects that exhibit envelopes with an overabundance of carbon and heavy elements (Z > 30) in comparison to the Sun.
 Barium stars exist as either intrinsic or extrinsic objects; intrinsic Barium stars are in the TP-AGB (thermally pulsing-asymptotic giant branch) phase, where the overabundance of both carbon and heavy elements are produced through the s-process and exist on the surface as the result of a thermal pulsing cycle.
 According to the mass-transfer hypothesis, extrinsic Barium stars are a consequence of stellar wind accretion \citep{boffin1988,jorissen1992} or Roche-lobe overflow \citep{webbink1986}, and are within a binary system containing a previous TP-AGB companion star (intrinsic Barium star) in its final phase as a white dwarf \citep{bohm1980,bohm1984}.
-In fact, \citet{mcclure1983} determines 85\% of all Barium stars are in binary systems and claims that those that appear singular are actually pole-on, or highly eccentric binaries with significant radial velocity variations only occurring in a small phase range as detailed by \citet{pourbaix2004}.
+In fact, \citet{mcclure1983} determines 85\% of all Barium stars are in binary systems and claims that those that appear singular are actually pole-on, or highly eccentric binaries with significant radial velocity variations only occuring in a small phase range as detailed by \citet{pourbaix2004}.
 For these reasons, the properties and occurrence rate of Barium stars are informative of the theoretical birth rate of AGB stars, the binary star fraction as a function of metallicity, the mass ratio of binary stars, as well as AGB yields across different masses and metallicities.
 
-The slow neutron capture process (s-process), occurring in the interior of AGB stars, synthesises roughly half of all elements heavier than iron \citep[e.g.][]{busso1999,travaglio2001,herwig2005,romano2010,kobayashi2011,prantzos2012,bisterzo2014,karakas12016}.
+The slow neutron capture process (s-process), occuring in the interior of AGB stars, synthesizes roughly half of all elements heavier than iron \citep[e.g.][]{busso1999,travaglio2001,herwig2005,romano2010,kobayashi2011,prantzos2012,bisterzo2014,karakas12016}.
 Late in the AGB phase, during the thermally pulsing-AGB (TP-AGB) phase, thermal instabilities occur in the He shell every $10^5$ years or so, depending on the H-exhausted core mass.
@@
 The energy from the thermal pulses force the star to expand, pushing the H-shell out to cooler regions and allowing the convective envelope to move inwards to regions previously mixed by the thermal pulse driven convective zones.
-This expansion and resulting inward movement is described as the third dredge up (TDU), and is theorised to occur after each thermal pulse.
-During the TP-AGB phase, enrichment on the surface in $^{12}$C and heavy elements produced by the s-process is a result of the repeated downwash extensions of TDU \citep[e.g.][]{busso2001}.
+This expansion and resultsing inward movement is classified as the third dredge up (TDU), and is theorised to occur after each thermal pulse.
+During the TP-AGB phase, enrichent on the surface in $^{12}$C and heavy elements produced by the s-process is a result of the repeated downwash extensions of TDU \citep[e.g.][]{busso2001}.
 The star contracts PDU and reignites the H-shell producing the majority of the surface luminosity for the next interpulse period.
-The interpulse, thermal pulse, and dredge up cycle may occur numerous times and is dependent on the initial mass, composition, and mass-loss rate of the star.
+The interpulse, thermal pulse, and dredge up cycle may occur numerous times and is dependent on the intitial mass, composition, and mass-loss rate of the star.
 
-Barium giants form within a metallicity-dependent initial mass range (approximately $0.8 - 8\,M_{\odot}$), with the minimum mass for core helium and carbon burning decreasing as metallicity decreases.
+Barium giants form within a metallicity-dependent initial mass range (approximately 0.8 - 8$M_{\odot}$), with the minimum mass for core helium and carbon burning decreasing as metallicity decreases.
 The age of these stars vary considerably, with observable stars in metal-poor globular clusters hosting populations of $\approx$12Gyr.
@@
 
-In this paper we analyse 454,180 giant stars from the second LAMOST data release (DR) to identify and examine 967 s-process candidates including Barium stars, and exclusively enhanced barium and strontium stars, respectively.
-In Section \ref{sec:methods} we describe the observations and candidate selection, as well as the analysis of high-resolution follow-up observations obtained for a few candidates.
+In this paper we analyse 454,180 giant stars from LAMOST data release (DR) 2 to identify and examine 967 s-process candidates including Barium stars, and exclusvely enhanced barium and strontium stars, respectively.
+Specifcally, the Barium star giants studied here display especially strong s-process enhancement for \ion{Ba}{II} and \ion{Sr}{II} at lines 4554\AA \hspace{0.2mm} and 4077\AA, respectively.
+Our exclusive barium and strontium candidates show s-process enhancement in 4554\AA \hspace{0.2mm} and 4934\AA for barium enhancement, and, 4554\AA \hspace{0.2mm} and 4215\AA for strontium enhancement.
+In Section \ref{sec:methods} we describe the observations and candidate selection, as well as the analysis follow up our follow-up observing campaign with Magellan.
 In Section \ref{sec:dis} we discuss the properties of our Barium stars in context of existing literature.
@@
 The Barium stars analysed in this research were obtained by filtering for significant flux residuals, taken as, a disparity between the normalised LAMOST flux and the data driven model derived by \citet{ho2017}.
-Specifically, we identified Barium stars by searching for \ion{Ba}{II} and \ion{Sr}{II} enhancement at the 4554\,\AA\ and 4077\,\AA, respectively.
-A negative residual, as shown in a candidate Barium star in Figure \ref{fig:figure1}, illustrates an enhancement in \ion{Ba}{II} and \ion{Sr}{II} at lines 4554\,\AA\, 4077\,\AA.
+A negative residual as shown in the randomly selected Figure \ref{fig:figure1}, illustrates an enhancement in \ion{Ba}{II} and \ion{Sr}{II} at lines 4554\AA \hspace{0.2mm}, 4077\AA.
 These \ion{Ba}{II} and \ion{Sr}{II} resonance lines are very strong, allowing us to identify stars enhanced in neutron-capture elements given a well-fit model for the data.
-Stars identified to just show high levels of barium required enhancement at both the 4554\,\AA\ and 4934\,\AA\ resonance lines, and for stars just enhanced in strontium we looked for significant residuals at the 4554\,\AA\ and 4215\,\AA\ absorption lines.
-
-We used five filters that each spectrum, for each set of absorption lines, had to meet in order to be considered a s-process candidate; these included:
+We used five filters that each spectrum, for both enhancement lines, had to meet in order to be considered a s-process candidate; these included:
 
@@
 \begin{enumerate} 
-\item Profile amplitude for both enhancement lines must be $A < -0.05$.
-\item Both amplitudes must be measured within 3$\sigma$ ($|A|/\sigma _A$ < 3).
-\item The wavelength at each absorption line must be within 2\,\AA\ ($\lambda$ < 2).
-\item The reduced $\chi^2$ from \emph{The Cannon} must be $\chi_r^2 < 3$.
-\item And finally, the LAMOST spectra must have a signal-to-noise ratio of $S/N > 30\,\textrm{pixel}^{-1}$.
+\item Profile amplitude for both enhancement lines must exceed A < -0.05.
+\item Both amplittudes must be measured within 3$\sigma$ ($|A|/\sigma _A$ < 3).
+\item The wavelength at each absorption line must be within $2$\AA \hspace{0.2mm}($\lambda$ < 2).
+\item Reduced $\chi^2$ from The Cannon must be < 3.
+\item And, the LAMOST spectra must have a signal-to-noise ratio of S/N > 30 per pixel.
 \end{enumerate}
@@
 
-\subsubsection{Enhancements due to sodium, technetium, and carbon}
-We performed an identical analysis to the process described in Section \ref{sec:cand} in order to identify sodium, technetium, or carbon enhancement in our sample of 257 Barium stars.
-We used the sodium doublet lines at 5889\,\AA\ and 5895\,\AA\ to select Barium stars enhanced in sodium, and required significant absorption in both features.
-Only 5/257 Barium stars met this criteria,  \todo{however something about the dust for those stars}.
-For technetium enhancement we searched for significant residual deviations at the 4049\,\AA, 4238\,\AA, 4262\,\AA, 4297\,\AA, and 5924\,\AA.
-These absorption lines are extremely weak, and would require a substantial amount of technetium before it would be visible in a high S/N LAMOST spectrum.
-We found 51 Barium stars exhibited some level of significant enhancement (based on the filters above) at a single technetium line, yet none showed enhancement at more than one technetium line.
-We note that the single enhancement near technetium for these 51 stars may be the consequence of data reduction/calibration artefacts, but we include details of which stars matched on technetium in Table \ref{tab:table} nonetheless.
-Finally, for carbon enhancement we searched for significant deviations at the CH and G band near 4300\,\AA.
-We found 178/257 stars to show significant carbon enhancement (e.g., $[\textrm{C/M}] \gtrsim 0.5$).
+\subsubsection{Further enhancements}
+We undertook an identical analysis to the process described in Section \ref{sec:cand} for sodium, technetium, and carbon enhancement.
+We filtered for negative residuals in the enhanced sodium doublet lines 5889.950\AA\hspace{0.2mm} and 5895.924\AA.
+Our analysis produced 5 matches with our Barium star candidates.
+51 canditdates were discovered to be enhanced in a single technetium line.
+And, for the CH and G band region at approximately 4300\AA\hspace{0.2mm} we matched 178 enhanced stars out of our total 257 stars.
 
@@
 	\includegraphics[width=\columnwidth]{HRdummy.png}
-    \caption{HR Diagram}
+    \caption{effective temperature $T_\rm{eff}$ and surface gravity $\log{g}$ for 257 candidate Barium stars from LAMOST.
+Stars with $\log{g} > 2$ (as marked) have not evolved through the thermally pulsing asymptotic giant branch phase, and therefore their abundance signature must be the result of an extrinsic pollution event.
+The classification of stars with $\log{g} < 2$ would require additional data}
     \label{fig:figure2}

### 2018-01-25 article/ms.tex
draft complete

--- 2018-01-25 article/ms.tex
@@
 However, despite previous claims indicating that Barium stars are preferentially enhanced in sodium due to the NeNa nucleosynthesis cycle occurring in massive AGB stars, only 5 ($<2$\,\%) of our Barium stars show any evidence of enhancement in sodium.
-\todo{A sentence about AGB yield comparison.} When binary properties become available from end-of-mission Gaia astrometry, this sample of s-process stars will be critical in explaining mass transfer in binary systems and refining AGB yields across a range of masses and metallicities.
+An AGB yield comparison demonstrates that the majority of our sample agree with the Salpeter IMF, and highlights a small percentage of intrinsic Barium stars present in our sample.
+When binary properties become available from end-of-mission Gaia astrometry, this sample of s-process stars will be critical in explaining mass transfer in binary systems and refining AGB yields across a range of masses and metallicities.
 \end{abstract}
@@
 From here on when we refer to extrinsic Barium stars, we specifically refer to those with $\log{g} > 2$.
+It is noted, in the previous literature \citet{van2017}, only 22\% of their stellar sample are post-main-sequence barium stars (extrinsic barium stars).
+In comparison, we find our Barium candidates constitute greater than 70\% extrinsic, this suggests the construction of our data-driven model may have missed some AGB Barium candidates.
 
@@
 Stars with a  minimum mass of $1.5\,M_\odot$ can also exhibit enhanced sodium abundances through the NeNa cycle \citep{denissenkov1987}.
-\citet{antipova2004} reported sodium enhancements in 16\todo{/??} of their Barium star candidates, and they relate this to the dredge-up of nuclear-burning material produced by convection during the red-giant phase.
+\citet{antipova2004} reported sodium enhancements in 3 of their 16 Barium star candidates, and they relate this to the dredge-up of nuclear-burning material produced by convection during the red-giant phase.
 Moreover, they suggest [Na/Fe] ratios exhibit systematically higher values for giants with lower $\log{g}$ values, but do not exhibit variations in metallicity.
@@
 These results suggest that sodium-rich material from a companion TP-AGB star has polluted these 5 Barium candidates, but importantly, sodium enhancement is by no means ubiquitous in Barium stars.
+It's important to note, sodium enhancement can occur due to the presence of interstellar dust, and using the IRSA's all-sky dust map \citep{schlafly2011}, E(B-V) values were calculated for our 5 candidates.
+The results show 2 sodium enhanced stars have strong ($\approx$0.35) E(B-V) values, higher then galactic stellar levels, suggesting these candidates are false positives.
+Whereas, 3 exhibit low ($\approx$0.045) E(B-V) values, validating our sodium enhancement results for these candidates.
 The comparisons made in \citep{decastro2016} made use of multiple literature comparisons, and therefore it is possible that there are systematic differences (biases) between Milky Way studies of normal FGK-type stars and those focussed on Barium stars, leading to unresolved differences in the reported [Na/Fe] abundance ratio.
@@
 
-% Could be removed:
-%Also, synonymous to our s-process candidates, synthesised sodium is brought to the surface of giants via the first dredge-up, therefore, these candidates may display sodium enhancement without mass transfer from a TP-AGB star.
+\subsection{Technetium enhancement}
 
-%Furthermore, this suggests other enhancements including our 5 sodium and 178 carbon enhanced Barium stars exist through TP-AGB companion pollution.
-
-\subsection{Technetium enhancement}
-\todo{Technetium has a half life of approximately 211,000 years and as a result cannot be present in an extrinsic Barium star.
-Enhancemnt in Tc would indicate the presence of AGB stars \citep{jorissen1993}, and suggest some of our candidates are intrinsic Barium stars.
+Technetium has a half life of approximately 211,000 years and as a result, Tc enhacnement is constrained to observations intrinsic Barium stars \citep{jorissen1993} or recently polluted extrinsic Barium stars.
 Our analyse discovered 51 single Tc line matches within our 257 Barium star candidate sample.
-However, for Tc to be present in  a star the enhancement lines must be considerably strong, and given that all 51 matches were at single lines it is concluded that these results are data artifacts.
+The majority (46/51) have $\log{g} > 2$, suggesting they cannot be AGB stars, and may indicate a recent ($<1\,\textrm{Myr}$) mass accretion event.
+However, for Tc to be present in  a star the enhancement lines must be considerably strong, and given that all 51 matches were at single lines it is concluded that these results are more likely data artifacts.
 In agreement with previous findings \citep[e.g.][]{little1987,smith1984,smith1983}, the results indicate that none of the evolved Barium stars in our sample exhibited the presence of Tc enhancement, and it can be concluded our Barium star sample is extrinsic.
-It is noted, Tc enhancement is a very difficult line to analyse and that this conclusion is not concrete.}
+It is noted, Tc enhancement is a very difficult line to analyse and that this conclusion is not concrete.
 
@@
 	\includegraphics[width=\columnwidth]{HRdummy.png}
-    \caption{HR Diagram}
+    \caption{Effective temperature $T_{eff}$ and surface gravity $\log{g}$ for 257 candidate Barium stars from LAMOST.
+Stars with $\log{g} > 2$ (as marked) have not evolved through the thermally pulsing asymptotic giant branch phase, and therefore their abundance signature must be the result of an extrinsic pollution event.
+The classification of stars with $\log{g} < 2$ would require additional data}
     \label{fig:figure2}
@@
 \subsection{AGB yields comparison}
+AGB stars, and chemically unique stars that show the chemical signature
+of mass transfer pollution from binary companion AGB stars, highlight the variation of s-process enhancement.
+\citet{karakas_lugaro2016} demonstrates through stellar yield models, that Barium stars will have a likely minimum yeild at [Fe/H]$\approx$ -1.2.
+Figure \ref{fig:figure3} confirms this as the majority of the Barium stars are contained above -1.2.
+The final surface s-process index [hs/ls], shown in \citet{cristallo2015}, highlights the relationship between [hs/ls] yields and the mass of AGB stars.
+The Salpeter IMF predicts the majority of stars in the Milky Way will be at lower mass, and as predicted the [hs/ls] values of our Barium stars approximately fit the lower mass yields shown in \citet{cristallo2015}.
+Barium stars not fitting this relationship represent the possibly more massive AGB stars (intrinsic Barium stars) within our sample.
+
+\begin{figure}
+	\includegraphics[width=\columnwidth]{basrtest4.png}
+    \caption{Final surface s-process indexes: [hs/ls]}
+    \label{fig:figure3}
+\end{figure}
 
@@
 Our research discovered 967 s-process candidates including; 257 Barium stars, 49 stars exhibiting exclusively barium enhancement, and 661 exhibiting exclusively strontium enhancement from 454,180 giant stars observed by LAMOST.
-This is the largest sample of s-process enhanced stars to date \todo{by a factor of how many?
-what's the next largest size sample?}.
+This is double the currently known stellar sample of Barium stars, and the largest sample of s-process enhanced stars known to date.
 Nearly all of our Barium candidates are disk stars, 178 exhibit CH and G band enhancement, no plausible technetium enhancement is discovered, and it is shown sodium enhancement is not ubiquitous in s-process stars as previously claimed.
-\todo{AGB yields comparison.
-Something about binary eccentricities.}
+AGB yields comparisons indicate the majority of our sample fit low steallar mass trends in agreement with Salpeter IMF theory.
+Additonally, a number of outliers highlight a small percentage of intrinsic Barium stars in our sample.
+todo{ Something about binary eccentricities.}
 \section*{Acknowledgements}
 
-Fired Status: yes
+Fired Status: maybe
 
@@
 ApJ, 557, 802
+\bibitem[\protect\citeauthoryear{Casey}{2014}]{casey2014}
+Casey, A.~R. 2014, 
+PhD Thesis, Australian National University
+\bibitem[\protect\citeauthoryear{Cristallo et al.}{2015}]{cristallo2015}
+Cristallo, S., Straniero, O., Piersanti, L.,\& Gobrecht, D. 2015, 
+ApJ, 219, 40
 \bibitem[\protect\citeauthoryear{deCastro et al.}{2016}]{decastro2016}
@@
 SAIt, 87, 229
+\bibitem[\protect\citeauthoryear{Karakas \& Lugaro}{2016}]{karakas_lugaro2016}
+Karakas, A.~I.,\& Lugaro M. 2016, 
+ApJS, 825, 26
 \bibitem[\protect\citeauthoryear{Kelson et al.}{2000}]{kelson2000}
@@
 A$\&$A, 522, A32
+\bibitem[\protect\citeauthoryear{Schlafly \& Finkbeiner}{2011}]{schlafly2011}
+Schlafly, E.~F.,\& Finkbeiner, D.~P. 2011, 
+Apj, 737, 103
 \bibitem[\protect\citeauthoryear{Smith \& Wallerstein}{1983}]{smith1983}
@@
 MNRAS, 428, 2216
-
-\bibitem[\protect\citeauthoryear{Casey}{2014}]{casey2014}
-Casey, A.~R. 2014, 
-PhDT, 394
-\todo{format Andy's ref properly}
-%@PHDTHESIS{2014PhDT.......394C,
-%   author = {{Casey}, A.~R.},
-%    title = "{A Tale of Tidal Tales in the Milky Way}",
-% keywords = {Astronomy, Astrophysics, Stellar streams},
-%   school = {Australian National University},
-%     year = 2014,
-%    month = May,
-%      doi = {10.5281/zenodo.49493},
-%   adsurl = {http://adsabs.harvard.edu/abs/2014PhDT.......394C},
-%  adsnote = {Provided by the SAO/NASA Astrophysics Data System}
-%}
+\bibitem[\protect\citeauthoryear{Van der Swaelmen et al.}{2017}]{van2017}
+Van der Swaelmen, M., Boffin, H.~M.~J., Jorissen, A.,\& Van Eck, S. 2017, 
+A$\&$A, 597, A68
 

### 2018-01-26 article/ms.tex
final draft

@@
 It is important to note, this sample is exclusive to giant stars presenting the possibility that this research missed dwarf s-process enhanced stars.
-Cross-validation experience shows that the typical uncertainties are 70K in effective temperature $T_{eff}$, 0.1 dex in surface gravity log g, 0.1 dex in metallicity [Fe/H], and 0.04 dex in the alpha abundance relative to iron [$\alpha$/M].
+Cross-validation experience shows that the typical uncertainties are 70K in effective temperature $\rm T_{\rm eff}$, 0.1 dex in surface gravity log g, 0.1 dex in metallicity [Fe/H], and 0.04 dex in the alpha abundance relative to iron [$\alpha$/M].
 These uncertainties are approximately comparable to the conservative APOGEE DR12 uncertainties.
@@
 \toprule
-2MASSID             & RA (hms         & DEC (hms)        & Vr (km/s) & S/N & Teff (K) & Log g & {[}Fe/H{]} & {[}$\alpha$/H{]} & $\chi^2$  \\ \midrule
+2MASSID             & RA (hms         & DEC (hms)        & Vr (km/s) & S/N & $\rm T_{\rm eff}$ (K) & Log g & {[}Fe/H{]} & {[}$\alpha$/H{]} & $\chi^2$  \\ \midrule
 J000134.95+490743.2 & 00:01:34.96 & +49:07:43.2 & -42.27    & 72  & 5044 & 3.11  & -0.54      & 0.11      & 0.79 \\ \midrule
@@
 We used the sodium doublet lines at 5889\,\AA\ and 5895\,\AA\ to select Barium stars enhanced in sodium, and required significant absorption in both features.
-Only 5/257 Barium stars met this criteria,  \todo{however something about the dust for those stars}.
+Only 5/257 Barium stars met this criteria, and it's important to note sodium enhancement can occur due to the presence of interstellar dust.
+Using the IRSA's all-sky dust map \citep{schlafly2011}, E(B-V) values were calculated for our 5 candidates.
+The results show 2 sodium enhanced stars have strong ($\approx$0.35) E(B-V) values, higher then galactic stellar levels, suggesting these candidates are false positives.
+Whereas, 3 exhibit low ($\approx$0.045) E(B-V) values, confirming sodium enhancement results for these candidates.
 For technetium enhancement we searched for significant residual deviations at the 4049\,\AA, 4238\,\AA, 4262\,\AA, 4297\,\AA, and 5924\,\AA.
@@
 The results show 2 sodium enhanced stars have strong ($\approx$0.35) E(B-V) values, higher then galactic stellar levels, suggesting these candidates are false positives.
-Whereas, 3 exhibit low ($\approx$0.045) E(B-V) values, validating our sodium enhancement results for these candidates.
+Whereas, 3 exhibit low ($\approx$0.045) E(B-V) values, confirming sodium enhancement results for these candidates.
 The comparisons made in \citep{decastro2016} made use of multiple literature comparisons, and therefore it is possible that there are systematic differences (biases) between Milky Way studies of normal FGK-type stars and those focussed on Barium stars, leading to unresolved differences in the reported [Na/Fe] abundance ratio.

### 2018-02-05 article/ms.tex
some text changes

@@
 J.~C. Lattanzio,$^{1}$
-and K.~C. Schlaufman$^{3}$
+K.~C. Schlaufman,$^{3}$
+and A.~Y.~Q. Ho$^{4}$
 \\
@@
 $^{2}$Faculty of Information Technology, Monash University, Clayton 3800, Victoria, Australia\\
-$^{3}$Department of Physics and Astronomy, Johns Hopkins University, 3400 N Charles St., Baltimore, MD 21218, USA
+$^{3}$Department of Physics and Astronomy, Johns Hopkins University, 3400 N Charles St., Baltimore, MD 21218, USA\\
+$^{4}$Cahill Center for Astrophysics, California Institute of Technology, MC 249-17, 1200 E California Blvd, Pasadena, Ca, 91125, USA
 }
@@
 Here we present the discovery of 967 s-process candidates from 454,180 giant stars observed by LAMOST.
-Our sample includes; 257 Barium stars, 49 stars exhibiting only significant barium enhancement, and 661 exhibiting only strontium enhancement.
+Our sample includes; 257 `Barium stars' that show enhancement in both barium and strontium, 49 stars showing only significant barium enhancement, and 661 exhibiting only strontium enhancement.
 This sample constitutes the largest number of s-process enhanced stars ever discovered, and represents the most comprehensive search for Barium stars in the Milky Way.
 All of our Barium stars are consistent with membership in the Milky Way disk, and we find an \todo{steady/increasing/decreasing} fraction of Barium stars with stellar metallicity, as \todo{expected} from AGB yields and stellar evolution theory.
-We find up to 51 Barium stars exhibit some evidence of technetium from LAMOST spectra, and most (46/51) have $\log{g} > 2$, which suggests they cannot be AGB stars and may indicate a recent ($<1\,\textrm{Myr}$) mass accretion event.
+We find up to 51 Barium stars exhibit some evidence of technetium from LAMOST spectra, and most (46/51) have $\log{g}>2$, which suggests they cannot be AGB stars and may indicate a recent ($<1\,\textrm{Myr}$) mass accretion event.
 Most (178/257) Barium stars in our sample show strong carbon enhancement, consistent with the literature.
 However, despite previous claims indicating that Barium stars are preferentially enhanced in sodium due to the NeNa nucleosynthesis cycle occurring in massive AGB stars, only 5 ($<2$\,\%) of our Barium stars show any evidence of enhancement in sodium.
-An AGB yield comparison demonstrates that the majority of our sample agree with the Salpeter IMF, and highlights a small percentage of intrinsic Barium stars present in our sample.
+A comparison with AGB yields suggests that the majority of our sample are consistent with a bottom-heavy IMF.
+% and highlights a small percentage of intrinsic Barium stars present in our sample. 
 When binary properties become available from end-of-mission Gaia astrometry, this sample of s-process stars will be critical in explaining mass transfer in binary systems and refining AGB yields across a range of masses and metallicities.
@@
 
-The slow neutron capture process (s-process), occurring in the interior of AGB stars, synthesises roughly half of all elements heavier than iron \citep[e.g.][]{busso1999,travaglio2001,herwig2005,romano2010,kobayashi2011,prantzos2012,bisterzo2014,karakas12016}.
+The slow neutron capture process (s-process), occurring in the interior of AGB stars, synthesises roughly half of all elements heavier than iron \citep[e.g.,][]{busso1999,travaglio2001,herwig2005,romano2010,kobayashi2011,prantzos2012,bisterzo2014,karakas12016}.
 Late in the AGB phase, during the thermally pulsing-AGB (TP-AGB) phase, thermal instabilities occur in the He shell every $10^5$ years or so, depending on the H-exhausted core mass.
@@
 This expansion and resulting inward movement is described as the third dredge up (TDU), and is theorised to occur after each thermal pulse.
-During the TP-AGB phase, enrichment on the surface in $^{12}$C and heavy elements produced by the s-process is a result of the repeated downwash extensions of TDU \citep[e.g.][]{busso2001}.
+During the TP-AGB phase, enrichment on the surface in $^{12}$C and heavy elements produced by the s-process is a result of the repeated downwash extensions of TDU \citep[e.g.,][]{busso2001}.
 The star contracts PDU and reignites the H-shell producing the majority of the surface luminosity for the next interpulse period.
@@
 Barium giants form within a metallicity-dependent initial mass range (approximately $0.8 - 8\,M_{\odot}$), with the minimum mass for core helium and carbon burning decreasing as metallicity decreases.
-The age of these stars vary considerably, with observable stars in metal-poor globular clusters hosting populations of $\approx$12Gyr.
-In contrast, metal rich, young observable stars may only reach $\approx$100Myr, this includes stars that are at the core carbon burning limit or very close to it \citep[e.g.][]{whitelock2013}.
+The age of these stars vary considerably, with some as old as $\approx$12\,Gyr in metal-poor globular clusters.
+In contrast, metal-rich, young observable stars may only reach $\approx$100Myr, this includes stars that are at the core carbon burning limit or very close to it \citep[e.g.,][]{whitelock2013}.
 
 Many Barium stars have been discovered in the disk and halo of the Milky Way \citep{gomez1997,mennessier1997}. 
-These studies show that the stellar populations of Barium stars can be separated into two groups when considering their absolute luminosity, kinematic, and spatial properties.
-Barium stars populating the halo have already been investigated \citep[e.g.][]{junqueira2001,drake2008,pereira2009,allen2006} and their relationship with metal-poor, yellow, symbiotic halo stars has been established by \citet{jorissen2005} and \citet{pereira2009}.
+%These studies show that the stellar populations of Barium stars can be separated into two groups when considering their absolute luminosity, kinematic, and spatial properties. 
+The relationship between Barium stars in the halo \citep[e.g.,][]{junqueira2001,drake2008,pereira2009,allen2006} and metal-poor, yellow, symbiotic halo stars has been established by \citet{jorissen2005} and \citet{pereira2009}.
 Additionally, \citet{pereira2011} concludes that metal-rich Barium stars share similar kinematics to other metal-rich and super metal-rich stars already analysed, suggesting that they do not belong to the bulge population.
@@
 
-In this paper we analyse 454,180 giant stars from the second LAMOST data release (DR) to identify and examine 967 s-process candidates including Barium stars, and exclusively enhanced barium and strontium stars, respectively.
+In this paper we analyse 454,180 giant stars from the second LAMOST data release \citep{luo2015} to identify 967 s-process candidates.
 In Section \ref{sec:methods} we describe the observations and candidate selection, as well as the analysis of high-resolution follow-up observations obtained for a few candidates.
 In Section \ref{sec:dis} we discuss the properties of our Barium stars in context of existing literature.
-We provide concluding remarks in Section \ref{sec:con}
+We provide concluding remarks in Section \ref{sec:con}.
 
@@
 The LAMOST (Large sky Area Multi-Object Fibre Spectrographic) survey released low-resolution ($\mathcal{R} \approx 1800$) optical spectra (3700\,\AA\ to 9000\,\AA) for over two million stars in their second data release \citep{luo2015}.
-Stellar parameters ($T_{\rm eff}$, $\log{g}$, [M/H], [$\alpha$/M]) were derived using a data-driven model constructed using high fidelity APOGEE labels of 9,952 giant stars in common between LAMOST and the APOGEE survey.
-It is important to note, this sample is exclusive to giant stars presenting the possibility that this research missed dwarf s-process enhanced stars.
-Cross-validation experience shows that the typical uncertainties are 70K in effective temperature $\rm T_{\rm eff}$, 0.1 dex in surface gravity log g, 0.1 dex in metallicity [Fe/H], and 0.04 dex in the alpha abundance relative to iron [$\alpha$/M].
-These uncertainties are approximately comparable to the conservative APOGEE DR12 uncertainties.
+Stellar parameters ($T_{\rm eff}$, $\log{g}$, [M/H], [$\alpha$/M]) were derived using a data-driven model constructed using high fidelity APOGEE labels of 9,952 giant stars in common between LAMOST and the APOGEE survey \citep{ho2017}.
+This data-driven model was used to estimate stellar labels for 454,180 giant stars.
+We note that this sample is exclusively giant stars, implying that we would not identify dwarf s-process enhanced stars.
+Cross-validation experience shows that the typical uncertainties are about 70\,K in effective temperature $\rm T_{\rm eff}$, 0.1\,dex in surface gravity $\log{g}$, 0.1\,dex in metallicity [M/H], and 0.04\,dex in the $\alpha$-element abundance relative to overall metallicity [$\alpha$/M].
+These uncertainties are approximately comparable to the APOGEE uncertainties \citep{alam2015}.
 
@@
 The Barium stars analysed in this research were obtained by filtering for significant flux residuals, taken as, a disparity between the normalised LAMOST flux and the data driven model derived by \citet{ho2017}.
-Specifically, we identified Barium stars by searching for \ion{Ba}{II} and \ion{Sr}{II} enhancement at the 4554\,\AA\ and 4077\,\AA, respectively.
+Specifically, we identified Barium stars by searching for \ion{Ba}{II} and \ion{Sr}{II} enhancement at the 4554\,\AA\ and 4077\,\AA\ wavelengths, respectively.
 A negative residual, as shown in a candidate Barium star in Figure \ref{fig:figure1}, illustrates an enhancement in \ion{Ba}{II} and \ion{Sr}{II} at lines 4554\,\AA\, 4077\,\AA.
 These \ion{Ba}{II} and \ion{Sr}{II} resonance lines are very strong, allowing us to identify stars enhanced in neutron-capture elements given a well-fit model for the data.
-Stars identified to just show high levels of barium required enhancement at both the 4554\,\AA\ and 4934\,\AA\ resonance lines, and for stars just enhanced in strontium we looked for significant residuals at the 4554\,\AA\ and 4215\,\AA\ absorption lines.
+Stars identified to just show high levels of barium (and not necessarily strontium) required enhancement at both the 4554\,\AA\ and 4934\,\AA\ \ion{Ba}{II} resonance lines, and for stars just enhanced in strontium we looked for significant residuals at the 4554\,\AA\ and 4215\,\AA\ absorption lines.
 
@@
 In addition, a visual inspection was undertaken to exclude any results containing, false positives, candidates exhibiting data reduction issues, apparent absorption finer then the spectral resolution, and overly noisy normalised LAMOST spectra.
-This combined method generated 967 s-process candidates including; 257 Barium stars, 49 stars exhibiting exclusively barium enhancement, and 661 exhibiting exclusively strontium enhancement, as listed in Table \ref{table:table1}.
+This combined method generated 967 s-process candidates including; 257 `Barium stars' enhanced in both barium and strontium, 49 stars exhibiting exclusively barium enhancement, and 661 exhibiting exclusively strontium enhancement, as listed in Table \ref{table:table1}.
 
-\begin{figure}
+For the remainder of this paper we restrict our analysis to the 257 classical `Barium stars' stars that show enhancement in both barium and strontium.
+While the 49 or 661 stars with only barium or strontium enhancements (respectively) may also be bonafide barium stars, there may be other explanations for their chemical abundance pattern \citep[e.g.,][]{maiorca2011}, and so we restrict our inferences to a gold sample of Barium stars.
+Nevertheless, this sample still constitutes the largest collection of Barium stars ever discovered.\todo{cite the next biggest one or two samples}
+
+\subsubsection{Abundance analysis from LAMOST spectra}
+
+\todo{For andy}
+
+\begin{figure*}
 	% To include a figure from a file named example.*
@@
 	% or pdf, png, jpg if compiling using pdflatex
-	\includegraphics[width=\columnwidth]{posterchild.png}
-    \caption{Random Barium Star Spectrum}
+	\includegraphics[width=\textwidth]{posterchild.png}
+    \caption{Pseudo-continuum-normalised LAMOST spectra for the s-process candidate \todo{CANDIDATENAME}.
+The data are shown in black and the best-fitting data-driven model is shown in red.
+We include zoom-in axes to show significant deviations in Sr and Ba at  4077\,\AA\ and 4554\,\AA\, respectively.}
     \label{fig:figure1}
-\end{figure}
+\end{figure*}
 
@@
 \centering
-\caption{Available online in its entirety. Here we show a portion to demonstrate its style and content}
+\caption{Table is available online in its entirety. Here we show a portion to demonstrate its style and content.}
 \label{table:table1}
-\begin{tabular}{@{}|l|l|l|l|l|l|l|l|l|l|@{}}
+\begin{tabular}{@{}|l|l|c|c|c|c|c|c|c|c|c|c|c|c|@{}}
 \toprule
-2MASSID             & RA (hms         & DEC (hms)        & Vr (km/s) & S/N & $\rm T_{\rm eff}$ (K) & Log g & {[}Fe/H{]} & {[}$\alpha$/H{]} & $\chi^2$  \\ \midrule
-J000134.95+490743.2 & 00:01:34.96 & +49:07:43.2 & -42.27    & 72  & 5044 & 3.11  & -0.54      & 0.11      & 0.79 \\ \midrule
-J000403.80+160257.1 & 00:04:03.80 & +16:02:57.2 & -35.38    & 42  & 5200 & 3.40  & -0.41      & 0.09      & 0.33 \\ \midrule
-J000908.48+421615.4 & 00:09:08.49 & +42:16:15.5 & -34.78    & 36  & 4825 & 3.02  & -0.46      & 0.16      & 0.25 \\ \midrule
-J001754.17+394140.0 & 00:17:54.17 & +39:41:40.0 & -42.87    & 39  & 5008 & 3.16  & -0.64      & 0.12      & 0.23 \\ \midrule
-J001841.57+040533.7 & 00:18:41.57 & +04:05:33.8 & -20.69    & 141 & 4840 & 3.68  & -0.52      & 0.06      & 0.93 \\ \midrule
-J002107.60+361533.0 & 00:21:07.60 & +36:15:33.1 & -53.06    & 44  & 4854 & 2.87  & 0.01       & 0.06      & 0.54 \\ \midrule
-J002537.59+411123.7 & 00:25:37.59 & +41:11:23.8 & -12.59    & 36  & 5075 & 3.30  & -0.32      & 0.10      & 0.33 \\ \midrule
-J003755.55+571706.8 & 00:37:55.55 & +57:17:06.9 & -5.70     & 49  & 4046 & 1.14  & -0.09      & -0.01     & 0.83 \\ \midrule
-J003813.23+423025.9 & 00:38:13.23 & +42:30:25.9 & -40.17    & 36  & 4475 & 2.12  & 0.14       & 0.00      & 0.51 \\ \midrule
-J003959.14+394614.6 & 00:39:59.14 & +39:46:14.6 & 5.10      & 35  & 4955 & 3.23  & -0.40      & 0.11      & 0.28 \\ \midrule
-J004119.68+324627.8 & 00:41:19.68 & +32:46:27.9 & 4.50      & 122 & 4861 & 2.59  & -0.31      & 0.08      & 1.67 \\ \midrule
-J004156.56+390945.6 & 00:41:56.57 & +39:09:45.6 & -254.52   & 44  & 4771 & 2.34  & -0.74      & 0.16      & 0.57 \\ \midrule
-J004743.01+433358.1 & 00:47:43.02 & +43:33:58.2 & -62.66    & 65  & 4834 & 2.64  & -0.60      & 0.17      & 1.06 \\ \midrule
-J005101.98+314045.6 & 00:51:01.98 & +31:40:45.7 & -23.68    & 98  & 5202 & 3.32  & -0.53      & 0.10      & 0.67 \\ \midrule
-J005254.69+203554.7 & 00:52:54.69 & +20:35:54.7 & 35.68     & 113 & 5026 & 3.17  & -0.82      & 0.20      & 1.01 \\ \midrule
-J010836.26+444435.9 & 01:08:36.26 & +44:44:35.9 & 12.59     & 49  & 5189 & 3.19  & -0.56      & 0.10      & 0.98 \\ \midrule
-J011919.20+195227.0 & 01:19:19.21 & +19:52:27.0 & -35.38    & 31  & 4897 & 2.77  & -0.54      & 0.11      & 0.29 \\ \midrule
-J011930.90-015027.3 & 01:19:30.91 & -01:50:27.4 & -143.30   & 44  & 5040 & 3.22  & -0.91      & 0.20      & 0.48 \\ \midrule
-J020316.40+462211.1 & 02:03:16.41 & +46:22:11.1 & 11.09     & 37  & 4897 & 2.89  & -0.39      & 0.11      & 0.51 \\ \bottomrule
+2MASSID             & R.~A.         & Dec.        & $v_{r}$ & S/N & $\rm T_{\rm eff}$ & $\log{g}$ & [Fe/H] & [$\alpha$/Fe] & $\chi_r^2$ & \ion{Ba}{II}? & \ion{Sr}{II}? & Tc?  \\
+& (J2000) & (J2000) & (km\,s$^{-1}$) & (pixel$^{-1}$) & (K)  \\ \midrule
+J000134.95+490743.2 & 00:01:34.96 & +49:07:43.2 & $-$42.3    & 72  & 5044 & 3.11  & $-$0.54      & $+$0.11      & 0.79 \\
+J000403.80+160257.1 & 00:04:03.80 & +16:02:57.2 & $-$35.4    & 42  & 5200 & 3.40  & $-$0.41      & $+$0.09      & 0.33 \\
+J000908.48+421615.4 & 00:09:08.49 & +42:16:15.5 & $-$34.8    & 36  & 4825 & 3.02  & $-$0.46      & $+$0.16      & 0.25 \\
+J001754.17+394140.0 & 00:17:54.17 & +39:41:40.0 & $-$42.9    & 39  & 5008 & 3.16  & $-$0.64      & $+$0.12      & 0.23 \\
+J001841.57+040533.7 & 00:18:41.57 & +04:05:33.8 & $-$20.7    & 141 & 4840 & 3.68  & $-$0.52      & $+$0.06      & 0.93 \\
+J002107.60+361533.0 & 00:21:07.60 & +36:15:33.1 & $-$53.1    & 44  & 4854 & 2.87  & $+$0.01      & $+$0.06      & 0.54 \\
+J002537.59+411123.7 & 00:25:37.59 & +41:11:23.8 & $-$12.6    & 36  & 5075 & 3.30  & $-$0.32      & $+$0.10      & 0.33 \\
+J003755.55+571706.8 & 00:37:55.55 & +57:17:06.9 & $-$5.7     & 49  & 4046 & 1.14  & $-$0.09      & $-$0.01      & 0.83 \\
+J003813.23+423025.9 & 00:38:13.23 & +42:30:25.9 & $-$40.2    & 36  & 4475 & 2.12  & $+$0.14      & $+$0.00      & 0.51 \\
+J003959.14+394614.6 & 00:39:59.14 & +39:46:14.6 & $+$5.1     & 35  & 4955 & 3.23  & $-$0.40      & $+$0.11      & 0.28 \\
+J004119.68+324627.8 & 00:41:19.68 & +32:46:27.9 & $+$4.5     & 122 & 4861 & 2.59  & $-$0.31      & $+$0.08      & 1.67 \\
+J004156.56+390945.6 & 00:41:56.57 & +39:09:45.6 & $-$254.5   & 44  & 4771 & 2.34  & $-$0.74      & $+$0.16      & 0.57 \\
+J004743.01+433358.1 & 00:47:43.02 & +43:33:58.2 & $-$62.7    & 65  & 4834 & 2.64  & $-$0.60      & $+$0.17      & 1.06 \\
+J005101.98+314045.6 & 00:51:01.98 & +31:40:45.7 & $-$23.7    & 98  & 5202 & 3.32  & $-$0.53      & $+$0.10      & 0.67 \\
+J005254.69+203554.7 & 00:52:54.69 & +20:35:54.7 & $+$35.7     & 113 & 5026 & 3.17  & $-$0.82     & $+$0.20      & 1.01 \\
+J010836.26+444435.9 & 01:08:36.26 & +44:44:35.9 & $+$12.6     & 49  & 5189 & 3.19  & $-$0.56     & $+$0.10      & 0.98 \\
+J011919.20+195227.0 & 01:19:19.21 & +19:52:27.0 & $-$35.4    & 31  & 4897 & 2.77  & $-$0.54      & $+$0.11      & 0.29 \\
+J011930.90-015027.3 & 01:19:30.91 & -01:50:27.4 & $-$143.3   & 44  & 5040 & 3.22  & $-$0.91      & $+$0.20      & 0.48 \\
+J020316.40+462211.1 & 02:03:16.41 & +46:22:11.1 & $+$11.1     & 37  & 4897 & 2.89  & $-$0.39     & $+$0.11      & 0.51 \\ \bottomrule
 \end{tabular}
@@
 Only 5/257 Barium stars met this criteria, and it's important to note sodium enhancement can occur due to the presence of interstellar dust.
-Using the IRSA's all-sky dust map \citep{schlafly2011}, E(B-V) values were calculated for our 5 candidates.
-The results show 2 sodium enhanced stars have strong ($\approx$0.35) E(B-V) values, higher then galactic stellar levels, suggesting these candidates are false positives.
-Whereas, 3 exhibit low ($\approx$0.045) E(B-V) values, confirming sodium enhancement results for these candidates.
+Using the IRSA's all-sky dust map \citep{schlafly2011}, we find that 2 of 5 of these stars have strong ($\approx$0.35) E(B-V) values, suggesting that the flux residuals around the Na doublet are due to interstellar absorption.
+However, 3 exhibit low ($\approx$0.045) E(B-V) values, indicating the enhancement is due to stellar absorption.
+
 For technetium enhancement we searched for significant residual deviations at the 4049\,\AA, 4238\,\AA, 4262\,\AA, 4297\,\AA, and 5924\,\AA.
@@
 We found 51 Barium stars exhibited some level of significant enhancement (based on the filters above) at a single technetium line, yet none showed enhancement at more than one technetium line.
-We note that the single enhancement near technetium for these 51 stars may be the consequence of data reduction/calibration artefacts, but we include details of which stars matched on technetium in Table \ref{tab:table} nonetheless.
+We note that the single enhancement near technetium for these 51 stars may be the consequence of data reduction/calibration artefacts, but we include details of which stars matched on technetium in Table \ref{table:table1} nonetheless.
 Finally, for carbon enhancement we searched for significant deviations at the CH and G band near 4300\,\AA.
-We found 178/257 stars to show significant carbon enhancement (e.g., $[\textrm{C/M}] \gtrsim 0.5$).
+We found 178/257 stars to show significant carbon enhancement (e.g., $[\textrm{C/Fe}] \gtrsim 0.5$).
 
@@
 Moreover, they suggest [Na/Fe] ratios exhibit systematically higher values for giants with lower $\log{g}$ values, but do not exhibit variations in metallicity.
-Similarly, \citet{decastro2016} highlights the possible weak anti-correlation between [Na/Fe] ratio and $\log{g}$, and highlights that this trend in previous studies \citep[e.g.][]{boyarchuk2002,mishenina2006,luck2007,takeda2008}.
+Similarly, \citet{decastro2016} highlights the possible weak anti-correlation between [Na/Fe] ratio and $\log{g}$, and highlights that this trend in previous studies \citep[e.g.,][]{boyarchuk2002,mishenina2006,luck2007,takeda2008}.
 
-We find only $<2$\,\% of our Barium stars show sodium enhancement, contrary to previous studies \citep[e.g.][]{decastro2016}.
+We find only $<2$\,\% of our Barium stars show sodium enhancement, contrary to previous studies \citep[e.g.,][]{decastro2016}.
 We also note that the 5 sodium-enhanced Barium stars all have $\log{g} \approx 3$, not at lower $\log{g}$ values as might be expected if low $\log{g}$ values systematically contributed to higher [Na/Fe] abundance ratios.
@@
 However, for Tc to be present in  a star the enhancement lines must be considerably strong, and given that all 51 matches were at single lines it is concluded that these results are more likely data artifacts.
-In agreement with previous findings \citep[e.g.][]{little1987,smith1984,smith1983}, the results indicate that none of the evolved Barium stars in our sample exhibited the presence of Tc enhancement, and it can be concluded our Barium star sample is extrinsic.
+In agreement with previous findings \citep[e.g.,][]{little1987,smith1984,smith1983}, the results indicate that none of the evolved Barium stars in our sample exhibited the presence of Tc enhancement, and it can be concluded our Barium star sample is extrinsic.
 It is noted, Tc enhancement is a very difficult line to analyse and that this conclusion is not concrete.
@@
 todo{ Something about binary eccentricities.}
+
 \section*{Acknowledgements}
-
-Fired Status: maybe
+We thank Alex Ji (Carnegie Observatories) for useful discussions.
+A.~R.~C. is supported through an Australian Research Council Discovery Project under grant DP160100637.
+A.~Y.~Q.~H. is supported by a Fulbright grant through the German-American Fulbright Commission and a National Science Foundation Graduate Research Fellowship under Grant No. DGE-1144469. 
+This research has made use of NASA's Astrophysics Data System.
+Guoshoujing Telescope (the Large Sky Area Multi-Object Fiber Spectroscopic Telescope LAMOST) is a National Major Scientific Project built by the Chinese Academy of Sciences.
+Funding for the project has been provided by the National Development and Reform Commission.
+LAMOST is operated and managed by the National Astronomical Observatories, Chinese Academy of Sciences.
 
@@
 \begin{thebibliography}{99}
+\bibitem[Alam et al.(2015)]{alam2015} Alam, S., Albareti, F.~D., Allende Prieto, C., et al.\ 2015, \apjs, 219, 12 
 \bibitem[\protect\citeauthoryear{Allen \& Barbuy}{2006}]{allen2006}
@@
 RAA, in press
+\bibitem[Maiorca et al.(2011)]{maiorca2011} Maiorca, E., Randich, S., Busso, M., Magrini, L., \& Palmerini, S.\ 2011, \apj, 736, 120 
 \bibitem[\protect\citeauthoryear{McClure}{1983}]{mcclure1983}

### 2018-02-05 article/ms.tex
chagnes

@@
 
-\subsubsection{Abundance analysis from LAMOST spectra}
-
-\todo{For andy}
-
 \begin{figure*}
@@
 We used the sodium doublet lines at 5889\,\AA\ and 5895\,\AA\ to select Barium stars enhanced in sodium, and required significant absorption in both features.
-Only 5/257 Barium stars met this criteria, and it's important to note sodium enhancement can occur due to the presence of interstellar dust.
-Using the IRSA's all-sky dust map \citep{schlafly2011}, we find that 2 of 5 of these stars have strong ($\approx$0.35) E(B-V) values, suggesting that the flux residuals around the Na doublet are due to interstellar absorption.
-However, 3 exhibit low ($\approx$0.045) E(B-V) values, indicating the enhancement is due to stellar absorption.
+Only 5/257 Barium stars met this criteria.
 
@@
 We found 178/257 stars to show significant carbon enhancement (e.g., $[\textrm{C/Fe}] \gtrsim 0.5$).
+
+\subsubsection{Abundance analysis from LAMOST spectra}
+We estimated [Ba/Fe] and [Sr/Fe] abundance ratios for all s-process candidates by synthesising spectra that would account for the observed flux residuals.
+We assumed that absorption due to metals is captured by \emph{The Cannon} model, and deviations in flux at the 4554\,\AA\ \ion{Ba}{II} line and the 4077\,\AA\ \ion{Sr}{II} transition are solely due to enhancements in Ba and Sr, respectively\citep{marcs,sme,vald,ispec}.
+We adopted the stellar parameters ($T_{\rm eff}$, $\log{g}$, [Fe/H]) from \citep{ho2017}, and assume a microturbulence of $v_{mic} = 2\,{\rm km\,s}^{-1}$.
+Uncertainties in [Ba/Fe] and [Sr/Fe] from LAMOST are taken as the fitting error due to noise, added in quadrature with an adopted $0.2\,{\rm dex}$ systematic error floor.
 
@@
 It is noted, in the previous literature \citet{van2017}, only 22\% of their stellar sample are post-main-sequence barium stars (extrinsic barium stars).
-In comparison, we find our Barium candidates constitute greater than 70\% extrinsic, this suggests the construction of our data-driven model may have missed some AGB Barium candidates.
+In comparison, we find our Barium candidates constitute greater than 70\% extrinsic, this suggests the construction of our data-driven model may have missed some AGB Barium candidates, or that previous studies were biased towards finding luminous intrinsic AGB Barium stars.
 
 \subsection{Sodium enhancment}
-According to \citet{el1995}, sodium overabundances observed in the atmospheres of supergiants is synthesised by the NeNa reaction chain in the convective core of main-sequence stars.
+Sodium overabundances observed in the atmospheres of supergiants is thought to be synthesised by the NeNa reaction chain in the convective core of main-sequence stars \citep{el1995}.
 Sodium is transported to the surface of these supergiants via mixing of CNO cycle products during the first dredge-up, although, it is important to note sodium enhancement is not constrained to supergiant stars.
@@
 \citet{antipova2004} reported sodium enhancements in 3 of their 16 Barium star candidates, and they relate this to the dredge-up of nuclear-burning material produced by convection during the red-giant phase.
-Moreover, they suggest [Na/Fe] ratios exhibit systematically higher values for giants with lower $\log{g}$ values, but do not exhibit variations in metallicity.
+Moreover, they suggest [Na/Fe] ratios are systematically higher for giants with lower $\log{g}$ values, \todo{but do not exhibit variations in metallicity}.
 Similarly, \citet{decastro2016} highlights the possible weak anti-correlation between [Na/Fe] ratio and $\log{g}$, and highlights that this trend in previous studies \citep[e.g.,][]{boyarchuk2002,mishenina2006,luck2007,takeda2008}.
 
-We find only $<2$\,\% of our Barium stars show sodium enhancement, contrary to previous studies \citep[e.g.,][]{decastro2016}.
+We find $<2$\,\% of our Barium stars show sodium enhancement, contrary to previous studies \citep[e.g.,][]{decastro2016}.
 We also note that the 5 sodium-enhanced Barium stars all have $\log{g} \approx 3$, not at lower $\log{g}$ values as might be expected if low $\log{g}$ values systematically contributed to higher [Na/Fe] abundance ratios.
-These results suggest that sodium-rich material from a companion TP-AGB star has polluted these 5 Barium candidates, but importantly, sodium enhancement is by no means ubiquitous in Barium stars.
-It's important to note, sodium enhancement can occur due to the presence of interstellar dust, and using the IRSA's all-sky dust map \citep{schlafly2011}, E(B-V) values were calculated for our 5 candidates.
-The results show 2 sodium enhanced stars have strong ($\approx$0.35) E(B-V) values, higher then galactic stellar levels, suggesting these candidates are false positives.
-Whereas, 3 exhibit low ($\approx$0.045) E(B-V) values, confirming sodium enhancement results for these candidates.
-The comparisons made in \citep{decastro2016} made use of multiple literature comparisons, and therefore it is possible that there are systematic differences (biases) between Milky Way studies of normal FGK-type stars and those focussed on Barium stars, leading to unresolved differences in the reported [Na/Fe] abundance ratio.
-These same systematic effects could contribute to the observed correlation between [Na/Fe] and $\log{g}$, which we do not observe in our sample.
+It's important to note sodium enhancement can occur due to the presence of interstellar dust.
+Using the IRSA's all-sky dust map \citep{schlafly2011}, we find that 2 of 5 of these stars have strong ($\approx$0.35) E(B-V) values, suggesting that the flux residuals around the Na doublet are due to interstellar absorption.
+However, 3 exhibit low ($\approx$0.045) E(B-V) values, indicating the enhancement is more likely due to stellar absorption.
+These results suggest that sodium-rich material from a companion TP-AGB star has polluted these 3 Barium candidates, but importantly, sodium enhancement is by no means ubiquitous in Barium stars.
+
+The data that led \citet{decastro2016} to conclude that Barium stars have higher [Na/Fe] ratios came from many literature sources.
+Therefore, it is possible that there are systematic differences (biases) between Milky Way studies of normal FGK-type stars and those focussed on Barium stars, leading to unresolved differences in the reported [Na/Fe] abundance ratio.
+These systematic effects would also contribute to the observed correlation between [Na/Fe] and $\log{g}$, since intrinsic Barium stars (by definition) have low $\log{g}$ values.
+We do not observe this correlation between [Na/Fe] and $\log{g}$ in our sample.
+From our data we conclude that Barium stars do not have higher [Na/Fe] abundance ratios on average, and suggest that the effect seen in previous works was due to systematic effects between literature sources.
 
@@
 The majority (46/51) have $\log{g} > 2$, suggesting they cannot be AGB stars, and may indicate a recent ($<1\,\textrm{Myr}$) mass accretion event.
-However, for Tc to be present in  a star the enhancement lines must be considerably strong, and given that all 51 matches were at single lines it is concluded that these results are more likely data artifacts.
+However, for Tc to be present in the LAMOST spectra the enhancement must be considerably strong, and given that all 51 matches were at single lines it is concluded that these results are more likely data artefacts.
 In agreement with previous findings \citep[e.g.,][]{little1987,smith1984,smith1983}, the results indicate that none of the evolved Barium stars in our sample exhibited the presence of Tc enhancement, and it can be concluded our Barium star sample is extrinsic.
-It is noted, Tc enhancement is a very difficult line to analyse and that this conclusion is not concrete.
+However, we caution that Tc enhancement is usually a very weak signature.
 
@@
 Giants and supergiants become enhanced in carbon through TDU process discussed in Section \ref{sec:intro}, and extrinsic carbon enhancement occurs via mass transfer from a binary AGB star.
-
-Our analsyse produced 178 CH and G band enhanced stars out of the total 257 Barium candidates.
-Similar to the s-process enhancement, this suggests our candidates are either intrinsic or extrinsic Barium stars.
+Our analysis produced 178 CH and G band enhanced stars out of the total 257 Barium candidates.
+Similar to the s-process enhancement, this suggests our candidates are consistent with being either intrinsic or extrinsic Barium stars.
 
@@
 	\includegraphics[width=\columnwidth]{HRdummy.png}
-    \caption{Effective temperature $T_{eff}$ and surface gravity $\log{g}$ for 257 candidate Barium stars from LAMOST.
+    \caption{Effective temperature $T_{\rm eff}$ and surface gravity $\log{g}$ for 257 candidate Barium stars from LAMOST.
 Stars with $\log{g} > 2$ (as marked) have not evolved through the thermally pulsing asymptotic giant branch phase, and therefore their abundance signature must be the result of an extrinsic pollution event.
-The classification of stars with $\log{g} < 2$ would require additional data}
+The classification of stars with $\log{g} < 2$ would require additional data.}
     \label{fig:figure2}
@@
 
-\subsection{AGB yields comparison}
+\subsection{Comparison to AGB yields}
 AGB stars, and chemically unique stars that show the chemical signature
 of mass transfer pollution from binary companion AGB stars, highlight the variation of s-process enhancement.
-\citet{karakas_lugaro2016} demonstrates through stellar yield models, that Barium stars will have a likely minimum yeild at [Fe/H]$\approx$ -1.2.
-Figure \ref{fig:figure3} confirms this as the majority of the Barium stars are contained above -1.2.
-The final surface s-process index [hs/ls], shown in \citet{cristallo2015}, highlights the relationship between [hs/ls] yields and the mass of AGB stars.
+\citet{karakas_lugaro2016} demonstrates through stellar yield models, that Barium stars will have a likely minimum yield at $[{\rm Fe/H}] \approx -1.2$.
+In Figure \ref{fig:figure3} we show the heavy-to-light s-process abundance ratio (taken as [Ba/Sr]) for all 257 Barium stars identified in LAMOST.
+Although the [hs/ls] ratio is quite noisy, the overall metallicity [Fe/H] is quite precise (0.1\,dex).
+Despite our LAMOST sample of 454,180 giants having metallicities down to about $[{\rm Fe/H}] = -2$, we only detect Barium stars down to metallicities of about $[{\rm Fe/H}] = -1.1$, consistent with expectations from \citep{karakas_lugaro2016}.
+
+\todo{The final surface s-process index [hs/ls], shown in \citet{cristallo2015}, highlights the relationship between [hs/ls] yields and the mass of AGB stars.
 The Salpeter IMF predicts the majority of stars in the Milky Way will be at lower mass, and as predicted the [hs/ls] values of our Barium stars approximately fit the lower mass yields shown in \citet{cristallo2015}.
 Barium stars not fitting this relationship represent the possibly more massive AGB stars (intrinsic Barium stars) within our sample.
+}
+
+\todo{Frequency with metallicity}
 
@@
 	\includegraphics[width=\columnwidth]{basrtest4.png}
-    \caption{Final surface s-process indexes: [hs/ls]}
+    \caption{Metallicities ([Fe/H]; x-axis) and heavy-to-light s-process abundance ratios ([hs/ls], taken as [Ba/Sr]; y-axis) for 257 Barium star candidates. \todo{Add Cristillo yields}}
     \label{fig:figure3}
@@
 
-Our research discovered 967 s-process candidates including; 257 Barium stars, 49 stars exhibiting exclusively barium enhancement, and 661 exhibiting exclusively strontium enhancement from 454,180 giant stars observed by LAMOST.
-This is double the currently known stellar sample of Barium stars, and the largest sample of s-process enhanced stars known to date.
-Nearly all of our Barium candidates are disk stars, 178 exhibit CH and G band enhancement, no plausible technetium enhancement is discovered, and it is shown sodium enhancement is not ubiquitous in s-process stars as previously claimed.
-AGB yields comparisons indicate the majority of our sample fit low steallar mass trends in agreement with Salpeter IMF theory.
-Additonally, a number of outliers highlight a small percentage of intrinsic Barium stars in our sample.
-todo{ Something about binary eccentricities.}
+We conducted the largest ever search for s-process enhanced stars using the LAMOST second data release.
+From 454,180 giant stars, we identify 967 s-process candidates including: 257 stars with significant enhancements in barium and strontium (so-called `Barium stars'); 49 stars exhibiting exclusively barium enhancement, and 661 exhibiting exclusively strontium enhancement.
+This sample size is double the total number of Barium stars known, and represents the largest sample of s-process enhanced stars to date.
+Nearly all of our Barium candidates are consistent with being disk stars.
+
+We find 178/257 to show carbon enhancement, consistent with the literature.
+However, in contrast with previous works, we do not find Barium stars to have significantly higher [Na/Fe] than Milky Way stars.
+Only 5/257 of our Barium stars show enhancement in Na, and the flux residuals in three of those are likely due to interstellar dust.
+We suggest that biases between literature sources and systematic effects in measuring [Na/Fe] from stars with low $\log{g}$ contributed to this effect.
+
+Despite our noisy estimates of [Ba/Fe] and [Sr/Fe] from LAMOST spectra, comparisons with AGB yields indicate that our sample is consistent with a bottom-heavy initial mass function.
+We encourage follow-up observations with high-resolution spectrographs in order to precisely measure neutron-capture abundances (including [hs/ls] ratios).
+These data would permit the most detailed comparisons with AGB star yields ever considered.
 
@@
 A$\&$A, 424, 727
+\bibitem[Blanco-Cuaresma et al.(2014)]{ispec} Blanco-Cuaresma, S., Soubiran, C., Heiter, U., \& Jofr{\'e}, P.\ 2014, \aap, 569, A111 
 \bibitem[\protect\citeauthoryear{Boffin \& Jorissen}{1988}]{boffin1988}
@@
 A$\&$A, 595, A1
+\bibitem[Gustafsson et al.(2008)]{marcs} Gustafsson, B., Edvardsson, B., Eriksson, K., et al.\ 2008, \aap, 486, 951 
 \bibitem[\protect\citeauthoryear{Gomez et al.}{1997}]{gomez1997}
@@
 MNRAS, 414, 3231
+\bibitem[Kupka et al.(1999)]{vald} Kupka, F., Piskunov, N., Ryabchikova, T.~A., Stempels, H.~C., \& Weiss, W.~W.\ 1999, \aaps, 138, 119 
 \bibitem[\protect\citeauthoryear{Little-Marenin \& Little}{1987}]{little1987}
@@
 MNRAS, 428, 2216
+\bibitem[Valenti \& Piskunov(1996)]{sme} Valenti, J.~A., \& Piskunov, N.\ 1996, \aaps, 118, 595 
 \bibitem[\protect\citeauthoryear{Van der Swaelmen et al.}{2017}]{van2017}

### 2018-02-05 article/ms.tex
update figure 1
draft

@@
 \newcommand{\countertodo}[1]{\textcolor{green}{#1}}
+\usepackage{adjustbox}
+\usepackage{pifont}
 
@@
 This sample constitutes the largest number of s-process enhanced stars ever discovered, and represents the most comprehensive search for Barium stars in the Milky Way.
-All of our Barium stars are consistent with membership in the Milky Way disk, and we find an \todo{steady/increasing/decreasing} fraction of Barium stars with stellar metallicity, as \todo{expected} from AGB yields and stellar evolution theory.
 We find up to 51 Barium stars exhibit some evidence of technetium from LAMOST spectra, and most (46/51) have $\log{g}>2$, which suggests they cannot be AGB stars and may indicate a recent ($<1\,\textrm{Myr}$) mass accretion event.
@@
 A comparison with AGB yields suggests that the majority of our sample are consistent with a bottom-heavy IMF.
-% and highlights a small percentage of intrinsic Barium stars present in our sample. 
 When binary properties become available from end-of-mission Gaia astrometry, this sample of s-process stars will be critical in explaining mass transfer in binary systems and refining AGB yields across a range of masses and metallicities.
@@
 \item The reduced $\chi^2$ from \emph{The Cannon} must be $\chi_r^2 < 3$.
-\item And finally, the LAMOST spectra must have a signal-to-noise ratio of $S/N > 30\,\textrm{pixel}^{-1}$.
+\item And, the LAMOST spectra must have a signal-to-noise ratio of $S/N > 30\,\textrm{pixel}^{-1}$.
 \end{enumerate}
@@
 While the 49 or 661 stars with only barium or strontium enhancements (respectively) may also be bonafide barium stars, there may be other explanations for their chemical abundance pattern \citep[e.g.,][]{maiorca2011}, and so we restrict our inferences to a gold sample of Barium stars.
-Nevertheless, this sample still constitutes the largest collection of Barium stars ever discovered.\todo{cite the next biggest one or two samples}
+Nevertheless, this sample still constitutes the largest collection of Barium stars ever discovered.\todo{\citet{decastro2016} merges all previously known Barium stars candidates into a confirmed Barium stellar sample cite the next biggest one or two samples}
 
@@
 \label{table:table1}
-\begin{tabular}{@{}|l|l|c|c|c|c|c|c|c|c|c|c|c|c|@{}}
+\begin{adjustbox}{width=1\textwidth}
+\begin{tabular}{@{}|l|l|c|c|c|c|c|c|c|c|c|c|c|c|c|c|@{}}
 \toprule
-2MASSID             & R.~A.         & Dec.        & $v_{r}$ & S/N & $\rm T_{\rm eff}$ & $\log{g}$ & [Fe/H] & [$\alpha$/Fe] & $\chi_r^2$ & \ion{Ba}{II}? & \ion{Sr}{II}? & Tc?  \\
+2MASSID             & R.~A.
+& Dec.
+& $v_{r}$ & S/N & $\rm T_{\rm eff}$ & $\log{g}$ & [Fe/H] & [$\alpha$/Fe] & $\chi_r^2$ & [Ba/Fe] & [Sr/Fe] & \ion{Ba}{II} & \ion{Sr}{II} &  \ion{Ba}{II}\& \ion{Sr}{II} & Tc\\
 & (J2000) & (J2000) & (km\,s$^{-1}$) & (pixel$^{-1}$) & (K)  \\ \midrule
-J000134.95+490743.2 & 00:01:34.96 & +49:07:43.2 & $-$42.3    & 72  & 5044 & 3.11  & $-$0.54      & $+$0.11      & 0.79 \\
-J000403.80+160257.1 & 00:04:03.80 & +16:02:57.2 & $-$35.4    & 42  & 5200 & 3.40  & $-$0.41      & $+$0.09      & 0.33 \\
-J000908.48+421615.4 & 00:09:08.49 & +42:16:15.5 & $-$34.8    & 36  & 4825 & 3.02  & $-$0.46      & $+$0.16      & 0.25 \\
-J001754.17+394140.0 & 00:17:54.17 & +39:41:40.0 & $-$42.9    & 39  & 5008 & 3.16  & $-$0.64      & $+$0.12      & 0.23 \\
-J001841.57+040533.7 & 00:18:41.57 & +04:05:33.8 & $-$20.7    & 141 & 4840 & 3.68  & $-$0.52      & $+$0.06      & 0.93 \\
-J002107.60+361533.0 & 00:21:07.60 & +36:15:33.1 & $-$53.1    & 44  & 4854 & 2.87  & $+$0.01      & $+$0.06      & 0.54 \\
-J002537.59+411123.7 & 00:25:37.59 & +41:11:23.8 & $-$12.6    & 36  & 5075 & 3.30  & $-$0.32      & $+$0.10      & 0.33 \\
-J003755.55+571706.8 & 00:37:55.55 & +57:17:06.9 & $-$5.7     & 49  & 4046 & 1.14  & $-$0.09      & $-$0.01      & 0.83 \\
-J003813.23+423025.9 & 00:38:13.23 & +42:30:25.9 & $-$40.2    & 36  & 4475 & 2.12  & $+$0.14      & $+$0.00      & 0.51 \\
-J003959.14+394614.6 & 00:39:59.14 & +39:46:14.6 & $+$5.1     & 35  & 4955 & 3.23  & $-$0.40      & $+$0.11      & 0.28 \\
-J004119.68+324627.8 & 00:41:19.68 & +32:46:27.9 & $+$4.5     & 122 & 4861 & 2.59  & $-$0.31      & $+$0.08      & 1.67 \\
-J004156.56+390945.6 & 00:41:56.57 & +39:09:45.6 & $-$254.5   & 44  & 4771 & 2.34  & $-$0.74      & $+$0.16      & 0.57 \\
-J004743.01+433358.1 & 00:47:43.02 & +43:33:58.2 & $-$62.7    & 65  & 4834 & 2.64  & $-$0.60      & $+$0.17      & 1.06 \\
-J005101.98+314045.6 & 00:51:01.98 & +31:40:45.7 & $-$23.7    & 98  & 5202 & 3.32  & $-$0.53      & $+$0.10      & 0.67 \\
-J005254.69+203554.7 & 00:52:54.69 & +20:35:54.7 & $+$35.7     & 113 & 5026 & 3.17  & $-$0.82     & $+$0.20      & 1.01 \\
-J010836.26+444435.9 & 01:08:36.26 & +44:44:35.9 & $+$12.6     & 49  & 5189 & 3.19  & $-$0.56     & $+$0.10      & 0.98 \\
-J011919.20+195227.0 & 01:19:19.21 & +19:52:27.0 & $-$35.4    & 31  & 4897 & 2.77  & $-$0.54      & $+$0.11      & 0.29 \\
-J011930.90-015027.3 & 01:19:30.91 & -01:50:27.4 & $-$143.3   & 44  & 5040 & 3.22  & $-$0.91      & $+$0.20      & 0.48 \\
-J020316.40+462211.1 & 02:03:16.41 & +46:22:11.1 & $+$11.1     & 37  & 4897 & 2.89  & $-$0.39     & $+$0.11      & 0.51 \\ \bottomrule
+J000019.26+501444.8 & 00:00:19.27 & +50:14:44.9 & -3.9  & 49      & 4973         & 3.27         & 0.21         & 0.08             & 0.66               & 0.25        & 0.83        & \ding{55} & \ding{51}  & \ding{55} & \ding{55}   \\
+J000020.55+411348.1 & 00:00:20.56 & +41:13:48.2 & -28.2 & 32      & 4882         & 2.74         & -0.22        & 0.04             & 0.23               & -0.17       & 0.90        & \ding{55}& \ding{51}  & \ding{55} & \ding{55}    \\
+J000134.95+490743.2 & 00:01:34.96 & +49:07:43.2 & -42.3 & 72      & 5044         & 3.11         & -0.54        & 0.11             & 0.79               & 1.02        & 0.45        & \ding{55} & \ding{55} & \ding{51}  & \ding{55}   \\
+J000258.09+410730.0 & 00:02:58.10 & +41:07:30.1 & -34.5 & 41      & 4697         & 2.57         & -0.22        & 0.12             & 0.98               & -0.10       & 0.80        & \ding{55} & \ding{51}  & \ding{55}  & \ding{55}   \\
+J000403.80+160257.1 & 00:04:03.80 & +16:02:57.2 & -35.4 & 42      & 5200         & 3.40         & -0.41        & 0.09             & 0.33               & 0.92        & 0.52        & \ding{55} & \ding{55} & \ding{51}  & \ding{55}   \\
+J000439.16+183350.3 & 00:04:39.17 & +18:33:50.4 & -38.7 & 31      & 4601         & 2.50         & 0.44         & 0.03             & 0.34               & -0.11       & 0.88        & \ding{55} & \ding{51}  & \ding{55}  & \ding{55}   \\
+J000444.87+400402.1 & 00:04:44.88 & +40:04:02.1 & -94.7 & 53      & 4172         & 1.46         & -0.08        & 0.09             & 0.72               & 0.03        & 0.91        & \ding{55} & \ding{51}  & \ding{55} & \ding{55}    \\
+J000552.76+261849.3 & 00:05:52.76 & +26:18:49.4 & -22.5 & 73      & 4924         & 3.14         & -0.05        & 0.09             & 0.67               & 0.28        & 0.85        & \ding{55} & \ding{51}  & \ding{55} & \ding{55}    \\
+J000737.70+394055.5 & 00:07:37.70 & +39:40:55.6 & -31.5 & 33      & 4700         & 2.80         & -0.04        & 0.07             & 0.28               & -0.13       & 0.81        & \ding{55} & \ding{51}  & \ding{55} & \ding{55}
 \end{tabular}
+\end{adjustbox}
 \end{table*}
@@
 \citet{antipova2004} reported sodium enhancements in 3 of their 16 Barium star candidates, and they relate this to the dredge-up of nuclear-burning material produced by convection during the red-giant phase.
-Moreover, they suggest [Na/Fe] ratios are systematically higher for giants with lower $\log{g}$ values, \todo{but do not exhibit variations in metallicity}.
+Moreover, they suggest [Na/Fe] ratios are systematically higher for giants with lower $\log{g}$ values, however, these [Na/Fe] ratios do not exhibit variations in metallicity.
 Similarly, \citet{decastro2016} highlights the possible weak anti-correlation between [Na/Fe] ratio and $\log{g}$, and highlights that this trend in previous studies \citep[e.g.,][]{boyarchuk2002,mishenina2006,luck2007,takeda2008}.
@@
 \begin{figure}
-	\includegraphics[width=\columnwidth]{HRdummy.png}
+	\includegraphics[width=\columnwidth]{hrd.pdf}
     \caption{Effective temperature $T_{\rm eff}$ and surface gravity $\log{g}$ for 257 candidate Barium stars from LAMOST.
@@
 
-\todo{The final surface s-process index [hs/ls], shown in \citet{cristallo2015}, highlights the relationship between [hs/ls] yields and the mass of AGB stars.
-The Salpeter IMF predicts the majority of stars in the Milky Way will be at lower mass, and as predicted the [hs/ls] values of our Barium stars approximately fit the lower mass yields shown in \citet{cristallo2015}.
-Barium stars not fitting this relationship represent the possibly more massive AGB stars (intrinsic Barium stars) within our sample.
-}
-
-\todo{Frequency with metallicity}
+The final surface s-process index [hs/ls], shown in \citet{cristallo2015} and illustrated in Figure \ref{fig:figure3}, highlights the relationship between [hs/ls] yields and the mass of AGB stars.
+The Salpeter IMF predicts the majority of stars in the Milky Way will be at lower mass, and as predicted the [hs/ls] values of our Barium stars approximately fit the lower mass yields as seen in Figure \ref{fig:figure3}.
+Our Barium candidates not fitting this relationship represent the possibly more massive AGB stars (intrinsic Barium stars) within our sample.
 

### 2018-02-05 article/ms.tex
drafty

@@
 While the 49 or 661 stars with only barium or strontium enhancements (respectively) may also be bonafide barium stars, there may be other explanations for their chemical abundance pattern \citep[e.g.,][]{maiorca2011}, and so we restrict our inferences to a gold sample of Barium stars.
-Nevertheless, this sample still constitutes the largest collection of Barium stars ever discovered.\todo{\citet{decastro2016} merges all previously known Barium stars candidates into a confirmed Barium stellar sample cite the next biggest one or two samples}
+Nevertheless, this sample still constitutes the largest collection of Barium stars ever discovered; the stellar sample given in \citet{decastro2016} constitutes the next largest Barium star candidate list.
 
@@
 From 454,180 giant stars, we identify 967 s-process candidates including: 257 stars with significant enhancements in barium and strontium (so-called `Barium stars'); 49 stars exhibiting exclusively barium enhancement, and 661 exhibiting exclusively strontium enhancement.
-This sample size is double the total number of Barium stars known, and represents the largest sample of s-process enhanced stars to date.
+This sample size is greatest total number of Barium stars known, and represents the largest sample of s-process enhanced stars to date.
 Nearly all of our Barium candidates are consistent with being disk stars.

### 2018-02-06 article/ms.tex
text updates; add mike summary

@@
 A.~J. Kemp,$^{1}$ 
-A.~I. Karakas,$^{1}$ \newauthor
+A.~I. Karakas,$^{1}$\newauthor
+A.~Y.~Q. Ho,$^{3}$
 J.~C. Lattanzio,$^{1}$
-K.~C. Schlaufman,$^{3}$
-and A.~Y.~Q. Ho$^{4}$
+K.~C. Schlaufman,$^{4}$
 \\
@@
 $^{2}$Faculty of Information Technology, Monash University, Clayton 3800, Victoria, Australia\\
-$^{3}$Department of Physics and Astronomy, Johns Hopkins University, 3400 N Charles St., Baltimore, MD 21218, USA\\
-$^{4}$Cahill Center for Astrophysics, California Institute of Technology, MC 249-17, 1200 E California Blvd, Pasadena, Ca, 91125, USA
+$^{3}$Cahill Center for Astrophysics, California Institute of Technology, MC 249-17, 1200 E California Blvd, Pasadena, Ca, 91125, USA\\
+$^{4}$Department of Physics and Astronomy, Johns Hopkins University, 3400 N Charles St., Baltimore, MD 21218, USA
 }
@@
 Our sample includes; 257 `Barium stars' that show enhancement in both barium and strontium, 49 stars showing only significant barium enhancement, and 661 exhibiting only strontium enhancement.
-This sample constitutes the largest number of s-process enhanced stars ever discovered, and represents the most comprehensive search for Barium stars in the Milky Way.
+This sample constitutes the largest number of s-process enhanced stars ever discovered.
 We find up to 51 Barium stars exhibit some evidence of technetium from LAMOST spectra, and most (46/51) have $\log{g}>2$, which suggests they cannot be AGB stars and may indicate a recent ($<1\,\textrm{Myr}$) mass accretion event.
 Most (178/257) Barium stars in our sample show strong carbon enhancement, consistent with the literature.
-However, despite previous claims indicating that Barium stars are preferentially enhanced in sodium due to the NeNa nucleosynthesis cycle occurring in massive AGB stars, only 5 ($<2$\,\%) of our Barium stars show any evidence of enhancement in sodium.
-A comparison with AGB yields suggests that the majority of our sample are consistent with a bottom-heavy IMF.
+However, despite previous claims indicating that Barium stars are preferentially enhanced in sodium due to the NeNa nucleosynthesis cycle occurring in massive AGB stars, only 5 ($<2$\,\%) of our Barium stars show any evidence of sodium enhancement.
+A comparison with AGB yields suggests that the majority of our sample are consistent with a bottom-heavy initial mass function.
 When binary properties become available from end-of-mission Gaia astrometry, this sample of s-process stars will be critical in explaining mass transfer in binary systems and refining AGB yields across a range of masses and metallicities.
@@
 During the TP-AGB phase, enrichment on the surface in $^{12}$C and heavy elements produced by the s-process is a result of the repeated downwash extensions of TDU \citep[e.g.,][]{busso2001}.
-The star contracts PDU and reignites the H-shell producing the majority of the surface luminosity for the next interpulse period.
+The star contracts after dredge up and reignites the H-shell producing the majority of the surface luminosity for the next interpulse period.
 The interpulse, thermal pulse, and dredge up cycle may occur numerous times and is dependent on the initial mass, composition, and mass-loss rate of the star.
@@
 The relationship between Barium stars in the halo \citep[e.g.,][]{junqueira2001,drake2008,pereira2009,allen2006} and metal-poor, yellow, symbiotic halo stars has been established by \citet{jorissen2005} and \citet{pereira2009}.
-Additionally, \citet{pereira2011} concludes that metal-rich Barium stars share similar kinematics to other metal-rich and super metal-rich stars already analysed, suggesting that they do not belong to the bulge population.
-Furthermore, it is necessary to establish known abundances of s-process elements in a greater sample of Barium stars in order to compare their birth rate to theoretical expectations \citep{han1995}, explore the binary fraction at different metallicities, and compare to AGB star yields at different masses and metallicities.
+\citet{pereira2011} also concludes that metal-rich Barium stars share similar kinematics to other metal-rich and super metal-rich stars already analysed, suggesting that they do not belong to the bulge population.
+It remains necessary to establish known abundances of s-process elements in a greater sample of Barium stars in order to compare their birth rate to theoretical expectations \citep{han1995}, explore the binary fraction at different metallicities, and compare to AGB star yields at different masses and metallicities.
 
@@
 Specifically, we identified Barium stars by searching for \ion{Ba}{II} and \ion{Sr}{II} enhancement at the 4554\,\AA\ and 4077\,\AA\ wavelengths, respectively.
-A negative residual, as shown in a candidate Barium star in Figure \ref{fig:figure1}, illustrates an enhancement in \ion{Ba}{II} and \ion{Sr}{II} at lines 4554\,\AA\, 4077\,\AA.
+A negative residual, as shown in a candidate Barium star in Figure \ref{fig:figure1}, illustrates an enhancement in \ion{Ba}{II} and \ion{Sr}{II} at lines 4554\,\AA\, and 4077\,\AA, respectively.
 These \ion{Ba}{II} and \ion{Sr}{II} resonance lines are very strong, allowing us to identify stars enhanced in neutron-capture elements given a well-fit model for the data.
@@
 For the remainder of this paper we restrict our analysis to the 257 classical `Barium stars' stars that show enhancement in both barium and strontium.
-While the 49 or 661 stars with only barium or strontium enhancements (respectively) may also be bonafide barium stars, there may be other explanations for their chemical abundance pattern \citep[e.g.,][]{maiorca2011}, and so we restrict our inferences to a gold sample of Barium stars.
-Nevertheless, this sample still constitutes the largest collection of Barium stars ever discovered; the stellar sample given in \citet{decastro2016} constitutes the next largest Barium star candidate list.
+While the 49 or 661 stars with only barium or strontium enhancements (respectively) may also be bonafide barium stars, there may be other explanations for their chemical abundance pattern \citep[e.g.,][]{maiorca2011}, and so we restrict our inferences to a `gold sample' of Barium stars.
+Nevertheless, this sample still constitutes the largest collection of Barium stars ever discovered \citep[e.g.,][]{decastro2016}.
 
@@
 	\includegraphics[width=\textwidth]{posterchild.png}
-    \caption{Pseudo-continuum-normalised LAMOST spectra for the s-process candidate \todo{CANDIDATENAME}.
+    \caption{Pseudo-continuum-normalised LAMOST spectra for the s-process candidate J064451.11+263239.2.
 The data are shown in black and the best-fitting data-driven model is shown in red.
@@
 & Dec.
-& $v_{r}$ & S/N & $\rm T_{\rm eff}$ & $\log{g}$ & [Fe/H] & [$\alpha$/Fe] & $\chi_r^2$ & [Ba/Fe] & [Sr/Fe] & \ion{Ba}{II} & \ion{Sr}{II} &  \ion{Ba}{II}\& \ion{Sr}{II} & Tc\\
+& $v_{r}$ & S/N & $\rm T_{\rm eff}$ & $\log{g}$ & [Fe/H] & [$\alpha$/Fe] & $\chi_r^2$ & [Ba/Fe] & [Sr/Fe] & \ion{Ba}{II} & \ion{Sr}{II} &  \ion{Ba}{II} \& \ion{Sr}{II} & Tc\\
 & (J2000) & (J2000) & (km\,s$^{-1}$) & (pixel$^{-1}$) & (K)  \\ \midrule
@@
 J000552.76+261849.3 & 00:05:52.76 & +26:18:49.4 & -22.5 & 73      & 4924         & 3.14         & -0.05        & 0.09             & 0.67               & 0.28        & 0.85        & \ding{55} & \ding{51}  & \ding{55} & \ding{55}    \\
-J000737.70+394055.5 & 00:07:37.70 & +39:40:55.6 & -31.5 & 33      & 4700         & 2.80         & -0.04        & 0.07             & 0.28               & -0.13       & 0.81        & \ding{55} & \ding{51}  & \ding{55} & \ding{55}
+J000737.70+394055.5 & 00:07:37.70 & +39:40:55.6 & -31.5 & 33      & 4700         & 2.80         & -0.04        & 0.07             & 0.28               & -0.13       & 0.81        & \ding{55} & \ding{51}  & \ding{55} & \ding{55}     \\ \hline
 \end{tabular}
@@
 
-For technetium enhancement we searched for significant residual deviations at the 4049\,\AA, 4238\,\AA, 4262\,\AA, 4297\,\AA, and 5924\,\AA.
+For technetium enhancement we searched for significant residual deviations at 4049\,\AA, 4238\,\AA, 4262\,\AA, 4297\,\AA, and 5924\,\AA.
 These absorption lines are extremely weak, and would require a substantial amount of technetium before it would be visible in a high S/N LAMOST spectrum.
@@
 Finally, for carbon enhancement we searched for significant deviations at the CH and G band near 4300\,\AA.
-We found 178/257 stars to show significant carbon enhancement (e.g., $[\textrm{C/Fe}] \gtrsim 0.5$).
+We found 178/257 stars to show significant carbon enhancement (i.e., $[\textrm{C/Fe}] \gtrsim 0.5$).
 
-\subsubsection{Abundance analysis from LAMOST spectra}
+\subsubsection{Abundances estimated from LAMOST spectra}
 We estimated [Ba/Fe] and [Sr/Fe] abundance ratios for all s-process candidates by synthesising spectra that would account for the observed flux residuals.
-We assumed that absorption due to metals is captured by \emph{The Cannon} model, and deviations in flux at the 4554\,\AA\ \ion{Ba}{II} line and the 4077\,\AA\ \ion{Sr}{II} transition are solely due to enhancements in Ba and Sr, respectively\citep{marcs,sme,vald,ispec}.
+We assumed that absorption due to metals is captured by \emph{The Cannon} model, and deviations in flux at the 4554\,\AA\ \ion{Ba}{II} line and the 4077\,\AA\ \ion{Sr}{II} transition are solely due to enhancements in Ba and Sr, respectively \citep{marcs,sme,vald,ispec}.
 We adopted the stellar parameters ($T_{\rm eff}$, $\log{g}$, [Fe/H]) from \citep{ho2017}, and assume a microturbulence of $v_{mic} = 2\,{\rm km\,s}^{-1}$.
@@
 
-\subsubsection{Observations}
-On the night of \todo{X} January 2018 we performed follow-up observations of \todo{X} Barium star candidates using the MIKE spectrograph on the Magellan Clay telescope at Las Campanas Observatory, Chile.
-Candidates for follow-up observations were chosen based on observability constraints and ranked by their apparent visual magnitude.
-We observed \todo{X} stars in good seeing using the 0.7 arcsecond slit and 2x2 spatial on-chip binning, which provides a spectral resolution of ($\mathcal{R} \approx \todo{22,000}$).
-Exposure times were set to achieve a S/N ratio of 30 per pixel at 4500\,\AA.
+\subsubsection{Observations and data reduction}
+On the night of 07 January 2018 we acquired a high-resolution spectrum of two Barium star candidates (J09162834+0259348 and J08351472-0548480) using the MIKE spectrograph on the Magellan Clay telescope at Las Campanas Observatory, Chile.
+Candidates for follow-up observations were chosen based on observability constraints and ranked by their apparent visual magnitude, with both candidates having $V \approx 12$.
+We observed both stars in good seeing using the 0.7 arcsecond slit and 2x2 spatial on-chip binning, providing a spectral resolution of ($\mathcal{R} \approx 28,000$).
+Exposure times of 100 seconds were sufficient to achieve a S/N ratio exceeding 30 per pixel at 4500\,\AA.
 We acquired calibration (biases, milky, quartz, and Th-Ar arc lamp) frames in the afternoon.
@@
 We adopted the stellar parameters ($T_{\rm eff}$, $\log_{10}g$, [Fe/H]) provided from the data-driven analysis of \citep{ho2017}.
-Following the procedure outlined in \citep{casey2014}, we measured the strength of atomic absorption lines by fitting Gaussian profiles to the continuum-normalised spectra.
-Most elemental abundances were derived directly from these line measurements, except for elements that show significant hyperfine splitting \todo{(e.g., )} or blending \todo{(e.g., X)}.
-In these situations, we adopted a spectral synthesis approach.
-\todo{citations for line lists}
-
-\todo{Some sentences for our fearless leader to add regarding abundance analysis and verification of stellar parameters from LAMOST}
+Following the procedure outlined in \citep{casey2014}, we measured the strength of \ion{Ba}{II} (4554\,\AA, 4934\,\AA, and 6496\,\AA) and \ion{Sr}{II} (4077\,\AA\ and 4215\,\AA) absorption lines by spectral synthesis, using s-process isotopic ratios from \citet{sneden08}.
+The abundance ratios we estimate from high-resolution spectra are in excellent agreement with our estimates from LAMOST spectra, all agreeing within the joint $1.2\sigma$.
+Specifically, for J09162834+02593480 from high- and low-resolution spectra, respectively, we find $[{\rm Sr/Fe}] = 0.76 \pm 0.10$ and $0.85 \pm 0.21$, and $[{\rm Ba/Fe}] = 0.92 \pm 0.10$ and $0.77 \pm 0.21$.
+The biggest discrepancy we find between high- and low-resolution spectra is [Sr/Fe] for J09162834+0259348, where we find $[{\rm Sr/Fe}] = 0.62 \pm 0.07$ and $0.90 \pm 0.22$ from Magellan/MIKE and LAMOST, respectively.
+Finally, for J09162834+0259348 we find $[{\rm Ba/Fe}] = 0.94 \pm 0.12$ from high-resolution spectra and $[{\rm Ba/Fe}] = 0.80 \pm 0.26$ from low-resolution spectra.
+Uncertainties on abundances derived from high-resolution spectra are taken as the standard deviation of multiple line measurements.
 
@@
 A$\&$A, 132, 326
+\bibitem[Sneden et al.(2008)]{sneden08} Sneden, C., Cowan, J.~J., \& Gallino, R.\ 2008, \araa, 46, 241 
 \bibitem[\protect\citeauthoryear{Takeda et al.}{2008}]{takeda2008}

### 2018-02-06 article/ms.tex
add seln fun things

@@
 Specifically, for J09162834+02593480 from high- and low-resolution spectra, respectively, we find $[{\rm Sr/Fe}] = 0.76 \pm 0.10$ and $0.85 \pm 0.21$, and $[{\rm Ba/Fe}] = 0.92 \pm 0.10$ and $0.77 \pm 0.21$.
-The biggest discrepancy we find between high- and low-resolution spectra is [Sr/Fe] for J09162834+0259348, where we find $[{\rm Sr/Fe}] = 0.62 \pm 0.07$ and $0.90 \pm 0.22$ from Magellan/MIKE and LAMOST, respectively.
+The biggest discrepancy we find between high- and low-resolution spectra is [Sr/Fe] for J09162834+0259348, where we find $[{\rm Sr/Fe}] = 0.62 \pm 0.07$ from our Magellan/MIKE spectra, and $0.90 \pm 0.22$ from LAMOST.
 Finally, for J09162834+0259348 we find $[{\rm Ba/Fe}] = 0.94 \pm 0.12$ from high-resolution spectra and $[{\rm Ba/Fe}] = 0.80 \pm 0.26$ from low-resolution spectra.
 Uncertainties on abundances derived from high-resolution spectra are taken as the standard deviation of multiple line measurements.
+The high-resolution abundances we find help validate our methodology for candidate selection, and for estimating abundances from LAMOST spectra.
 
@@
 We integrated galactic orbits for 21 Barium stars using recent astrometry from Gaia/TGAS \citep{gaia2016a,gaia2016b}.
-Using the \texttt{gala} Python package, we integrated each star backwards for $0.5\,\textrm{Gyr}$ in a Milky Way-like potential that consists of four components: a \citet{hernquist1990} bulge and nucleus, a \citet{miyamoto1975} disk, and the \citet{nfw1997} halo.
+Using the \texttt{gala} Python package \citep{price2017}, we integrated each star backwards for $0.5\,\textrm{Gyr}$ in a Milky Way-like potential that consists of four components: a \citet{hernquist1990} bulge and nucleus, a \citet{miyamoto1975} disk, and the \citet{nfw1997} halo.
 In this potential, the disk and bulge parameters were adjusted to be consistent with previous work \citep{bovy2015}, and to vary the scale mass and radius, of the nucleus and halo, respectively.
@@
 In comparison, we find our Barium candidates constitute greater than 70\% extrinsic, this suggests the construction of our data-driven model may have missed some AGB Barium candidates, or that previous studies were biased towards finding luminous intrinsic AGB Barium stars.
+Given that our analysis limits us to only giant stars, such that we do not find any extrinsic Barium stars on the main-sequence, na\"ively we would expect that our sample would be biased \emph{towards} finding a higher fraction of intrinsic AGB Barium stars.
+Despite this expected bias against extrinsic Barium stars, fully 70\% of our sample are extrinsic Barium stars, suggesting unaccounted selection biases in previous studies towards luminous intrinsic Barium stars.
 
@@
 LAMOST is operated and managed by the National Astronomical Observatories, Chinese Academy of Sciences.
+This work has made use of data from the European Space Agency (ESA) mission Gaia (http://www.cosmos.esa.int/gaia), processed by the Gaia Data Processing and Analysis Consortium (DPAC, http://www.cosmos.esa.int/web/gaia/dpac/consortium).
+Funding for the DPAC has been provided by national institutions, in particular the institutions participating in the Gaia Multilateral Agreement.
 

### 2018-02-06 article/ms.tex
text  done

@@
 It's important to note sodium enhancement can occur due to the presence of interstellar dust.
-Using the IRSA's all-sky dust map \citep{schlafly2011}, we find that 2 of 5 of these stars have strong ($\approx$0.35) E(B-V) values, suggesting that the flux residuals around the Na doublet are due to interstellar absorption.
+Using the IRSA's all-sky dust map \citep{schlafly2011}, we find that 2 of 5 of these stars have E(B-V)$\approx$ 0.35, suggesting that the flux residuals around the Na doublet are due to interstellar absorption.
 However, 3 exhibit low ($\approx$0.045) E(B-V) values, indicating the enhancement is more likely due to stellar absorption.
@@
 The final surface s-process index [hs/ls], shown in \citet{cristallo2015} and illustrated in Figure \ref{fig:figure3}, highlights the relationship between [hs/ls] yields and the mass of AGB stars.
-The Salpeter IMF predicts the majority of stars in the Milky Way will be at lower mass, and as predicted the [hs/ls] values of our Barium stars approximately fit the lower mass yields as seen in Figure \ref{fig:figure3}.
-Our Barium candidates not fitting this relationship represent the possibly more massive AGB stars (intrinsic Barium stars) within our sample.
+The Salpeter initial mass function (or any bottom-heavy initial mass function) predicts the majority of stars in the Milky Way will have lower masses, and as predicted the [hs/ls] values of our Barium stars approximately fit the lower mass yields as seen in Figure \ref{fig:figure3}.
+Our Barium candidates not fitting this relationship represent the possibly more massive, and expectedly rarer, AGB stars (intrinsic Barium stars) within our sample.
 
@@
 Despite our noisy estimates of [Ba/Fe] and [Sr/Fe] from LAMOST spectra, comparisons with AGB yields indicate that our sample is consistent with a bottom-heavy initial mass function.
-We encourage follow-up observations with high-resolution spectrographs in order to precisely measure neutron-capture abundances (including [hs/ls] ratios).
+We encourage follow-up observations with high-resolution spectrographs in order to precisely measure a full suite of neutron-capture abundances.
 These data would permit the most detailed comparisons with AGB star yields ever considered.

### 2018-02-06 article/ms.tex
add acks
typo
add fig3

@@
 A.~Y.~Q. Ho,$^{3}$
-J.~C. Lattanzio,$^{1}$
-K.~C. Schlaufman,$^{4}$
+J.~C. Lattanzio,$^{1}$ and
+K.~C. Schlaufman$^{4}$
 \\
@@
 \begin{figure}
-	\includegraphics[width=\columnwidth]{basrtest4.png}
-    \caption{Metallicities ([Fe/H]; x-axis) and heavy-to-light s-process abundance ratios ([hs/ls], taken as [Ba/Sr]; y-axis) for 257 Barium star candidates. \todo{Add Cristillo yields}}
+	\includegraphics[width=\columnwidth]{yields.pdf}
+    \caption{Metallicities ([Fe/H]; x-axis) and heavy-to-light s-process abundance ratios ([hs/ls], taken as [Ba/Sr] as measured from LAMOST; y-axis) for 257 Barium star candidates.
+Coloured lines indicate surface [hs/ls] yields from \citet{cristallo2015} for different masses.}
     \label{fig:figure3}
@@
 \section*{Acknowledgements}
-We thank Alex Ji (Carnegie Observatories) for useful discussions.
+We thank Alex Ji (Carnegie Observatories), David W. Hogg (NYU), Melissa Ness (Columbia), and Hans-Walter Rix (MPIA) for useful discussions. 
 A.~R.~C. is supported through an Australian Research Council Discovery Project under grant DP160100637.

### 2018-02-06 article/plot_yields.py

@@ -1,0 +1,68 @@
+import numpy as np
+import matplotlib.pyplot as plt
+from matplotlib.ticker import MaxNLocator
+from astropy.table import Table
+
+data = Table.read("Bastar_candidates_with_abundances.csv")
+
+ba = np.vstack([data["BA_FE_4554"], data["BA_FE_4934"]])
+ba_err = np.vstack([data["BA_FE_4554_err"], data["BA_FE_4934_err"]])
+
+sr = np.vstack([data["SR_FE_4077"], data["SR_FE_4215"]])
+sr_err = np.vstack([data["SR_FE_4077_err"], data["SR_FE_4215_err"]])
+
+sr_avg = np.nanmean(sr, axis=0)
+ba_avg = np.nanmean(ba, axis=0)
+
+ba_err[(ba_err == 0) + ~np.isfinite(ba_err)] = 0.20
+sr_err[(sr_err == 0) + ~np.isfinite(sr_err)] = 0.20
+
+ba_err = np.nanmean(ba_err, axis=0)
+sr_err = np.nanmean(sr_err, axis=0)
+
+hs_ls = ba_avg - sr_avg
+hs_ls_err = np.sqrt(0.2**2 +  ba_err**2 + sr_err**2)
+
+fig, ax = plt.subplots(figsize=(4, 4))
+
+ax.scatter(data["cannon_m_h_1"], hs_ls,
+           facecolor="#000000", edgecolor="#000000", linewidths=1, s=5, zorder=5,
+           label="_")
+ax.errorbar(data["cannon_m_h_1"], hs_ls,
+            xerr=data["cannon_m_h_err_1"], yerr=hs_ls_err,
+            fmt=None, ecolor="#BBBBBB", elinewidth=1, label="_")
+
+
+cristallo = Table.read("cristallo_data.csv")
+fehs = np.array(cristallo.dtype.names[1:]).astype(float)
+
+masses = cristallo["Mass/[Fe/H]"]
+
+colors = {
+    "2.0": "r",
+    "3.0": "g",
+    "4.0": "m",
+    "5.0": "b",
+    "6.0": "k"
+}
+
+for i, mass in enumerate(masses):
+    model_hs_ls = [cristallo[feh][i] for feh in cristallo.dtype.names[1:]]
+    ax.plot(fehs, model_hs_ls, label=r"${{{:.1f}}}\,M_\odot$".format(mass),
[…]

### 2018-02-18 article/ms.tex
close to submit

@@
 
-\author[B.~J. Norfolk et al.]{B.~J. Norfolk,$^{1}$\thanks{E-mail: bjee7@student.monash.edu (MU)}
-A.~R. Casey,$^{1,2}$
-M.~T. Miles,$^{1}$
-A.~J. Kemp,$^{1}$ 
-A.~I. Karakas,$^{1}$\newauthor
-A.~Y.~Q. Ho,$^{3}$
-J.~C. Lattanzio,$^{1}$ and
-K.~C. Schlaufman$^{4}$
+\author[Brodie.~J.
+Norfolk et al.]{B.~J.
+Norfolk,$^{1}$\thanks{E-mail: bjee7@student.monash.edu (MU)}\thanks{This paper includes data gathered with the 6.5 meter Magellan Telescopes located at Las Campanas Observatory, Chile.}
+Andrew.~R. Casey,$^{1,2}$
+Matthew T. Miles,$^{1}$
+Alex J. Kemp,$^{1}$ \newauthor
+Amanda I. Karakas,$^{1}$
+Melissa Ness,
+Kevin C. Schlaufman$^{4}$,
+Anna Y.~Q. Ho,$^{3}$, \newauthor
+and John C. Lattanzio,$^{1}$
 \\
@@
 \begin{abstract}
-Stars with peculiar enhancements of carbon and heavy elements ($Z > 30$) are historically referred to as `Barium stars'.
-While this chemical abundance pattern can be explained by thermally pulsing asymptotic giant branch (AGB) stars, many so-called Barium stars have not evolved through the red giant phase and therefore cannot be AGB stars.
-These less-evolved stars are generally thought to have accreted mass from a more-evolved AGB companion.
-For this reason the frequency and properties of less-evolved Barium stars are uniquely informative on the binary fraction, AGB yields, mass transfer, and stellar evolution.
-Here we present the discovery of 967 s-process candidates from 454,180 giant stars observed by LAMOST.
-Our sample includes; 257 `Barium stars' that show enhancement in both barium and strontium, 49 stars showing only significant barium enhancement, and 661 exhibiting only strontium enhancement.
-This sample constitutes the largest number of s-process enhanced stars ever discovered.
-We find up to 51 Barium stars exhibit some evidence of technetium from LAMOST spectra, and most (46/51) have $\log{g}>2$, which suggests they cannot be AGB stars and may indicate a recent ($<1\,\textrm{Myr}$) mass accretion event.
-Most (178/257) Barium stars in our sample show strong carbon enhancement, consistent with the literature.
-However, despite previous claims indicating that Barium stars are preferentially enhanced in sodium due to the NeNa nucleosynthesis cycle occurring in massive AGB stars, only 5 ($<2$\,\%) of our Barium stars show any evidence of sodium enhancement.
-A comparison with AGB yields suggests that the majority of our sample are consistent with a bottom-heavy initial mass function.
-When binary properties become available from end-of-mission Gaia astrometry, this sample of s-process stars will be critical in explaining mass transfer in binary systems and refining AGB yields across a range of masses and metallicities.
+
+In this paper we present the discovery of 967 s-process candidates from 454,180 giant stars observed by LAMOST: this sample constitutes the largest number of s-process enhanced stars ever discovered.
+We identify these stars in the LAMOST sample by using a data-driven search approach on the spectra directly and then measure the s-process abundance enhancements directly using stellar synthesis.
+Finally, we validate our results using high resolution spectra of a number of candidates.
+Our sample includes; 257 'barium stars', that are enhanced in both barium and strontium, 49 stars with significant barium enhancement only, and 661 stars which exhibit strontium enhancement only.
+Our entire barium star stellar sample exists within temperature and luminosity ranges not enveloped by the AGB, which may indicate a recent ($<1\,\textrm{Myr}$) mass accretion event from an AGB companion.
+Most of our barium stars ($69\%$) show strong carbon enhancements, only 5 candidates ($<2$\,\%) show evidence of sodium enhancement.
+In contrast with previous claims of preferential sodium enhancement, we argue this may have been a selection bias in previous studies.
+A comparison with AGB yields suggests that the majority of our sample are consistent with Salpeter-like initial mass function, with pollution from a low mass AGB star.
+
+%The abundances of the slow neutron capture process (s-process) elements in stars are a measure of the nucleosyntheic processes that occur primarily in Asymptotic Giant Branch (AGB) stars.
+Due to their associated enrichment of the s-process element barium, stars with peculiar enhancements of carbon and heavy elements (Z > 30) are historically referred to as 'barium stars'.
+Here, we present the discovery of 967 s-process candidates from 454,180 giant stars observed by LAMOST: this sample constitutes the largest number of s-process enhanced stars ever discovered.
+We identify these stars in the LAMOST sample by using a data-driven search approach on the spectra directly and then measure the s-process abundance enhancements directly using stellar synthesis.
+Finally, we validate our results using high resolution spectra of a number of candidates.
+Our sample includes; 257 'barium stars', that are enhanced in both barium and strontium, 49 stars with significant barium enhancement only, and 661 stars which exhibit strontium enhancement only.
+The unusual chemical abundance patterns of barium stars can be explained if these are in the AGB of stellar evolution.
+However, many barium stars  have not yet evolved through the red giant phase.
+Instead, these less evolved 'barium stars' are generally thought to have accreted mass from a more evolved AGB companion.
+Our entire barium star stellar sample exists within temperature and luminosity ranges not enveloped by the AGB, which may indicate a recent ($<1\,\textrm{Myr}$) mass accretion event from an AGB companion.
+These less evolved stars are uniquely informative on the binary fraction, AGB yields, mass transfer and stellar evolution.
+A comparison with AGB yields suggests that the majority of our sample are consistent with Salpeter-like initial mass function, with pollution from a low mass AGB star.
+Most of our barium stars (put in percentage) show strong carbon enhancements, consistent with mass transfer from a low-mass AGB companion.
+Although, only 5 candidates ($<2$\,\%) show evidence of sodium enhancement, in contrast with previous claims of preferential sodium enhancement, we argue this may have been a selection bias in previous studies.
+When binary properties become available from end-of-mission Gaia astrometry, our sample of s-process stars will be critical in explaining mass transfer in binary systems and refining AGB yields across a range of masses and metallicities.
+
 \end{abstract}
@@
 
-Barium stars as first recognised by \citet{Bidelman1951}, are chemically unique objects that exhibit envelopes with an overabundance of carbon and heavy elements (Z > 30) in comparison to the Sun.
-Barium stars exist as either intrinsic or extrinsic objects; intrinsic Barium stars are in the TP-AGB (thermally pulsing-asymptotic giant branch) phase, where the overabundance of both carbon and heavy elements are produced through the s-process and exist on the surface as the result of a thermal pulsing cycle.
-According to the mass-transfer hypothesis, extrinsic Barium stars are a consequence of stellar wind accretion \citep{boffin1988,jorissen1992} or Roche-lobe overflow \citep{webbink1986}, and are within a binary system containing a previous TP-AGB companion star (intrinsic Barium star) in its final phase as a white dwarf \citep{bohm1980,bohm1984}.
-In fact, \citet{mcclure1983} determines 85\% of all Barium stars are in binary systems and claims that those that appear singular are actually pole-on, or highly eccentric binaries with significant radial velocity variations only occurring in a small phase range as detailed by \citet{pourbaix2004}.
-For these reasons, the properties and occurrence rate of Barium stars are informative of the theoretical birth rate of AGB stars, the binary star fraction as a function of metallicity, the mass ratio of binary stars, as well as AGB yields across different masses and metallicities.
+Barium stars as first recognised by \citet{Bidelman1951}, are chemically unusual objects that exhibit envelopes with an overabundance of carbon and heavy elements (Z > 30) in comparison to the Sun.
+Barium enhanced stars exist as either intrinsic or extrinsic objects, stars intrinsically enhanced in barium and other s-process elements are known as AGB S stars.
+These stars are in the TP-AGB (thermally pulsing-asymptotic giant branch) phase, where the overabundance of both carbon and heavy elements produced through the slow neutron capture process and exist on the surface as the result of a thermal pulsing cycle.
+According to the mass-transfer hypothesis, extrinsic barium stars are a consequence of stellar wind accretion \citep{boffin1988,jorissen1992} or Roche-lobe overflow \citep{webbink1986}, and are within a binary system containing a previous TP-AGB companion star (AGB S star) in its final phase as a white dwarf \citep{bohm1980,bohm1984}.
+In fact, \citet{mcclure1983} determined 85\% of all barium stars are in binary systems and claimed that those that appear to be singular are actually pole-on, or highly eccentric binaries with significant radial velocity variations only occurring in a small ranges as detailed by \citet{pourbaix2004}.
+For these reasons, the properties and occurrence rate of barium stars are informative of the binary star fraction as a function of metallicity, the mass ratio of binary stars, as well as AGB yields across different masses and metallicities.
 
-The slow neutron capture process (s-process), occurring in the interior of AGB stars, synthesises roughly half of all elements heavier than iron \citep[e.g.,][]{busso1999,travaglio2001,herwig2005,romano2010,kobayashi2011,prantzos2012,bisterzo2014,karakas12016}.
-Late in the AGB phase, during the thermally pulsing-AGB (TP-AGB) phase, thermal instabilities occur in the He shell every $10^5$ years or so, depending on the H-exhausted core mass.
-These energy bursts drive a convective zone that sweeps the entire region lying between the core mass and He-shell; mixing the products of nucleosynthesis within these regions.
-The energy from the thermal pulses force the star to expand, pushing the H-shell out to cooler regions and allowing the convective envelope to move inwards to regions previously mixed by the thermal pulse driven convective zones.
-This expansion and resulting inward movement is described as the third dredge up (TDU), and is theorised to occur after each thermal pulse.
-During the TP-AGB phase, enrichment on the surface in $^{12}$C and heavy elements produced by the s-process is a result of the repeated downwash extensions of TDU \citep[e.g.,][]{busso2001}.
-The star contracts after dredge up and reignites the H-shell producing the majority of the surface luminosity for the next interpulse period.
-The interpulse, thermal pulse, and dredge up cycle may occur numerous times and is dependent on the initial mass, composition, and mass-loss rate of the star.
+The slow neutron capture process (s-process), occurring in the interior of AGB stars, synthesises roughly half of all elements heavier than iron \citep[e.g.,][]{busso1999,travaglio2001,herwig2005,bisterzo2014,fishlock2014}.
+Late in the AGB phase, during the TP-AGB phase, thermal instabilities occur in the He shell every $10^5$ years or so, depending on the mass of the H-exhausted core.
+These energy bursts drive a convective zone that sweeps almost the entire region lying between the core and the He-shell, mixing the products of nucleosynthesis within these regions.
+The energy from the thermal pulses forces the star to expand, pushing the H-shell out to cooler regions and allowing the convective envelope to move inwards to regions previously mixed by the thermal pulse driven convective zones.
+This phase of expansion and resulting inward movement called the third dredge up (TDU), and is theorised to occur after each thermal pulse.
+During the TP-AGB phase, surface enrichment in $^{12}$C and heavy elements produced by the s-process, is a result of the repeated inward extensions of TDU \citep[e.g.,][]{busso2001}.
+The star contracts post dredge up and reignites the H-shell producing the majority of the surface luminosity for the next interpulse period.
+The interpulse, thermal pulse, and dredge up cycle may occur numerous times, and its frequency is dependent on the initial mass, composition, and mass-loss rate of the star.
 
-Barium giants form within a metallicity-dependent initial mass range (approximately $0.8 - 8\,M_{\odot}$), with the minimum mass for core helium and carbon burning decreasing as metallicity decreases.
-The age of these stars vary considerably, with some as old as $\approx$12\,Gyr in metal-poor globular clusters.
-In contrast, metal-rich, young observable stars may only reach $\approx$100Myr, this includes stars that are at the core carbon burning limit or very close to it \citep[e.g.,][]{whitelock2013}.
+Barium giants can form within a metallicity-dependent initial mass range of approximately $0.8 - 8\,M_{\odot}$.
+The minimum mass for these giants is defined by the mass needed for core helium and carbon burning, which decrease as metallicity decreases.
+The age of these stars vary considerably, with some as old as $\approx$ 12\,Gyr in metal-poor globular clusters.
+Metal poor stars enhanced in barium are defined in the literature as CH stars.
+In contrast, metal-rich, less massive stars may reach ages of $\approx$ 100Myr, this includes stars that are at the core carbon burning limit or very close to it \citep[e.g.,][]{whitelock2013}.
+Furthermore, metal rich stars enhanced in barium are defined in the literature as Bariu stars.
 
-Many Barium stars have been discovered in the disk and halo of the Milky Way \citep{gomez1997,mennessier1997}. 
-%These studies show that the stellar populations of Barium stars can be separated into two groups when considering their absolute luminosity, kinematic, and spatial properties. 
-The relationship between Barium stars in the halo \citep[e.g.,][]{junqueira2001,drake2008,pereira2009,allen2006} and metal-poor, yellow, symbiotic halo stars has been established by \citet{jorissen2005} and \citet{pereira2009}.
-\citet{pereira2011} also concludes that metal-rich Barium stars share similar kinematics to other metal-rich and super metal-rich stars already analysed, suggesting that they do not belong to the bulge population.
-It remains necessary to establish known abundances of s-process elements in a greater sample of Barium stars in order to compare their birth rate to theoretical expectations \citep{han1995}, explore the binary fraction at different metallicities, and compare to AGB star yields at different masses and metallicities.
+Many barium stars have been discovered in the disk and halo of the Milky Way \citep{gomez1997,mennessier1997}.
+In \citet{pereira2011} it is concluded that metal-rich barium stars share similar kinematics to other metal-rich and super metal-rich stars already analysed, suggesting that they do not belong to the bulge population.
+It remains necessary to establish known abundances of s-process elements in a greater sample of barium stars in order to compare their birth rate to theoretical expectations \citep{han1995}, explore the binary fraction at different metallicities, and to compare to AGB star yields at different masses and metallicities.
+%The relationship between barium stars in the halo \citep[e.g.,][]{junqueira2001,drake2008,pereira2009,allen2006} and metal-poor, yellow, symbiotic halo stars has been established by \citet{jorissen2005} and \citet{pereira2009}.
 
-In this paper we analyse 454,180 giant stars from the second LAMOST data release \citep{luo2015} to identify 967 s-process candidates.
+In this paper we analyse 454,180 giant stars from the second LAMOST data release \citep{luo2015} and identify 967 s-process candidates.
 In Section \ref{sec:methods} we describe the observations and candidate selection, as well as the analysis of high-resolution follow-up observations obtained for a few candidates.
-In Section \ref{sec:dis} we discuss the properties of our Barium stars in context of existing literature.
+In Section \ref{sec:dis} we discuss the properties of our barium stars in context of existing literature.
 We provide concluding remarks in Section \ref{sec:con}.
@@
 Cross-validation experience shows that the typical uncertainties are about 70\,K in effective temperature $\rm T_{\rm eff}$, 0.1\,dex in surface gravity $\log{g}$, 0.1\,dex in metallicity [M/H], and 0.04\,dex in the $\alpha$-element abundance relative to overall metallicity [$\alpha$/M].
-These uncertainties are approximately comparable to the APOGEE uncertainties \citep{alam2015}.
+These uncertainties are comparable to the APOGEE uncertainties \citep{alam2015}.
 
 \subsubsection{Candidate selection} \label{sec:cand}
-The Barium stars analysed in this research were obtained by filtering for significant flux residuals, taken as, a disparity between the normalised LAMOST flux and the data driven model derived by \citet{ho2017}.
-Specifically, we identified Barium stars by searching for \ion{Ba}{II} and \ion{Sr}{II} enhancement at the 4554\,\AA\ and 4077\,\AA\ wavelengths, respectively.
-A negative residual, as shown in a candidate Barium star in Figure \ref{fig:figure1}, illustrates an enhancement in \ion{Ba}{II} and \ion{Sr}{II} at lines 4554\,\AA\, and 4077\,\AA, respectively.
+The barium stars analysed in this research were obtained by filtering for significant flux residuals, taken as a disparity between the normalised LAMOST flux and the data driven model derived by \citet{ho2017}.
+Specifically, we identified barium stars by searching for \ion{Ba}{II} and \ion{Sr}{II} enhancement at the 4554\,\AA\ and 4077\,\AA\ wavelengths, respectively.
+A negative residual, as shown in a candidate barium star in Figure \ref{fig:figure1}, illustrates an enhancement in the \ion{Ba}{II} and \ion{Sr}{II} lines at 4554\,\AA\, and 4077\,\AA, respectively.
 These \ion{Ba}{II} and \ion{Sr}{II} resonance lines are very strong, allowing us to identify stars enhanced in neutron-capture elements given a well-fit model for the data.
-Stars identified to just show high levels of barium (and not necessarily strontium) required enhancement at both the 4554\,\AA\ and 4934\,\AA\ \ion{Ba}{II} resonance lines, and for stars just enhanced in strontium we looked for significant residuals at the 4554\,\AA\ and 4215\,\AA\ absorption lines.
+Stars identified high levels of barium (and not necessarily strontium) required enhancement in both the 4554\,\AA\ and 4934\,\AA\ \ion{Ba}{II} resonance lines, and for stars exclusively enhanced in strontium we looked for significant residuals at the 4077\,\AA\ and 4215\,\AA\ absorption lines.
 
-We used five filters that each spectrum, for each set of absorption lines, had to meet in order to be considered a s-process candidate; these included:
+We used five filters that each spectrum, for each set of absorption lines, had to meet in order to be considered a s-process rich candidate; these included:
 
@@
 \end{enumerate}
-In addition, a visual inspection was undertaken to exclude any results containing, false positives, candidates exhibiting data reduction issues, apparent absorption finer then the spectral resolution, and overly noisy normalised LAMOST spectra.
-This combined method generated 967 s-process candidates including; 257 `Barium stars' enhanced in both barium and strontium, 49 stars exhibiting exclusively barium enhancement, and 661 exhibiting exclusively strontium enhancement, as listed in Table \ref{table:table1}.
+In addition, a visual inspection was undertaken to exclude any results containing false positives, candidates exhibiting data reduction issues, apparent absorption finer then the spectral resolution, and overly noisy normalised LAMOST spectra.
+This combined method generated 967 s-process rich candidates which are provided in Table \ref{table:table1} including; 257 `barium stars' enhanced in both barium and strontium, 49 stars exhibiting exclusively barium enhancement, and 661 exhibiting exclusively strontium enhancement.
 
-For the remainder of this paper we restrict our analysis to the 257 classical `Barium stars' stars that show enhancement in both barium and strontium.
-While the 49 or 661 stars with only barium or strontium enhancements (respectively) may also be bonafide barium stars, there may be other explanations for their chemical abundance pattern \citep[e.g.,][]{maiorca2011}, and so we restrict our inferences to a `gold sample' of Barium stars.
-Nevertheless, this sample still constitutes the largest collection of Barium stars ever discovered \citep[e.g.,][]{decastro2016}.
+For the remainder of this paper we restrict our analysis to the 257 classical `barium stars' stars that show enhancement in both barium and strontium.
+While the 49 or 661 stars with only barium or strontium enhancements (respectively) may also be bonafide barium stars, there may be other explanations for their chemical abundance pattern \citep[e.g.,][]{maiorca2011}, and so we restrict our inferences to a `gold sample' of barium stars.
+Nevertheless, this sample still constitutes the largest collection of barium stars ever discovered, with the next sample of significant size containing 182 barium stars \citep[e.g.,][]{decastro2016}.
 
@@
 \centering
-\caption{Table is available online in its entirety. Here we show a portion to demonstrate its style and content.}
+\caption{Properties of 967 s-process candidates, the table is available online in its entirety. Here we show a portion to demonstrate its style and content.}
 \label{table:table1}
 \begin{adjustbox}{width=1\textwidth}
-\begin{tabular}{@{}|l|l|c|c|c|c|c|c|c|c|c|c|c|c|c|c|@{}}
+\begin{tabular}{@{}|l|l|c|c|c|c|c|c|c|c|c|c|c|c|c|@{}}
 \toprule
@@
 & Dec.
-& $v_{r}$ & S/N & $\rm T_{\rm eff}$ & $\log{g}$ & [Fe/H] & [$\alpha$/Fe] & $\chi_r^2$ & [Ba/Fe] & [Sr/Fe] & \ion{Ba}{II} & \ion{Sr}{II} &  \ion{Ba}{II} \& \ion{Sr}{II} & Tc\\
+& $v_{r}$ & S/N & $\rm T_{\rm eff}$ & $\log{g}$ & [Fe/H] & [$\alpha$/Fe] & $\chi_r^2$ & [Ba/Fe] & [Sr/Fe] & \ion{Ba}{II} & \ion{Sr}{II} &  \ion{Ba}{II} \& \ion{Sr}{II} \\
 & (J2000) & (J2000) & (km\,s$^{-1}$) & (pixel$^{-1}$) & (K)  \\ \midrule
-J000019.26+501444.8 & 00:00:19.27 & +50:14:44.9 & -3.9  & 49      & 4973         & 3.27         & 0.21         & 0.08             & 0.66               & 0.25        & 0.83        & \ding{55} & \ding{51}  & \ding{55} & \ding{55}   \\
-J000020.55+411348.1 & 00:00:20.56 & +41:13:48.2 & -28.2 & 32      & 4882         & 2.74         & -0.22        & 0.04             & 0.23               & -0.17       & 0.90        & \ding{55}& \ding{51}  & \ding{55} & \ding{55}    \\
-J000134.95+490743.2 & 00:01:34.96 & +49:07:43.2 & -42.3 & 72      & 5044         & 3.11         & -0.54        & 0.11             & 0.79               & 1.02        & 0.45        & \ding{55} & \ding{55} & \ding{51}  & \ding{55}   \\
-J000258.09+410730.0 & 00:02:58.10 & +41:07:30.1 & -34.5 & 41      & 4697         & 2.57         & -0.22        & 0.12             & 0.98               & -0.10       & 0.80        & \ding{55} & \ding{51}  & \ding{55}  & \ding{55}   \\
-J000403.80+160257.1 & 00:04:03.80 & +16:02:57.2 & -35.4 & 42      & 5200         & 3.40         & -0.41        & 0.09             & 0.33               & 0.92        & 0.52        & \ding{55} & \ding{55} & \ding{51}  & \ding{55}   \\
-J000439.16+183350.3 & 00:04:39.17 & +18:33:50.4 & -38.7 & 31      & 4601         & 2.50         & 0.44         & 0.03             & 0.34               & -0.11       & 0.88        & \ding{55} & \ding{51}  & \ding{55}  & \ding{55}   \\
-J000444.87+400402.1 & 00:04:44.88 & +40:04:02.1 & -94.7 & 53      & 4172         & 1.46         & -0.08        & 0.09             & 0.72               & 0.03        & 0.91        & \ding{55} & \ding{51}  & \ding{55} & \ding{55}    \\
-J000552.76+261849.3 & 00:05:52.76 & +26:18:49.4 & -22.5 & 73      & 4924         & 3.14         & -0.05        & 0.09             & 0.67               & 0.28        & 0.85        & \ding{55} & \ding{51}  & \ding{55} & \ding{55}    \\
-J000737.70+394055.5 & 00:07:37.70 & +39:40:55.6 & -31.5 & 33      & 4700         & 2.80         & -0.04        & 0.07             & 0.28               & -0.13       & 0.81        & \ding{55} & \ding{51}  & \ding{55} & \ding{55}     \\ \hline
+J000019.26+501444.8 & 00:00:19.27 & +50:14:44.9 & -3.9  & 49      & 4973         & 3.27         & 0.21         & 0.08             & 0.66               & 0.25        & 0.83        & \ding{55} & \ding{51}  & \ding{55}   \\
+J000020.55+411348.1 & 00:00:20.56 & +41:13:48.2 & -28.2 & 32      & 4882         & 2.74         & -0.22        & 0.04             & 0.23               & -0.17       & 0.90        & \ding{55}& \ding{51}  & \ding{55}    \\
+J000134.95+490743.2 & 00:01:34.96 & +49:07:43.2 & -42.3 & 72      & 5044         & 3.11         & -0.54        & 0.11             & 0.79               & 1.02        & 0.45        & \ding{55} & \ding{55} & \ding{51}  \\
+J000258.09+410730.0 & 00:02:58.10 & +41:07:30.1 & -34.5 & 41      & 4697         & 2.57         & -0.22        & 0.12             & 0.98               & -0.10       & 0.80        & \ding{55} & \ding{51}  & \ding{55}  \\
+J000403.80+160257.1 & 00:04:03.80 & +16:02:57.2 & -35.4 & 42      & 5200         & 3.40         & -0.41        & 0.09             & 0.33               & 0.92        & 0.52        & \ding{55} & \ding{55} & \ding{51}  \\
+J000439.16+183350.3 & 00:04:39.17 & +18:33:50.4 & -38.7 & 31      & 4601         & 2.50         & 0.44         & 0.03             & 0.34               & -0.11       & 0.88        & \ding{55} & \ding{51}  & \ding{55}  \\
+J000444.87+400402.1 & 00:04:44.88 & +40:04:02.1 & -94.7 & 53      & 4172         & 1.46         & -0.08        & 0.09             & 0.72               & 0.03        & 0.91        & \ding{55} & \ding{51}  & \ding{55}  \\
+J000552.76+261849.3 & 00:05:52.76 & +26:18:49.4 & -22.5 & 73      & 4924         & 3.14         & -0.05        & 0.09             & 0.67               & 0.28        & 0.85        & \ding{55} & \ding{51}  & \ding{55}  \\
+J000737.70+394055.5 & 00:07:37.70 & +39:40:55.6 & -31.5 & 33      & 4700         & 2.80         & -0.04        & 0.07             & 0.28               & -0.13       & 0.81        & \ding{55} & \ding{51}  & \ding{55}  \\ \hline
 \end{tabular}
@@
 \subsubsection{Enhancements due to sodium, technetium, and carbon}
-We performed an identical analysis to the process described in Section \ref{sec:cand} in order to identify sodium, technetium, or carbon enhancement in our sample of 257 Barium stars.
-We used the sodium doublet lines at 5889\,\AA\ and 5895\,\AA\ to select Barium stars enhanced in sodium, and required significant absorption in both features.
-Only 5/257 Barium stars met this criteria.
+Enhancements in sodium, technetium, and carbon are useful indicators when determining whether a stellar sample is populated by intrinsically enhanced AGB S stars, or polluted extrinsic barium stars.
+We performed an identical analysis to the process described in Section \ref{sec:cand} in order to identify sodium, technetium, or carbon enhancement in our sample of 257 barium stars.
+We used the sodium doublet lines at 5889\,\AA\ and 5895\,\AA\ to select barium stars enhanced in sodium, and required significant absorption in both features.
+Only 5/257 barium stars met this criteria.
 
@@
 These absorption lines are extremely weak, and would require a substantial amount of technetium before it would be visible in a high S/N LAMOST spectrum.
-We found 51 Barium stars exhibited some level of significant enhancement (based on the filters above) at a single technetium line, yet none showed enhancement at more than one technetium line.
+We found that 51 barium stars exhibited some level of significant enhancement (based on the filters above) at a single technetium line, yet none showed enhancement at more than one technetium line.
 We note that the single enhancement near technetium for these 51 stars may be the consequence of data reduction/calibration artefacts, but we include details of which stars matched on technetium in Table \ref{table:table1} nonetheless.
@@
 \subsubsection{Abundances estimated from LAMOST spectra}
-We estimated [Ba/Fe] and [Sr/Fe] abundance ratios for all s-process candidates by synthesising spectra that would account for the observed flux residuals.
+We estimated [Ba/Fe] and [Sr/Fe] abundance ratios for all s-process enhanced candidates by synthesising spectra that would account for the observed flux residuals.
 We assumed that absorption due to metals is captured by \emph{The Cannon} model, and deviations in flux at the 4554\,\AA\ \ion{Ba}{II} line and the 4077\,\AA\ \ion{Sr}{II} transition are solely due to enhancements in Ba and Sr, respectively \citep{marcs,sme,vald,ispec}.
-We adopted the stellar parameters ($T_{\rm eff}$, $\log{g}$, [Fe/H]) from \citep{ho2017}, and assume a microturbulence of $v_{mic} = 2\,{\rm km\,s}^{-1}$.
+We adopted the stellar parameters ($T_{\rm eff}$, $\log{g}$, [Fe/H]) from \citet{ho2017}, and assume a microturbulence of $v_{mic} = 2\,{\rm km\,s}^{-1}$.
 Uncertainties in [Ba/Fe] and [Sr/Fe] from LAMOST are taken as the fitting error due to noise, added in quadrature with an adopted $0.2\,{\rm dex}$ systematic error floor.
 
-\subsection{Follow-up observations with Magellan/MIKE}
+\subsection{Dynamics}
+We integrated galactic orbits for 21 barium stars using recent astrometry from Gaia/TGAS \citep{gaia2016a,gaia2016b}.
+Using the \texttt{gala} Python package \citep{price2017}, we integrated each star backwards for $0.5\,\textrm{Gyr}$ in a Milky Way-like potential that consists of four components: a \citet{hernquist1990} bulge and nucleus, a \citet{miyamoto1975} disk, and the \citet{nfw1997} halo.
+In this potential, the disk and bulge parameters were adjusted to be consistent with previous work \citep{bovy2015}.
+And, it is also used to vary the scale mass and radius, of the nucleus and halo, respectively.
+We computed orbital periods, energy, apocenters, pericenters, eccentricities, and angular momentum in the $z$-direction.
+All 21 stars showed prograde orbits that were consistent with membership in the Milky Way disk, indicating they do not originate from an unusual stellar event.
 
-\subsubsection{Observations and data reduction}
-On the night of 07 January 2018 we acquired a high-resolution spectrum of two Barium star candidates (J09162834+0259348 and J08351472-0548480) using the MIKE spectrograph on the Magellan Clay telescope at Las Campanas Observatory, Chile.
+\section{Follow-up observations with Magellan/MIKE}
+
+\subsection{Observations and data reduction}
+On the night of 07 January 2018 we acquired a high-resolution spectrum of two barium star candidates (J09162834+0259348 and J08351472-0548480) using the MIKE (Magellan Inamori Kyocera Echelle) \citep{bernstein2003} spectrograph on the Magellan Clay telescope \citep{schectman2003} at Las Campanas Observatory, Chile.
 Candidates for follow-up observations were chosen based on observability constraints and ranked by their apparent visual magnitude, with both candidates having $V \approx 12$.
@@
 
-\subsubsection{Abundance analysis}
-We adopted the stellar parameters ($T_{\rm eff}$, $\log_{10}g$, [Fe/H]) provided from the data-driven analysis of \citep{ho2017}.
-Following the procedure outlined in \citep{casey2014}, we measured the strength of \ion{Ba}{II} (4554\,\AA, 4934\,\AA, and 6496\,\AA) and \ion{Sr}{II} (4077\,\AA\ and 4215\,\AA) absorption lines by spectral synthesis, using s-process isotopic ratios from \citet{sneden08}.
+\subsection{Abundance analysis}
+We adopted the stellar parameters ($T_{\rm eff}$, $\log_{10}g$, [Fe/H]) provided from the data-driven analysis of \citet{ho2017}.
+Following the procedure outlined in \citet{casey2014}, we measured the strength of \ion{Ba}{II} (4554\,\AA, 4934\,\AA, and 6496\,\AA) and \ion{Sr}{II} (4077\,\AA\ and 4215\,\AA) absorption lines by spectral synthesis, using s-process isotopic ratios from \citet{sneden08}.
 The abundance ratios we estimate from high-resolution spectra are in excellent agreement with our estimates from LAMOST spectra, all agreeing within the joint $1.2\sigma$.
@@
 
-\subsection{Dynamics}
-We integrated galactic orbits for 21 Barium stars using recent astrometry from Gaia/TGAS \citep{gaia2016a,gaia2016b}.
-Using the \texttt{gala} Python package \citep{price2017}, we integrated each star backwards for $0.5\,\textrm{Gyr}$ in a Milky Way-like potential that consists of four components: a \citet{hernquist1990} bulge and nucleus, a \citet{miyamoto1975} disk, and the \citet{nfw1997} halo.
-In this potential, the disk and bulge parameters were adjusted to be consistent with previous work \citep{bovy2015}, and to vary the scale mass and radius, of the nucleus and halo, respectively.
-We computed orbital periods, energy, apocenters, pericenters, eccentricities, and angular momentum in the $z$-direction.
-All 21 stars showed prograde orbits that were consistent with membership in the Milky Way disk.
-
 \section{Discussion}  \label{sec:dis}
 
-\subsection{Extrinsic and intrinsic Barium stars}
-Barium stars exist as either intrinsic or extrinsic objects.
-Intrinsic Barium stars must be massive enough to reach the TP-AGB phase, and extrinsic Barium stars must be in a binary with a previously polluting TP-AGB star companion.
-Figure \ref{fig:figure2} shows that the majority of our Barium stars have $\log{g} > 2$, highlighting that most stars in our sample are not massive enough to have already reached the TP-AGB phase and therefore, must be extrinsic Barium stars.
-The classification for Barium stars with $\log{g} < 2$ is uncertain: these stars could be intrinsic or extrinsic.
-From here on when we refer to extrinsic Barium stars, we specifically refer to those with $\log{g} > 2$.
-It is noted, in the previous literature \citet{van2017}, only 22\% of their stellar sample are post-main-sequence barium stars (extrinsic barium stars).
-In comparison, we find our Barium candidates constitute greater than 70\% extrinsic, this suggests the construction of our data-driven model may have missed some AGB Barium candidates, or that previous studies were biased towards finding luminous intrinsic AGB Barium stars.
-Given that our analysis limits us to only giant stars, such that we do not find any extrinsic Barium stars on the main-sequence, na\"ively we would expect that our sample would be biased \emph{towards} finding a higher fraction of intrinsic AGB Barium stars.
-Despite this expected bias against extrinsic Barium stars, fully 70\% of our sample are extrinsic Barium stars, suggesting unaccounted selection biases in previous studies towards luminous intrinsic Barium stars.
+\subsection{Extrinsic or intrinsic}
+Barium enhanced stars exist as either intrinsic or extrinsic objects.
+Intrinsically enhanced barium stars must be massive enough to reach the TP-AGB phase, and extrinsic barium stars must be in a binary with a previously polluting TP-AGB star companion (AGB S star).
+Figure \ref{fig:figure2} shows that the majority of our stellar sample exists within temperature and luminosity ranges not enveloped by the AGB, highlighting that all stars in our sample are not evolved enough to have already reached the TP-AGB phase and therefore, must be extrinsic barium stars.
+Although, it is noted, stars with temperatures below 3800K in Figure \ref{fig:figure2} are possible AGB stars, and their intrinsic or extrinsic nature is not certain.
+It is noted, in the previous literature \citep{van2017}, only 22\% of their stellar sample are post-main-sequence barium stars (extrinsic barium stars).
+In comparison, we find that all our barium candidates to be extrinsic.
+This suggests, the construction of our data-driven model may have missed some AGB barium candidates, or that previous studies were biased towards finding luminous intrinsic AGB barium stars.
+Given that our analysis limits us to only giant stars, such that we do not find any extrinsic barium stars on the main-sequence, na\"ively we would expect that our sample would be biased \emph{towards} finding a higher fraction of AGB S stars.
+Despite this expected bias against extrinsic barium stars, our entire barium star sample are extrinsic, suggesting unaccounted selection biases in previous studies towards luminous AGB S stars.
 
@@
 Sodium overabundances observed in the atmospheres of supergiants is thought to be synthesised by the NeNa reaction chain in the convective core of main-sequence stars \citep{el1995}.
-Sodium is transported to the surface of these supergiants via mixing of CNO cycle products during the first dredge-up, although, it is important to note sodium enhancement is not constrained to supergiant stars.
+Sodium is transported to the surface of these supergiants via mixing during the first dredge-up.
+Although, it is important to note, sodium enhancement is not constrained to supergiant stars.
 Stars with a  minimum mass of $1.5\,M_\odot$ can also exhibit enhanced sodium abundances through the NeNa cycle \citep{denissenkov1987}.
-\citet{antipova2004} reported sodium enhancements in 3 of their 16 Barium star candidates, and they relate this to the dredge-up of nuclear-burning material produced by convection during the red-giant phase.
-Moreover, they suggest [Na/Fe] ratios are systematically higher for giants with lower $\log{g}$ values, however, these [Na/Fe] ratios do not exhibit variations in metallicity.
-Similarly, \citet{decastro2016} highlights the possible weak anti-correlation between [Na/Fe] ratio and $\log{g}$, and highlights that this trend in previous studies \citep[e.g.,][]{boyarchuk2002,mishenina2006,luck2007,takeda2008}.
+\citet{antipova2004} reported sodium enhancements in 3 of their 16 barium star candidates, and they relate this to the dredge-up of nuclear-burning material produced by convection during the red-giant phase.
+Moreover, they suggest that [Na/Fe] ratios are systematically higher for giants with lower $\log{g}$ values, however, these [Na/Fe] ratios do not exhibit variations in metallicity.
+Similarly, \citet{decastro2016} highlights the possible weak anti-correlation between [Na/Fe] ratio and $\log{g}$, and highlights that this trend is present in previous studies \citep[e.g.,][]{boyarchuk2002,mishenina2006,luck2007,takeda2008}.
 
-We find $<2$\,\% of our Barium stars show sodium enhancement, contrary to previous studies \citep[e.g.,][]{decastro2016}.
-We also note that the 5 sodium-enhanced Barium stars all have $\log{g} \approx 3$, not at lower $\log{g}$ values as might be expected if low $\log{g}$ values systematically contributed to higher [Na/Fe] abundance ratios.
-It's important to note sodium enhancement can occur due to the presence of interstellar dust.
+We find that $<2$\,\% of our barium stars show sodium enhancement, contrary to previous studies \citep[e.g.,][]{decastro2016}, indicating all s-process enhanced stars will exhibit Na enhancement.
+We also note that the 5 sodium-enhanced barium stars all have $\log{g} \approx 3$, not at lower $\log{g}$ values as might be expected if low $\log{g}$ values systematically contributed to higher [Na/Fe] abundance ratios.
+It is important to note, sodium enhancement can occur due to the presence of interstellar dust.
 Using the IRSA's all-sky dust map \citep{schlafly2011}, we find that 2 of 5 of these stars have E(B-V)$\approx$ 0.35, suggesting that the flux residuals around the Na doublet are due to interstellar absorption.
-However, 3 exhibit low ($\approx$0.045) E(B-V) values, indicating the enhancement is more likely due to stellar absorption.
-These results suggest that sodium-rich material from a companion TP-AGB star has polluted these 3 Barium candidates, but importantly, sodium enhancement is by no means ubiquitous in Barium stars.
+However, 3 exhibit low ($\approx$0.045) E(B-V) values, indicating, the enhancement is more likely due to stellar absorption.
+These results suggest that sodium-rich material from a companion TP-AGB star has polluted these 3 barium candidates, but more importantly, sodium enhancement is by no means ubiquitous in barium stars.
+However, it should be highlighted that low resolution spectra can result in Na line saturation, limiting the flux enhancement even with an abundance enhancement.
 
-The data that led \citet{decastro2016} to conclude that Barium stars have higher [Na/Fe] ratios came from many literature sources.
-Therefore, it is possible that there are systematic differences (biases) between Milky Way studies of normal FGK-type stars and those focussed on Barium stars, leading to unresolved differences in the reported [Na/Fe] abundance ratio.
-These systematic effects would also contribute to the observed correlation between [Na/Fe] and $\log{g}$, since intrinsic Barium stars (by definition) have low $\log{g}$ values.
+The data that led \citet{decastro2016} to conclude that barium stars have higher [Na/Fe] ratios came from many literature sources.
+Therefore, it is possible that there are systematic differences (biases) between Milky Way studies of normal FGK-type stars and those focussed on barium stars, leading to unresolved differences in the reported [Na/Fe] abundance ratio.
+These systematic effects would also contribute to the observed correlation between [Na/Fe] and $\log{g}$, since intrinsic barium stars (by definition) have low $\log{g}$ values.
 We do not observe this correlation between [Na/Fe] and $\log{g}$ in our sample.
-From our data we conclude that Barium stars do not have higher [Na/Fe] abundance ratios on average, and suggest that the effect seen in previous works was due to systematic effects between literature sources.
+From our data we conclude that barium stars do not have higher [Na/Fe] abundance ratios on average, and suggest that the effect seen in previous works was due to systematic effects between literature sources.
 
@@
 
-Technetium has a half life of approximately 211,000 years and as a result, Tc enhacnement is constrained to observations intrinsic Barium stars \citep{jorissen1993} or recently polluted extrinsic Barium stars.
-Our analyse discovered 51 single Tc line matches within our 257 Barium star candidate sample.
-The majority (46/51) have $\log{g} > 2$, suggesting they cannot be AGB stars, and may indicate a recent ($<1\,\textrm{Myr}$) mass accretion event.
+Technetium has a half life of approximately 211,000 years and as a result, the presence of Tc enhacnement is constrained to observations of AGB S stars \citep{jorissen1993} or recently polluted extrinsic barium stars.
+Our analysis discovered 51 single Tc line matches within our 257 barium star candidate sample.
+The majority (46/51) have $\log{g} > 2$, suggesting they cannot be AGB S stars, and may indicate a recent ($<1\,\textrm{Myr}$) mass accretion event.
 However, for Tc to be present in the LAMOST spectra the enhancement must be considerably strong, and given that all 51 matches were at single lines it is concluded that these results are more likely data artefacts.
-In agreement with previous findings \citep[e.g.,][]{little1987,smith1984,smith1983}, the results indicate that none of the evolved Barium stars in our sample exhibited the presence of Tc enhancement, and it can be concluded our Barium star sample is extrinsic.
-However, we caution that Tc enhancement is usually a very weak signature.
+In agreement with previous findings \citep[e.g.,][]{little1987,smith1984,smith1983}, the results indicate that none of the evolved barium stars in our sample exhibited the presence of Tc enhancement, and it can be concluded our barium star sample is extrinsic.
+However, we caution that Tc enhancement is usually a very weak signature, and the presence of Tc would require multiple lines of enhancement.
 
 \subsection{Carbon bands}
-Barium stars are excellent candidates for investigating the relationship between neutron-capture elements and other species that may be depleted or enhanced, since they act as neutron seeds during the operation of the s-process.
+barium stars are excellent candidates for investigating the relationship between neutron-capture elements and other species that may be depleted or enhanced, since iron within these stars act as neutron seeds during the operation of the s-process.
 In the AGB phase the abundance of carbon is a product of helium fusion, specifically the triple-alpha process within a star.
@@
 Giants and supergiants become enhanced in carbon through TDU process discussed in Section \ref{sec:intro}, and extrinsic carbon enhancement occurs via mass transfer from a binary AGB star.
-Our analysis produced 178 CH and G band enhanced stars out of the total 257 Barium candidates.
-Similar to the s-process enhancement, this suggests our candidates are consistent with being either intrinsic or extrinsic Barium stars.
+Our analysis produced 178 CH and G band significantly enhanced stars (i.e., $[\textrm{C/Fe}] \gtrsim 0.5$) out of the total 257 barium candidates.
+These 178 stars exist in a metallicity range of 0 to -1.2, and can be termed "CH stars" are defined in previous literature \citep[e.g.][]{luck1991, mcclure1997}.
+%Similar to the s-process enhancement, this suggests our candidates are consistent with being either intrinsic or extrinsic Barium stars.
 
 \begin{figure}
-	\includegraphics[width=\columnwidth]{hrd.pdf}
-    \caption{Effective temperature $T_{\rm eff}$ and surface gravity $\log{g}$ for 257 candidate Barium stars from LAMOST.
+	\includegraphics[width=\columnwidth]{hrd_new.pdf}
+    \caption{Effective temperature $T_{\rm eff}$ and surface gravity $\log{g}$ for 257 candidate barium stars from LAMOST.
 Stars with $\log{g} > 2$ (as marked) have not evolved through the thermally pulsing asymptotic giant branch phase, and therefore their abundance signature must be the result of an extrinsic pollution event.
@@
 \subsection{Comparison to AGB yields}
-AGB stars, and chemically unique stars that show the chemical signature
-of mass transfer pollution from binary companion AGB stars, highlight the variation of s-process enhancement.
-\citet{karakas_lugaro2016} demonstrates through stellar yield models, that Barium stars will have a likely minimum yield at $[{\rm Fe/H}] \approx -1.2$.
-In Figure \ref{fig:figure3} we show the heavy-to-light s-process abundance ratio (taken as [Ba/Sr]) for all 257 Barium stars identified in LAMOST.
-Although the [hs/ls] ratio is quite noisy, the overall metallicity [Fe/H] is quite precise (0.1\,dex).
-Despite our LAMOST sample of 454,180 giants having metallicities down to about $[{\rm Fe/H}] = -2$, we only detect Barium stars down to metallicities of about $[{\rm Fe/H}] = -1.1$, consistent with expectations from \citep{karakas_lugaro2016}.
+AGB stars, and chemically unusual stars that show the chemical signature of mass transfer pollution from binary companion AGB stars, highlight the variety of s-process enhancement.
+In Figure \ref{fig:figure3} we show the heavy-to-light s-process abundance ratio (taken as [Ba/Sr]) for all 257 barium stars identified in LAMOST.
+Although the [Ba/Sr] ratio is quite noisy, the overall metallicity [Fe/H] is quite precise (0.1\,dex).
+Despite our LAMOST sample of 454,180 giants having metallicities down to about $[{\rm Fe/H}] = -2$, we only detect barium stars down to metallicities of about $[{\rm Fe/H}] = -1.1$.
+Given our barium stars exist in this metallicity range of 0 to -1.1, we can dfeine them as CH stars as done in previous literature \citep[e.g.][]{luck1991, mcclure1997}.
 
-The final surface s-process index [hs/ls], shown in \citet{cristallo2015} and illustrated in Figure \ref{fig:figure3}, highlights the relationship between [hs/ls] yields and the mass of AGB stars.
-The Salpeter initial mass function (or any bottom-heavy initial mass function) predicts the majority of stars in the Milky Way will have lower masses, and as predicted the [hs/ls] values of our Barium stars approximately fit the lower mass yields as seen in Figure \ref{fig:figure3}.
-Our Barium candidates not fitting this relationship represent the possibly more massive, and expectedly rarer, AGB stars (intrinsic Barium stars) within our sample.
+The final surface s-process index [Ba/Sr], shown in \citet{cristallo2015} and \citet{karakas} illustrated in Figure \ref{fig:figure3}, highlights the relationship between [Ba/Sr] yields and the mass of AGB stars.
+The Salpeter initial mass function (or any bottom-heavy initial mass function) predicts the majority of stars in the Milky Way will have lower masses, and as predicted the [Ba/Sr] values of our barium stars approximately fit the lower mass yields as seen in Figure \ref{fig:figure3}.
+It's important to note, our results do not indicate when the mass transfer occured, and our candidates fitting these theoratical yeilds may not have the indicated binary companion masses.
+Instead mass transfer may have occured early on in the AGB S binary companion star's lifespan.
+Additionally, this can be extended to our candidates not approximated by theoratical yeilds.
+Other barium candidates not fitting this relationship represent the possibly more massive, and expectedly rarer, AGB S stars within our sample.
 
 \begin{figure}
-	\includegraphics[width=\columnwidth]{yields.pdf}
-    \caption{Metallicities ([Fe/H]; x-axis) and heavy-to-light s-process abundance ratios ([hs/ls], taken as [Ba/Sr] as measured from LAMOST; y-axis) for 257 Barium star candidates.
+	\includegraphics[width=\columnwidth]{yields_test.pdf}
+    \caption{Metallicities ([Fe/H]; x-axis) and heavy-to-light s-process abundance ratios ([hs/ls], taken as [Ba/Sr] as measured from LAMOST; y-axis) for 257 barium star candidates.
 Coloured lines indicate surface [hs/ls] yields from \citet{cristallo2015} for different masses.}
@@
 We conducted the largest ever search for s-process enhanced stars using the LAMOST second data release.
-From 454,180 giant stars, we identify 967 s-process candidates including: 257 stars with significant enhancements in barium and strontium (so-called `Barium stars'); 49 stars exhibiting exclusively barium enhancement, and 661 exhibiting exclusively strontium enhancement.
-This sample size is greatest total number of Barium stars known, and represents the largest sample of s-process enhanced stars to date.
-Nearly all of our Barium candidates are consistent with being disk stars.
+From 454,180 giant stars, we identify 967 s-process candidates including: 257 stars with significant enhancements in barium and strontium (so-called `barium stars'); 49 stars exhibiting exclusively barium enhancement, and 661 exhibiting exclusively strontium enhancement.
+This sample size is the greatest total number of barium stars known, and represents the largest sample of s-process enhanced stars to date.
+Nearly all of our barium candidates are consistent with being disk stars, indicating our sample was not produced through an unusual galactic event.
 
-We find 178/257 to show carbon enhancement, consistent with the literature.
-However, in contrast with previous works, we do not find Barium stars to have significantly higher [Na/Fe] than Milky Way stars.
-Only 5/257 of our Barium stars show enhancement in Na, and the flux residuals in three of those are likely due to interstellar dust.
+We find 178/257 barium star candidates show carbon enhancement, consistent with the literature, and are possible CH stars.
+However, in contrast with previous works, we do not find barium stars to have significantly higher [Na/Fe] than Milky Way stars.
+Only 5/257 of our barium stars show enhancement in Na, and the flux residuals in three of those are likely due to interstellar dust.
 We suggest that biases between literature sources and systematic effects in measuring [Na/Fe] from stars with low $\log{g}$ contributed to this effect.
 
-Despite our noisy estimates of [Ba/Fe] and [Sr/Fe] from LAMOST spectra, comparisons with AGB yields indicate that our sample is consistent with a bottom-heavy initial mass function.
+Despite our noisy estimates of [Ba/Fe] and [Sr/Fe] from LAMOST spectra, comparisons with AGB yields indicate that our sample is consistent with a Salpeter-like initial mass function, and indicate the possible mass of the binary companion to the extrinsic barium star.
 We encourage follow-up observations with high-resolution spectrographs in order to precisely measure a full suite of neutron-capture abundances.
@@
 A.~R.~C. is supported through an Australian Research Council Discovery Project under grant DP160100637.
-A.~Y.~Q.~H. is supported by a Fulbright grant through the German-American Fulbright Commission and a National Science Foundation Graduate Research Fellowship under Grant No. DGE-1144469. 
+A.
+Y.
+Q.
+H.
+was supported by the GROWTH project funded by the National Science Foundation under PIRE Grant No 1545949, and a National Science Foundation Graduate Research Fellowship under Grant No.
+DGE-1144469.
 This research has made use of NASA's Astrophysics Data System.
@@
 \bibitem[Alam et al.(2015)]{alam2015} Alam, S., Albareti, F.~D., Allende Prieto, C., et al.\ 2015, \apjs, 219, 12 
-\bibitem[\protect\citeauthoryear{Allen \& Barbuy}{2006}]{allen2006}
-Allen, D.~M.,\& Barbuy B. 2006, 
-A$\&$A, 454, 917
+%\bibitem[\protect\citeauthoryear{Allen \& Barbuy}{2006}]{allen2006}
+%Allen, D.~M.,\& Barbuy B. 2006, 
+%A$\&$A, 454, 917
 \bibitem[\protect\citeauthoryear{Antipova et al.}{2004}]{antipova2004}
@@
 ARep, 48, 597
+\bibitem[\protect\citeauthoryear{Bernstein et al.}{2003}]{bernstein2003}
+Bernstein, R., Shectman, S.~A., Gunnels, S.~M., Mochnacki, S.,\& Athey, A.~E. 2003, 
+SPIE, 4841, 1694    
 \bibitem[\protect\citeauthoryear{Bidelman \& Keenan}{1951}]{Bidelman1951}
@@
 SvAL, 13, 214
-\bibitem[\protect\citeauthoryear{Drake \& Pereira}{2008}]{drake2008}
-Drake N.,~A.,\& Pereira, C.~B. 2008, 
-AJ, 135, 1070
+%\bibitem[\protect\citeauthoryear{Drake \& Pereira}{2008}]{drake2008}
+%Drake N.,~A.,\& Pereira, C.~B. 2008, 
+%AJ, 135, 1070
 \bibitem[\protect\citeauthoryear{El Eid \& Champagne}{1995}]{el1995}
@@
 ApJ, 451, 298
+\bibitem[\protect\citeauthoryear{Fishlock et all}{2014}]{fishlock2014}
+Fishlock, C.~K., Karakas, A.~I., Lugaro, M.,\& Yong, D. 2014, 
+ApJ, 797, 44
 \bibitem[\protect\citeauthoryear{Gaia Collaboration et al.}{2016a}]{gaia2016a}
@@
 A$\&$A, 441, 1135
-\bibitem[\protect\citeauthoryear{Junqueira \& Pereira}{2001}]{junqueira2001}
-Junqueira S.,\& Pereira, C.~B. 2001, 
-AJ, 122, 360
-\bibitem[\protect\citeauthoryear{Karakas}{2016}]{karakas12016}
-Karakas, A. 2016, 
-SAIt, 87, 229
+%\bibitem[\protect\citeauthoryear{Junqueira \& Pereira}{2001}]{junqueira2001}
+%Junqueira S.,\& Pereira, C.~B. 2001, 
+%AJ, 122, 360
 \bibitem[\protect\citeauthoryear{Karakas \& Lugaro}{2016}]{karakas_lugaro2016}
@@
 PASP, 115, 688
-\bibitem[\protect\citeauthoryear{Kobayashi et al.}{2011}]{kobayashi2011}
-Kobayashi, C., Karakas, A., \& Umeda, H. 2011, 
-MNRAS, 414, 3231
+%\bibitem[\protect\citeauthoryear{Kobayashi et al.}{2011}]{kobayashi2011}
+%Kobayashi, C., Karakas, A., \& Umeda, H. 2011, 
+%MNRAS, 414, 3231
 \bibitem[Kupka et al.(1999)]{vald} Kupka, F., Piskunov, N., Ryabchikova, T.~A., Stempels, H.~C., \& Weiss, W.~W.\ 1999, \aaps, 138, 119 
@@
 AJ, 93, 1539
+\bibitem[\protect\citeauthoryear{Luck \& Bond}{1991}]{luck1991}
+Luck R.~E.,\& Bond, H.~E. 1991, 
+ApJS, 77, 515
 \bibitem[\protect\citeauthoryear{Luck \& Heiter}{2007}]{luck2007}
@@
 ApJ, 268, 264
+\bibitem[\protect\citeauthoryear{McClure}{1997}]{mcclure1997}
+McClure, R.~D. 1997, 
+PASP, 109, 536
 \bibitem[\protect\citeauthoryear{Mennessier et al.}{1997}]{mennessier1997}
@@
 PASJ, 27, 533
-\bibitem[\protect\citeauthoryear{NFW}{1997}]{nfw1997}
+\bibitem[\protect\citeauthoryear{Navarro, Frenk \& White}{1997}]{nfw1997}
 Navarro, J.~F., Frenk, C.~S.,\& White, S.~D.~M. 1997, 
 ApJ, 490, 493
-\bibitem[\protect\citeauthoryear{Pereira \& Drake}{2009}]{pereira2009}
-Pereira, C.~B.,\& Drake N.,~A. 2009, 
-A$\&$A, 496, 791
+%\bibitem[\protect\citeauthoryear{Pereira \& Drake}{2009}]{pereira2009}
+%Pereira, C.~B.,\& Drake N.,~A. 2009, 
+%A$\&$A, 496, 791
 \bibitem[\protect\citeauthoryear{Pereira et al.}{2011}]{pereira2011}
@@
 Pourbaix, D., Tokovinin, A.~A., Batten, A.~H., Fekel, F.~C., Hartkopf, W.~I. et al. 2001, 
-\bibitem[\protect\citeauthoryear{Prantzos}{2012}]{prantzos2012}
-Prantzos, N. 2012, 
-A$\&$A, 542, A67
+%\bibitem[\protect\citeauthoryear{Prantzos}{2012}]{prantzos2012}
+%Prantzos, N. 2012, 
+%A$\&$A, 542, A67
 \bibitem[\protect\citeauthoryear{Price-Whelan}{2017}]{price2017}
@@
 The Journal of Open Source Software, 2, 388
-\bibitem[\protect\citeauthoryear{Romano et al.}{2010}]{romano2010}
-Romano, D., et al. 2010, 
-A$\&$A, 522, A32
+%\bibitem[\protect\citeauthoryear{Romano et al.}{2010}]{romano2010}
+%Romano, D., et al. 2010, 
+%A$\&$A, 522, A32
+\bibitem[\protect\citeauthoryear{Schectman \& Johns}{2003}]{schectman2003}
+Shectman, S.~A.,\& Johns, M. 2003, 
+SPIE, 4837, 910
 \bibitem[\protect\citeauthoryear{Schlafly \& Finkbeiner}{2011}]{schlafly2011}

### 2018-02-18 article/plot_hrd_new.py

@@ -1,0 +1,30 @@
+import matplotlib.pyplot as plt
+from matplotlib.ticker import MaxNLocator
+from astropy.table import Table
+
+data = Table.read("Bastar_candidates.csv")
+
+fig, ax = plt.subplots(figsize=(4, 4))
+
+ax.scatter(data["cannon_teff_1"], data["cannon_logg_1"],
+           facecolor="#000000", edgecolor="#000000", linewidths=1, s=5, zorder=100)
+ax.errorbar(data["cannon_teff_1"], data["cannon_logg_1"],
+            xerr=data["cannon_teff_err_1"], yerr=data["cannon_logg_err_1"],
+            fmt=None, ecolor="#666666", elinewidth=1)
+
+ax.set_xlim(ax.get_xlim()[::-1])
+ax.set_ylim(4, 0)
+ax.set_yticks([0, 1, 2, 3, 4])
+
+lhs = 5400
+
+
+ax.xaxis.set_major_locator(MaxNLocator(6))
+ax.yaxis.set_major_locator(MaxNLocator(6))
+
+
+ax.set_xlabel(r"Effective temperature $T_{\rm eff}$ $({\rm K})$")
+ax.set_ylabel(r"Surface gravity $\log{g}$")
+
+fig.tight_layout()
+fig.savefig("hrd_new.pdf", dpi=300, overwrite=True)

### 2018-02-18 article/plot_yeilds_b.py

@@ -33,33 +33,33 @@ ax.errorbar(data["cannon_m_h_1"], hs_ls,
             fmt=None, ecolor="#BBBBBB", elinewidth=1, label="_")
 
 
-cristallo = Table.read("cristallo_data_new.csv")
-fehs = np.array(cristallo.dtype.names[1:]).astype(float)
+#cristallo = Table.read("cristallo_data_new.csv")
+#fehs = np.array(cristallo.dtype.names[1:]).astype(float)
 
-masses = cristallo["Mass/[Fe/H]"]
+#masses = cristallo["Mass/[Fe/H]"]
 
-colors = {
-    "2.0": "r",
-    "3.0": "g",
-}
+#colors = {
+    #"2.0": "r",
+    #"3.0": "g",
+#}
 
-for i, mass in enumerate(masses):
-    model_hs_ls = [cristallo[feh][i] for feh in cristallo.dtype.names[1:]]
-    ax.plot(fehs, model_hs_ls, label=r"${{{:.1f}}}\,M_\odot$".format(mass),
-            lw=5, alpha=0.75)
+#for i, mass in enumerate(masses):
+    #model_hs_ls = [cristallo[feh][i] for feh in cristallo.dtype.names[1:]]
+    #ax.plot(fehs, model_hs_ls, label=r"${{{:.1f}}}\,M_\odot$".format(mass),
+            #lw=5, alpha=0.75)
 
 
-plt.legend()
+#plt.legend()
 ax.set_xlim(-2.3, 0.4)
 ax.set_ylim(-1, 1.5)
 
 ax.xaxis.set_major_locator(MaxNLocator(6))
 ax.yaxis.set_major_locator(MaxNLocator(6))
 
-ax.legend(ncol=1, loc="upper left", frameon=True, fontsize=10)
+#ax.legend(ncol=1, loc="upper left", frameon=True, fontsize=10)
 ax.set_xlabel(r"Metallicity [Fe/H]")
-ax.set_ylabel(r"Surface [Ba/Sr]")
+ax.set_ylabel(r"Surface [ba/sr]")
 
 fig.tight_layout()
 
-fig.savefig("yields_new.pdf", dpi=300, overwrite=True)
+fig.savefig("yields_basr.pdf", dpi=300, overwrite=True)

### 2018-02-18 article/plot_yields_amanda.py

@@ -32,19 +32,18 @@ ax.errorbar(data["cannon_m_h_1"], hs_ls,
             xerr=data["cannon_m_h_err_1"], yerr=hs_ls_err,
             fmt=None, ecolor="#BBBBBB", elinewidth=1, label="_")
 
+amanda = Table.read("amanda_yields.csv")
+fehs = np.array(amanda.dtype.names[1:]).astype(float)
 
-cristallo = Table.read("cristallo_data_new.csv")
-fehs = np.array(cristallo.dtype.names[1:]).astype(float)
-
-masses = cristallo["Mass/[Fe/H]"]
+masses = amanda["mass/[Fe/H]"]
 
 colors = {
-    "2.0": "r",
-    "3.0": "g",
+    "2.0": "k",
+    "3.0": "m",
 }
 
 for i, mass in enumerate(masses):
-    model_hs_ls = [cristallo[feh][i] for feh in cristallo.dtype.names[1:]]
+    model_hs_ls = [amanda[feh][i] for feh in amanda.dtype.names[1:]]
     ax.plot(fehs, model_hs_ls, label=r"${{{:.1f}}}\,M_\odot$".format(mass),
             lw=5, alpha=0.75)
 
@@ -62,4 +61,4 @@ ax.set_ylabel(r"Surface [Ba/Sr]")
 
 fig.tight_layout()
 
-fig.savefig("yields_new.pdf", dpi=300, overwrite=True)
+fig.savefig("yields_amanda.pdf", dpi=300, overwrite=True)

### 2018-02-18 article/plot_yields_total.py

@@ -39,12 +39,27 @@ fehs = np.array(cristallo.dtype.names[1:]).astype(float)
 masses = cristallo["Mass/[Fe/H]"]
 
 colors = {
-    "2.0": "r",
+    "2.0": "k",
     "3.0": "g",
 }
 
 for i, mass in enumerate(masses):
     model_hs_ls = [cristallo[feh][i] for feh in cristallo.dtype.names[1:]]
+    ax.plot(fehs, model_hs_ls, label=r"${{{:.1f}}}\,M_\odot$".format(mass),
+            lw=5, alpha=0.75)
+
+amanda = Table.read("amanda_yields.csv")
+fehs = np.array(amanda.dtype.names[1:]).astype(float)
+
+masses = amanda["mass/[Fe/H]"]
+
+colors = {
+    "2.0": "k",
+    "3.0": "m",
+}
+
+for i, mass in enumerate(masses):
+    model_hs_ls = [amanda[feh][i] for feh in amanda.dtype.names[1:]]
     ax.plot(fehs, model_hs_ls, label=r"${{{:.1f}}}\,M_\odot$".format(mass),
             lw=5, alpha=0.75)
 
@@ -62,4 +77,4 @@ ax.set_ylabel(r"Surface [Ba/Sr]")
 
 fig.tight_layout()
 
-fig.savefig("yields_new.pdf", dpi=300, overwrite=True)
+fig.savefig("yields_test.pdf", dpi=300, overwrite=True)

### 2018-02-20 article/ms.tex
draft

@@
 
-\title[S-process stars in LAMOST]{Discovery of s-process stars in the LAMOST survey}
+\title[S-process stars in LAMOST]{Discovery of s-process enhanced stars in the LAMOST survey}
 
 \author[Brodie.~J.
-Norfolk et al.]{B.~J.
+Norfolk et al.]{Brodie.~J.
 Norfolk,$^{1}$\thanks{E-mail: bjee7@student.monash.edu (MU)}\thanks{This paper includes data gathered with the 6.5 meter Magellan Telescopes located at Las Campanas Observatory, Chile.}
 Andrew.~R. Casey,$^{1,2}$
-Matthew T. Miles,$^{1}$
-Alex J. Kemp,$^{1}$ \newauthor
-Amanda I. Karakas,$^{1}$
-Melissa Ness,
-Kevin C. Schlaufman$^{4}$,
+Matthew ~T. Miles,$^{1}$
+Alex ~J. Kemp,$^{1}$ \newauthor
+Amanda ~I. Karakas,$^{1}$,
+Kevin ~C. Schlaufman$^{4}$,
+Melissa Ness,$^{5}$,
 Anna Y.~Q. Ho,$^{3}$, \newauthor
-and John C. Lattanzio,$^{1}$
+John ~C. Lattanzio,$^{1}$ and
+Alexander ~P. Ji,$^{6}$
 \\
@@
 $^{4}$Department of Physics and Astronomy, Johns Hopkins University, 3400 N Charles St., Baltimore, MD 21218, USA
+\\
+$^{5}$Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117 Heidelberg, Germany
+\\
+$^{6}$Department of Physics, Kavli Institute for Astrophysics and Space Research, Massachusetts Institute of Technology,
+Cambridge, MA 02139, USA
 }
@@
 
-The slow neutron capture process (s-process), occurring in the interior of AGB stars, synthesises roughly half of all elements heavier than iron \citep[e.g.,][]{busso1999,travaglio2001,herwig2005,bisterzo2014,fishlock2014}.
+The slow neutron capture process (s-process), occurring in the interior of AGB stars, synthesises roughly half of all elements heavier than iron \citep[e.g.,][]{busso1999,travaglio2001,herwig2005,bisterzo2014,karakas2014}.
 Late in the AGB phase, during the TP-AGB phase, thermal instabilities occur in the He shell every $10^5$ years or so, depending on the mass of the H-exhausted core.
@@
 In \citet{pereira2011} it is concluded that metal-rich barium stars share similar kinematics to other metal-rich and super metal-rich stars already analysed, suggesting that they do not belong to the bulge population.
-It remains necessary to establish known abundances of s-process elements in a greater sample of barium stars in order to compare their birth rate to theoretical expectations \citep{han1995}, explore the binary fraction at different metallicities, and to compare to AGB star yields at different masses and metallicities.
+It remains necessary to establish known abundances of s-process elements in a greater sample of barium stars in order to compare their birth rate to theoretical expectations \citep{han1995}, to explore the binary fraction at different metallicities, and then to compare to AGB star yields at different masses and metallicities.
 %The relationship between barium stars in the halo \citep[e.g.,][]{junqueira2001,drake2008,pereira2009,allen2006} and metal-poor, yellow, symbiotic halo stars has been established by \citet{jorissen2005} and \citet{pereira2009}.
@@
 While the 49 or 661 stars with only barium or strontium enhancements (respectively) may also be bonafide barium stars, there may be other explanations for their chemical abundance pattern \citep[e.g.,][]{maiorca2011}, and so we restrict our inferences to a `gold sample' of barium stars.
+
+It's important to note, previous studies \citet{malaney1988} define barium stars through an abundance criteria $\rm[Ba/Fe]\geq +0.3$, out of our 257 barium star sample, only one star ($\rm J092155.95+265253.4$) exhibits a lower [Ba/Fe] of 0.12.
+However, as previously discussed, a negative residual at the \ion{Ba}{II} resonance line 4554\,\AA\, indicates barium enhancement.
+Furthermore, as discussed in section \ref{sec:other enhancements}, an enhancement in carbon is observed frequently with barium enhancement.
+$\rm J092155.95+265253.4$ shows both a negative residual at 4554\,\AA\, and carbon enhancement, we therefor conclude that this single deviant case can be classified as a barium star.
+Additionally, it should be mentioned, our average abundance error is .
+.
+., although, these results still indicate our sample can be classified as barium stars since they exhibit enhancement at the BaII resonance line 4554, and have a $\rm[Ba/Fe] \geq 0.2$.
 Nevertheless, this sample still constitutes the largest collection of barium stars ever discovered, with the next sample of significant size containing 182 barium stars \citep[e.g.,][]{decastro2016}.
@@
 
-\subsubsection{Enhancements due to sodium, technetium, and carbon}
+\subsubsection{Enhancements due to sodium, technetium, and carbon} \label{sec:other enhancements}
 Enhancements in sodium, technetium, and carbon are useful indicators when determining whether a stellar sample is populated by intrinsically enhanced AGB S stars, or polluted extrinsic barium stars.
@@
 This suggests, the construction of our data-driven model may have missed some AGB barium candidates, or that previous studies were biased towards finding luminous intrinsic AGB barium stars.
-Given that our analysis limits us to only giant stars, such that we do not find any extrinsic barium stars on the main-sequence, na\"ively we would expect that our sample would be biased \emph{towards} finding a higher fraction of AGB S stars.
-Despite this expected bias against extrinsic barium stars, our entire barium star sample are extrinsic, suggesting unaccounted selection biases in previous studies towards luminous AGB S stars.
+Given that our analysis limits us to only giant stars, such that we do not find any extrinsic barium stars on the main-sequence, na\"ively we would expect that our sample would be biased \emph{towards} finding a higher fraction of red giant stars.
+Given this bias, Figure \ref{fig:figure3} illustrates through the temperature, and log g ranges present, that our sample is entirely populated by red giant extrinsic barium stars.
+This suggests unaccounted selection biases in previous studies towards luminous AGB S stars.
 
 \subsection{Sodium enhancment}
-Sodium overabundances observed in the atmospheres of supergiants is thought to be synthesised by the NeNa reaction chain in the convective core of main-sequence stars \citep{el1995}.
-Sodium is transported to the surface of these supergiants via mixing during the first dredge-up.
-Although, it is important to note, sodium enhancement is not constrained to supergiant stars.
-Stars with a  minimum mass of $1.5\,M_\odot$ can also exhibit enhanced sodium abundances through the NeNa cycle \citep{denissenkov1987}.
+Sodium overabundances observed in the atmospheres of giants is thought to be synthesised by the NeNa reaction chain in the convective core of main-sequence stars \citep{el1995}.
+Sodium is transported to the surface of these giants via mixing during the first dredge-up and stars with a  minimum mass of $1.5\,M_\odot$ can exhibit enhanced sodium abundances through the NeNa cycle \citep{denissenkov1987,smiljanic2012}.
 \citet{antipova2004} reported sodium enhancements in 3 of their 16 barium star candidates, and they relate this to the dredge-up of nuclear-burning material produced by convection during the red-giant phase.
@@
 
-The final surface s-process index [Ba/Sr], shown in \citet{cristallo2015} and \citet{karakas} illustrated in Figure \ref{fig:figure3}, highlights the relationship between [Ba/Sr] yields and the mass of AGB stars.
+The final surface s-process index [Ba/Sr], illustrated in Figure \ref{fig:figure3}, highlights the relationship between [Ba/Sr] yields and the mass of AGB stars.
 The Salpeter initial mass function (or any bottom-heavy initial mass function) predicts the majority of stars in the Milky Way will have lower masses, and as predicted the [Ba/Sr] values of our barium stars approximately fit the lower mass yields as seen in Figure \ref{fig:figure3}.
-It's important to note, our results do not indicate when the mass transfer occured, and our candidates fitting these theoratical yeilds may not have the indicated binary companion masses.
-Instead mass transfer may have occured early on in the AGB S binary companion star's lifespan.
+However, it's important to note, our results do not indicate when the mass transfer occured, and our candidates fitting these theoratical yeilds may not have the indicated binary companion masses.
+Instead, mass transfer may have occured early on in the AGB S binary companion star's lifespan, and the resulting s-process element abundance present in our barium candidates may relfect a lower ABG S star mass.
 Additionally, this can be extended to our candidates not approximated by theoratical yeilds.
@@
 	\includegraphics[width=\columnwidth]{yields_test.pdf}
-    \caption{Metallicities ([Fe/H]; x-axis) and heavy-to-light s-process abundance ratios ([hs/ls], taken as [Ba/Sr] as measured from LAMOST; y-axis) for 257 barium star candidates.
-Coloured lines indicate surface [hs/ls] yields from \citet{cristallo2015} for different masses.}
+    \caption{Metallicities ([Fe/H]; x-axis) and heavy-to-light s-process abundance ratios ([Ba/Sr] as measured from LAMOST; y-axis) for 257 barium star candidates.
+Coloured lines blue, orange, and green, indicate surface [hs/ls] yields from \citet{cristallo2015} for different masses.
+Coloured lines red, purple, and brown indicate surface [hs/ls] yields from \citet{karakas_lugaro2016} for [Fe/H] at +0.3.
+0.0, and -0.3.
+From \citet{karakas2018} for [Fe/H] at -0.7, and from \citet{fishlock2014} for [Fe/H] at -1.2.}
     \label{fig:figure3}
@@
 We find 178/257 barium star candidates show carbon enhancement, consistent with the literature, and are possible CH stars.
-However, in contrast with previous works, we do not find barium stars to have significantly higher [Na/Fe] than Milky Way stars.
+However, in contrast with previous works, we do not find barium stars to have significantly higher [Na/Fe] than Milky Way field giants.
 Only 5/257 of our barium stars show enhancement in Na, and the flux residuals in three of those are likely due to interstellar dust.
@@
 \section*{Acknowledgements}
-We thank Alex Ji (Carnegie Observatories), David W. Hogg (NYU), Melissa Ness (Columbia), and Hans-Walter Rix (MPIA) for useful discussions. 
+We thank  Alex Ji (Carnegie Observatories), David W. Hogg (NYU), Melissa Ness (Columbia), Hans-Walter Rix (MPIA) and especially Andrew Casey (Monash) for useful discussions. 
 A.~R.~C. is supported through an Australian Research Council Discovery Project under grant DP160100637.
@@
 ApJ, 451, 298
-\bibitem[\protect\citeauthoryear{Fishlock et all}{2014}]{fishlock2014}
+\bibitem[\protect\citeauthoryear{Fishlock et al}{2014}]{fishlock2014}
 Fishlock, C.~K., Karakas, A.~I., Lugaro, M.,\& Yong, D. 2014, 
@@
 %AJ, 122, 360
+\bibitem[\protect\citeauthoryear{Karakas \& Lattanzio}{2014}]{karakas2014}
+Karakas, A.~I.,\& Lattanzio C.~J. 2014, 
+PASA, 31, 30
 \bibitem[\protect\citeauthoryear{Karakas \& Lugaro}{2016}]{karakas_lugaro2016}
@@
 ApJS, 825, 26
+\bibitem[\protect\citeauthoryear{Karakas et al.}{2018}]{karakas2018}
+Karakas, A.~I. 2018, 
+MNRAS, submitted
 \bibitem[\protect\citeauthoryear{Kelson et al.}{2000}]{kelson2000}
@@
 \bibitem[Maiorca et al.(2011)]{maiorca2011} Maiorca, E., Randich, S., Busso, M., Magrini, L., \& Palmerini, S.\ 2011, \apj, 736, 120 
+\bibitem[\protect\citeauthoryear{Malaney \& Lambert}{1988}]{malaney1988}
+Malaney, R.~A.,\& Lambert, D.~L. 1988, 
+MNRAS, 235, 695
 \bibitem[\protect\citeauthoryear{McClure}{1983}]{mcclure1983}
@@
 Apj, 737, 103
+\bibitem[\protect\citeauthoryear{Smiljanic}{2012}]{smiljanic2012}
+Smiljanic, R. 2012, 
+MNRAS, 422, 1562
 \bibitem[\protect\citeauthoryear{Smith \& Wallerstein}{1983}]{smith1983}

### 2018-02-20 article/ms.tex
summer project submission

@@
 In this paper we present the discovery of 967 s-process candidates from 454,180 giant stars observed by LAMOST: this sample constitutes the largest number of s-process enhanced stars ever discovered.
-We identify these stars in the LAMOST sample by using a data-driven search approach on the spectra directly and then measure the s-process abundance enhancements directly using stellar synthesis.
+We identify these stars in the LAMOST sample by using a data-driven search approach on the spectra directly, and then measure the s-process abundance enhancements directly using stellar synthesis.
 Finally, we validate our results using high resolution spectra of a number of candidates.
@@
 Our entire barium star stellar sample exists within temperature and luminosity ranges not enveloped by the AGB, which may indicate a recent ($<1\,\textrm{Myr}$) mass accretion event from an AGB companion.
-Most of our barium stars ($69\%$) show strong carbon enhancements, only 5 candidates ($<2$\,\%) show evidence of sodium enhancement.
-In contrast with previous claims of preferential sodium enhancement, we argue this may have been a selection bias in previous studies.
+Most of our barium stars ($69\%$) show strong carbon enhancements, yet, only 5 candidates ($<2$\,\%) show evidence of sodium enhancement, in contrast with previous claims of preferential sodium enhancement.
+We argue this may have been a selection bias in previous studies.
 A comparison with AGB yields suggests that the majority of our sample are consistent with Salpeter-like initial mass function, with pollution from a low mass AGB star.
@@
 \begin{keywords}
-keyword1 -- keyword2 -- keyword3
+stars: chemically peculiar -- stars: abundances
 \end{keywords}
@@
 
-Barium stars as first recognised by \citet{Bidelman1951}, are chemically unusual objects that exhibit envelopes with an overabundance of carbon and heavy elements (Z > 30) in comparison to the Sun.
+The abundances of the slow neutron capture process (s-process) elements in stars are a measure of the nucleosyntheic processes that occur primarily in Asymptotic Giant Branch (AGB) stars.
+Due to their associated enrichment of the s-process element barium, stars with peculiar enhancements of carbon, and heavy elements (Z > 30) are historically referred to as 'barium stars' as first recognised by \citet{Bidelman1951}.
 Barium enhanced stars exist as either intrinsic or extrinsic objects, stars intrinsically enhanced in barium and other s-process elements are known as AGB S stars.
@@
 
-The slow neutron capture process (s-process), occurring in the interior of AGB stars, synthesises roughly half of all elements heavier than iron \citep[e.g.,][]{busso1999,travaglio2001,herwig2005,bisterzo2014,karakas2014}.
+The s-process, occurring in the interior of AGB stars, synthesises roughly half of all elements heavier than iron \citep[e.g.,][]{busso1999,travaglio2001,herwig2005,bisterzo2014,karakas2014}.
 Late in the AGB phase, during the TP-AGB phase, thermal instabilities occur in the He shell every $10^5$ years or so, depending on the mass of the H-exhausted core.
@@
 
-It's important to note, previous studies \citet{malaney1988} define barium stars through an abundance criteria $\rm[Ba/Fe]\geq +0.3$, out of our 257 barium star sample, only one star ($\rm J092155.95+265253.4$) exhibits a lower [Ba/Fe] of 0.12.
+It's important to note, previous studies \citet{malaney1988} define barium stars through an abundance criteria $\rm[Ba/Fe]\geq +0.3$, and out of our 257 barium star sample using this criteria , only one star ($\rm J092155.95+265253.4$) exhibits a lower [Ba/Fe] of 0.12.
 However, as previously discussed, a negative residual at the \ion{Ba}{II} resonance line 4554\,\AA\, indicates barium enhancement.
@@
 $\rm J092155.95+265253.4$ shows both a negative residual at 4554\,\AA\, and carbon enhancement, we therefor conclude that this single deviant case can be classified as a barium star.
-Additionally, it should be mentioned, our average abundance error is .
-.
-., although, these results still indicate our sample can be classified as barium stars since they exhibit enhancement at the BaII resonance line 4554, and have a $\rm[Ba/Fe] \geq 0.2$.
+Additionally, it should be mentioned, our average abundance error is 0.1, although, these results still indicate our sample can be classified as barium stars since they exhibit enhancement at the BaII resonance line 4554, and have a $\rm[Ba/Fe] \geq 0.2$.
 Nevertheless, this sample still constitutes the largest collection of barium stars ever discovered, with the next sample of significant size containing 182 barium stars \citep[e.g.,][]{decastro2016}.
@@
 	% or pdf, png, jpg if compiling using pdflatex
-	\includegraphics[width=\textwidth]{posterchild.png}
+	\includegraphics[width=\textwidth]{posterchild_final.pdf}
     \caption{Pseudo-continuum-normalised LAMOST spectra for the s-process candidate J064451.11+263239.2.
@@
 The Salpeter initial mass function (or any bottom-heavy initial mass function) predicts the majority of stars in the Milky Way will have lower masses, and as predicted the [Ba/Sr] values of our barium stars approximately fit the lower mass yields as seen in Figure \ref{fig:figure3}.
-However, it's important to note, our results do not indicate when the mass transfer occured, and our candidates fitting these theoratical yeilds may not have the indicated binary companion masses.
-Instead, mass transfer may have occured early on in the AGB S binary companion star's lifespan, and the resulting s-process element abundance present in our barium candidates may relfect a lower ABG S star mass.
+However, it's important to note, our results do not indicate when the mass transfer occured, and our candidates fitting these theoratical yeilds may not have the correlating binary companion masses.
+Instead, mass transfer may have occured early on in the AGB S binary companion star's lifespan, and the resulting [Ba/Sr] abundance present in our barium candidates may relfect pollution from a lower ABG S star mass.
 Additionally, this can be extended to our candidates not approximated by theoratical yeilds.

### 2018-02-23 article/ms.tex
final draft

@@
 
+\begin{figure*}
+	% To include a figure from a file named example.*
+	% Allowable file formats are eps or ps if compiling using latex
+	% or pdf, png, jpg if compiling using pdflatex
+	\includegraphics[width=\textwidth]{posterchild_final.pdf}
+    \caption{Pseudo-continuum-normalised LAMOST spectra for the s-process candidate J064451.11+263239.2.
+The data are shown in black and the best-fitting data-driven model is shown in red.
+We include zoom-in axes to show significant deviations in Sr and Ba at  4077\,\AA\ and 4554\,\AA\, respectively.}
+    \label{fig:figure1}
+\end{figure*}
+
 \section{Methods} \label{sec:methods}
@@
 In addition, a visual inspection was undertaken to exclude any results containing false positives, candidates exhibiting data reduction issues, apparent absorption finer then the spectral resolution, and overly noisy normalised LAMOST spectra.
-This combined method generated 967 s-process rich candidates which are provided in Table \ref{table:table1} including; 257 `barium stars' enhanced in both barium and strontium, 49 stars exhibiting exclusively barium enhancement, and 661 exhibiting exclusively strontium enhancement.
+This combined method generated 967 s-process rich candidates which are provided in Table 1 (online only material) including; 257 `barium stars' enhanced in both barium and strontium, 49 stars exhibiting exclusively barium enhancement, and 661 exhibiting exclusively strontium enhancement.
 
@@
 
-\begin{figure*}
-	% To include a figure from a file named example.*
-	% Allowable file formats are eps or ps if compiling using latex
-	% or pdf, png, jpg if compiling using pdflatex
-	\includegraphics[width=\textwidth]{posterchild_final.pdf}
-    \caption{Pseudo-continuum-normalised LAMOST spectra for the s-process candidate J064451.11+263239.2.
-The data are shown in black and the best-fitting data-driven model is shown in red.
-We include zoom-in axes to show significant deviations in Sr and Ba at  4077\,\AA\ and 4554\,\AA\, respectively.}
-    \label{fig:figure1}
-\end{figure*}
-
-\begin{table*}
-\centering
-\caption{Properties of 967 s-process candidates, the table is available online in its entirety. Here we show a portion to demonstrate its style and content.}
-\label{table:table1}
-\begin{adjustbox}{width=1\textwidth}
-\begin{tabular}{@{}|l|l|c|c|c|c|c|c|c|c|c|c|c|c|c|@{}}
-\toprule
-2MASSID             & R.~A.
+%\begin{table*}
+%\centering
+%\caption{Properties of 967 s-process candidates, the table is available online in its entirety. Here we show a portion to demonstrate its style and content.}
+%\label{table:table1}
+%\begin{adjustbox}{width=1\textwidth}
+%\begin{tabular}{@{}|l|l|c|c|c|c|c|c|c|c|c|c|c|c|c|@{}}
+%\toprule
+%2MASSID             & R.~A.
 & Dec.
 & $v_{r}$ & S/N & $\rm T_{\rm eff}$ & $\log{g}$ & [Fe/H] & [$\alpha$/Fe] & $\chi_r^2$ & [Ba/Fe] & [Sr/Fe] & \ion{Ba}{II} & \ion{Sr}{II} &  \ion{Ba}{II} \& \ion{Sr}{II} \\
-& (J2000) & (J2000) & (km\,s$^{-1}$) & (pixel$^{-1}$) & (K)  \\ \midrule
-J000019.26+501444.8 & 00:00:19.27 & +50:14:44.9 & -3.9  & 49      & 4973         & 3.27         & 0.21         & 0.08             & 0.66               & 0.25        & 0.83        & \ding{55} & \ding{51}  & \ding{55}   \\
-J000020.55+411348.1 & 00:00:20.56 & +41:13:48.2 & -28.2 & 32      & 4882         & 2.74         & -0.22        & 0.04             & 0.23               & -0.17       & 0.90        & \ding{55}& \ding{51}  & \ding{55}    \\
-J000134.95+490743.2 & 00:01:34.96 & +49:07:43.2 & -42.3 & 72      & 5044         & 3.11         & -0.54        & 0.11             & 0.79               & 1.02        & 0.45        & \ding{55} & \ding{55} & \ding{51}  \\
-J000258.09+410730.0 & 00:02:58.10 & +41:07:30.1 & -34.5 & 41      & 4697         & 2.57         & -0.22        & 0.12             & 0.98               & -0.10       & 0.80        & \ding{55} & \ding{51}  & \ding{55}  \\
-J000403.80+160257.1 & 00:04:03.80 & +16:02:57.2 & -35.4 & 42      & 5200         & 3.40         & -0.41        & 0.09             & 0.33               & 0.92        & 0.52        & \ding{55} & \ding{55} & \ding{51}  \\
-J000439.16+183350.3 & 00:04:39.17 & +18:33:50.4 & -38.7 & 31      & 4601         & 2.50         & 0.44         & 0.03             & 0.34               & -0.11       & 0.88        & \ding{55} & \ding{51}  & \ding{55}  \\
-J000444.87+400402.1 & 00:04:44.88 & +40:04:02.1 & -94.7 & 53      & 4172         & 1.46         & -0.08        & 0.09             & 0.72               & 0.03        & 0.91        & \ding{55} & \ding{51}  & \ding{55}  \\
-J000552.76+261849.3 & 00:05:52.76 & +26:18:49.4 & -22.5 & 73      & 4924         & 3.14         & -0.05        & 0.09             & 0.67               & 0.28        & 0.85        & \ding{55} & \ding{51}  & \ding{55}  \\
-J000737.70+394055.5 & 00:07:37.70 & +39:40:55.6 & -31.5 & 33      & 4700         & 2.80         & -0.04        & 0.07             & 0.28               & -0.13       & 0.81        & \ding{55} & \ding{51}  & \ding{55}  \\ \hline
-\end{tabular}
-\end{adjustbox}
-\end{table*}
+%& (J2000) & (J2000) & (km\,s$^{-1}$) & (pixel$^{-1}$) & (K)  \\ \midrule
+%J000019.26+501444.8 & 00:00:19.27 & +50:14:44.9 & -3.9  & 49      & 4973         & 3.27         & 0.21         & 0.08             & 0.66               & 0.25        & 0.83        & \ding{55} & \ding{51}  & \ding{55}   \\
+%J000020.55+411348.1 & 00:00:20.56 & +41:13:48.2 & -28.2 & 32      & 4882         & 2.74         & -0.22        & 0.04             & 0.23               & -0.17       & 0.90        & \ding{55}& \ding{51}  & \ding{55}    \\
+%J000134.95+490743.2 & 00:01:34.96 & +49:07:43.2 & -42.3 & 72      & 5044         & 3.11         & -0.54        & 0.11             & 0.79               & 1.02        & 0.45        & \ding{55} & \ding{55} & \ding{51}  \\
+%J000258.09+410730.0 & 00:02:58.10 & +41:07:30.1 & -34.5 & 41      & 4697         & 2.57         & -0.22        & 0.12             & 0.98               & -0.10       & 0.80        & \ding{55} & \ding{51}  & \ding{55}  \\
+%J000403.80+160257.1 & 00:04:03.80 & +16:02:57.2 & -35.4 & 42      & 5200         & 3.40         & -0.41        & 0.09             & 0.33               & 0.92        & 0.52        & \ding{55} & \ding{55} & \ding{51}  \\
+%J000439.16+183350.3 & 00:04:39.17 & +18:33:50.4 & -38.7 & 31      & 4601         & 2.50         & 0.44         & 0.03             & 0.34               & -0.11       & 0.88        & \ding{55} & \ding{51}  & \ding{55}  \\
+%J000444.87+400402.1 & 00:04:44.88 & +40:04:02.1 & -94.7 & 53      & 4172         & 1.46         & -0.08        & 0.09             & 0.72               & 0.03        & 0.91        & \ding{55} & \ding{51}  & \ding{55}  \\
+%J000552.76+261849.3 & 00:05:52.76 & +26:18:49.4 & -22.5 & 73      & 4924         & 3.14         & -0.05        & 0.09             & 0.67               & 0.28        & 0.85        & \ding{55} & \ding{51}  & \ding{55}  \\
+%J000737.70+394055.5 & 00:07:37.70 & +39:40:55.6 & -31.5 & 33      & 4700         & 2.80         & -0.04        & 0.07             & 0.28               & -0.13       & 0.81        & \ding{55} & \ding{51}  & \ding{55}  \\ \hline
+%\end{tabular}
+%\end{adjustbox}
+%\end{table*}
 
@@
 We found that 51 barium stars exhibited some level of significant enhancement (based on the filters above) at a single technetium line, yet none showed enhancement at more than one technetium line.
-We note that the single enhancement near technetium for these 51 stars may be the consequence of data reduction/calibration artefacts, but we include details of which stars matched on technetium in Table \ref{table:table1} nonetheless.
+We note that the single enhancement near technetium for these 51 stars may be the consequence of data reduction/calibration artefacts, but we include details of which stars matched on technetium in Table 1 nonetheless.
 Finally, for carbon enhancement we searched for significant deviations at the CH and G band near 4300\,\AA.
@@
 
+\begin{figure}
+	\includegraphics[width=\columnwidth]{hrd_new.pdf}
+    \caption{Effective temperature $T_{\rm eff}$ and surface gravity $\log{g}$ for 257 candidate barium stars from LAMOST.
+Stars with $\log{g} > 2$ (as marked) have not evolved through the thermally pulsing asymptotic giant branch phase, and therefore their abundance signature must be the result of an extrinsic pollution event.
+The classification of stars with $\log{g} < 2$ would require additional data.}
+    \label{fig:figure2}
+\end{figure}
+
 \subsection{Sodium enhancment}
@@
 %Similar to the s-process enhancement, this suggests our candidates are consistent with being either intrinsic or extrinsic Barium stars.
-
-\begin{figure}
-	\includegraphics[width=\columnwidth]{hrd_new.pdf}
-    \caption{Effective temperature $T_{\rm eff}$ and surface gravity $\log{g}$ for 257 candidate barium stars from LAMOST.
-Stars with $\log{g} > 2$ (as marked) have not evolved through the thermally pulsing asymptotic giant branch phase, and therefore their abundance signature must be the result of an extrinsic pollution event.
-The classification of stars with $\log{g} < 2$ would require additional data.}
-    \label{fig:figure2}
-\end{figure}
 
@@
 \section*{Acknowledgements}
-We thank  Alex Ji (Carnegie Observatories), David W. Hogg (NYU), Melissa Ness (Columbia), Hans-Walter Rix (MPIA) and especially Andrew Casey (Monash) for useful discussions. 
+We thank  Alex Ji (Carnegie Observatories), David W. Hogg (NYU), Melissa Ness (Columbia), and Hans-Walter Rix (MPIA) for useful discussions. 
 A.~R.~C. is supported through an Australian Research Council Discovery Project under grant DP160100637.

### 2018-02-23 article/ms.tex
fix latex

@@
 Norfolk,$^{1}$\thanks{E-mail: bjee7@student.monash.edu (MU)}\thanks{This paper includes data gathered with the 6.5 meter Magellan Telescopes located at Las Campanas Observatory, Chile.}
-Andrew.~R. Casey,$^{1,2}$
-Matthew ~T. Miles,$^{1}$
-Alex ~J. Kemp,$^{1}$ \newauthor
-Amanda ~I. Karakas,$^{1}$,
+Andrew.~R. Casey$^{1,2}$,
+Matthew ~T. Miles$^{1}$,
+Alex ~J. Kemp$^{1}$, \newauthor
+Amanda ~I. Karakas$^{1}$,
 Kevin ~C. Schlaufman$^{4}$,
-Melissa Ness,$^{5}$,
-Anna Y.~Q. Ho,$^{3}$, \newauthor
-John ~C. Lattanzio,$^{1}$ and
-Alexander ~P. Ji,$^{6}$
+Melissa Ness$^{5}$,
+Anna Y.~Q. Ho$^{3}$, \newauthor
+John ~C. Lattanzio$^{1}$, 
+Alexander ~P. Ji$^{6}$
 \\
@@
 \\
-$^{6}$Department of Physics, Kavli Institute for Astrophysics and Space Research, Massachusetts Institute of Technology,
-Cambridge, MA 02139, USA
+$^{6}$Carnegie Observatories
 }
@@
 We note that this sample is exclusively giant stars, implying that we would not identify dwarf s-process enhanced stars.
-Cross-validation experience shows that the typical uncertainties are about 70\,K in effective temperature $\rm T_{\rm eff}$, 0.1\,dex in surface gravity $\log{g}$, 0.1\,dex in metallicity [M/H], and 0.04\,dex in the $\alpha$-element abundance relative to overall metallicity [$\alpha$/M].
+Cross-validation tests shows that the typical uncertainties are about 70\,K in effective temperature $\rm T_{\rm eff}$, 0.1\,dex in surface gravity $\log{g}$, 0.1\,dex in metallicity [M/H], and 0.04\,dex in the $\alpha$-element abundance relative to overall metallicity [$\alpha$/M].
 These uncertainties are comparable to the APOGEE uncertainties \citep{alam2015}.
@@
 We used five filters that each spectrum, for each set of absorption lines, had to meet in order to be considered a s-process rich candidate; these included:
+
+% FOR SOME REASON LATEX FALLS OVER IF WE DONT HAVE IT HERE
+\begin{table}\end{table}
 
@@
 In addition, a visual inspection was undertaken to exclude any results containing false positives, candidates exhibiting data reduction issues, apparent absorption finer then the spectral resolution, and overly noisy normalised LAMOST spectra.
-This combined method generated 967 s-process rich candidates which are provided in Table 1 (online only material) including; 257 `barium stars' enhanced in both barium and strontium, 49 stars exhibiting exclusively barium enhancement, and 661 exhibiting exclusively strontium enhancement.
+This combined method generated 967 s-process rich candidates which are provided in Table 1 (online only material) including; 257 `barium stars' enhanced in both barium and strontium, 49 stars exhibiting exclusively barium enhancement, and 661 with exclusively strontium enhancement.
 
@@
 Nevertheless, this sample still constitutes the largest collection of barium stars ever discovered, with the next sample of significant size containing 182 barium stars \citep[e.g.,][]{decastro2016}.
-
-%\begin{table*}
-%\centering
-%\caption{Properties of 967 s-process candidates, the table is available online in its entirety. Here we show a portion to demonstrate its style and content.}
-%\label{table:table1}
-%\begin{adjustbox}{width=1\textwidth}
-%\begin{tabular}{@{}|l|l|c|c|c|c|c|c|c|c|c|c|c|c|c|@{}}
-%\toprule
-%2MASSID             & R.~A.
-& Dec.
-& $v_{r}$ & S/N & $\rm T_{\rm eff}$ & $\log{g}$ & [Fe/H] & [$\alpha$/Fe] & $\chi_r^2$ & [Ba/Fe] & [Sr/Fe] & \ion{Ba}{II} & \ion{Sr}{II} &  \ion{Ba}{II} \& \ion{Sr}{II} \\
-%& (J2000) & (J2000) & (km\,s$^{-1}$) & (pixel$^{-1}$) & (K)  \\ \midrule
-%J000019.26+501444.8 & 00:00:19.27 & +50:14:44.9 & -3.9  & 49      & 4973         & 3.27         & 0.21         & 0.08             & 0.66               & 0.25        & 0.83        & \ding{55} & \ding{51}  & \ding{55}   \\
-%J000020.55+411348.1 & 00:00:20.56 & +41:13:48.2 & -28.2 & 32      & 4882         & 2.74         & -0.22        & 0.04             & 0.23               & -0.17       & 0.90        & \ding{55}& \ding{51}  & \ding{55}    \\
-%J000134.95+490743.2 & 00:01:34.96 & +49:07:43.2 & -42.3 & 72      & 5044         & 3.11         & -0.54        & 0.11             & 0.79               & 1.02        & 0.45        & \ding{55} & \ding{55} & \ding{51}  \\
-%J000258.09+410730.0 & 00:02:58.10 & +41:07:30.1 & -34.5 & 41      & 4697         & 2.57         & -0.22        & 0.12             & 0.98               & -0.10       & 0.80        & \ding{55} & \ding{51}  & \ding{55}  \\
-%J000403.80+160257.1 & 00:04:03.80 & +16:02:57.2 & -35.4 & 42      & 5200         & 3.40         & -0.41        & 0.09             & 0.33               & 0.92        & 0.52        & \ding{55} & \ding{55} & \ding{51}  \\
-%J000439.16+183350.3 & 00:04:39.17 & +18:33:50.4 & -38.7 & 31      & 4601         & 2.50         & 0.44         & 0.03             & 0.34               & -0.11       & 0.88        & \ding{55} & \ding{51}  & \ding{55}  \\
-%J000444.87+400402.1 & 00:04:44.88 & +40:04:02.1 & -94.7 & 53      & 4172         & 1.46         & -0.08        & 0.09             & 0.72               & 0.03        & 0.91        & \ding{55} & \ding{51}  & \ding{55}  \\
-%J000552.76+261849.3 & 00:05:52.76 & +26:18:49.4 & -22.5 & 73      & 4924         & 3.14         & -0.05        & 0.09             & 0.67               & 0.28        & 0.85        & \ding{55} & \ding{51}  & \ding{55}  \\
-%J000737.70+394055.5 & 00:07:37.70 & +39:40:55.6 & -31.5 & 33      & 4700         & 2.80         & -0.04        & 0.07             & 0.28               & -0.13       & 0.81        & \ding{55} & \ding{51}  & \ding{55}  \\ \hline
-%\end{tabular}
-%\end{adjustbox}
-%\end{table*}
 
@@
 We acquired calibration (biases, milky, quartz, and Th-Ar arc lamp) frames in the afternoon.
-
-We reduced the data using the \texttt{CarPy} Python package \citep{kelson2000,kelson2003}.
-We used spline functions to continuum-normalise individual echelle orders, and resampled the normalised spectra onto a uniform-sized wavelength map.
-We used a rest-frame normalised template of a FGK-type star to place the observed spectra in the rest frame.
+We reduced the data using the \texttt{CarPy} package \citep{kelson2000}.
+We used spline functions to continuum-normalise all echelle orders, and resampled the normalised spectra onto a uniform-sized wavelength map.
+We used a rest-frame normalised template of a FGK-type star to place the observed spectra at rest.
 
@@
 \begin{figure}
-	\includegraphics[width=\columnwidth]{hrd_new.pdf}
-    \caption{Effective temperature $T_{\rm eff}$ and surface gravity $\log{g}$ for 257 candidate barium stars from LAMOST.
-Stars with $\log{g} > 2$ (as marked) have not evolved through the thermally pulsing asymptotic giant branch phase, and therefore their abundance signature must be the result of an extrinsic pollution event.
+\centering
+	\includegraphics[width=0.4\textwidth]{hrd_new.pdf}
+    \caption{Effective temperature $T_{\rm eff}$ and surface gravity $\log{g}$ for 257 candidate barium stars from LAMOST.}
+    %Stars with $\log{g} > 2$ (as marked) have not evolved through the thermally pulsing asymptotic giant branch phase, and therefore their abundance signature must be the result of an extrinsic pollution event.
 The classification of stars with $\log{g} < 2$ would require additional data.}
@@
 
+\begin{figure}
+	\includegraphics[width=0.5\textwidth]{yields_test.pdf}
+    \caption{Metallicities ([Fe/H]; x-axis) and heavy-to-light s-process abundance ratios ([Ba/Sr] as measured from LAMOST; y-axis) for 257 barium star candidates.
+Coloured lines blue, orange, and green, indicate surface [hs/ls] yields from \citet{cristallo2015} for different masses.
+Coloured lines red, purple, and brown indicate surface [hs/ls] yields from \citet{karakas_lugaro2016} for [Fe/H] at +0.3.
+0.0, and -0.3.
+From \citet{karakas2018} for [Fe/H] at -0.7, and from \citet{fishlock2014} for [Fe/H] at -1.2.}
+    \label{fig:figure3}
+\end{figure}
+
 \subsection{Carbon bands}
-barium stars are excellent candidates for investigating the relationship between neutron-capture elements and other species that may be depleted or enhanced, since iron within these stars act as neutron seeds during the operation of the s-process.
+Barium stars are excellent candidates for investigating the relationship between neutron-capture elements and other species that may be depleted or enhanced, since iron within these stars act as neutron seeds during the operation of the s-process.
 In the AGB phase the abundance of carbon is a product of helium fusion, specifically the triple-alpha process within a star.
@@
 Despite our LAMOST sample of 454,180 giants having metallicities down to about $[{\rm Fe/H}] = -2$, we only detect barium stars down to metallicities of about $[{\rm Fe/H}] = -1.1$.
-Given our barium stars exist in this metallicity range of 0 to -1.1, we can dfeine them as CH stars as done in previous literature \citep[e.g.][]{luck1991, mcclure1997}.
+Given our barium stars exist in this metallicity range of 0 to -1.1, we can define them as CH stars as done in previous literature \citep[e.g.][]{luck1991, mcclure1997}.
 
@@
 The Salpeter initial mass function (or any bottom-heavy initial mass function) predicts the majority of stars in the Milky Way will have lower masses, and as predicted the [Ba/Sr] values of our barium stars approximately fit the lower mass yields as seen in Figure \ref{fig:figure3}.
-However, it's important to note, our results do not indicate when the mass transfer occured, and our candidates fitting these theoratical yeilds may not have the correlating binary companion masses.
-Instead, mass transfer may have occured early on in the AGB S binary companion star's lifespan, and the resulting [Ba/Sr] abundance present in our barium candidates may relfect pollution from a lower ABG S star mass.
-Additionally, this can be extended to our candidates not approximated by theoratical yeilds.
+However, it's important to note, our results do not indicate when the mass transfer occurred, and our candidates fitting these theoretical yields may not have the correlating binary companion masses.
+Instead, mass transfer may have occurred early on in the AGB S binary companion star's lifespan, and the resulting [Ba/Sr] abundance present in our barium candidates may reflect pollution from a lower ABG S star mass.
+Additionally, this can be extended to our candidates not approximated by theoretical yields.
 Other barium candidates not fitting this relationship represent the possibly more massive, and expectedly rarer, AGB S stars within our sample.
-
-\begin{figure}
-	\includegraphics[width=\columnwidth]{yields_test.pdf}
-    \caption{Metallicities ([Fe/H]; x-axis) and heavy-to-light s-process abundance ratios ([Ba/Sr] as measured from LAMOST; y-axis) for 257 barium star candidates.
-Coloured lines blue, orange, and green, indicate surface [hs/ls] yields from \citet{cristallo2015} for different masses.
-Coloured lines red, purple, and brown indicate surface [hs/ls] yields from \citet{karakas_lugaro2016} for [Fe/H] at +0.3.
-0.0, and -0.3.
-From \citet{karakas2018} for [Fe/H] at -0.7, and from \citet{fishlock2014} for [Fe/H] at -1.2.}
-    \label{fig:figure3}
-\end{figure}
 
@@
 \section*{Acknowledgements}
-We thank  Alex Ji (Carnegie Observatories), David W. Hogg (NYU), Melissa Ness (Columbia), and Hans-Walter Rix (MPIA) for useful discussions. 
+We thank David W. Hogg (NYU) and Hans-Walter Rix (MPIA) for useful discussions. 
 A.~R.~C. is supported through an Australian Research Council Discovery Project under grant DP160100637.
@@
 LAMOST is operated and managed by the National Astronomical Observatories, Chinese Academy of Sciences.
-This work has made use of data from the European Space Agency (ESA) mission Gaia (http://www.cosmos.esa.int/gaia), processed by the Gaia Data Processing and Analysis Consortium (DPAC, http://www.cosmos.esa.int/web/gaia/dpac/consortium).
+%This work has made use of data from the European Space Agency (ESA) mission Gaia (http://www.cosmos.esa.int/gaia), processed by the Gaia Data Processing and Analysis Consortium (DPAC, http://www.cosmos.esa.int/web/gaia/dpac/consortium).
 Funding for the DPAC has been provided by national institutions, in particular the institutions participating in the Gaia Multilateral Agreement.
@@
 Kelson, D.~D., Illingworth, G.~D., van Dokkum, P.~G.,\& Franx, M. 2000, ApJ, 531, 159
-\bibitem[\protect\citeauthoryear{Kelson}{2003}]{kelson2003}
-Kelson, D.~D. 2003, 
-PASP, 115, 688
+%\bibitem[\protect\citeauthoryear{Kelson}{2003}]{kelson2003}
+%Kelson, D.~D. 2003, 
+%PASP, 115, 688
 %\bibitem[\protect\citeauthoryear{Kobayashi et al.}{2011}]{kobayashi2011}
@@
 A$\&$A, 597, A68
-
 \end{thebibliography}
-
 % Don't change these lines

### 2018-02-23 article/ms.tex
5 pages fuck you mnrasl

@@
 
-% FOR SOME REASON LATEX FALLS OVER IF WE DONT HAVE IT HERE
-\begin{table}\end{table}
-
 \renewcommand\labelenumi{(\roman{enumi})}
@@
 Nevertheless, this sample still constitutes the largest collection of barium stars ever discovered, with the next sample of significant size containing 182 barium stars \citep[e.g.,][]{decastro2016}.
+
+\begin{table*}
+\centering
+\caption{Properties of 967 s-process candidates, the table is available online in its entirety. Here we show a portion to demonstrate its style and content.}
+\label{table:table1}
+\begin{adjustbox}{width=1\textwidth}
+\begin{tabular}{@{}|l|l|c|c|c|c|c|c|c|c|c|c|c|c|c|@{}}
+\toprule
+2MASSID             & R.~A.
+& Dec.
+& $v_{r}$ & S/N & $\rm T_{\rm eff}$ & $\log{g}$ & [Fe/H] & [$\alpha$/Fe] & $\chi_r^2$ & [Ba/Fe] & [Sr/Fe] & \ion{Ba}{II} & \ion{Sr}{II} &  \ion{Ba}{II} \& \ion{Sr}{II} \\
+& (J2000) & (J2000) & (km\,s$^{-1}$) & (pixel$^{-1}$) & (K)  \\ \midrule
+J000019.26+501444.8 & 00:00:19.27 & +50:14:44.9 & -3.9  & 49      & 4973         & 3.27         & 0.21         & 0.08             & 0.66               & 0.25        & 0.83        & \ding{55} & \ding{51}  & \ding{55}   \\
+J000020.55+411348.1 & 00:00:20.56 & +41:13:48.2 & -28.2 & 32      & 4882         & 2.74         & -0.22        & 0.04             & 0.23               & -0.17       & 0.90        & \ding{55}& \ding{51}  & \ding{55}    \\
+J000134.95+490743.2 & 00:01:34.96 & +49:07:43.2 & -42.3 & 72      & 5044         & 3.11         & -0.54        & 0.11             & 0.79               & 1.02        & 0.45        & \ding{55} & \ding{55} & \ding{51}  \\
+J000258.09+410730.0 & 00:02:58.10 & +41:07:30.1 & -34.5 & 41      & 4697         & 2.57         & -0.22        & 0.12             & 0.98               & -0.10       & 0.80        & \ding{55} & \ding{51}  & \ding{55}  \\
+J000403.80+160257.1 & 00:04:03.80 & +16:02:57.2 & -35.4 & 42      & 5200         & 3.40         & -0.41        & 0.09             & 0.33               & 0.92        & 0.52        & \ding{55} & \ding{55} & \ding{51}  \\
+J000439.16+183350.3 & 00:04:39.17 & +18:33:50.4 & -38.7 & 31      & 4601         & 2.50         & 0.44         & 0.03             & 0.34               & -0.11       & 0.88        & \ding{55} & \ding{51}  & \ding{55}  \\
+J000444.87+400402.1 & 00:04:44.88 & +40:04:02.1 & -94.7 & 53      & 4172         & 1.46         & -0.08        & 0.09             & 0.72               & 0.03        & 0.91        & \ding{55} & \ding{51}  & \ding{55}  \\
+J000552.76+261849.3 & 00:05:52.76 & +26:18:49.4 & -22.5 & 73      & 4924         & 3.14         & -0.05        & 0.09             & 0.67               & 0.28        & 0.85        & \ding{55} & \ding{51}  & \ding{55}  \\
+J000737.70+394055.5 & 00:07:37.70 & +39:40:55.6 & -31.5 & 33      & 4700         & 2.80         & -0.04        & 0.07             & 0.28               & -0.13       & 0.81        & \ding{55} & \ding{51}  & \ding{55}  \\ \hline
+\end{tabular}
+\end{adjustbox}
+\end{table*}
 
@@
 \begin{figure}
-\centering
-	\includegraphics[width=0.4\textwidth]{hrd_new.pdf}
+	\includegraphics[width=0.5\textwidth]{hrd_new.pdf}
     \caption{Effective temperature $T_{\rm eff}$ and surface gravity $\log{g}$ for 257 candidate barium stars from LAMOST.}
@@
 LAMOST is operated and managed by the National Astronomical Observatories, Chinese Academy of Sciences.
-%This work has made use of data from the European Space Agency (ESA) mission Gaia (http://www.cosmos.esa.int/gaia), processed by the Gaia Data Processing and Analysis Consortium (DPAC, http://www.cosmos.esa.int/web/gaia/dpac/consortium).
+This work has made use of data from the European Space Agency (ESA) mission Gaia (http://www.cosmos.esa.int/gaia), processed by the Gaia Data Processing and Analysis Consortium (DPAC, http://www.cosmos.esa.int/web/gaia/dpac/consortium).
 Funding for the DPAC has been provided by national institutions, in particular the institutions participating in the Gaia Multilateral Agreement.

### 2018-04-15 article/ms.tex
i got git work good

@@
 In this paper we present the discovery of 967 s-process candidates from 454,180 giant stars observed by LAMOST: this sample constitutes the largest number of s-process enhanced stars ever discovered.
-We identify these stars in the LAMOST sample by using a data-driven search approach on the spectra directly, and then measure the s-process abundance enhancements directly using stellar synthesis.
-Finally, we validate our results using high resolution spectra of a number of candidates.
+We identify these stars in the LAMOST sample by using a data-driven search approach on the spectra directly, and then measure the s-process abundance enhancements using stellar synthesis.
+Finally, we take advantage of free observing time, and obtain high resolution spectra of a number of candidates.
 Our sample includes; 257 'barium stars', that are enhanced in both barium and strontium, 49 stars with significant barium enhancement only, and 661 stars which exhibit strontium enhancement only.
@@
 We argue this may have been a selection bias in previous studies.
-A comparison with AGB yields suggests that the majority of our sample are consistent with Salpeter-like initial mass function, with pollution from a low mass AGB star.
+A comparison with AGB yields suggests the main neutron source responsible for the Ba and Sr enhancements is the $C^{13}(\alpha,n)O^{16}$ reaction chain.
+Additionally, theoretical models show that this source is dominant in low-mass AGB stars thus, it follows that most of the progenitors of s-process elements in our sample are low-mass AGB stars between $1 - 3\,M_{\odot}$.
 
-%The abundances of the slow neutron capture process (s-process) elements in stars are a measure of the nucleosyntheic processes that occur primarily in Asymptotic Giant Branch (AGB) stars.
+%that the majority of our sample are consistent with Salpeter-like initial mass function, with pollution from a low mass AGB star.
+
+%The abundances of the slow neutron capture process (s-process) elements in stars are a measure of the nucleosynthetic processes that occur primarily in Asymptotic Giant Branch (AGB) stars.
 Due to their associated enrichment of the s-process element barium, stars with peculiar enhancements of carbon and heavy elements (Z > 30) are historically referred to as 'barium stars'.
@@
 
-The abundances of the slow neutron capture process (s-process) elements in stars are a measure of the nucleosyntheic processes that occur primarily in Asymptotic Giant Branch (AGB) stars.
-Due to their associated enrichment of the s-process element barium, stars with peculiar enhancements of carbon, and heavy elements (Z > 30) are historically referred to as 'barium stars' as first recognised by \citet{Bidelman1951}.
-Barium enhanced stars exist as either intrinsic or extrinsic objects, stars intrinsically enhanced in barium and other s-process elements are known as AGB S stars.
-These stars are in the TP-AGB (thermally pulsing-asymptotic giant branch) phase, where the overabundance of both carbon and heavy elements produced through the slow neutron capture process and exist on the surface as the result of a thermal pulsing cycle.
-According to the mass-transfer hypothesis, extrinsic barium stars are a consequence of stellar wind accretion \citep{boffin1988,jorissen1992} or Roche-lobe overflow \citep{webbink1986}, and are within a binary system containing a previous TP-AGB companion star (AGB S star) in its final phase as a white dwarf \citep{bohm1980,bohm1984}.
-In fact, \citet{mcclure1983} determined 85\% of all barium stars are in binary systems and claimed that those that appear to be singular are actually pole-on, or highly eccentric binaries with significant radial velocity variations only occurring in a small ranges as detailed by \citet{pourbaix2004}.
+The abundances of the slow neutron capture process (s-process) elements in stars are a measure of the nucleosynthetic processes, that occur primarily in Asymptotic Giant Branch (AGB) stars.
+Due to their associated enrichment of the s-process element barium, stars with peculiar enhancements of carbon, and heavy elements (Z > 30) are referred to as 'barium stars' as first recognised by \citet{Bidelman1951}.
+The naming convention associated with barium stars is historical, it is therefore, for the purposes of this paper, necessary to classify definitions used for subsequent discussions.
+Barium enhanced stars exist as either extrinsic or intrinsic objects, extrinsic barium stars are stellar phenomena exhibiting s-process element enhancement as the result of some polluting process.
+Stars intrinsically enhanced in barium and other s-process elements are known as AGB S stars.
+These stars are in the TP-AGB (thermally pulsing-asymptotic giant branch) phase.
+During this stage of nucleosynthesis, this is an overabundance of both carbon and heavy elements produced through the slow neutron capture process, and exist on the surface as the result of a thermal pulsing cycle.
+According to the mass-transfer hypothesis, extrinsic barium stars are a consequence of stellar wind accretion \citep{boffin1988,jorissen1992} or Roche-lobe overflow \citep{webbink1986}.
+Both dynamical systems require a binary configuration a previous TP-AGB companion star (AGB S star), in its final phase as a white dwarf \citep{bohm1980,bohm1984}.
+In fact, \citet{mcclure1983} determined 85\% of all barium stars exist within binary systems.
+They further claimed that stellar objects which appeared to be singular are actually pole-on, or highly eccentric binaries with significant radial velocity variations, only occurring in a small ranges as detailed by \citet{pourbaix2004}.
 For these reasons, the properties and occurrence rate of barium stars are informative of the binary star fraction as a function of metallicity, the mass ratio of binary stars, as well as AGB yields across different masses and metallicities.
@@
 The energy from the thermal pulses forces the star to expand, pushing the H-shell out to cooler regions and allowing the convective envelope to move inwards to regions previously mixed by the thermal pulse driven convective zones.
-This phase of expansion and resulting inward movement called the third dredge up (TDU), and is theorised to occur after each thermal pulse.
+This phase of expansion and resulting inward movement is defined as the third dredge up (TDU), and is theorised to occur after each thermal pulse.
 During the TP-AGB phase, surface enrichment in $^{12}$C and heavy elements produced by the s-process, is a result of the repeated inward extensions of TDU \citep[e.g.,][]{busso2001}.
@@
 In contrast, metal-rich, less massive stars may reach ages of $\approx$ 100Myr, this includes stars that are at the core carbon burning limit or very close to it \citep[e.g.,][]{whitelock2013}.
-Furthermore, metal rich stars enhanced in barium are defined in the literature as Bariu stars.
+Furthermore, metal rich stars enhanced in barium are defined in the literature classically as barium stars.
 
@@
 In \citet{pereira2011} it is concluded that metal-rich barium stars share similar kinematics to other metal-rich and super metal-rich stars already analysed, suggesting that they do not belong to the bulge population.
-It remains necessary to establish known abundances of s-process elements in a greater sample of barium stars in order to compare their birth rate to theoretical expectations \citep{han1995}, to explore the binary fraction at different metallicities, and then to compare to AGB star yields at different masses and metallicities.
+It remains necessary to establish known abundances of s-process elements in a greater sample of barium stars in order to: compare their birth rate to theoretical expectations \citep{han1995}, explore the binary fraction at different metallicities, and compare to AGB star yields at different masses and metallicities.
 %The relationship between barium stars in the halo \citep[e.g.,][]{junqueira2001,drake2008,pereira2009,allen2006} and metal-poor, yellow, symbiotic halo stars has been established by \citet{jorissen2005} and \citet{pereira2009}.
@@
 In this paper we analyse 454,180 giant stars from the second LAMOST data release \citep{luo2015} and identify 967 s-process candidates.
-In Section \ref{sec:methods} we describe the observations and candidate selection, as well as the analysis of high-resolution follow-up observations obtained for a few candidates.
-In Section \ref{sec:dis} we discuss the properties of our barium stars in context of existing literature.
+In Section \ref{sec:methods}, we describe the observations and candidate selection.
+Section \ref{sec:observations} details the analysis of high-resolution follow-up observations obtained for a few candidates.
+In Section \ref{sec:dis}, we discuss the properties of our barium stars in context of existing literature.
 We provide concluding remarks in Section \ref{sec:con}.
@@
 The LAMOST (Large sky Area Multi-Object Fibre Spectrographic) survey released low-resolution ($\mathcal{R} \approx 1800$) optical spectra (3700\,\AA\ to 9000\,\AA) for over two million stars in their second data release \citep{luo2015}.
-Stellar parameters ($T_{\rm eff}$, $\log{g}$, [M/H], [$\alpha$/M]) were derived using a data-driven model constructed using high fidelity APOGEE labels of 9,952 giant stars in common between LAMOST and the APOGEE survey \citep{ho2017}.
+Stellar parameters ($T_{\rm eff}$, $\log{g}$, [M/H], [$\alpha$/M]) were derived using a data-driven model, and constructed using high fidelity APOGEE labels of 9,952 giant stars in common between LAMOST and the APOGEE survey \citep{ho2017}.
 This data-driven model was used to estimate stellar labels for 454,180 giant stars.
 We note that this sample is exclusively giant stars, implying that we would not identify dwarf s-process enhanced stars.
-Cross-validation tests shows that the typical uncertainties are about 70\,K in effective temperature $\rm T_{\rm eff}$, 0.1\,dex in surface gravity $\log{g}$, 0.1\,dex in metallicity [M/H], and 0.04\,dex in the $\alpha$-element abundance relative to overall metallicity [$\alpha$/M].
+Cross-validation tests shows that the typical uncertainties are approximately 70\,K in effective temperature $\rm T_{\rm eff}$, 0.1\,dex in surface gravity $\log{g}$, 0.1\,dex in metallicity [M/H], and 0.04\,dex in the $\alpha$-element abundance relative to overall metallicity [$\alpha$/M].
 These uncertainties are comparable to the APOGEE uncertainties \citep{alam2015}.
@@
 \subsubsection{Candidate selection} \label{sec:cand}
-The barium stars analysed in this research were obtained by filtering for significant flux residuals, taken as a disparity between the normalised LAMOST flux and the data driven model derived by \citet{ho2017}.
+The barium stars analysed in this research were obtained by filtering for significant flux residuals, taken as a disparity between the normalised LAMOST flux and the data driven model, \emph{The Cannon}, derived by \citet{ho2017}.
 Specifically, we identified barium stars by searching for \ion{Ba}{II} and \ion{Sr}{II} enhancement at the 4554\,\AA\ and 4077\,\AA\ wavelengths, respectively.
 A negative residual, as shown in a candidate barium star in Figure \ref{fig:figure1}, illustrates an enhancement in the \ion{Ba}{II} and \ion{Sr}{II} lines at 4554\,\AA\, and 4077\,\AA, respectively.
-These \ion{Ba}{II} and \ion{Sr}{II} resonance lines are very strong, allowing us to identify stars enhanced in neutron-capture elements given a well-fit model for the data.
+These \ion{Ba}{II} and \ion{Sr}{II} resonance lines are very strong, allowing us to identify stars enhanced in neutron-capture elements, given a well-fit model for the data.
 Stars identified high levels of barium (and not necessarily strontium) required enhancement in both the 4554\,\AA\ and 4934\,\AA\ \ion{Ba}{II} resonance lines, and for stars exclusively enhanced in strontium we looked for significant residuals at the 4077\,\AA\ and 4215\,\AA\ absorption lines.
@@
 In addition, a visual inspection was undertaken to exclude any results containing false positives, candidates exhibiting data reduction issues, apparent absorption finer then the spectral resolution, and overly noisy normalised LAMOST spectra.
-This combined method generated 967 s-process rich candidates which are provided in Table 1 (online only material) including; 257 `barium stars' enhanced in both barium and strontium, 49 stars exhibiting exclusively barium enhancement, and 661 with exclusively strontium enhancement.
+This combined method generated 967 s-process rich candidates which are provided in Table 1, for which a portion is shown to demonstrate its style and content, it's available online in its entirety.
+This stellar sample consists of; 257 `barium stars' enhanced in both barium and strontium, 49 stars exhibiting exclusively barium enhancement, and 661 with exclusively strontium enhancement.
 
 For the remainder of this paper we restrict our analysis to the 257 classical `barium stars' stars that show enhancement in both barium and strontium.
-While the 49 or 661 stars with only barium or strontium enhancements (respectively) may also be bonafide barium stars, there may be other explanations for their chemical abundance pattern \citep[e.g.,][]{maiorca2011}, and so we restrict our inferences to a `gold sample' of barium stars.
+While the 49 or 661 stars with only barium or strontium enhancements (respectively) may also be bona fide barium stars, there may be other explanations for their chemical abundance pattern \citep[e.g.,][]{maiorca2011}, and so we restrict our inferences to a `gold sample' of barium stars.
 
@@
 Furthermore, as discussed in section \ref{sec:other enhancements}, an enhancement in carbon is observed frequently with barium enhancement.
-$\rm J092155.95+265253.4$ shows both a negative residual at 4554\,\AA\, and carbon enhancement, we therefor conclude that this single deviant case can be classified as a barium star.
+$\rm J092155.95+265253.4$ shows both a negative residual at 4554\,\AA\, and carbon enhancement, we therefore conclude that this single deviant case can be classified as a barium star.
 Additionally, it should be mentioned, our average abundance error is 0.1, although, these results still indicate our sample can be classified as barium stars since they exhibit enhancement at the BaII resonance line 4554, and have a $\rm[Ba/Fe] \geq 0.2$.
@@
 We performed an identical analysis to the process described in Section \ref{sec:cand} in order to identify sodium, technetium, or carbon enhancement in our sample of 257 barium stars.
-We used the sodium doublet lines at 5889\,\AA\ and 5895\,\AA\ to select barium stars enhanced in sodium, and required significant absorption in both features.
+We used the sodium doublet lines at 5889\,\AA\ and 5895\,\AA\, and required significant absorption in both features.
 Only 5/257 barium stars met this criteria.
@@
 For technetium enhancement we searched for significant residual deviations at 4049\,\AA, 4238\,\AA, 4262\,\AA, 4297\,\AA, and 5924\,\AA.
-These absorption lines are extremely weak, and would require a substantial amount of technetium before it would be visible in a high S/N LAMOST spectrum.
-We found that 51 barium stars exhibited some level of significant enhancement (based on the filters above) at a single technetium line, yet none showed enhancement at more than one technetium line.
-We note that the single enhancement near technetium for these 51 stars may be the consequence of data reduction/calibration artefacts, but we include details of which stars matched on technetium in Table 1 nonetheless.
+These absorption lines are extremely weak, and would require a substantial amount of technetium enhancement before it would be visible in a high S/N LAMOST spectrum.
+We found that 51 barium stars exhibited some level of significant enhancement (based on the filters above) at the single technetium line 4238\,\AA, yet none showed enhancement at more than one technetium line.
+We note that the single enhancement near technetium for these 51 stars may be the consequence of data reduction/calibration artefacts, but we include details of which stars matched on technetium in Table 1 (available online in its entirety) nonetheless.
 Finally, for carbon enhancement we searched for significant deviations at the CH and G band near 4300\,\AA.
@@
 
-\section{Follow-up observations with Magellan/MIKE}
+\section{Follow-up observations with Magellan/MIKE} \label{sec:observations}
 
@@
 \subsection{Extrinsic or intrinsic}
-Barium enhanced stars exist as either intrinsic or extrinsic objects.
+Barium enhanced stars exist as either intrinsic or extrinsic stellar objects.
 Intrinsically enhanced barium stars must be massive enough to reach the TP-AGB phase, and extrinsic barium stars must be in a binary with a previously polluting TP-AGB star companion (AGB S star).
-Figure \ref{fig:figure2} shows that the majority of our stellar sample exists within temperature and luminosity ranges not enveloped by the AGB, highlighting that all stars in our sample are not evolved enough to have already reached the TP-AGB phase and therefore, must be extrinsic barium stars.
-Although, it is noted, stars with temperatures below 3800K in Figure \ref{fig:figure2} are possible AGB stars, and their intrinsic or extrinsic nature is not certain.
-It is noted, in the previous literature \citep{van2017}, only 22\% of their stellar sample are post-main-sequence barium stars (extrinsic barium stars).
+Figure \ref{fig:figure2} shows that the majority of our stellar sample exists within temperature and luminosity ranges not enveloped by the AGB.
+This highlights that our sample does not contain stars to the degree of evolution required to reach the TP-AGB phase, and therefore, must be extrinsic barium stars.
+However, stars with temperatures below 3800K in Figure \ref{fig:figure2} are potential AGB stars, and their intrinsic or extrinsic nature is not certain.
+Additionally, it's important to note, previous literature \citep{van2017}, state only 33\% of their stellar sample are post-main-sequence barium stars (extrinsic barium stars).
 In comparison, we find that all our barium candidates to be extrinsic.
-This suggests, the construction of our data-driven model may have missed some AGB barium candidates, or that previous studies were biased towards finding luminous intrinsic AGB barium stars.
+This suggests, the construction of our data-driven model may have missed some AGB barium candidates, or that previous studies were biased towards finding luminous AGB S stars.
 Given that our analysis limits us to only giant stars, such that we do not find any extrinsic barium stars on the main-sequence, na\"ively we would expect that our sample would be biased \emph{towards} finding a higher fraction of red giant stars.
-Given this bias, Figure \ref{fig:figure3} illustrates through the temperature, and log g ranges present, that our sample is entirely populated by red giant extrinsic barium stars.
+Given this bias, Figure \ref{fig:figure3} illustrates through the temperature, and log g ranges present, that our sample is exclusively populated by red giant extrinsic barium stars.
 This suggests unaccounted selection biases in previous studies towards luminous AGB S stars.
@@
 
-\subsection{Sodium enhancment}
+\subsection{Sodium enhancement}
 Sodium overabundances observed in the atmospheres of giants is thought to be synthesised by the NeNa reaction chain in the convective core of main-sequence stars \citep{el1995}.
-Sodium is transported to the surface of these giants via mixing during the first dredge-up and stars with a  minimum mass of $1.5\,M_\odot$ can exhibit enhanced sodium abundances through the NeNa cycle \citep{denissenkov1987,smiljanic2012}.
+Sodium is transported to the surface of these giants via mixing during the first dredge-up, and stars with a  minimum mass of $1.5\,M_\odot$ can exhibit enhanced sodium abundances through the NeNa cycle \citep{denissenkov1987,smiljanic2012}.
 \citet{antipova2004} reported sodium enhancements in 3 of their 16 barium star candidates, and they relate this to the dredge-up of nuclear-burning material produced by convection during the red-giant phase.
@@
 We find that $<2$\,\% of our barium stars show sodium enhancement, contrary to previous studies \citep[e.g.,][]{decastro2016}, indicating all s-process enhanced stars will exhibit Na enhancement.
-We also note that the 5 sodium-enhanced barium stars all have $\log{g} \approx 3$, not at lower $\log{g}$ values as might be expected if low $\log{g}$ values systematically contributed to higher [Na/Fe] abundance ratios.
+We also note that the 5 sodium-enhanced barium stars all have values of, $\log{g} \approx 3$, which is inconsistent with the literature.
+Previous studies suggest, lower $\log{g}$ values are expected, given low $\log{g}$ values systematically contribute to higher [Na/Fe] abundance ratios.
 It is important to note, sodium enhancement can occur due to the presence of interstellar dust.
@@
 
-The data that led \citet{decastro2016} to conclude that barium stars have higher [Na/Fe] ratios came from many literature sources.
-Therefore, it is possible that there are systematic differences (biases) between Milky Way studies of normal FGK-type stars and those focussed on barium stars, leading to unresolved differences in the reported [Na/Fe] abundance ratio.
+The data that led \citet{decastro2016} to conclude that barium stars have higher [Na/Fe] ratios is subject to systematic differences (biases) between Milky Way studies of normal FGK-type stars, and those focussed on barium stars.
+This has the potential to contain unresolved differences in the reported [Na/Fe] abundance ratio.
 These systematic effects would also contribute to the observed correlation between [Na/Fe] and $\log{g}$, since intrinsic barium stars (by definition) have low $\log{g}$ values.
-We do not observe this correlation between [Na/Fe] and $\log{g}$ in our sample.
-From our data we conclude that barium stars do not have higher [Na/Fe] abundance ratios on average, and suggest that the effect seen in previous works was due to systematic effects between literature sources.
+We do not observe this correlation between [Na/Fe] and $\log{g}$ in our sample, and we conclude that barium stars do not have higher [Na/Fe] abundance ratios on average.
 
@@
 
-Technetium has a half life of approximately 211,000 years and as a result, the presence of Tc enhacnement is constrained to observations of AGB S stars \citep{jorissen1993} or recently polluted extrinsic barium stars.
-Our analysis discovered 51 single Tc line matches within our 257 barium star candidate sample.
+Technetium has a half life of approximately 211,000 years and as a result, the presence of Tc enhancement is constrained to observations of AGB S stars \citep{jorissen1993} or recently polluted extrinsic barium stars.
+Our analysis, undertaken for the TC lines 4049\,\AA, 4238\,\AA, 4262\,\AA, 4297\,\AA, and 5924\,\AA, discovered 51 single Tc line matches at 4238,\AA, within our 257 barium star candidate sample.
 The majority (46/51) have $\log{g} > 2$, suggesting they cannot be AGB S stars, and may indicate a recent ($<1\,\textrm{Myr}$) mass accretion event.
 However, for Tc to be present in the LAMOST spectra the enhancement must be considerably strong, and given that all 51 matches were at single lines it is concluded that these results are more likely data artefacts.
-In agreement with previous findings \citep[e.g.,][]{little1987,smith1984,smith1983}, the results indicate that none of the evolved barium stars in our sample exhibited the presence of Tc enhancement, and it can be concluded our barium star sample is extrinsic.
+In agreement with previous findings \citep[e.g.,][]{little1987,smith1984,smith1983}, the results indicate that none of the evolved barium stars in our sample exhibited the presence of Tc enhancement, and in accordance with previous literature, it can be concluded that our barium star sample is extrinsic.
 However, we caution that Tc enhancement is usually a very weak signature, and the presence of Tc would require multiple lines of enhancement.
+Additionally, it is universally known that numerous Tc lines are considerably blended by other s-process enhancement lines \citep[e.g.,][]{van1999}.
 
@@
 Our analysis produced 178 CH and G band significantly enhanced stars (i.e., $[\textrm{C/Fe}] \gtrsim 0.5$) out of the total 257 barium candidates.
-These 178 stars exist in a metallicity range of 0 to -1.2, and can be termed "CH stars" are defined in previous literature \citep[e.g.][]{luck1991, mcclure1997}.
+These 178 stars exist in a metallicity range of 0 to -1.2, and can be termed "CH stars" in accordance with definitions used in the literature \citep[e.g.][]{luck1991, mcclure1997}.
 %Similar to the s-process enhancement, this suggests our candidates are consistent with being either intrinsic or extrinsic Barium stars.
@@
 \subsection{Comparison to AGB yields}
-AGB stars, and chemically unusual stars that show the chemical signature of mass transfer pollution from binary companion AGB stars, highlight the variety of s-process enhancement.
+AGB stars, and chemically unusual stars that show the chemical signature of mass transfer pollution from a binary AGB companion, highlight the variety of s-process enhancement.
 In Figure \ref{fig:figure3} we show the heavy-to-light s-process abundance ratio (taken as [Ba/Sr]) for all 257 barium stars identified in LAMOST.
@@
 Despite our LAMOST sample of 454,180 giants having metallicities down to about $[{\rm Fe/H}] = -2$, we only detect barium stars down to metallicities of about $[{\rm Fe/H}] = -1.1$.
-Given our barium stars exist in this metallicity range of 0 to -1.1, we can define them as CH stars as done in previous literature \citep[e.g.][]{luck1991, mcclure1997}.
+Given our barium stars exist in this metallicity range of 0 to -1.1, we can classify them as CH stars as defined in previous literature \citep[e.g.][]{luck1991, mcclure1997}.
 
-The final surface s-process index [Ba/Sr], illustrated in Figure \ref{fig:figure3}, highlights the relationship between [Ba/Sr] yields and the mass of AGB stars.
-The Salpeter initial mass function (or any bottom-heavy initial mass function) predicts the majority of stars in the Milky Way will have lower masses, and as predicted the [Ba/Sr] values of our barium stars approximately fit the lower mass yields as seen in Figure \ref{fig:figure3}.
+The final surface s-process index [Ba/Sr], illustrated in Figure \ref{fig:figure3}, illustrates the relationship between [Ba/Sr] yields and the mass of AGB stars.
+This highlights the main neutron source, the $C^{13}(\alpha,n)O^{16}$ reaction chain, is responsible for the Ba and Sr enhancements.
+Additionally, theoretical models show that this source is dominant in low-mass AGB stars, and it follows, that most of the progenitors of s-process elements in our sample are low-mass AGB stars between $1 - 3\,M_{\odot}$.
 However, it's important to note, our results do not indicate when the mass transfer occurred, and our candidates fitting these theoretical yields may not have the correlating binary companion masses.
-Instead, mass transfer may have occurred early on in the AGB S binary companion star's lifespan, and the resulting [Ba/Sr] abundance present in our barium candidates may reflect pollution from a lower ABG S star mass.
+Instead, mass transfer may have occurred early on in the AGB S binary companion star's lifespan, and the resulting [Ba/Sr] abundance present in our barium candidates may reflect pollution from a lower AGB S star mass.
 Additionally, this can be extended to our candidates not approximated by theoretical yields.
 Other barium candidates not fitting this relationship represent the possibly more massive, and expectedly rarer, AGB S stars within our sample.
+
+%The Salpeter initial mass function (or any bottom-heavy initial mass function) predicts the majority of stars in the Milky Way will have lower masses, and as predicted the [Ba/Sr] values of our barium stars approximately fit the lower mass yields as seen in Figure \ref{fig:figure3}.
 
@@
 We conducted the largest ever search for s-process enhanced stars using the LAMOST second data release.
-From 454,180 giant stars, we identify 967 s-process candidates including: 257 stars with significant enhancements in barium and strontium (so-called `barium stars'); 49 stars exhibiting exclusively barium enhancement, and 661 exhibiting exclusively strontium enhancement.
+From 454,180 giant stars, we identify 967 s-process candidates including: 257 stars with significant enhancements in barium and strontium (so-called `barium stars'), 49 stars exhibiting exclusively barium enhancement, and 661 exhibiting exclusively strontium enhancement.
 This sample size is the greatest total number of barium stars known, and represents the largest sample of s-process enhanced stars to date.
@@
 
-Despite our noisy estimates of [Ba/Fe] and [Sr/Fe] from LAMOST spectra, comparisons with AGB yields indicate that our sample is consistent with a Salpeter-like initial mass function, and indicate the possible mass of the binary companion to the extrinsic barium star.
+Despite our noisy estimates of [Ba/Fe] and [Sr/Fe] from LAMOST spectra, comparisons with AGB yields indicate the main neutron source responsible for the Ba and Sr enhancements, the $C^{13}(\alpha,n)O^{16}$ reaction chain, and theoretical yields suggest the progenitors of our s-process enhanced sample are low-mass AGB stars, between $1 - 3\,M_{\odot}$.
 We encourage follow-up observations with high-resolution spectrographs in order to precisely measure a full suite of neutron-capture abundances.
@@
 \bibitem[Valenti \& Piskunov(1996)]{sme} Valenti, J.~A., \& Piskunov, N.\ 1996, \aaps, 118, 595 
+\bibitem[\protect\citeauthoryear{Van Eck \& Jorissen}{1999}]{van1999}
+Van Eck, S. \& Jorissen, A. 1999, 
+A$\&$A, 345, 127
 \bibitem[\protect\citeauthoryear{Van der Swaelmen et al.}{2017}]{van2017}

### 2018-04-15 article/plot_hrd.py

@@ -1,0 +1,35 @@
+import matplotlib.pyplot as plt
+from matplotlib.ticker import MaxNLocator
+from astropy.table import Table
+
+data = Table.read("Bastar_candidates.csv")
+
+fig, ax = plt.subplots(figsize=(4, 4))
+
+ax.scatter(data["cannon_teff_1"], data["cannon_logg_1"],
+           facecolor="#000000", edgecolor="#000000", linewidths=1, s=5, zorder=100)
+ax.errorbar(data["cannon_teff_1"], data["cannon_logg_1"],
+            xerr=data["cannon_teff_err_1"], yerr=data["cannon_logg_err_1"],
+            fmt=None, ecolor="#666666", elinewidth=1)
+
+ax.set_xlim(ax.get_xlim()[::-1])
+ax.set_ylim(4, 0)
+ax.set_yticks([0, 1, 2, 3, 4])
+
+lhs = 5400
+separator, offset = (2, 0.10)
+ax.axhline(separator, c="#666666", linestyle=":", zorder=-1, lw=1)
+ax.text(lhs, separator - offset, r"Intrinsic/extrinsic",
+        verticalalignment="bottom", fontdict=dict(color="#666666"))
+ax.text(lhs, separator + offset, r"Extrinsic", 
+        verticalalignment="top", fontdict=dict(color="#666666"))
+
+ax.xaxis.set_major_locator(MaxNLocator(6))
+ax.yaxis.set_major_locator(MaxNLocator(6))
+
+
+ax.set_xlabel(r"Effective temperature $T_{\rm eff}$ $({\rm K})$")
+ax.set_ylabel(r"Surface gravity $\log{g}$")
+
+fig.tight_layout()
+fig.savefig("hrd.pdf", dpi=300)

### 2018-04-15 article/plot_yeilds_b.py

@@ -1,0 +1,65 @@
+import numpy as np
+import matplotlib.pyplot as plt
+from matplotlib.ticker import MaxNLocator
+from astropy.table import Table
+
+data = Table.read("Bastar_candidates_with_abundances.csv")
+
+ba = np.vstack([data["BA_FE_4554"], data["BA_FE_4934"]])
+ba_err = np.vstack([data["BA_FE_4554_err"], data["BA_FE_4934_err"]])
+
+sr = np.vstack([data["SR_FE_4077"], data["SR_FE_4215"]])
+sr_err = np.vstack([data["SR_FE_4077_err"], data["SR_FE_4215_err"]])
+
+sr_avg = np.nanmean(sr, axis=0)
+ba_avg = np.nanmean(ba, axis=0)
+
+ba_err[(ba_err == 0) + ~np.isfinite(ba_err)] = 0.20
+sr_err[(sr_err == 0) + ~np.isfinite(sr_err)] = 0.20
+
+ba_err = np.nanmean(ba_err, axis=0)
+sr_err = np.nanmean(sr_err, axis=0)
+
+hs_ls = ba_avg - sr_avg
+hs_ls_err = np.sqrt(0.2**2 +  ba_err**2 + sr_err**2)
+
+fig, ax = plt.subplots(figsize=(4, 4))
+
+ax.scatter(data["cannon_m_h_1"], hs_ls,
+           facecolor="#000000", edgecolor="#000000", linewidths=1, s=5, zorder=5,
+           label="_")
+ax.errorbar(data["cannon_m_h_1"], hs_ls,
+            xerr=data["cannon_m_h_err_1"], yerr=hs_ls_err,
+            fmt=None, ecolor="#BBBBBB", elinewidth=1, label="_")
+
+
+#cristallo = Table.read("cristallo_data_new.csv")
+#fehs = np.array(cristallo.dtype.names[1:]).astype(float)
+
+#masses = cristallo["Mass/[Fe/H]"]
+
+#colors = {
+    #"2.0": "r",
+    #"3.0": "g",
+#}
+
+#for i, mass in enumerate(masses):
+    #model_hs_ls = [cristallo[feh][i] for feh in cristallo.dtype.names[1:]]
+    #ax.plot(fehs, model_hs_ls, label=r"${{{:.1f}}}\,M_\odot$".format(mass),
+            #lw=5, alpha=0.75)
+
+
[…]

### 2018-04-15 article/plot_yields.py

@@ -1,0 +1,65 @@
+import numpy as np
+import matplotlib.pyplot as plt
+from matplotlib.ticker import MaxNLocator
+from astropy.table import Table
+
+data = Table.read("Bastar_candidates_with_abundances.csv")
+
+ba = np.vstack([data["BA_FE_4554"], data["BA_FE_4934"]])
+ba_err = np.vstack([data["BA_FE_4554_err"], data["BA_FE_4934_err"]])
+
+sr = np.vstack([data["SR_FE_4077"], data["SR_FE_4215"]])
+sr_err = np.vstack([data["SR_FE_4077_err"], data["SR_FE_4215_err"]])
+
+sr_avg = np.nanmean(sr, axis=0)
+ba_avg = np.nanmean(ba, axis=0)
+
+ba_err[(ba_err == 0) + ~np.isfinite(ba_err)] = 0.20
+sr_err[(sr_err == 0) + ~np.isfinite(sr_err)] = 0.20
+
+ba_err = np.nanmean(ba_err, axis=0)
+sr_err = np.nanmean(sr_err, axis=0)
+
+hs_ls = ba_avg - sr_avg
+hs_ls_err = np.sqrt(0.2**2 +  ba_err**2 + sr_err**2)
+
+fig, ax = plt.subplots(figsize=(4, 4))
+
+ax.scatter(data["cannon_m_h_1"], hs_ls,
+           facecolor="#000000", edgecolor="#000000", linewidths=1, s=5, zorder=5,
+           label="_")
+ax.errorbar(data["cannon_m_h_1"], hs_ls,
+            xerr=data["cannon_m_h_err_1"], yerr=hs_ls_err,
+            fmt=None, ecolor="#BBBBBB", elinewidth=1, label="_")
+
+
+cristallo = Table.read("cristallo_data_new.csv")
+fehs = np.array(cristallo.dtype.names[1:]).astype(float)
+
+masses = cristallo["Mass/[Fe/H]"]
+
+colors = {
+    "2.0": "r",
+    "3.0": "g",
+}
+
+for i, mass in enumerate(masses):
+    model_hs_ls = [cristallo[feh][i] for feh in cristallo.dtype.names[1:]]
+    ax.plot(fehs, model_hs_ls, label=r"${{{:.1f}}}\,M_\odot$".format(mass),
+            lw=5, alpha=0.75)
+
+
+plt.legend()
[…]

### 2018-04-15 article/plot_yields_amanda.py

@@ -1,0 +1,64 @@
+import numpy as np
+import matplotlib.pyplot as plt
+from matplotlib.ticker import MaxNLocator
+from astropy.table import Table
+
+data = Table.read("Bastar_candidates_with_abundances.csv")
+
+ba = np.vstack([data["BA_FE_4554"], data["BA_FE_4934"]])
+ba_err = np.vstack([data["BA_FE_4554_err"], data["BA_FE_4934_err"]])
+
+sr = np.vstack([data["SR_FE_4077"], data["SR_FE_4215"]])
+sr_err = np.vstack([data["SR_FE_4077_err"], data["SR_FE_4215_err"]])
+
+sr_avg = np.nanmean(sr, axis=0)
+ba_avg = np.nanmean(ba, axis=0)
+
+ba_err[(ba_err == 0) + ~np.isfinite(ba_err)] = 0.20
+sr_err[(sr_err == 0) + ~np.isfinite(sr_err)] = 0.20
+
+ba_err = np.nanmean(ba_err, axis=0)
+sr_err = np.nanmean(sr_err, axis=0)
+
+hs_ls = ba_avg - sr_avg
+hs_ls_err = np.sqrt(0.2**2 +  ba_err**2 + sr_err**2)
+
+fig, ax = plt.subplots(figsize=(4, 4))
+
+ax.scatter(data["cannon_m_h_1"], hs_ls,
+           facecolor="#000000", edgecolor="#000000", linewidths=1, s=5, zorder=5,
+           label="_")
+ax.errorbar(data["cannon_m_h_1"], hs_ls,
+            xerr=data["cannon_m_h_err_1"], yerr=hs_ls_err,
+            fmt=None, ecolor="#BBBBBB", elinewidth=1, label="_")
+
+amanda = Table.read("amanda_yields.csv")
+fehs = np.array(amanda.dtype.names[1:]).astype(float)
+
+masses = amanda["mass/[Fe/H]"]
+
+colors = {
+    "2.0": "k",
+    "3.0": "m",
+}
+
+for i, mass in enumerate(masses):
+    model_hs_ls = [amanda[feh][i] for feh in amanda.dtype.names[1:]]
+    ax.plot(fehs, model_hs_ls, label=r"${{{:.1f}}}\,M_\odot$".format(mass),
+            lw=5, alpha=0.75)
+
+
+plt.legend()
+ax.set_xlim(-2.3, 0.4)
[…]

### 2018-04-15 article/plot_yields_total.py

@@ -1,0 +1,80 @@
+import numpy as np
+import matplotlib.pyplot as plt
+from matplotlib.ticker import MaxNLocator
+from astropy.table import Table
+
+data = Table.read("Bastar_candidates_with_abundances.csv")
+
+ba = np.vstack([data["BA_FE_4554"], data["BA_FE_4934"]])
+ba_err = np.vstack([data["BA_FE_4554_err"], data["BA_FE_4934_err"]])
+
+sr = np.vstack([data["SR_FE_4077"], data["SR_FE_4215"]])
+sr_err = np.vstack([data["SR_FE_4077_err"], data["SR_FE_4215_err"]])
+
+sr_avg = np.nanmean(sr, axis=0)
+ba_avg = np.nanmean(ba, axis=0)
+
+ba_err[(ba_err == 0) + ~np.isfinite(ba_err)] = 0.20
+sr_err[(sr_err == 0) + ~np.isfinite(sr_err)] = 0.20
+
+ba_err = np.nanmean(ba_err, axis=0)
+sr_err = np.nanmean(sr_err, axis=0)
+
+hs_ls = ba_avg - sr_avg
+hs_ls_err = np.sqrt(0.2**2 +  ba_err**2 + sr_err**2)
+
+fig, ax = plt.subplots(figsize=(4, 4))
+
+ax.scatter(data["cannon_m_h_1"], hs_ls,
+           facecolor="#000000", edgecolor="#000000", linewidths=1, s=5, zorder=5,
+           label="_")
+ax.errorbar(data["cannon_m_h_1"], hs_ls,
+            xerr=data["cannon_m_h_err_1"], yerr=hs_ls_err,
+            fmt=None, ecolor="#BBBBBB", elinewidth=1, label="_")
+
+
+cristallo = Table.read("cristallo_data_new.csv")
+fehs = np.array(cristallo.dtype.names[1:]).astype(float)
+
+masses = cristallo["Mass/[Fe/H]"]
+
+colors = {
+    "2.0": "k",
+    "3.0": "g",
+}
+
+for i, mass in enumerate(masses):
+    model_hs_ls = [cristallo[feh][i] for feh in cristallo.dtype.names[1:]]
+    ax.plot(fehs, model_hs_ls, label=r"${{{:.1f}}}\,M_\odot$".format(mass),
+            lw=5, alpha=0.75)
+
[…]

### 2018-05-07 article/ms.tex
referee comments plus reply plus paper changes
toomre skillz

@@
 \subsection{Dynamics}
-We integrated galactic orbits for 21 barium stars using recent astrometry from Gaia/TGAS \citep{gaia2016a,gaia2016b}.
-Using the \texttt{gala} Python package \citep{price2017}, we integrated each star backwards for $0.5\,\textrm{Gyr}$ in a Milky Way-like potential that consists of four components: a \citet{hernquist1990} bulge and nucleus, a \citet{miyamoto1975} disk, and the \citet{nfw1997} halo.
-In this potential, the disk and bulge parameters were adjusted to be consistent with previous work \citep{bovy2015}.
-And, it is also used to vary the scale mass and radius, of the nucleus and halo, respectively.
-We computed orbital periods, energy, apocenters, pericenters, eccentricities, and angular momentum in the $z$-direction.
-All 21 stars showed prograde orbits that were consistent with membership in the Milky Way disk, indicating they do not originate from an unusual stellar event.
 
@@
 We encourage follow-up observations with high-resolution spectrographs in order to precisely measure a full suite of neutron-capture abundances.
-These data would permit the most detailed comparisons with AGB star yields ever considered.
+This data would permit the most detailed comparisons with AGB star yields ever considered.
 

### 2018-05-07 article/DynamicMotionScript.py

@@ -1,0 +1,195 @@
+# Some imports we'll need later:
+
+# Third-party
+import astropy.units as u
+import astropy.coordinates as coord
+from astropy.io import ascii
+from astropy.table import Table
+import matplotlib.pyplot as plt
+import numpy as np
+import pandas as pd
+
+# Gala
+from gala.mpl_style import mpl_style
+plt.style.use(mpl_style)
+import gala.dynamics as gd
+import gala.integrate as gi
+import gala.potential as gp
+from gala.units import galactic
+
+#d = Table.read("Updated_88_data_gaia.fits")
+#d.write("Updated_88_data_gaia.csv")
+
+#data=pd.read_csv('Updated_88_data_gaia.csv')
+
+#csv=np.array(data)
+
+stars = Table.read("dynamics_complete.csv")
+
+Ba_velx = []
+Ba_vely = []
+Ba_velz = []
+Ba_y = []
+Sr_velx = []
+Sr_vely = []
+Sr_velz = []
+Sr_y = []
+Barium_velx = []
+Barium_vely = []
+Barium_velz = []
+Barium_y = []
+
+for index, star in enumerate(stars):
+
+  potential = gp.MilkyWayPotential()
+
+  icrs = coord.ICRS(ra=star["ra"] * u.deg,
+                  dec=star["dec"] * u.deg,
+                  distance=1.0 / star["parallax"] * u.kpc,
+                  pm_ra_cosdec=star["pmra"]*u.mas/u.yr,
+                  pm_dec=star["pmdec"]*u.mas/u.yr,
+                  radial_velocity=-0*u.km/u.s)
+
+  """
+  icrs_err = coord.ICRS(ra=0*u.deg, dec=0*u.deg, distance=6*u.kpc,
+                      pm_ra_cosdec=0.009*u.mas/u.yr,
+                      pm_dec=0.009*u.mas/u.yr,
+                      radial_velocity=0.1*u.km/u.s)
+
+  """
+  v_sun = coord.CartesianDifferential([11.1, 250, 7.25]*u.km/u.s)
+  gc_frame = coord.Galactocentric(galcen_distance=8.3*u.kpc,
+                                z_sun=0*u.pc,
+                                galcen_v_sun=v_sun)
+
+
[…]

### 2018-05-16 galactic_contour.py
skillz

@@ -1,0 +1,38 @@
+import numpy as np
+import matplotlib.pyplot as plt
+from astropy.table import Table
+
+stars = Table.read("dynamics_complete_test.csv")
+lamosts = Table.read("lamost_gaia_result.fits")
+
+xs = stars['GAL_LONG']
+ys = stars['GAL_LAT']
+xl = lamosts['GAL_LONG']
+yl = lamosts['GAL_LAT']
+
+grid_xs = np.linspace(0, 360, 160)
+grid_xl = np.linspace(0, 360, 160)
+grid_ys = np.linspace(-70, 90, 120)
+grid_yl = np.linspace(-70, 90, 120)
+
+grid_s, _, _ = np.histogram2d(xs, ys, bins=[grid_xs, grid_ys])
+grid_l, _, _ = np.histogram2d(xl, yl, bins=[grid_xl, grid_yl])
+
+div = np.divide(grid_s, grid_l, out=np.zeros_like(grid_s), where=grid_l!=0)
+grid_sl = div
+grid_sl = np.transpose(grid_sl)
+
+grid_slm = np.ma.masked_where(grid_sl < 0.001, grid_sl)
+
+cmap = plt.cm.viridis
+cmap.set_bad(color='white')
+plt.pcolormesh(grid_xs, grid_ys, grid_slm, cmap=cmap, edgecolors = 'None', vmin =0 , vmax = 0.1)
+plt.colorbar()
+
+plt.title('Contour Percentage')
+plt.xlabel('Galactic Longitude')
+plt.ylabel('Galactic Lattitude')
+plt.savefig('DynamicFigures/'+'testcontour'+'.png')
+
+
+

### 2018-05-16 toomre_diagram.py
toomre

@@ -1,0 +1,188 @@
+# Some imports we'll need later:
+
+# Third-party
+import astropy.units as u
+import astropy.coordinates as coord
+from astropy.io import ascii
+from astropy.table import Table
+import matplotlib.pyplot as plt
+import numpy as np
+import pandas as pd
+
+# Gala
+from gala.mpl_style import mpl_style
+plt.style.use(mpl_style)
+import gala.dynamics as gd
+import gala.integrate as gi
+import gala.potential as gp
+from gala.units import galactic
+
+stars = Table.read("dynamics_complete.csv")
+
+controls = Table.read("lamost_gaia_result.fits")
+L = len(stars)
+N=1
+
+Ba_velx = []
+Ba_vely = []
+Ba_velz = []
+Ba_y = []
+Sr_velx = []
+Sr_vely = []
+Sr_velz = []
+Sr_y = []
+Barium_velx = []
+Barium_vely = []
+Barium_velz = []
+Barium_y = []
+C_velx = []
+C_vely = []
+C_velz = []
+C_y = []
+
+
+U = np.zeros((L, N))
+U = U.flatten(L)
+V = np.zeros((L, N))
+V = V.flatten(L)
+W = np.zeros((L, N))
+W = W.flatten(L)
+
+L = len(controls)
+
+U_lamost = np.zeros((L, N))
+U_lamost = U_lamost.flatten(L)
+V_lamost = np.zeros((L, N))
+V_lamost = V_lamost.flatten(L)
+W_lamost = np.zeros((L, N))
+W_lamost = W_lamost.flatten(L)
+
+for index, star in enumerate(stars):
+
+  icrs = coord.ICRS(ra=star["ra"] * u.deg,
+                  dec=star["dec"] * u.deg,
+                  distance=1.0 / star["parallax"] * u.kpc,
+                  pm_ra_cosdec=star["pmra"]*u.mas/u.yr,
+                  pm_dec=star["pmdec"]*u.mas/u.yr,
+                  radial_velocity=star['radial_velocity']*u.km/u.s)
+
+  """
+  icrs_err = coord.ICRS(ra=0*u.deg, dec=0*u.deg, distance=6*u.kpc,
+                      pm_ra_cosdec=0.009*u.mas/u.yr,
[…]

### 2018-05-16 orbit_dynamics.py
ecc

@@ -1,0 +1,257 @@
+# Some imports we'll need later:
+
+# Third-party
+import astropy.units as u
+import astropy.coordinates as coord
+from astropy.io import ascii
+from astropy.table import Table
+import matplotlib.pyplot as plt
+import numpy as np
+import pandas as pd
+
+# Gala
+from gala.mpl_style import mpl_style
+plt.style.use(mpl_style)
+import gala.dynamics as gd
+import gala.integrate as gi
+import gala.potential as gp
+from gala.units import galactic
+
+stars = Table.read("dynamics_complete.csv")
+
+controls = Table.read("lamost_gaia_result.fits")
+L = len(stars)
+N=1
+
+Ba_ecc = []
+Sr_ecc = []
+Barium_ecc = []
+
+ecc = np.zeros((L, N))
+ecc = ecc.flatten(L)
+apocenter = np.zeros((L, N))
+apocenter = apocenter.flatten(L)
+
+orbit_energy = np.zeros((L, N))
+orbit_energy = orbit_energy.flatten(L)
+
+angular_mom_z = np.zeros((L, N))
+angular_mom_z = angular_mom_z.flatten(L)
+
+L = len(controls)
+
+ecc_lamost = np.zeros((L, N))
+ecc_lamost = ecc.flatten(L)
+
+apocenter_lamost = np.zeros((L, N))
+apocenter_lamost = apocenter_lamost.flatten(L)
+
+orbit_energy_lamost = np.zeros((L, N))
+orbit_energy_lamost = orbit_energy_lamost.flatten(L)
+
+angular_mom_z_lamost = np.zeros((L, N))
+angular_mom_z_lamost = angular_mom_z_lamost.flatten(L)
+
+for index, star in enumerate(stars):
+
+  potential = gp.MilkyWayPotential()
+
+  icrs = coord.ICRS(ra=star["ra"] * u.deg,
+                  dec=star["dec"] * u.deg,
+                  distance=1.0 / star["parallax"] * u.kpc,
+                  pm_ra_cosdec=star["pmra"]*u.mas/u.yr,
+                  pm_dec=star["pmdec"]*u.mas/u.yr,
+                  radial_velocity=star['radial_velocity']*u.km/u.s)
+
+  """
+  icrs_err = coord.ICRS(ra=0*u.deg, dec=0*u.deg, distance=6*u.kpc,
+                      pm_ra_cosdec=0.009*u.mas/u.yr,
[…]

### 2018-05-16 galactic_contour.py
plz help

@@ -1,6 +1,8 @@
 import numpy as np
 import matplotlib.pyplot as plt
 from astropy.table import Table
+import matplotlib.colors as colors
+
 
 stars = Table.read("dynamics_complete_test.csv")
 lamosts = Table.read("lamost_gaia_result.fits")
@@ -24,15 +26,24 @@ grid_sl = np.transpose(grid_sl)
 
 grid_slm = np.ma.masked_where(grid_sl < 0.001, grid_sl)
 
-cmap = plt.cm.viridis
+fig = plt.figure()  # create a figure object
+ax1 = fig.add_subplot(3, 1, 1)  # create an axes object in the figure
+ax1.fig.plot(xs, ys,s=1, alpha=0.5, facecolor='#FF9309', edgecolor='none')
+ax1.fig.set_xlabel('Galactic Longitude')
+ax1.fig.set_ylabel('Galactic Lattitude')
+
+ax2 = fig.add_subplot(3, 1, 2)
+ax2.fig.plot(xl, yl,s=1, alpha=0.5, facecolor='#FF9309', edgecolor='none')
+ax2.fig.set_xlabel('Galactic Longitude')
+ax2.fig.set_ylabel('Galactic Lattitude')
+
+ax3 = fig.add_subplot(3, 1, 3)
+cmap = ax3.cm.viridis
 cmap.set_bad(color='white')
-plt.pcolormesh(grid_xs, grid_ys, grid_slm, cmap=cmap, edgecolors = 'None', vmin =0 , vmax = 0.1)
-plt.colorbar()
-
-plt.title('Contour Percentage')
-plt.xlabel('Galactic Longitude')
-plt.ylabel('Galactic Lattitude')
-plt.savefig('DynamicFigures/'+'testcontour'+'.png')
+ax3.fig.pcolormesh(grid_xs, grid_ys, grid_slm, cmap=cmap, edgecolors = 'None', norm=colors.LogNorm(vmin=0+0.001, vmax=0.1))
+ax3.fig.colorbar().set_label('Candidate fraction', rotation=270)
+ax3.fig.set_xlabel('Galactic Longitude')
+ax3.fig.set_ylabel('Galactic Lattitude')
 
 
-
+plt.savefig('DynamicFigures/'+'testcontoursub'+'.png')

### 2018-05-16 galactic_contour.py
changes and betterise

@@ -1,8 +1,11 @@
 import numpy as np
 import matplotlib.pyplot as plt
 from astropy.table import Table
-import matplotlib.colors as colors
+from matplotlib import (colors, cm, ticker)
 
+from mpl_utils import mpl_style
+
+plt.style.use(mpl_style)
 
 stars = Table.read("dynamics_complete_test.csv")
 lamosts = Table.read("lamost_gaia_result.fits")
@@ -26,24 +29,29 @@ grid_sl = np.transpose(grid_sl)
 
 grid_slm = np.ma.masked_where(grid_sl < 0.001, grid_sl)
 
-fig = plt.figure()  # create a figure object
-ax1 = fig.add_subplot(3, 1, 1)  # create an axes object in the figure
-ax1.fig.plot(xs, ys,s=1, alpha=0.5, facecolor='#FF9309', edgecolor='none')
-ax1.fig.set_xlabel('Galactic Longitude')
-ax1.fig.set_ylabel('Galactic Lattitude')
+fig, axes = plt.subplots(3, 1)
+axes[0].plot(xs, ys,s=1, alpha=0.5, facecolor='#FF9309', edgecolor='none')
+axes[0].set_xlabel(r'$l$ $[^\circ]$')
+axes[0].set_ylabel(r'$b$ $[^\circ]$')
 
-ax2 = fig.add_subplot(3, 1, 2)
-ax2.fig.plot(xl, yl,s=1, alpha=0.5, facecolor='#FF9309', edgecolor='none')
-ax2.fig.set_xlabel('Galactic Longitude')
-ax2.fig.set_ylabel('Galactic Lattitude')
+axes[1].plot(xl, yl,s=1, alpha=0.5, facecolor='#FF9309', edgecolor='none')
+axes[1].set_xlabel(r'$l$ $[^\circ]$')
+axes[1].set_ylabel(r'$b$ $[^\circ]$')
 
-ax3 = fig.add_subplot(3, 1, 3)
-cmap = ax3.cm.viridis
+cmap = cm.viridis
 cmap.set_bad(color='white')
-ax3.fig.pcolormesh(grid_xs, grid_ys, grid_slm, cmap=cmap, edgecolors = 'None', norm=colors.LogNorm(vmin=0+0.001, vmax=0.1))
-ax3.fig.colorbar().set_label('Candidate fraction', rotation=270)
-ax3.fig.set_xlabel('Galactic Longitude')
[…]

### 2018-05-16 mpl_utils.py
add  style  file

@@ -1,0 +1,90 @@
+
+# A matplotlib style based on the gala package by @adrn:
+# github.com/adrn/gala
+
+import numpy as np
+
+mpl_style = {
+
+    # Lines
+    'lines.linewidth': 1.7,
+    'lines.antialiased': True,
+    'lines.marker': '.',
+    'lines.markersize': 5.,
+
+    # Patches
+    'patch.linewidth': 1.0,
+    'patch.facecolor': '#348ABD',
+    'patch.edgecolor': '#CCCCCC',
+    'patch.antialiased': True,
+
+    # images
+    'image.origin': 'upper',
+
+    # colormap
+    'image.cmap': 'viridis',
+
+    # Font
+    'font.size': 12.0,
+    'text.usetex': True,
+    'text.latex.preamble': r'\usepackage{amsmath}',
+    'text.latex.preview': True,
+    'axes.unicode_minus': False,
+
+    # Axes
+    'axes.facecolor': '#FFFFFF',
+    'axes.edgecolor': '#AAAAAA',
+    'axes.linewidth': 1.0,
+    'axes.grid': False,
+    'axes.titlesize': 'x-large',
+    'axes.labelsize': 'large',
+    'axes.labelcolor': 'k',
+    'axes.axisbelow': True,
+
+    # Ticks
+    'xtick.major.size': 8,
+    'xtick.minor.size': 4,
+    'xtick.major.pad': 6,
+    'xtick.minor.pad': 6,
+    'xtick.color': '#565656',
+    'xtick.direction': 'in',
+    'ytick.major.size': 8,
+    'ytick.minor.size': 4,
+    'ytick.major.pad': 6,
+    'ytick.minor.pad': 6,
+    'ytick.color': '#565656',
+    'ytick.direction': 'in',
+    'xtick.labelsize': 'medium',
+    'ytick.labelsize': 'medium',
+
+    # Legend
+    'legend.fancybox': True,
+    'legend.loc': 'best',
+
+    # Figure
+    'figure.figsize': [6, 6],
+    'figure.facecolor': '1.0',
+    'figure.edgecolor': '0.50',
+    'figure.subplot.hspace': 0.5,
+
+    # Other
+    'savefig.dpi': 300,
+}
+
+
+
+
+def plot_histogram_steps(ax, x_bins, y, y_err):
+
+    xx = np.array(x_bins).repeat(2)[1:]
[…]

### 2018-05-16 galactic_contour.py
minor

@@ -30,19 +30,22 @@ grid_sl = np.transpose(grid_sl)
 grid_slm = np.ma.masked_where(grid_sl < 0.001, grid_sl)
 
 fig, axes = plt.subplots(3, 1)
-axes[0].plot(xs, ys,s=1, alpha=0.5, facecolor='#FF9309', edgecolor='none')
+axes[0].scatter(xs, ys, s=1, alpha=0.5, facecolor='#FF9309', edgecolor='none',
+                rasterized=True)
 axes[0].set_xlabel(r'$l$ $[^\circ]$')
 axes[0].set_ylabel(r'$b$ $[^\circ]$')
 
-axes[1].plot(xl, yl,s=1, alpha=0.5, facecolor='#FF9309', edgecolor='none')
+axes[1].scatter(xl, yl, s=1, alpha=0.5, facecolor='#FF9309', edgecolor='none',
+                rasterized=True)
 axes[1].set_xlabel(r'$l$ $[^\circ]$')
 axes[1].set_ylabel(r'$b$ $[^\circ]$')
 
 cmap = cm.viridis
 cmap.set_bad(color='white')
-axes[2].pcolormesh(grid_xs, grid_ys, grid_slm, cmap=cmap, edgecolors='None',
-    norm=colors.LogNorm(vmin=0+0.001, vmax=0.1))
-axes[2].colorbar().set_label(r'\textrm{Candidate fraction}', rotation=270)
+pmesh = axes[2].pcolormesh(grid_xs, grid_ys, grid_slm, 
+    cmap=cmap, edgecolors='None', norm=colors.LogNorm(vmin=0+0.001, vmax=0.1))
+cbar = plt.colorbar(pmesh)
+cbar.set_label(r'\textrm{Candidate fraction}', rotation=270)
 axes[2].set_xlabel(r'$l$ $[^\circ]$')
 axes[2].set_ylabel(r'$b$ $[^\circ]$')
 

### 2018-05-16 toomre_diagram.py
toomre

@@ -180,8 +180,8 @@ plt.text(90,75, 'Thick', fontsize=12)
 plt.text(150, 150, 'Halo', fontsize=12)
 plt.xlim(-310, 310)
 plt.ylim(0, 400)
-plt.title('Toomre Diagram')
-plt.xlabel('V (km/s)')
+plt.title(r'\textrm{Toomre Diagram}')
+plt.xlabel(r'\textrm{V (km/s)}')
 plt.ylabel(r'$\sqrt{U^2+W^2}$ (km/s)')
 plt.savefig('DynamicFigures/'+'toomre'+'.png')
 

### 2018-05-17 toomre_data.py
data analysis for toomre diagram

@@ -1,0 +1,187 @@
+# Some imports we'll need later:
+
+# Third-party
+import astropy.units as u
+import astropy.coordinates as coord
+from astropy.io import ascii
+from astropy.table import Table
+import matplotlib.pyplot as plt
+import numpy as np
+import pandas as pd
+
+# Gala
+from gala.mpl_style import mpl_style
+plt.style.use(mpl_style)
+import gala.dynamics as gd
+import gala.integrate as gi
+import gala.potential as gp
+from gala.units import galactic
+
+stars = Table.read("dynamics_complete.csv")
+
+controls = Table.read("lamost_gaia_result.fits")
+L = len(stars)
+N=1
+
+Ba_velx = []
+Ba_vely = []
+Ba_velz = []
+Ba_y = []
+Sr_velx = []
+Sr_vely = []
+Sr_velz = []
+Sr_y = []
+Barium_velx = []
+Barium_vely = []
+Barium_velz = []
+Barium_y = []
+C_velx = []
+C_vely = []
+C_velz = []
+C_y = []
+
+
+U = np.zeros((L, N))
+U = U.flatten(L)
+V = np.zeros((L, N))
+V = V.flatten(L)
+W = np.zeros((L, N))
+W = W.flatten(L)
+
+L = len(controls)
+
+U_lamost = np.zeros((L, N))
+U_lamost = U_lamost.flatten(L)
+V_lamost = np.zeros((L, N))
+V_lamost = V_lamost.flatten(L)
+W_lamost = np.zeros((L, N))
+W_lamost = W_lamost.flatten(L)
+
+for index, star in enumerate(stars):
+
+  icrs = coord.ICRS(ra=star["ra"] * u.deg,
+                  dec=star["dec"] * u.deg,
+                  distance=1.0 / star["parallax"] * u.kpc,
+                  pm_ra_cosdec=star["pmra"]*u.mas/u.yr,
+                  pm_dec=star["pmdec"]*u.mas/u.yr,
+                  radial_velocity=star['radial_velocity']*u.km/u.s)
+
+  """
+  icrs_err = coord.ICRS(ra=0*u.deg, dec=0*u.deg, distance=6*u.kpc,
+                      pm_ra_cosdec=0.009*u.mas/u.yr,
[…]

### 2018-05-17 toomre_diagram.py
shit graph

@@ -1,28 +1,18 @@
-# Some imports we'll need later:
-
-# Third-party
+import numpy as np
+import matplotlib.pyplot as plt
+from astropy.table import Table
+from mpl_utils import mpl_style
+from matplotlib import (colors, cm, ticker)
 import astropy.units as u
 import astropy.coordinates as coord
 from astropy.io import ascii
-from astropy.table import Table
-import matplotlib.pyplot as plt
-import numpy as np
-import pandas as pd
-
-# Gala
-from gala.mpl_style import mpl_style
-plt.style.use(mpl_style)
 import gala.dynamics as gd
 import gala.integrate as gi
 import gala.potential as gp
 from gala.units import galactic
 
-stars = Table.read("dynamics_complete.csv")
-
-controls = Table.read("lamost_gaia_result.fits")
-L = len(stars)
-N=1
-
+stars = Table.read("velocity_dynamics.csv")
+lamost = Table.read("lamostUVW_dynamics.csv")
 Ba_velx = []
 Ba_vely = []
 Ba_velz = []
@@ -35,36 +25,15 @@ Barium_velx = []
 Barium_vely = []
 Barium_velz = []
 Barium_y = []
-C_velx = []
-C_vely = []
-C_velz = []
-C_y = []
-
-
-U = np.zeros((L, N))
-U = U.flatten(L)
-V = np.zeros((L, N))
-V = V.flatten(L)
-W = np.zeros((L, N))
-W = W.flatten(L)
-
-L = len(controls)
-
-U_lamost = np.zeros((L, N))
-U_lamost = U_lamost.flatten(L)
-V_lamost = np.zeros((L, N))
-V_lamost = V_lamost.flatten(L)
-W_lamost = np.zeros((L, N))
-W_lamost = W_lamost.flatten(L)
 
 for index, star in enumerate(stars):
 
-  icrs = coord.ICRS(ra=star["ra"] * u.deg,
-                  dec=star["dec"] * u.deg,
-                  distance=1.0 / star["parallax"] * u.kpc,
-                  pm_ra_cosdec=star["pmra"]*u.mas/u.yr,
-                  pm_dec=star["pmdec"]*u.mas/u.yr,
[…]

### 2018-05-17 galactic_contour.py
dynamics graphs code

@@ -57,4 +57,5 @@ fig.tight_layout()
 
 plt.show()
 
-plt.savefig('DynamicFigures/'+'testcontoursub'+'.png')
+fig.savefig('DynamicFigures/'+'testcontoursub'+'.png')
+fig.savefig("DynamicFigures/contour.pdf", dpi=150)

### 2018-05-17 toomre_diagram.py

@@ -1,18 +1,26 @@
-import numpy as np
-import matplotlib.pyplot as plt
-from astropy.table import Table
-from mpl_utils import mpl_style
-from matplotlib import (colors, cm, ticker)
+# Some imports we'll need later:
+
+# Third-party
 import astropy.units as u
 import astropy.coordinates as coord
 from astropy.io import ascii
+from astropy.table import Table
+import matplotlib.pyplot as plt
+import numpy as np
+import pandas as pd
+
+# Gala
+from gala.mpl_style import mpl_style
+plt.style.use(mpl_style)
 import gala.dynamics as gd
 import gala.integrate as gi
 import gala.potential as gp
 from gala.units import galactic
 
-stars = Table.read("velocity_dynamics.csv")
-lamost = Table.read("lamostUVW_dynamics.csv")
+stars = Table.read("dynamics_complete_test.csv")
+L = len(stars)
+N=1
+
 Ba_velx = []
 Ba_vely = []
 Ba_velz = []
@@ -25,6 +33,13 @@ Barium_velx = []
 Barium_vely = []
 Barium_velz = []
 Barium_y = []
+
+U = np.zeros((L, N))
+U = U.flatten(L)
+V = np.zeros((L, N))
+V = V.flatten(L)
+W = np.zeros((L, N))
+W = W.flatten(L)
 
 for index, star in enumerate(stars):
 
@@ -76,25 +91,16 @@ for index, star in enumerate(stars):
    Barium_velz.append(w0.v_z.to(u.km/u.s).value)
    Barium_y.append(np.sqrt(Barium_velx[-1]**2+Barium_velz[-1]**2))
 
-
-xs = stars['V_vel(km/s)_1']
-ys = np.sqrt(stars['U_vel(km/s)_1']**2+stars['W_vel(km/s)_1']**2)
-xl = lamost['V_vel']
-yl = np.sqrt(lamost['U_vel']**2+lamost['W_vel']**2)
+  U[index]= w0.v_x.to(u.km/u.s).value
+  V[index]= w0.v_y.to(u.km/u.s).value
+  W[index]= w0.v_z.to(u.km/u.s).value
 
 
-grid_xs = np.linspace(-310, 310, 620)
-grid_xl = np.linspace(-310, 310, 620)
[…]

### 2018-05-18 article/ms.tex
paper

@@
 We argue this may have been a selection bias in previous studies.
+Our kinematical analysis revealed our stellar sample contains \% disk stars (\% thin and \% thick), and \% halo stars.
 A comparison with AGB yields suggests the main neutron source responsible for the Ba and Sr enhancements is the $C^{13}(\alpha,n)O^{16}$ reaction chain.
@@
 
-Many barium stars have been discovered in the disk and halo of the Milky Way \citep{gomez1997,mennessier1997}.
+Many barium stars have been discovered in the disk and halo of the Milky Way \citep{jorissen1993,gomez1997,mennessier1997}.
 In \citet{pereira2011} it is concluded that metal-rich barium stars share similar kinematics to other metal-rich and super metal-rich stars already analysed, suggesting that they do not belong to the bulge population.
@@
 \subsection{Dynamics}
+Using recent astrometry from Gaia/TGAS \citep{gaia2016,gaia2018b, cropper2018, katz2018, lindegren2018, sartoretti2018}, with section filters parallax > 0, and parallax/parallax error >5, we integrated the galactic orbits for 898 s-process enhanced stars.
+Utilising the \texttt{gala} Python package \citep{price2017}, we integrated each star backwards for $0.5\,\textrm{Gyr}$ in a Milky Way-like potential that consists of four components: a \citet{hernquist1990} bulge and nucleus, a \citet{miyamoto1975} disk, and the \citet{nfw1997} halo.
+In this potential, the disk and bulge parameters were adjusted to be consistent with previous work \citep{bovy2015}.
+For our Gaia matched sample, we computed spatial velocities and galactic longitude and latitudes.
+Spatial velocities are relative to the local standard of rest, where $U_{LSR}$ is positive towards the Galactic centre, $V_{LSR}$ is positive in the direction of Galactic rotation ($l=90^{\circ}, b=0^{\circ}$), and $W_{LSR}$ is positive towards the north galactic pole ($b=90^{\circ}$).
+Our analysis revealed our stellar sample contains \% disk stars (\% thin and \% thick), and \% halo stars.
 
@@
 
+\subsection{Dynamics}
+
+The majority of our sample showed pro-grade orbits that were consistent with membership in the Milky Way disk, indicating they do not originate from an unusual stellar event.
+Figure \ref{fig:figure4} illustrates the galactic position of each class of s-process enhanced star investigated.
+For our entire 898 sample, the figure shows \% reside within the galactic disk(\% thin disk and \% thick disk ), and \% within the halo.
+Our results show similar trends to the literature, samples from \cite{gomez1997} and \cite{mennessier1997} present populations of 75\% contained within the disk, and 25\% within the halo.
+\cite{pereira2011}’s entire sample resides within the disk, and \cite{decastro2016} states their sample contains 90\% thin disk stars.
+Although, excluding \cite{decastro2016}’s sample, it is important to note previous studies contain limited stellar populations ranging from 4 to 12 stars, and cannot be representative of the overall galactic position of s-process enhanced stars.
+\cite{jorissen1993} attributes the galactic position of s-process enhanced stars as dependent on their intrinsic or extrinsic nature, given our sample is entirely extrinsic we cannot comment on the comparison between the two enhancement sources.
+However, given our extrinsically s-process enhanced sample concentrates towards the galactic plane, we can propose the sample in \cite{jorissen1993} was not large enough to represent the overall galactic position of extrinsic S stars.
+
+\begin{figure}
+	\includegraphics[width=0.5\textwidth]{toomre.pdf}
+	\caption{Toomre diagram Spatial velocities ([V (km/s)]; x-axis) and ([$\sqrt{U^2+W^2}$ (km/s)]; y-axis) for number of s-process enhanced candidates matched with Gaia DR2.
+Coloured markers red, blue, and purple highlight barium, strontium, and both barium and strontium enhancement respectively.}
+	\label{fig:figure4}
+\end{figure}
+
+\begin{figure}
+	\includegraphics[width=0.5\textwidth]{contour.pdf}
+	\caption{Galactic longitude ([$l^{\circ}$]; x-axis) and galactic latitude ([$b^{\circ}$]; y-axis) shown for: number of s-process enhanced candidates matched with Gaia DR2, the LAMOST sample matched with Gaia DR2, and a density contour between the latter two}
+	\label{fig:figure5}
+\end{figure}
+
 \section{Conclusions} \label{sec:con}
@@
 This sample size is the greatest total number of barium stars known, and represents the largest sample of s-process enhanced stars to date.
-Nearly all of our barium candidates are consistent with being disk stars, indicating our sample was not produced through an unusual galactic event.
+Our kinematical analysis revealed our stellar sample contains \% disk stars (\% thin and \% thick), and \% halo stars, indicating our barium stars were not produced through an unusual galactic event.
 
@@
 LAMOST is operated and managed by the National Astronomical Observatories, Chinese Academy of Sciences.
-This work has made use of data from the European Space Agency (ESA) mission Gaia (http://www.cosmos.esa.int/gaia), processed by the Gaia Data Processing and Analysis Consortium (DPAC, http://www.cosmos.esa.int/web/gaia/dpac/consortium).
-Funding for the DPAC has been provided by national institutions, in particular the institutions participating in the Gaia Multilateral Agreement.
+This work has made use of data from the European Space Agency (ESA) mission
+{\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed by the {\it Gaia}
+Data Processing and Analysis Consortium (DPAC,
+\url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the DPAC
+has been provided by national institutions, in particular the institutions
+participating in the {\it Gaia} Multilateral Agreement.
 
@@
 ApJ, 219, 40
+\bibitem[\protect\citeauthoryear{Cropper et al.}{2018}]{cropper2018}
+Cropper, M., Katz, D., Sartoretti, P., Prusti, T., de Bruijne, J.~H.~J., Chassat, F., Charvet, P., Boyadijan, J., Perryman, M., Sarri, G., Gare, P., Erdmann, M., Munari, U., Zwitter, T., Wilkinson, M., Arenou, F., Vallenari, A., G{\'o}mez, A., Panuzzo, P., Seabroke, G., Allende Prieto, C., Benson, K., Marchal, O., Huckle, H., Smith, M., Dolding, C., Jan{\ss}en, K., Viala, Y., Blomme, R., Baker, S., Boudreault, S., Crifo, F., Soubiran, C., Fr{\'e}mat, Y., Jasniewicz, G., Guerrier, A., Guy, L.~P., Turon, C., Jean-Antoine-Piccolo, A., Th{\'e}venin, F., David, M.
+Gosset, E.,\& Damerdji, Y.
+2018
 \bibitem[\protect\citeauthoryear{deCastro et al.}{2016}]{decastro2016}
@@
 ApJ, 797, 44
-\bibitem[\protect\citeauthoryear{Gaia Collaboration et al.}{2016a}]{gaia2016a}
-Gaia Collaboration, Brown, A.~G.~A., Vallenari, A., Prusti, T., de Bruijne, J.~H.~J., Mignard, F., Drimmel, R., Babusiaux, C., Bailer-Jones, C.~A.~L.,\& Bastian, U., et al. 2016, 
-A$\&$A, 595, A2
-\bibitem[\protect\citeauthoryear{Gaia Collaboration et al.}{2016b}]{gaia2016b}
+\bibitem[\protect\citeauthoryear{Gaia Collaboration et al.}{2016}]{gaia2016}
 Gaia Collaboration, Prusti, T., de Bruijne, J.~H.~J., Brown, A.~G.~A., Vallenari, A., Babusiaux, C., Bailer-Jones, C.~A.~L., Bastian, U., Biermann, M.,\& Evans, D.~W. et al. 2016, 
 A$\&$A, 595, A1
+\bibitem[\protect\citeauthoryear{Gaia Collaboration et al.}{2018b}]{gaia2018b}
+Gaia Collaboration, Brown, A.~G.~A., Vallenari, A, Prusti, T., de Bruijne, J.~H.~J., Babusiaux, C.,\& Bailer-Jones, C.~A.~L. 2018, 
 \bibitem[Gustafsson et al.(2008)]{marcs} Gustafsson, B., Edvardsson, B., Eriksson, K., et al.\ 2008, \aap, 486, 951 
@@
 MNRAS, submitted
+\bibitem[\protect\citeauthoryear{Katz et al.}{2018}]{katz2018}
+Katz, D., Sartoretti, P., Cropper, M., Panuzzo, P., Seabroke, G.~M., Viala, Y., Benson, K., Blomme, R., Jasniewicz, G., Jean-Antoine, A., Huckle, H., Smith, M., Baker, S., Crifo, F., Damerdji, Y., David, M., Dolding, C., Fr{\'e}mat, Y., Gosset, E., Guerrier, A., Guy, L.~P., Haigron, R., Jan{\ss}en, K., Marchal, O., Plum, G., Soubiran, C., Th{\'e}venin, F.
+,Ajaj, M., Allende Prieto, C., Babusiaux, C., Boudreault, S., Chemin, L., Delle Luche, C., Fabre, C., Gueguen, A., Hambly, N.~C., Lasne, Y., Meynadier, F., Pailler, F., Panem, C., Royer, F., Tauran, G., Zurbach, C., Zwitter, T., Arenou, F., Bossini, D., Gomez, A., Lemaitre, V., Leclerc, N., Morel, T., Munari, U., Turon, C., Vallenari, A.,\& {\v Z}erjal, M.
+2018
 \bibitem[\protect\citeauthoryear{Kelson et al.}{2000}]{kelson2000}
@@
 \bibitem[Kupka et al.(1999)]{vald} Kupka, F., Piskunov, N., Ryabchikova, T.~A., Stempels, H.~C., \& Weiss, W.~W.\ 1999, \aaps, 138, 119 
+\bibitem[\protect\citeauthoryear{Lindegren et al.}{2018}]{lindegren2018}
+Lindegren, L., Hernandez, J., Bombrun, A., Klioner, S., Bastian, U., Ramos-Lerate, M., de Torres, A., Steidelmuller, H, Stephenson, C., Hobbs, D., Lammers, U., Biermann, M.
+,Geyer, R., Hilger, T., Michalik, D., Stampa, U., McMillan, P.~J., Castaneda, J., Clotet, M., Comoretto, G., Davidson, M., Fabricius, C., Gracia, G., Hambly, N.~C., Hutton, A., Mora, A., Portell, J., van Leeuwen, F., Abbas, U., Abreu, A., Altmann, M., Andrei, A., Anglada, E., Balaguer-Nunez, L., Barache, C., Becciani, U., Bertone, S., Bianchi, L., Bouquillon, S., Bourda, G., Brusemeister, T., Bucciarelli, B., Busonero, D., Buzzi, R., Cancelliere, R., Carlucci, T., Charlot, P., Cheek, N., Crosta, M., Crowley, C., de Bruijne, J., de Felice, F., Drimmel, R.
+Esquej, P., Fienga, A., Fraile, E., Gai, M., Garralda, N., Gonzalez-Vidal, J.~J., Guerra, R., Hauser, M., Hofmann, W., Holl, B., Jordan, S., Lattanzi, M.~G., Lenhardt, H., Liao, S., Licata, E., Lister, T., Loffler, W., Marchant, J., Martin-Fleitas, J.-M., Messineo, R., Mignard, F., Morbidelli, R., Poggio, E., Riva, A., Rowell, N., Salguero, E., Sarasso, M., Sciacca, E., Siddiqui, H., Smart, R.~L., Spagna, A., Steele, I., Taris, F., Torra, J., van Elteren, A., van Reeven, W.,\& Vecchiato, A.
+2018
 \bibitem[\protect\citeauthoryear{Little-Marenin \& Little}{1987}]{little1987}
@@
 %A$\&$A, 522, A32
+\bibitem[\protect\citeauthoryear{Sartoretti et al.}{2018}]{sartoretti2018}
+Sartoretti, P., Katz, D., Cropper, M., Panuzzo, P., Seabroke, G.~M.
+,Viala, Y., Benson, K., Blomme, R., Jasniewicz, G., Jean-Antoine, A., Huckle, H., Smith, M., Baker, S., Crifo, F., Damerdji, Y., David, M., Dolding, C., Fremat, Y., Gosset, E., Guerrier, A., Guy, L.~P., Haigron, R., Janssen, K., Marchal, O., Plum, G., Soubiran, C., Thevenin, F., Ajaj, M., Allende Prieto, C., Babusiaux, C., Boudreault, S., Chemin, L., Delle Luche, C., Fabre, C., Gueguen, A., Hambly, N.~C., Lasne, Y., Meynadier, F., Pailler, F., Panem, C., Riclet, F., Royer, F., Tauran, G., Zurbach, C., Zwitter, T., Arenou, F., Gomez, A., Lemaitre, V., Leclerc, N., Morel, T., Munari, U., Turon, C.,\& Zerjal, M.
+2018
 \bibitem[\protect\citeauthoryear{Schectman \& Johns}{2003}]{schectman2003}

### 2018-05-23 article/ms.tex
paper

@@
 
-In this paper we present the discovery of 967 s-process candidates from 454,180 giant stars observed by LAMOST: this sample constitutes the largest number of s-process enhanced stars ever discovered.
+In this paper we present the discovery of 895 s-process candidates from 454,180 giant stars observed by LAMOST: this sample constitutes the largest number of s-process enhanced stars ever discovered.
 We identify these stars in the LAMOST sample by using a data-driven search approach on the spectra directly, and then measure the s-process abundance enhancements using stellar synthesis.
 Finally, we take advantage of free observing time, and obtain high resolution spectra of a number of candidates.
-Our sample includes; 257 'barium stars', that are enhanced in both barium and strontium, 49 stars with significant barium enhancement only, and 661 stars which exhibit strontium enhancement only.
+Our sample includes; 187 'barium stars', that are enhanced in both barium and strontium, 49 stars with significant barium enhancement only, and 659 stars which exhibit strontium enhancement only.
 Our entire barium star stellar sample exists within temperature and luminosity ranges not enveloped by the AGB, which may indicate a recent ($<1\,\textrm{Myr}$) mass accretion event from an AGB companion.
-Most of our barium stars ($69\%$) show strong carbon enhancements, yet, only 5 candidates ($<2$\,\%) show evidence of sodium enhancement, in contrast with previous claims of preferential sodium enhancement.
+The majority of our barium stars ($95\%$) show strong carbon enhancements, yet, only 5 candidates ($<3$\,\%) show evidence of sodium enhancement, in contrast with previous claims of preferential sodium enhancement.
 We argue this may have been a selection bias in previous studies.
-Our kinematical analysis revealed our stellar sample contains \% disk stars (\% thin and \% thick), and \% halo stars.
+Our kinematical analysis revealed our stellar sample contains 97\% disk stars (81\% thin and 16\% thick), and 3\% halo stars.
 A comparison with AGB yields suggests the main neutron source responsible for the Ba and Sr enhancements is the $C^{13}(\alpha,n)O^{16}$ reaction chain.
@@
 
-In this paper we analyse 454,180 giant stars from the second LAMOST data release \citep{luo2015} and identify 967 s-process candidates.
+In this paper we analyse 454,180 giant stars from the second LAMOST data release \citep{luo2015} and identify 895 s-process candidates.
 In Section \ref{sec:methods}, we describe the observations and candidate selection.
@@
 In addition, a visual inspection was undertaken to exclude any results containing false positives, candidates exhibiting data reduction issues, apparent absorption finer then the spectral resolution, and overly noisy normalised LAMOST spectra.
-This combined method generated 967 s-process rich candidates which are provided in Table 1, for which a portion is shown to demonstrate its style and content, it's available online in its entirety.
-This stellar sample consists of; 257 `barium stars' enhanced in both barium and strontium, 49 stars exhibiting exclusively barium enhancement, and 661 with exclusively strontium enhancement.
+This combined method generated 895 s-process rich candidates which are provided in Table 1, for which a portion is shown to demonstrate its style and content, it's available online in its entirety.
+This stellar sample consists of; 187 `barium stars' enhanced in both barium and strontium, 49 stars exhibiting exclusively barium enhancement, and 659 with exclusively strontium enhancement.
 
-For the remainder of this paper we restrict our analysis to the 257 classical `barium stars' stars that show enhancement in both barium and strontium.
-While the 49 or 661 stars with only barium or strontium enhancements (respectively) may also be bona fide barium stars, there may be other explanations for their chemical abundance pattern \citep[e.g.,][]{maiorca2011}, and so we restrict our inferences to a `gold sample' of barium stars.
+For the remainder of this paper we restrict our analysis to the 187 classical `barium stars' stars that show enhancement in both barium and strontium.
+While the 49 or 659 stars with only barium or strontium enhancements (respectively) may also be bona fide barium stars, there may be other explanations for their chemical abundance pattern \citep[e.g.,][]{maiorca2011}, and so we restrict our inferences to a `gold sample' of barium stars.
 
-It's important to note, previous studies \citet{malaney1988} define barium stars through an abundance criteria $\rm[Ba/Fe]\geq +0.3$, and out of our 257 barium star sample using this criteria , only one star ($\rm J092155.95+265253.4$) exhibits a lower [Ba/Fe] of 0.12.
+It's important to note, previous studies \citet{malaney1988} define barium stars through an abundance criteria $\rm[Ba/Fe]\geq +0.3$, and out of our 187 barium star sample using this criteria , only one star ($\rm J092155.95+265253.4$) exhibits a lower [Ba/Fe] of 0.12.
 However, as previously discussed, a negative residual at the \ion{Ba}{II} resonance line 4554\,\AA\, indicates barium enhancement.
@@
 \centering
-\caption{Properties of 967 s-process candidates, the table is available online in its entirety. Here we show a portion to demonstrate its style and content.}
+\caption{Properties of 895 s-process candidates, the table is available online in its entirety. Here we show a portion to demonstrate its style and content.}
 \label{table:table1}
@@
 Enhancements in sodium, technetium, and carbon are useful indicators when determining whether a stellar sample is populated by intrinsically enhanced AGB S stars, or polluted extrinsic barium stars.
-We performed an identical analysis to the process described in Section \ref{sec:cand} in order to identify sodium, technetium, or carbon enhancement in our sample of 257 barium stars.
+We performed an identical analysis to the process described in Section \ref{sec:cand} in order to identify sodium, technetium, or carbon enhancement in our sample of 187 barium stars.
 We used the sodium doublet lines at 5889\,\AA\ and 5895\,\AA\, and required significant absorption in both features.
-Only 5/257 barium stars met this criteria.
+Only 5/187 barium stars met this criteria.
 
@@
 Finally, for carbon enhancement we searched for significant deviations at the CH and G band near 4300\,\AA.
-We found 178/257 stars to show significant carbon enhancement (i.e., $[\textrm{C/Fe}] \gtrsim 0.5$).
+We found 178/187 stars to show significant carbon enhancement (i.e., $[\textrm{C/Fe}] \gtrsim 0.5$).
 
@@
 \subsection{Dynamics}
-Using recent astrometry from Gaia/TGAS \citep{gaia2016,gaia2018b, cropper2018, katz2018, lindegren2018, sartoretti2018}, with section filters parallax > 0, and parallax/parallax error >5, we integrated the galactic orbits for 898 s-process enhanced stars.
+Using recent astrometry from Gaia/TGAS \citep{gaia2016,gaia2018b, cropper2018, katz2018, lindegren2018, sartoretti2018}, with section filters parallax > 0, and parallax/parallax error >5, we integrated the galactic orbits for 871/895 Gaia matched s-process enhanced stars.
 Utilising the \texttt{gala} Python package \citep{price2017}, we integrated each star backwards for $0.5\,\textrm{Gyr}$ in a Milky Way-like potential that consists of four components: a \citet{hernquist1990} bulge and nucleus, a \citet{miyamoto1975} disk, and the \citet{nfw1997} halo.
@@
 Spatial velocities are relative to the local standard of rest, where $U_{LSR}$ is positive towards the Galactic centre, $V_{LSR}$ is positive in the direction of Galactic rotation ($l=90^{\circ}, b=0^{\circ}$), and $W_{LSR}$ is positive towards the north galactic pole ($b=90^{\circ}$).
-Our analysis revealed our stellar sample contains \% disk stars (\% thin and \% thick), and \% halo stars.
+Our analysis revealed our stellar sample contains 97\% disk stars (81\% thin and 16\% thick), and 3\% halo stars.
 
@@
 Technetium has a half life of approximately 211,000 years and as a result, the presence of Tc enhancement is constrained to observations of AGB S stars \citep{jorissen1993} or recently polluted extrinsic barium stars.
-Our analysis, undertaken for the TC lines 4049\,\AA, 4238\,\AA, 4262\,\AA, 4297\,\AA, and 5924\,\AA, discovered 51 single Tc line matches at 4238,\AA, within our 257 barium star candidate sample.
+Our analysis, undertaken for the TC lines 4049\,\AA, 4238\,\AA, 4262\,\AA, 4297\,\AA, and 5924\,\AA, discovered 51 single Tc line matches at 4238,\AA, within our 187 barium star candidate sample.
 The majority (46/51) have $\log{g} > 2$, suggesting they cannot be AGB S stars, and may indicate a recent ($<1\,\textrm{Myr}$) mass accretion event.
@@
 	\includegraphics[width=0.5\textwidth]{yields_test.pdf}
-    \caption{Metallicities ([Fe/H]; x-axis) and heavy-to-light s-process abundance ratios ([Ba/Sr] as measured from LAMOST; y-axis) for 257 barium star candidates.
+    \caption{Metallicities ([Fe/H]; x-axis) and heavy-to-light s-process abundance ratios ([Ba/Sr] as measured from LAMOST; y-axis) for 187 barium star candidates.
 Coloured lines blue, orange, and green, indicate surface [hs/ls] yields from \citet{cristallo2015} for different masses.
@@
 Giants and supergiants become enhanced in carbon through TDU process discussed in Section \ref{sec:intro}, and extrinsic carbon enhancement occurs via mass transfer from a binary AGB star.
-Our analysis produced 178 CH and G band significantly enhanced stars (i.e., $[\textrm{C/Fe}] \gtrsim 0.5$) out of the total 257 barium candidates.
+Our analysis produced 178 CH and G band significantly enhanced stars (i.e., $[\textrm{C/Fe}] \gtrsim 0.5$) out of the total 187 barium candidates.
 These 178 stars exist in a metallicity range of 0 to -1.2, and can be termed "CH stars" in accordance with definitions used in the literature \citep[e.g.][]{luck1991, mcclure1997}.
@@
 AGB stars, and chemically unusual stars that show the chemical signature of mass transfer pollution from a binary AGB companion, highlight the variety of s-process enhancement.
-In Figure \ref{fig:figure3} we show the heavy-to-light s-process abundance ratio (taken as [Ba/Sr]) for all 257 barium stars identified in LAMOST.
+In Figure \ref{fig:figure3} we show the heavy-to-light s-process abundance ratio (taken as [Ba/Sr]) for all 187 barium stars identified in LAMOST.
 Although the [Ba/Sr] ratio is quite noisy, the overall metallicity [Fe/H] is quite precise (0.1\,dex).
@@
 Figure \ref{fig:figure4} illustrates the galactic position of each class of s-process enhanced star investigated.
-For our entire 898 sample, the figure shows \% reside within the galactic disk(\% thin disk and \% thick disk ), and \% within the halo.
+For our entire 898 sample, the figure shows 97\% reside within the galactic disk(81\% thin disk and 16\% thick disk ), and \% within the halo.
 Our results show similar trends to the literature, samples from \cite{gomez1997} and \cite{mennessier1997} present populations of 75\% contained within the disk, and 25\% within the halo.
 \cite{pereira2011}’s entire sample resides within the disk, and \cite{decastro2016} states their sample contains 90\% thin disk stars.
-Although, excluding \cite{decastro2016}’s sample, it is important to note previous studies contain limited stellar populations ranging from 4 to 12 stars, and cannot be representative of the overall galactic position of s-process enhanced stars.
+Although, excluding the candidate sample presented by \cite{decastro2016}, it is important to note previous studies contain limited stellar populations ranging from 4 to 12 stars, and cannot be representative of the overall galactic position of s-process enhanced stars.
 \cite{jorissen1993} attributes the galactic position of s-process enhanced stars as dependent on their intrinsic or extrinsic nature, given our sample is entirely extrinsic we cannot comment on the comparison between the two enhancement sources.
@@
 We conducted the largest ever search for s-process enhanced stars using the LAMOST second data release.
-From 454,180 giant stars, we identify 967 s-process candidates including: 257 stars with significant enhancements in barium and strontium (so-called `barium stars'), 49 stars exhibiting exclusively barium enhancement, and 661 exhibiting exclusively strontium enhancement.
+From 454,180 giant stars, we identify 895 s-process candidates including: 187 stars with significant enhancements in barium and strontium (so-called `barium stars'), 49 stars exhibiting exclusively barium enhancement, and 659 exhibiting exclusively strontium enhancement.
 This sample size is the greatest total number of barium stars known, and represents the largest sample of s-process enhanced stars to date.
-Our kinematical analysis revealed our stellar sample contains \% disk stars (\% thin and \% thick), and \% halo stars, indicating our barium stars were not produced through an unusual galactic event.
+Our kinematical analysis revealed our stellar sample contains 97\% disk stars (81\% thin and 16\% thick), and 3\% halo stars, indicating our barium stars were not produced through an unusual galactic event.
 

### 2018-05-24 article/ms.tex
fin

@@
 Figure \ref{fig:figure4} illustrates the galactic position of each class of s-process enhanced star investigated.
-For our entire 898 sample, the figure shows 97\% reside within the galactic disk(81\% thin disk and 16\% thick disk ), and \% within the halo.
+For our entire 898 sample, Figure \ref{fig:figure4} shows 97\% reside within the galactic disk (81\% thin disk and 16\% thick disk), and 3\% within the halo.
 Our results show similar trends to the literature, samples from \cite{gomez1997} and \cite{mennessier1997} present populations of 75\% contained within the disk, and 25\% within the halo.
 \cite{pereira2011}’s entire sample resides within the disk, and \cite{decastro2016} states their sample contains 90\% thin disk stars.
-Although, excluding the candidate sample presented by \cite{decastro2016}, it is important to note previous studies contain limited stellar populations ranging from 4 to 12 stars, and cannot be representative of the overall galactic position of s-process enhanced stars.
+Although, excluding the candidate sample presented by \cite{decastro2016}, it is important to note previous studies contain limited stellar populations ranging from 4 to 12 stars, and cannot be representative of the overall galactic distribution of s-process enhanced stars.
 \cite{jorissen1993} attributes the galactic position of s-process enhanced stars as dependent on their intrinsic or extrinsic nature, given our sample is entirely extrinsic we cannot comment on the comparison between the two enhancement sources.
-However, given our extrinsically s-process enhanced sample concentrates towards the galactic plane, we can propose the sample in \cite{jorissen1993} was not large enough to represent the overall galactic position of extrinsic S stars.
+However, given our extrinsically s-process enhanced sample concentrates towards the galactic plane, we can propose the sample in \cite{jorissen1993} was not sufficiently large enough to represent the overarching galactic distribution of extrinsic S stars.
 
@@
 	\includegraphics[width=0.5\textwidth]{toomre.pdf}
-	\caption{Toomre diagram Spatial velocities ([V (km/s)]; x-axis) and ([$\sqrt{U^2+W^2}$ (km/s)]; y-axis) for number of s-process enhanced candidates matched with Gaia DR2.
+	\caption{Galactic distribution represented by a Toomre diagram, spatial velocities ([V (km/s)]; x-axis) and ([$\sqrt{U^2+W^2}$ (km/s)]; y-axis) for number of s-process enhanced candidates matched with Gaia DR2.
 Coloured markers red, blue, and purple highlight barium, strontium, and both barium and strontium enhancement respectively.}
@@
 
-\begin{figure}
-	\includegraphics[width=0.5\textwidth]{contour.pdf}
-	\caption{Galactic longitude ([$l^{\circ}$]; x-axis) and galactic latitude ([$b^{\circ}$]; y-axis) shown for: number of s-process enhanced candidates matched with Gaia DR2, the LAMOST sample matched with Gaia DR2, and a density contour between the latter two}
-	\label{fig:figure5}
-\end{figure}
+%\begin{figure}
+%	\includegraphics[width=0.5\textwidth]{contour.pdf}
+%	\caption{Galactic longitude ([$l^{\circ}$]; x-axis) and galactic latitude ([$b^{\circ}$]; y-axis) shown for: number of s-process enhanced candidates matched with Gaia DR2, the LAMOST sample matched with Gaia DR2, and a density contour between the latter two}
+%	\label{fig:figure5}
+%\end{figure}
 

### 2018-05-24 toomre_diagram.py
final toomre code

@@ -17,7 +17,7 @@ import gala.integrate as gi
 import gala.potential as gp
 from gala.units import galactic
 
-stars = Table.read("dynamics_complete_test.csv")
+stars = Table.read("dynamics_final.csv")
 L = len(stars)
 N=1
 
@@ -43,8 +43,8 @@ W = W.flatten(L)
 
 for index, star in enumerate(stars):
 
-  icrs = coord.ICRS(ra=star["ra_1"] * u.deg,
-                  dec=star["dec_1"] * u.deg,
+  icrs = coord.ICRS(ra=star["ra_1_1"] * u.deg,
+                  dec=star["dec_1_1"] * u.deg,
                   distance=1.0 / star["parallax_1"] * u.kpc,
                   pm_ra_cosdec=star["pmra_1"]*u.mas/u.yr,
                   pm_dec=star["pmdec_1"]*u.mas/u.yr,
@@ -68,7 +68,7 @@ for index, star in enumerate(stars):
 
   w0 = gd.PhaseSpacePosition(gc.data)
 
-  if (star["Ba_only_candidate_1"]=='true' and star["Ba_Sr_candidate_1"]=='false'):
+  if (star["Ba_only_candidate_1_1"]=='true' and star["Ba_Sr_candidate_1_1"]=='false'):
 
    Ba_velx.append(w0.v_x.to(u.km/u.s).value)
    Ba_vely.append(w0.v_y.to(u.km/u.s).value)
@@ -76,7 +76,7 @@ for index, star in enumerate(stars):
    Ba_y.append(np.sqrt(Ba_velx[-1]**2+Ba_velz[-1]**2))
 
    
-  if (star["Sr_only_candidate_1"]=='true' and star["Ba_Sr_candidate_1"]=='false'):
+  if (star["Sr_only_candidate_1_1"]=='true' and star["Ba_Sr_candidate_1_1"]=='false'):
 
    Sr_velx.append(w0.v_x.to(u.km/u.s).value)
    Sr_vely.append(w0.v_y.to(u.km/u.s).value)
@@ -84,7 +84,7 @@ for index, star in enumerate(stars):
    Sr_y.append(np.sqrt(Sr_velx[-1]**2+Sr_velz[-1]**2))
 
    
-  if (star["Ba_Sr_candidate_1"]=='true'):
+  if (star["Ba_Sr_candidate_1_1"]=='true'):
 
[…]

### 2018-05-24 article/ms.tex
paper final

@@
 The majority of our sample showed pro-grade orbits that were consistent with membership in the Milky Way disk, indicating they do not originate from an unusual stellar event.
-Figure \ref{fig:figure4} illustrates the galactic position of each class of s-process enhanced star investigated.
+Figures \ref{fig:figure4} and \ref{fig:figure5} illustrate the galactic distribution of each class of s-process enhanced star investigated.
 For our entire 898 sample, Figure \ref{fig:figure4} shows 97\% reside within the galactic disk (81\% thin disk and 16\% thick disk), and 3\% within the halo.
@@
 
-%\begin{figure}
-%	\includegraphics[width=0.5\textwidth]{contour.pdf}
-%	\caption{Galactic longitude ([$l^{\circ}$]; x-axis) and galactic latitude ([$b^{\circ}$]; y-axis) shown for: number of s-process enhanced candidates matched with Gaia DR2, the LAMOST sample matched with Gaia DR2, and a density contour between the latter two}
-%	\label{fig:figure5}
-%\end{figure}
+\begin{figure}
+	\includegraphics[width=0.5\textwidth]{contour.pdf}
+	\caption{Galactic longitude ([$l^{\circ}$]; x-axis) and galactic latitude ([$b^{\circ}$]; y-axis) shown for: number of s-process enhanced candidates matched with Gaia DR2, the LAMOST sample matched with Gaia DR2, and a density contour between the latter two}
+	\label{fig:figure5}
+\end{figure}
 

### 2018-08-24 article/ms.tex
changes

@@
 \\
-$^{5}$Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117 Heidelberg, Germany
+$^{5}$Department of Astronomy, Columbia University, 550 West 120th Street New York, New York 10027
 \\
@@
 
-In this paper we present the discovery of 895 s-process candidates from 454,180 giant stars observed by LAMOST: this sample constitutes the largest number of s-process enhanced stars ever discovered.
-We identify these stars in the LAMOST sample by using a data-driven search approach on the spectra directly, and then measure the s-process abundance enhancements using stellar synthesis.
-Finally, we take advantage of free observing time, and obtain high resolution spectra of a number of candidates.
-Our sample includes; 187 'barium stars', that are enhanced in both barium and strontium, 49 stars with significant barium enhancement only, and 659 stars which exhibit strontium enhancement only.
-Our entire barium star stellar sample exists within temperature and luminosity ranges not enveloped by the AGB, which may indicate a recent ($<1\,\textrm{Myr}$) mass accretion event from an AGB companion.
-The majority of our barium stars ($95\%$) show strong carbon enhancements, yet, only 5 candidates ($<3$\,\%) show evidence of sodium enhancement, in contrast with previous claims of preferential sodium enhancement.
-We argue this may have been a selection bias in previous studies.
-Our kinematical analysis revealed our stellar sample contains 97\% disk stars (81\% thin and 16\% thick), and 3\% halo stars.
-A comparison with AGB yields suggests the main neutron source responsible for the Ba and Sr enhancements is the $C^{13}(\alpha,n)O^{16}$ reaction chain.
-Additionally, theoretical models show that this source is dominant in low-mass AGB stars thus, it follows that most of the progenitors of s-process elements in our sample are low-mass AGB stars between $1 - 3\,M_{\odot}$.
-
-%that the majority of our sample are consistent with Salpeter-like initial mass function, with pollution from a low mass AGB star.
-
-%The abundances of the slow neutron capture process (s-process) elements in stars are a measure of the nucleosynthetic processes that occur primarily in Asymptotic Giant Branch (AGB) stars.
-Due to their associated enrichment of the s-process element barium, stars with peculiar enhancements of carbon and heavy elements (Z > 30) are historically referred to as 'barium stars'.
-Here, we present the discovery of 967 s-process candidates from 454,180 giant stars observed by LAMOST: this sample constitutes the largest number of s-process enhanced stars ever discovered.
-We identify these stars in the LAMOST sample by using a data-driven search approach on the spectra directly and then measure the s-process abundance enhancements directly using stellar synthesis.
-Finally, we validate our results using high resolution spectra of a number of candidates.
-Our sample includes; 257 'barium stars', that are enhanced in both barium and strontium, 49 stars with significant barium enhancement only, and 661 stars which exhibit strontium enhancement only.
-The unusual chemical abundance patterns of barium stars can be explained if these are in the AGB of stellar evolution.
-However, many barium stars  have not yet evolved through the red giant phase.
-Instead, these less evolved 'barium stars' are generally thought to have accreted mass from a more evolved AGB companion.
-Our entire barium star stellar sample exists within temperature and luminosity ranges not enveloped by the AGB, which may indicate a recent ($<1\,\textrm{Myr}$) mass accretion event from an AGB companion.
-These less evolved stars are uniquely informative on the binary fraction, AGB yields, mass transfer and stellar evolution.
-A comparison with AGB yields suggests that the majority of our sample are consistent with Salpeter-like initial mass function, with pollution from a low mass AGB star.
-Most of our barium stars (put in percentage) show strong carbon enhancements, consistent with mass transfer from a low-mass AGB companion.
-Although, only 5 candidates ($<2$\,\%) show evidence of sodium enhancement, in contrast with previous claims of preferential sodium enhancement, we argue this may have been a selection bias in previous studies.
-When binary properties become available from end-of-mission Gaia astrometry, our sample of s-process stars will be critical in explaining mass transfer in binary systems and refining AGB yields across a range of masses and metallicities.
+Here we present the discovery of 895 stars enriched in s-process elements from the LAMOST spectra using a data-driven approach.
+This sample constitutes the largest number of s-process enhanced stars ever discovered.
+Our sample includes; 187 s-process candidates that are enhanced in both barium and strontium, 49 stars with significant barium enhancement only, and 659 stars that show only strontium enhancement.
+Our entire s-process candidate sample exists within temperature and luminosity ranges not enveloped by the AGB?, which may indicate a recent ($<1\,\textrm{Myr}$) mass accretion event from an AGB companion.
+The majority of our barium stars ($95\%$) show strong carbon enhancements yet, only 5 candidates ($<3$\,\%) show evidence of sodium enhancement, in tension with previous observations of enhanced Na among s-process candidates.
+We argue this may have been a selection bias?
+in previous studies.
+Our kinematical analysis reveals our sample is composed of 97\% disk stars, and 3\% with velocity consistent to the halo.
+A comparison with AGB yields suggests the main neutron source responsible for Ba and Sr enhancements is the $\text{C}^{13}$(\textrm{$\alpha$},n)$\text{O}^{16}$ reaction chain.
+Theoretical models show that this source is dominant in low-mass AGB stars.
+We conclude that the progenitors for s-process enhancement in our sample are AGB companion stars with masses $1 - 3\,M_{\odot}$.
 
@@
 
-The abundances of the slow neutron capture process (s-process) elements in stars are a measure of the nucleosynthetic processes, that occur primarily in Asymptotic Giant Branch (AGB) stars.
-Due to their associated enrichment of the s-process element barium, stars with peculiar enhancements of carbon, and heavy elements (Z > 30) are referred to as 'barium stars' as first recognised by \citet{Bidelman1951}.
-The naming convention associated with barium stars is historical, it is therefore, for the purposes of this paper, necessary to classify definitions used for subsequent discussions.
-Barium enhanced stars exist as either extrinsic or intrinsic objects, extrinsic barium stars are stellar phenomena exhibiting s-process element enhancement as the result of some polluting process.
-Stars intrinsically enhanced in barium and other s-process elements are known as AGB S stars.
+The abundance of elements created through the slow neutron-capture process (s-process), is a measure of the nucleosynthetic reactions that occur primarily in Asymptotic Giant Branch (AGB) stars.
+Due to their associated enrichment of the s-process element barium, stars with peculiar enhancements of carbon, and heavy elements (Z > 30) are commonly referred to as 'barium stars' \citep{Bidelman1951}.
+The naming convention associated with 'barium stars' is historical, for the purposes of this paper it is necessary to classify definitions used for subsequent discussions.
+Stars with Ba and Sr enrichment will be refereed to as s-process candidates, and singular enhancement samples will be named according to their respective element.
+Metallicity-dependent classifications also exist in the literature.
+Metal-poor stars ([Fe/H] $\approx$ [0,-1.2]) enriched by s-process elements are classically refereed to as CH stars, we will simply define them as metal poor s-process candidates.
+An abundance criteria may also be used to define s-process enrichment, this is typically taken as threshold of $\rm[Ba/Fe]\geq +0.3$ \citep{malaney1988}.
+For the purposes of this paper, s-process enrichment will be determined solely on the presence significant flux residuals as described in Section \ref{sec:cand}.
+S-process candidates can be classified as either extrinsic or intrinsic objects.
+Extrinsic s-process stars are stellar phenomena exhibiting an enhancement as the result of some polluting process.
+Stars intrinsically enhanced in s-process elements are known as AGB S stars.
 These stars are in the TP-AGB (thermally pulsing-asymptotic giant branch) phase.
-During this stage of nucleosynthesis, this is an overabundance of both carbon and heavy elements produced through the slow neutron capture process, and exist on the surface as the result of a thermal pulsing cycle.
-According to the mass-transfer hypothesis, extrinsic barium stars are a consequence of stellar wind accretion \citep{boffin1988,jorissen1992} or Roche-lobe overflow \citep{webbink1986}.
-Both dynamical systems require a binary configuration a previous TP-AGB companion star (AGB S star), in its final phase as a white dwarf \citep{bohm1980,bohm1984}.
-In fact, \citet{mcclure1983} determined 85\% of all barium stars exist within binary systems.
-They further claimed that stellar objects which appeared to be singular are actually pole-on, or highly eccentric binaries with significant radial velocity variations, only occurring in a small ranges as detailed by \citet{pourbaix2004}.
-For these reasons, the properties and occurrence rate of barium stars are informative of the binary star fraction as a function of metallicity, the mass ratio of binary stars, as well as AGB yields across different masses and metallicities.
-
-The s-process, occurring in the interior of AGB stars, synthesises roughly half of all elements heavier than iron \citep[e.g.,][]{busso1999,travaglio2001,herwig2005,bisterzo2014,karakas2014}.
-Late in the AGB phase, during the TP-AGB phase, thermal instabilities occur in the He shell every $10^5$ years or so, depending on the mass of the H-exhausted core.
-These energy bursts drive a convective zone that sweeps almost the entire region lying between the core and the He-shell, mixing the products of nucleosynthesis within these regions.
-The energy from the thermal pulses forces the star to expand, pushing the H-shell out to cooler regions and allowing the convective envelope to move inwards to regions previously mixed by the thermal pulse driven convective zones.
-This phase of expansion and resulting inward movement is defined as the third dredge up (TDU), and is theorised to occur after each thermal pulse.
-During the TP-AGB phase, surface enrichment in $^{12}$C and heavy elements produced by the s-process, is a result of the repeated inward extensions of TDU \citep[e.g.,][]{busso2001}.
-The star contracts post dredge up and reignites the H-shell producing the majority of the surface luminosity for the next interpulse period.
-The interpulse, thermal pulse, and dredge up cycle may occur numerous times, and its frequency is dependent on the initial mass, composition, and mass-loss rate of the star.
-
-Barium giants can form within a metallicity-dependent initial mass range of approximately $0.8 - 8\,M_{\odot}$.
-The minimum mass for these giants is defined by the mass needed for core helium and carbon burning, which decrease as metallicity decreases.
-The age of these stars vary considerably, with some as old as $\approx$ 12\,Gyr in metal-poor globular clusters.
-Metal poor stars enhanced in barium are defined in the literature as CH stars.
-In contrast, metal-rich, less massive stars may reach ages of $\approx$ 100Myr, this includes stars that are at the core carbon burning limit or very close to it \citep[e.g.,][]{whitelock2013}.
-Furthermore, metal rich stars enhanced in barium are defined in the literature classically as barium stars.
-
-Many barium stars have been discovered in the disk and halo of the Milky Way \citep{jorissen1993,gomez1997,mennessier1997}.
-In \citet{pereira2011} it is concluded that metal-rich barium stars share similar kinematics to other metal-rich and super metal-rich stars already analysed, suggesting that they do not belong to the bulge population.
-It remains necessary to establish known abundances of s-process elements in a greater sample of barium stars in order to: compare their birth rate to theoretical expectations \citep{han1995}, explore the binary fraction at different metallicities, and compare to AGB star yields at different masses and metallicities.
-%The relationship between barium stars in the halo \citep[e.g.,][]{junqueira2001,drake2008,pereira2009,allen2006} and metal-poor, yellow, symbiotic halo stars has been established by \citet{jorissen2005} and \citet{pereira2009}.
-
-In this paper we analyse 454,180 giant stars from the second LAMOST data release \citep{luo2015} and identify 895 s-process candidates.
-In Section \ref{sec:methods}, we describe the observations and candidate selection.
-Section \ref{sec:observations} details the analysis of high-resolution follow-up observations obtained for a few candidates.
-In Section \ref{sec:dis}, we discuss the properties of our barium stars in context of existing literature.
-We provide concluding remarks in Section \ref{sec:con}.
+During this stage of nucleosynthesis, the s-process produces an over-abundance of both carbon and heavy elements.
+The thermal pulsing cycle transports these elements to surface of TP-AGB stars.
+According to the mass-transfer hypothesis, extrinsic s-process stars are a consequence of stellar wind accretion \citep{boffin1988,jorissen1992} or Roche-lobe overflow \citep{webbink1986}.
+Both dynamical systems require a binary configuration with a previous TP-AGB companion star (AGB S star) in its final phase as a white dwarf \citep{bohm1980,bohm1984}.
+In fact, \citet{mcclure1983} determined 85\% of all s-process candidates are in binary systems.
+They further claimed that stars which appeared to be singular are actually pole-on, or highly eccentric binaries with significant radial velocity variations only occurring in a small ranges \citep{pourbaix2004}.
+For these reasons, the properties and occurrence rate of s-process candidates are informative of the binary star fraction as a function of metallicity, the mass ratio of binary stars, as well as AGB yields across different masses and metallicities.
 
@@
 
+Occurring in the interior of AGB stars, the s-process synthesises roughly half of all elements heavier than iron \citep[e.g.,][]{busso1999,travaglio2001,herwig2005,bisterzo2014,karakas2014}.
+During the subsequent TP-AGB phase, thermal instabilities occur in the He shell every $10^5$ years or so, depending on the mass of the H-exhausted core.
+These energy bursts drive a convective zone that sweeps almost the entire region lying between the core and the He-shell, mixing the products of nucleosynthesis within these regions.
+While simultaneously, forcing the star to expand and pushing the H-shell out to cooler regions \citep{karakas2002}.
+The convective envelope will then move inwards towards regions previously mixed by the thermal pulse driven convective zones.
+This phase of expansion and resulting inward movement is defined as the third dredge up (TDU), and is theorised to occur after each thermal pulse.
+During the TP-AGB phase, the TDU is responsible for the surface enrichment in $^{12}$C and heavy elements produced by the s-process \citep[e.g.,][]{busso2001}.
+Post dredge up the star contracts, reigniting the H-shell, and producing the majority of the surface luminosity for the next interpulse period.
+The interpulse, thermal pulse, and dredge up cycle may occur numerous times and the frequency depends on the initial mass, composition, and mass-loss rate of the star.
+
+S-process candidate can form within a metallicity-dependent initial mass range of approximately $0.8 - 8\,M_{\odot}$ \citep{karakas2016cp}.
+The minimum mass is defined by the onset of core helium burning, and the maximum by core carbon burning.
+The age of these stars varies considerably, with some reaching ages $\approx$ 12\,Gyr in metal-poor globular clusters.
+Less massive metal-rich stars may reach ages of $\approx$ 100Myr, this includes stars that are at the core carbon burning limit or very close to it \citep[e.g.,][]{whitelock2013}.
+
+The majority s-process candidates are observed to be members of the disk\citep{jorissen1993,gomez1997,mennessier1997}.
+In \citet{pereira2011}, it is shown that metal-rich s-process candidates share similar kinematics to other metal-rich and super metal-rich stars already analysed, suggesting that they do not belong to the bulge population.
+\cite{jorissen1993} ?
+
+In this paper we analyse 454,180 giant stars from the second LAMOST data release \citep{luo2015} and identify 895 s-process candidates.
+In Section \ref{sec:methods} we describe the observations and candidate selection.
+Section \ref{sec:observations} details the analysis of high-resolution follow-up observations obtained for a few candidates.
+In Section \ref{sec:dis} we discuss the properties of our s-process candidates in context of existing literature.
+We provide concluding remarks in Section \ref{sec:con}.
+
 \section{Methods} \label{sec:methods}
@@
 \subsubsection{Data-driven analysis}
-The LAMOST (Large sky Area Multi-Object Fibre Spectrographic) survey released low-resolution ($\mathcal{R} \approx 1800$) optical spectra (3700\,\AA\ to 9000\,\AA) for over two million stars in their second data release \citep{luo2015}.
-Stellar parameters ($T_{\rm eff}$, $\log{g}$, [M/H], [$\alpha$/M]) were derived using a data-driven model, and constructed using high fidelity APOGEE labels of 9,952 giant stars in common between LAMOST and the APOGEE survey \citep{ho2017}.
-This data-driven model was used to estimate stellar labels for 454,180 giant stars.
-We note that this sample is exclusively giant stars, implying that we would not identify dwarf s-process enhanced stars.
+The LAMOST (Large sky Area Multi-Object Fibre Spectrographic) survey released low-resolution ($\mathcal{R} \approx 1800$) optical spectra (3700\,\AA\ to 9000\,\AA) for 2,207,189 stars in their second data release \citep{luo2015}.
+Stellar parameters ($T_{\rm eff}$, $\log{g}$, [M/H], [$\alpha$/M]) were derived by \citep{ho2017} using a \emph{The Cannon} \citet{ness2016}, with labels for 9,952 giant stars in common between LAMOST and the APOGEE survey.
+We note that this sample is limited to giant stars, implying that we would not identify dwarf s-process enhanced stars.
 Cross-validation tests shows that the typical uncertainties are approximately 70\,K in effective temperature $\rm T_{\rm eff}$, 0.1\,dex in surface gravity $\log{g}$, 0.1\,dex in metallicity [M/H], and 0.04\,dex in the $\alpha$-element abundance relative to overall metallicity [$\alpha$/M].
-These uncertainties are comparable to the APOGEE uncertainties \citep{alam2015}.
+These uncertainties are comparable to the those present in APOGEE \citep{alam2015}.
 
 \subsubsection{Candidate selection} \label{sec:cand}
-The barium stars analysed in this research were obtained by filtering for significant flux residuals, taken as a disparity between the normalised LAMOST flux and the data driven model, \emph{The Cannon}, derived by \citet{ho2017}.
-Specifically, we identified barium stars by searching for \ion{Ba}{II} and \ion{Sr}{II} enhancement at the 4554\,\AA\ and 4077\,\AA\ wavelengths, respectively.
-A negative residual, as shown in a candidate barium star in Figure \ref{fig:figure1}, illustrates an enhancement in the \ion{Ba}{II} and \ion{Sr}{II} lines at 4554\,\AA\, and 4077\,\AA, respectively.
-These \ion{Ba}{II} and \ion{Sr}{II} resonance lines are very strong, allowing us to identify stars enhanced in neutron-capture elements, given a well-fit model for the data.
-Stars identified high levels of barium (and not necessarily strontium) required enhancement in both the 4554\,\AA\ and 4934\,\AA\ \ion{Ba}{II} resonance lines, and for stars exclusively enhanced in strontium we looked for significant residuals at the 4077\,\AA\ and 4215\,\AA\ absorption lines.
-
-We used five filters that each spectrum, for each set of absorption lines, had to meet in order to be considered a s-process rich candidate; these included:
+The s-process candidates in this work were identified by filtering for significant flux residuals.
+We fit a Gaussian distribution with amplitude A to the flux residuals at each s-process element absorption line.
+These included; 4554\,\AA\ (\ion{Ba}{II}) and 4077\,\AA\ (\ion{Sr}{II}) wavelengths for s-process candidates, 4554\,\AA\ (\ion{Ba}{II}) and 4934\,\AA\ (\ion{Ba}{II}) wavelengths for barium enriched candidates, and wavelengths at 4077\,\AA\ (\ion{Sr}{II}) and 4215\,\AA\ (\ion{Sr}{II}) for strontium enriched candidates.
+The amplitude of each Gaussian fit at each wavelength is analogous to the depth of each absorption line.
+The discrepancy is then measured as the difference between the normalised LAMOST flux and the data driven model.
+A negative residual indicates enrichment, this is shown for a randomly chosen s-process candidate in Figure \ref{fig:figure1}.
+We used five filters for each spectrum and subsequent set of absorption lines in order to identify s-process enrichment, these included:
 
@@
 \begin{enumerate} 
-\item Profile amplitude for both enhancement lines must be $A < -0.05$.
+\item Profile amplitude for both enhancement lines must be $A < -0.05$, indicating a stronger absorption line than expected by the model.
 \item Both amplitudes must be measured within 3$\sigma$ ($|A|/\sigma _A$ < 3).
-\item The wavelength at each absorption line must be within 2\,\AA\ ($\lambda$ < 2).
+\item The wavelength at each absorption line must be within 2\,\AA\ ($\lambda$ < 2) of the rest frame laboratory model.
 \item The reduced $\chi^2$ from \emph{The Cannon} must be $\chi_r^2 < 3$.
-\item And, the LAMOST spectra must have a signal-to-noise ratio of $S/N > 30\,\textrm{pixel}^{-1}$.
+\item The LAMOST spectra must have a signal-to-noise ratio of $S/N > 30\,\textrm{pixel}^{-1}$.
 \end{enumerate}
-In addition, a visual inspection was undertaken to exclude any results containing false positives, candidates exhibiting data reduction issues, apparent absorption finer then the spectral resolution, and overly noisy normalised LAMOST spectra.
-This combined method generated 895 s-process rich candidates which are provided in Table 1, for which a portion is shown to demonstrate its style and content, it's available online in its entirety.
-This stellar sample consists of; 187 `barium stars' enhanced in both barium and strontium, 49 stars exhibiting exclusively barium enhancement, and 659 with exclusively strontium enhancement.
+We use visual inspection with all candidates to exclude any results containing false positives: candidates with data reduction issues; apparent absorption finer then the spectral resolution; or overly noisy normalised LAMOST spectra.
+This approach discovers 895 s-process rich candidates which are provided in Table 1.
+This sample consists of; 187 s-process candidates, 49 barium enriched stars, and 659 stars with strontium enrichment.
 
-For the remainder of this paper we restrict our analysis to the 187 classical `barium stars' stars that show enhancement in both barium and strontium.
-While the 49 or 659 stars with only barium or strontium enhancements (respectively) may also be bona fide barium stars, there may be other explanations for their chemical abundance pattern \citep[e.g.,][]{maiorca2011}, and so we restrict our inferences to a `gold sample' of barium stars.
+For the remainder of this paper we restrict our analysis to the 187 s-process candidates that show enhancement in both barium and strontium.
+While the 49 or 659 stars with only barium or strontium enhancements (respectively) may also be classified as s-process candidates, there may be other explanations for their chemical abundance pattern \citep[e.g.,][]{maiorca2011}.
 
-It's important to note, previous studies \citet{malaney1988} define barium stars through an abundance criteria $\rm[Ba/Fe]\geq +0.3$, and out of our 187 barium star sample using this criteria , only one star ($\rm J092155.95+265253.4$) exhibits a lower [Ba/Fe] of 0.12.
-However, as previously discussed, a negative residual at the \ion{Ba}{II} resonance line 4554\,\AA\, indicates barium enhancement.
-Furthermore, as discussed in section \ref{sec:other enhancements}, an enhancement in carbon is observed frequently with barium enhancement.
-$\rm J092155.95+265253.4$ shows both a negative residual at 4554\,\AA\, and carbon enhancement, we therefore conclude that this single deviant case can be classified as a barium star.
-Additionally, it should be mentioned, our average abundance error is 0.1, although, these results still indicate our sample can be classified as barium stars since they exhibit enhancement at the BaII resonance line 4554, and have a $\rm[Ba/Fe] \geq 0.2$.
-Nevertheless, this sample still constitutes the largest collection of barium stars ever discovered, with the next sample of significant size containing 182 barium stars \citep[e.g.,][]{decastro2016}.
+\subsubsection{Enhancements due to sodium, technetium, and carbon} \label{sec:other enhancements}
+Enhancements in sodium, technetium, and carbon are useful indicators when determining whether a sample is populated by intrinsically enhanced AGB S stars, or polluted extrinsic barium stars.
+We?
+performed an identical analysis to the process described in Section \ref{sec:cand} in order to identify sodium, technetium, or carbon enhancement in our sample of 187 s-process candidates.
+We used the sodium doublet lines at 5889\,\AA\ and 5895\,\AA\, and required significant absorption in both features.
+Only 5/187 s-process candidates met this criteria.
+For technetium enhancement we searched for significant residual deviations at 4049\,\AA, 4238\,\AA, 4262\,\AA, 4297\,\AA, and 5924\,\AA.
+These absorption lines are extremely weak, and would require a substantial amount of technetium enhancement before it would be visible in a high S/N LAMOST spectrum.
+We found that 51 s-process candidates exhibited some level of significant enhancement at the single absorption line 4238\,\AA.This single technetium enhancement is very likely attributed to data reduction/calibration artefacts.
+Finally, for carbon enhancement we searched for significant deviations at the CH and G band near 4300\,\AA.
+We found 178/187 stars to show significant carbon enhancement (i.e., $[\textrm{C/Fe}] \gtrsim 0.5$).
 
@@
 
-\subsubsection{Enhancements due to sodium, technetium, and carbon} \label{sec:other enhancements}
-Enhancements in sodium, technetium, and carbon are useful indicators when determining whether a stellar sample is populated by intrinsically enhanced AGB S stars, or polluted extrinsic barium stars.
-We performed an identical analysis to the process described in Section \ref{sec:cand} in order to identify sodium, technetium, or carbon enhancement in our sample of 187 barium stars.
-We used the sodium doublet lines at 5889\,\AA\ and 5895\,\AA\, and required significant absorption in both features.
-Only 5/187 barium stars met this criteria.
-
-For technetium enhancement we searched for significant residual deviations at 4049\,\AA, 4238\,\AA, 4262\,\AA, 4297\,\AA, and 5924\,\AA.
-These absorption lines are extremely weak, and would require a substantial amount of technetium enhancement before it would be visible in a high S/N LAMOST spectrum.
-We found that 51 barium stars exhibited some level of significant enhancement (based on the filters above) at the single technetium line 4238\,\AA, yet none showed enhancement at more than one technetium line.
-We note that the single enhancement near technetium for these 51 stars may be the consequence of data reduction/calibration artefacts, but we include details of which stars matched on technetium in Table 1 (available online in its entirety) nonetheless.
-Finally, for carbon enhancement we searched for significant deviations at the CH and G band near 4300\,\AA.
-We found 178/187 stars to show significant carbon enhancement (i.e., $[\textrm{C/Fe}] \gtrsim 0.5$).
-
 \subsubsection{Abundances estimated from LAMOST spectra}
@@
 Uncertainties in [Ba/Fe] and [Sr/Fe] from LAMOST are taken as the fitting error due to noise, added in quadrature with an adopted $0.2\,{\rm dex}$ systematic error floor.
+
+It's important to note, previous studies \citet{malaney1988} define barium stars through an abundance criteria $\rm[Ba/Fe]\geq +0.3$, and out of our 187 barium star sample using this criteria , only one star ($\rm J092155.95+265253.4$) exhibits a lower [Ba/Fe] of 0.12.
+However, as previously discussed, a negative residual at the \ion{Ba}{II} resonance line 4554\,\AA\, indicates barium enhancement.
+Furthermore, as discussed in section \ref{sec:other enhancements}, an enhancement in carbon is observed frequently with barium enhancement.
+$\rm J092155.95+265253.4$ shows both a negative residual at 4554\,\AA\, and carbon enhancement, we therefore conclude that this single deviant case can be classified as a barium star.
+Additionally, it should be mentioned, our average abundance error is 0.1, although, these results still indicate our sample can be classified as barium stars since they exhibit enhancement at the BaII resonance line 4554, and have a $\rm[Ba/Fe] \geq 0.2$.
+Nevertheless, this sample still constitutes the largest collection of barium stars ever discovered, with the next sample of significant size containing 182 barium stars \citep[e.g.,][]{decastro2016}.
 
@@
 %AJ, 122, 360
+\bibitem[\protect\citeauthoryear{Karakas et al.}{2002}]{karakas2002}
+Karakas, A.~I.,\& Lattanzio C.~J.,\& Pols, O.~R. 2002, 
+PASA, 515, 19
 \bibitem[\protect\citeauthoryear{Karakas \& Lattanzio}{2014}]{karakas2014}
@@
 ApJS, 825, 26
-\bibitem[\protect\citeauthoryear{Karakas et al.}{2018}]{karakas2018}
+\bibitem[\protect\citeauthoryear{Karakas et al.}{2016}]{karakas2016cp}
+Karakas, A.~I. 2016, 
+S.A.Lt, 229, 87
+\bibitem[\protect\citeauthoryear{Karakas}{2018}]{karakas2018}
 Karakas, A.~I. 2018, 
@@
 ApJ, 490, 493
+\bibitem[\protect\citeauthoryear{Ness et al.}{2016}]{ness2016}
+Ness M., Hogg D.~W., Rix H.~W., Martig M., Pinsonneault M.~H., Ho A. 2016, 
+ApJ, 823, 114
 %\bibitem[\protect\citeauthoryear{Pereira \& Drake}{2009}]{pereira2009}

### 2018-08-26 article/ms.tex
changes

@@
 Less massive metal-rich stars may reach ages of $\approx$ 100Myr, this includes stars that are at the core carbon burning limit or very close to it \citep[e.g.,][]{whitelock2013}.
-
-The majority s-process candidates are observed to be members of the disk\citep{jorissen1993,gomez1997,mennessier1997}.
+The majority s-process candidates are observed to be members of the disk \citep{jorissen1993,gomez1997,mennessier1997}.
 In \citet{pereira2011}, it is shown that metal-rich s-process candidates share similar kinematics to other metal-rich and super metal-rich stars already analysed, suggesting that they do not belong to the bulge population.
-\cite{jorissen1993} ?
+\cite{jorissen1993} relates galactic position to the extrinsic or intrinsic nature of the s-process candidate.
+They show that intrinsically enhanced stars are more concentrated towards the galactic plane than extrinsic enhanced stars.
 
@@
 This sample consists of; 187 s-process candidates, 49 barium enriched stars, and 659 stars with strontium enrichment.
+It is the largest collection of s-process enhanced stars ever discovered, with the next sample of significant size containing 182 s-process candidates \citep[e.g.,][]{decastro2016}.
 
@@
 performed an identical analysis to the process described in Section \ref{sec:cand} in order to identify sodium, technetium, or carbon enhancement in our sample of 187 s-process candidates.
-We used the sodium doublet lines at 5889\,\AA\ and 5895\,\AA\, and required significant absorption in both features.
+For sodium enrichment, we required significant absorption in the doublet lines at 5889\,\AA\ and 5895\,\AA\.
 Only 5/187 s-process candidates met this criteria.
-For technetium enhancement we searched for significant residual deviations at 4049\,\AA, 4238\,\AA, 4262\,\AA, 4297\,\AA, and 5924\,\AA.
+For technetium enhancement, we searched for significant residual deviations at 4049\,\AA, 4238\,\AA, 4262\,\AA, 4297\,\AA, and 5924\,\AA.
 These absorption lines are extremely weak, and would require a substantial amount of technetium enhancement before it would be visible in a high S/N LAMOST spectrum.
-We found that 51 s-process candidates exhibited some level of significant enhancement at the single absorption line 4238\,\AA.This single technetium enhancement is very likely attributed to data reduction/calibration artefacts.
-Finally, for carbon enhancement we searched for significant deviations at the CH and G band near 4300\,\AA.
-We found 178/187 stars to show significant carbon enhancement (i.e., $[\textrm{C/Fe}] \gtrsim 0.5$).
+We found that 51 s-process candidates exhibited some level of significant enhancement at the single absorption line 4238\,\AA.
+Single line enrichment discovered by our data driven approach are very likely attributed to data reduction/calibration artefacts present.
+These artefacts exist within in our data as a result of fitting a model to the LAMOST spectral data.
+As such, the 51 stars enhanced in a single Tc line can be ruled out as false positives.
+For carbon enhancement we searched for significant deviations at the CH and G band near 4300\,\AA, of which 178/187 s-process candidates exhibited significant carbon enhancement (i.e., $[\textrm{C/Fe}] \gtrsim 0.5$).
 
@@
 \subsubsection{Abundances estimated from LAMOST spectra}
-We estimated [Ba/Fe] and [Sr/Fe] abundance ratios for all s-process enhanced candidates by synthesising spectra that would account for the observed flux residuals.
-We assumed that absorption due to metals is captured by \emph{The Cannon} model, and deviations in flux at the 4554\,\AA\ \ion{Ba}{II} line and the 4077\,\AA\ \ion{Sr}{II} transition are solely due to enhancements in Ba and Sr, respectively \citep{marcs,sme,vald,ispec}.
+We estimated [Ba/Fe] and [Sr/Fe] abundance ratios for all s-process enhanced candidates by synthesising spectra.
+We assumed that absorption due to metals is captured by \emph{The Cannon} model, and deviations in flux at the 4554\,\AA\ \ion{Ba}{II} line and the 4077\,\AA\ \ion{Sr}{II} transition are solely due to enhancements in Ba and Sr, respectively.
+We used an extensive grid of model
+atmospheres developed by the MARCS program \citep{marcs}, determined stellar parameters using the SME code\citep{sme},?
+
+In analyses of stellar spectra and colours, and for the analysis of integrated light from galaxies, a homogeneous grid of model
+atmospheres of late-type stars and corresponding flux spectra is needed
+We construct an extensive grid of spherically-symmetric models (supplemented with plane-parallel ones for the highest surface
+gravities), built on up-to-date atomic and molecular data, and make it available for public use.
+
+\citep{marcs,sme,vald,ispec}.
 We adopted the stellar parameters ($T_{\rm eff}$, $\log{g}$, [Fe/H]) from \citet{ho2017}, and assume a microturbulence of $v_{mic} = 2\,{\rm km\,s}^{-1}$.
@@
 
-It's important to note, previous studies \citet{malaney1988} define barium stars through an abundance criteria $\rm[Ba/Fe]\geq +0.3$, and out of our 187 barium star sample using this criteria , only one star ($\rm J092155.95+265253.4$) exhibits a lower [Ba/Fe] of 0.12.
-However, as previously discussed, a negative residual at the \ion{Ba}{II} resonance line 4554\,\AA\, indicates barium enhancement.
-Furthermore, as discussed in section \ref{sec:other enhancements}, an enhancement in carbon is observed frequently with barium enhancement.
-$\rm J092155.95+265253.4$ shows both a negative residual at 4554\,\AA\, and carbon enhancement, we therefore conclude that this single deviant case can be classified as a barium star.
-Additionally, it should be mentioned, our average abundance error is 0.1, although, these results still indicate our sample can be classified as barium stars since they exhibit enhancement at the BaII resonance line 4554, and have a $\rm[Ba/Fe] \geq 0.2$.
-Nevertheless, this sample still constitutes the largest collection of barium stars ever discovered, with the next sample of significant size containing 182 barium stars \citep[e.g.,][]{decastro2016}.
+Our analysis shows 186/187 of our s-process candidates exhibit enhancement at the BaII resonance line 4554 with a $\rm[Ba/Fe] \geq +0.3$, and a average abundance error of 0.1.
+Previous studies \citet{malaney1988} have defined s-process candidates through an abundance criteria of $\rm[Ba/Fe]\geq +0.3$.
+Using this measure, only one star ($\rm J092155.95+265253.4$) from our sample exhibits a lower [Ba/Fe] of 0.12.
+This however does not rule out s-process enhancement for this candidate.
+As previously discussed, a negative residual at the \ion{Ba}{II} resonance line 4554\,\AA\ indicates s-process enhancement and as discussed in section \ref{sec:other enhancements}, carbon enrichment is observed frequently with s-process enhancement.
+$\rm J092155.95+265253.4$ shows both a negative residual at 4554\,\AA\ and carbon enrichment, we therefore conclude that this single deviant case can be classified as a s-process candidate.
+This additionally applies to candidates that fall under $\rm[Ba/Fe]\geq +0.3$ due to the average abundance error.
 
 \subsection{Dynamics}
-Using recent astrometry from Gaia/TGAS \citep{gaia2016,gaia2018b, cropper2018, katz2018, lindegren2018, sartoretti2018}, with section filters parallax > 0, and parallax/parallax error >5, we integrated the galactic orbits for 871/895 Gaia matched s-process enhanced stars.
-Utilising the \texttt{gala} Python package \citep{price2017}, we integrated each star backwards for $0.5\,\textrm{Gyr}$ in a Milky Way-like potential that consists of four components: a \citet{hernquist1990} bulge and nucleus, a \citet{miyamoto1975} disk, and the \citet{nfw1997} halo.
-In this potential, the disk and bulge parameters were adjusted to be consistent with previous work \citep{bovy2015}.
-For our Gaia matched sample, we computed spatial velocities and galactic longitude and latitudes.
-Spatial velocities are relative to the local standard of rest, where $U_{LSR}$ is positive towards the Galactic centre, $V_{LSR}$ is positive in the direction of Galactic rotation ($l=90^{\circ}, b=0^{\circ}$), and $W_{LSR}$ is positive towards the north galactic pole ($b=90^{\circ}$).
-Our analysis revealed our stellar sample contains 97\% disk stars (81\% thin and 16\% thick), and 3\% halo stars.
+We integrated the galactic orbits using recent astrometry from Gaia \citep{gaia2016,gaia2018b, cropper2018, katz2018, lindegren2018, sartoretti2018} for 871/895 s-process enhanced stars with parallax > 0 and parallax/parallax error > 5 selection filters.
+We integrated each star backwards for $0.5\,\textrm{Gyr}$ using the \texttt{gala} Python package \citep{price2017} in a Milky Way-like potential \citep{mwpotential2014} that consists of four components: a \citet{hernquist1990} bulge and nucleus, a \citet{miyamoto1975} disk, and a \citet{nfw1997} halo.
+We computed spatial velocities relative to the local standard of rest, where $U_{LSR}$ is positive towards the Galactic centre, $V_{LSR}$ is positive in the direction of Galactic rotation ($l=90^{\circ}, b=0^{\circ}$), and $W_{LSR}$ is positive towards the north galactic pole ($b=90^{\circ}$).
+Our analysis revealed 97\% disk star membership and 3\% with velocity consistent to the halo which is shown using a Toomre diagram in Figure \ref{fig:figure4}.
 
@@
 \subsection{Observations and data reduction}
-On the night of 07 January 2018 we acquired a high-resolution spectrum of two barium star candidates (J09162834+0259348 and J08351472-0548480) using the MIKE (Magellan Inamori Kyocera Echelle) \citep{bernstein2003} spectrograph on the Magellan Clay telescope \citep{schectman2003} at Las Campanas Observatory, Chile.
-Candidates for follow-up observations were chosen based on observability constraints and ranked by their apparent visual magnitude, with both candidates having $V \approx 12$.
-We observed both stars in good seeing using the 0.7 arcsecond slit and 2x2 spatial on-chip binning, providing a spectral resolution of ($\mathcal{R} \approx 28,000$).
+On 07 January 2018 we acquired a high-resolution spectrum of two s-process candidates (J09162834+0259348 and J08351472-0548480) using the MIKE (Magellan Inamori Kyocera Echelle) \citep{bernstein2003} spectrograph on the Magellan Clay telescope \citep{schectman2003} at Las Campanas Observatory, Chile.
+Candidates were observed as part of another program not a detailed follow-up campaign.
+They were chosen based on observability constraints and ranked by their apparent visual magnitude, with both candidates having $V \approx 12$.
+We observed both stars in good seeing using the 0.7 arcsecond slit and 2x2 spatial on-chip binning, providing a spectral resolution of $\mathcal{R} \approx 28,000$.
 Exposure times of 100 seconds were sufficient to achieve a S/N ratio exceeding 30 per pixel at 4500\,\AA.
@@
 We reduced the data using the \texttt{CarPy} package \citep{kelson2000}.
-We used spline functions to continuum-normalise all echelle orders, and resampled the normalised spectra onto a uniform-sized wavelength map.
+We used spline functions to continuum-normalise all echelle orders, and resampled the normalised spectra onto a uniform-spaced wavelength map.
 We used a rest-frame normalised template of a FGK-type star to place the observed spectra at rest.
@@
 %A$\&$A, 542, A67
+\bibitem[\protect\citeauthoryear{Price-Whelan}{2014}]{mwpotential2014}
+Price-Whelan, A.~M., Hogg, D.~W., Johnston, K.~V.,\& Hendel, D. 2014, 
+Apj, 4, 794
 \bibitem[\protect\citeauthoryear{Price-Whelan}{2017}]{price2017}

### 2018-09-08 article/ms.tex
paper progress

@@
 On 07 January 2018 we acquired a high-resolution spectrum of two s-process candidates (J09162834+0259348 and J08351472-0548480) using the MIKE (Magellan Inamori Kyocera Echelle) \citep{bernstein2003} spectrograph on the Magellan Clay telescope \citep{schectman2003} at Las Campanas Observatory, Chile.
-Candidates were observed as part of another program not a detailed follow-up campaign.
-They were chosen based on observability constraints and ranked by their apparent visual magnitude, with both candidates having $V \approx 12$.
+These two candidates were observed as part of another program not a detailed follow-up campaign.
+They were selected based on observability constraints and ranked by their apparent visual magnitude, with both candidates having $V \approx 12$.
 We observed both stars in good seeing using the 0.7 arcsecond slit and 2x2 spatial on-chip binning, providing a spectral resolution of $\mathcal{R} \approx 28,000$.
@@
 The abundance ratios we estimate from high-resolution spectra are in excellent agreement with our estimates from LAMOST spectra, all agreeing within the joint $1.2\sigma$.
-Specifically, for J09162834+02593480 from high- and low-resolution spectra, respectively, we find $[{\rm Sr/Fe}] = 0.76 \pm 0.10$ and $0.85 \pm 0.21$, and $[{\rm Ba/Fe}] = 0.92 \pm 0.10$ and $0.77 \pm 0.21$.
+Specifically, for J09162834+0259348 from high- and low-resolution spectra, respectively, we find $[{\rm Sr/Fe}] = 0.76 \pm 0.10$ and $0.85 \pm 0.21$, and $[{\rm Ba/Fe}] = 0.92 \pm 0.10$ and $0.77 \pm 0.21$.
 The biggest discrepancy we find between high- and low-resolution spectra is [Sr/Fe] for J09162834+0259348, where we find $[{\rm Sr/Fe}] = 0.62 \pm 0.07$ from our Magellan/MIKE spectra, and $0.90 \pm 0.22$ from LAMOST.
@@
 \subsection{Extrinsic or intrinsic}
-Barium enhanced stars exist as either intrinsic or extrinsic stellar objects.
-Intrinsically enhanced barium stars must be massive enough to reach the TP-AGB phase, and extrinsic barium stars must be in a binary with a previously polluting TP-AGB star companion (AGB S star).
-Figure \ref{fig:figure2} shows that the majority of our stellar sample exists within temperature and luminosity ranges not enveloped by the AGB.
-This highlights that our sample does not contain stars to the degree of evolution required to reach the TP-AGB phase, and therefore, must be extrinsic barium stars.
-However, stars with temperatures below 3800K in Figure \ref{fig:figure2} are potential AGB stars, and their intrinsic or extrinsic nature is not certain.
-Additionally, it's important to note, previous literature \citep{van2017}, state only 33\% of their stellar sample are post-main-sequence barium stars (extrinsic barium stars).
-In comparison, we find that all our barium candidates to be extrinsic.
-This suggests, the construction of our data-driven model may have missed some AGB barium candidates, or that previous studies were biased towards finding luminous AGB S stars.
-Given that our analysis limits us to only giant stars, such that we do not find any extrinsic barium stars on the main-sequence, na\"ively we would expect that our sample would be biased \emph{towards} finding a higher fraction of red giant stars.
-Given this bias, Figure \ref{fig:figure3} illustrates through the temperature, and log g ranges present, that our sample is exclusively populated by red giant extrinsic barium stars.
-This suggests unaccounted selection biases in previous studies towards luminous AGB S stars.
+S-process enrichment can be explained by intrinsic or extrinsic phenomena.
+Intrinsically enhanced s-process candidates must be massive enough to reach the TP-AGB phase, and extrinsic s-process candidates must be in a binary with a previously polluting TP-AGB star companion (AGB S star).
+Previous literature \citep{van2017} states only 33\% of their sample are post-main-sequence s-process candidates (extrinsic).
+In comparison, Figure \ref{fig:figure2} shows that the majority of our sample have temperatures and luminosity not covered by the AGB.
+This highlights that our sample does not contain stars evolved enough to reach the TP-AGB phase and therefore, must be extrinsic s-process candidates.
+This is in agreement with our sample selection given we were predominantly restricted to RGB stars.
+However stars with temperatures below 3800K in Figure \ref{fig:figure2} are consistent with being AGB stars, and their intrinsic or extrinsic nature is not certain.
 
@@
 	\includegraphics[width=0.5\textwidth]{hrd_new.pdf}
-    \caption{Effective temperature $T_{\rm eff}$ and surface gravity $\log{g}$ for 257 candidate barium stars from LAMOST.}
+    \caption{Effective temperature $T_{\rm eff}$ and surface gravity $\log{g}$ for 187 s-process candidates from LAMOST.}
     %Stars with $\log{g} > 2$ (as marked) have not evolved through the thermally pulsing asymptotic giant branch phase, and therefore their abundance signature must be the result of an extrinsic pollution event.
@@
 \subsection{Sodium enhancement}
-Sodium overabundances observed in the atmospheres of giants is thought to be synthesised by the NeNa reaction chain in the convective core of main-sequence stars \citep{el1995}.
-Sodium is transported to the surface of these giants via mixing during the first dredge-up, and stars with a  minimum mass of $1.5\,M_\odot$ can exhibit enhanced sodium abundances through the NeNa cycle \citep{denissenkov1987,smiljanic2012}.
-\citet{antipova2004} reported sodium enhancements in 3 of their 16 barium star candidates, and they relate this to the dredge-up of nuclear-burning material produced by convection during the red-giant phase.
-Moreover, they suggest that [Na/Fe] ratios are systematically higher for giants with lower $\log{g}$ values, however, these [Na/Fe] ratios do not exhibit variations in metallicity.
-Similarly, \citet{decastro2016} highlights the possible weak anti-correlation between [Na/Fe] ratio and $\log{g}$, and highlights that this trend is present in previous studies \citep[e.g.,][]{boyarchuk2002,mishenina2006,luck2007,takeda2008}.
+Sodium overabundances observed in the atmospheres of giants are primarily synthesised by the NeNa reaction chain in the convective core of main-sequence stars \citep{el1995}.
+Sodium is transported to the surface via mixing during the first dredge-up and stars with masses more than $1.5\,M_\odot$ can show enhanced sodium abundances \citep{denissenkov1987,smiljanic2012}.
+\citet{antipova2004} reported  enhanced sodium in 3 of their 16 barium star candidates.
+They relate this to the dredge-up of nuclear-burning material produced by convection during the red-giant phase and suggest that [Na/Fe] ratios are systematically higher for giants with lower $\log{g}$ values.
+Similarly, \citet{decastro2016} proposes a possible weak anti-correlation between [Na/Fe] ratio and $\log{g}$, and highlights that this trend is present in previous studies \citep[e.g.,][]{boyarchuk2002,mishenina2006,luck2007,takeda2008}.
 
-We find that $<2$\,\% of our barium stars show sodium enhancement, contrary to previous studies \citep[e.g.,][]{decastro2016}, indicating all s-process enhanced stars will exhibit Na enhancement.
-We also note that the 5 sodium-enhanced barium stars all have values of, $\log{g} \approx 3$, which is inconsistent with the literature.
-Previous studies suggest, lower $\log{g}$ values are expected, given low $\log{g}$ values systematically contribute to higher [Na/Fe] abundance ratios.
-It is important to note, sodium enhancement can occur due to the presence of interstellar dust.
-Using the IRSA's all-sky dust map \citep{schlafly2011}, we find that 2 of 5 of these stars have E(B-V)$\approx$ 0.35, suggesting that the flux residuals around the Na doublet are due to interstellar absorption.
-However, 3 exhibit low ($\approx$0.045) E(B-V) values, indicating, the enhancement is more likely due to stellar absorption.
-These results suggest that sodium-rich material from a companion TP-AGB star has polluted these 3 barium candidates, but more importantly, sodium enhancement is by no means ubiquitous in barium stars.
-However, it should be highlighted that low resolution spectra can result in Na line saturation, limiting the flux enhancement even with an abundance enhancement.
+%however, these [Na/Fe] ratios do not exhibit variations in metallicity
+We find that less than $3$\,\% of our s-process candidates show enhanced sodium all of which have values of $\log{g} \approx 3$.
+It is possible our 5/187 enhanced sodium candidates are false-positives resulting from interstellar dust absorption.
+Using the IRSA's all-sky dust map \citep{schlafly2011}, we find that 2/5 of these candidates have E(B-V)$\approx$ 0.35 confirming that the flux residuals around the Na doublet are due to interstellar absorption.
+However 3/5 candidates exhibit low ($\approx$0.045) E(B-V) values indicating the enhancement is more likely due to stellar absorption.
+These results suggest that sodium-rich material from a companion TP-AGB star has polluted these 3 s-process candidates.
+It also highlights sodium enhancement is by no means ubiquitous in s-process candidates.
+Yet, low resolution spectra can imitate Na line saturation and limits flux enhancement even if an abundance enhancement is present.
+%Previous studies \citep[e.g.,][]{decastro2016} suggest lower $\log{g}$ values systematically contribute to higher [Na/Fe] abundance ratios.
 
-The data that led \citet{decastro2016} to conclude that barium stars have higher [Na/Fe] ratios is subject to systematic differences (biases) between Milky Way studies of normal FGK-type stars, and those focussed on barium stars.
+The data that led \citet{decastro2016} to conclude that s-process candidates have higher [Na/Fe] ratios is subject to systematic differences (biases) between Milky Way studies of normal FGK-type stars, and those focussed on s-process candidates.
 This has the potential to contain unresolved differences in the reported [Na/Fe] abundance ratio.
-These systematic effects would also contribute to the observed correlation between [Na/Fe] and $\log{g}$, since intrinsic barium stars (by definition) have low $\log{g}$ values.
-We do not observe this correlation between [Na/Fe] and $\log{g}$ in our sample, and we conclude that barium stars do not have higher [Na/Fe] abundance ratios on average.
+These systematic effects would also contribute to the observed correlation between [Na/Fe] and $\log{g}$, since intrinsic s-process candidates (by definition) have low $\log{g}$ values.
+We do not observe this correlation between [Na/Fe] and $\log{g}$ in our sample.
+We find that s-process candidates do not have higher [Na/Fe] abundance ratios on average.
 
@@
 
-Technetium has a half life of approximately 211,000 years and as a result, the presence of Tc enhancement is constrained to observations of AGB S stars \citep{jorissen1993} or recently polluted extrinsic barium stars.
-Our analysis, undertaken for the TC lines 4049\,\AA, 4238\,\AA, 4262\,\AA, 4297\,\AA, and 5924\,\AA, discovered 51 single Tc line matches at 4238,\AA, within our 187 barium star candidate sample.
-The majority (46/51) have $\log{g} > 2$, suggesting they cannot be AGB S stars, and may indicate a recent ($<1\,\textrm{Myr}$) mass accretion event.
-However, for Tc to be present in the LAMOST spectra the enhancement must be considerably strong, and given that all 51 matches were at single lines it is concluded that these results are more likely data artefacts.
-In agreement with previous findings \citep[e.g.,][]{little1987,smith1984,smith1983}, the results indicate that none of the evolved barium stars in our sample exhibited the presence of Tc enhancement, and in accordance with previous literature, it can be concluded that our barium star sample is extrinsic.
-However, we caution that Tc enhancement is usually a very weak signature, and the presence of Tc would require multiple lines of enhancement.
-Additionally, it is universally known that numerous Tc lines are considerably blended by other s-process enhancement lines \citep[e.g.,][]{van1999}.
+Technetium has a half life of approximately 211,000 years and as a result, the presence of Tc enhancement is constrained to observations of AGB S stars \citep{jorissen1993} or recently polluted extrinsic s-process candidates.
+Our analysis searches for flux residuals around the Tc enhancement lines 4049\,\AA, 4238\,\AA, 4262\,\AA, 4297\,\AA, and 5924\,\AA.
+We found 51/187 of our s-process candidates to show enhanced Tc at the single line 4238,\AA.
+The majority (46/51) have $\log{g} > 2$ suggesting they cannot be AGB S stars and may indicate a recent ($<1\,\textrm{Myr}$) mass accretion event.
+However we caution that Tc enhancement is usually a very weak signature and would require multiple lines of enhancement.
+Since all 51 matches were at single lines we concluded Tc enhanced candidates are more likely a result of data artefacts.
+Also, it is universally known that numerous Tc lines are considerably blended by other s-process enhancement lines \citep[e.g.,][]{van1999}.
+We therefore conclude our analysis finds no enhanced Tc s-process candidates and is in agreement with previous findings \citep[e.g.,][]{little1987,smith1984,smith1983}.
+The absence of Tc indicates our s-process candidates are not massive enough to produce the element, and suggests that our sample is populated solely by extrinsic s-process candidates.
 
@@
 \subsection{Carbon bands}
-Barium stars are excellent candidates for investigating the relationship between neutron-capture elements and other species that may be depleted or enhanced, since iron within these stars act as neutron seeds during the operation of the s-process.
-In the AGB phase the abundance of carbon is a product of helium fusion, specifically the triple-alpha process within a star.
-In an identical mechanism to the presence of s-process element enhancement, carbon enhanced stars exist intrinsically or extrinsically.
+During the AGB phase of a star, carbon abundance is a product of helium fusion via the triple-alpha process.
 Giants and supergiants become enhanced in carbon through TDU process discussed in Section \ref{sec:intro}, and extrinsic carbon enhancement occurs via mass transfer from a binary AGB star.
-Our analysis produced 178 CH and G band significantly enhanced stars (i.e., $[\textrm{C/Fe}] \gtrsim 0.5$) out of the total 187 barium candidates.
-These 178 stars exist in a metallicity range of 0 to -1.2, and can be termed "CH stars" in accordance with definitions used in the literature \citep[e.g.][]{luck1991, mcclure1997}.
-%Similar to the s-process enhancement, this suggests our candidates are consistent with being either intrinsic or extrinsic Barium stars.
+Our analysis identifies carbon enhanced candidates by searching for flux residuals in the CH and G band regions at lines 4050\,\AA\hspace{0.5mm} and 4550\,\AA.
+We found 178/187 of our s-process candidates to have carbon enrichment (i.e., $[\textrm{C/Fe}] \gtrsim 0.5$).
+These 178 stars have in a metallicities ranging of 0 to -1.2, and are classically referred to as CH stars \citep[e.g.][]{luck1991, mcclure1997}, we simply define them as metal poor s-process candidates.
 
 \subsection{Comparison to AGB yields}
-AGB stars, and chemically unusual stars that show the chemical signature of mass transfer pollution from a binary AGB companion, highlight the variety of s-process enhancement.
-In Figure \ref{fig:figure3} we show the heavy-to-light s-process abundance ratio (taken as [Ba/Sr]) for all 187 barium stars identified in LAMOST.
-Although the [Ba/Sr] ratio is quite noisy, the overall metallicity [Fe/H] is quite precise (0.1\,dex).
-Despite our LAMOST sample of 454,180 giants having metallicities down to about $[{\rm Fe/H}] = -2$, we only detect barium stars down to metallicities of about $[{\rm Fe/H}] = -1.1$.
-Given our barium stars exist in this metallicity range of 0 to -1.1, we can classify them as CH stars as defined in previous literature \citep[e.g.][]{luck1991, mcclure1997}.
-
-The final surface s-process index [Ba/Sr], illustrated in Figure \ref{fig:figure3}, illustrates the relationship between [Ba/Sr] yields and the mass of AGB stars.
-This highlights the main neutron source, the $C^{13}(\alpha,n)O^{16}$ reaction chain, is responsible for the Ba and Sr enhancements.
-Additionally, theoretical models show that this source is dominant in low-mass AGB stars, and it follows, that most of the progenitors of s-process elements in our sample are low-mass AGB stars between $1 - 3\,M_{\odot}$.
-However, it's important to note, our results do not indicate when the mass transfer occurred, and our candidates fitting these theoretical yields may not have the correlating binary companion masses.
-Instead, mass transfer may have occurred early on in the AGB S binary companion star's lifespan, and the resulting [Ba/Sr] abundance present in our barium candidates may reflect pollution from a lower AGB S star mass.
-Additionally, this can be extended to our candidates not approximated by theoretical yields.
-Other barium candidates not fitting this relationship represent the possibly more massive, and expectedly rarer, AGB S stars within our sample.
-
-%The Salpeter initial mass function (or any bottom-heavy initial mass function) predicts the majority of stars in the Milky Way will have lower masses, and as predicted the [Ba/Sr] values of our barium stars approximately fit the lower mass yields as seen in Figure \ref{fig:figure3}.
+In Figure \ref{fig:figure3} we show the heavy-to-light s-process abundance ratio (taken as [Ba/Sr]) for all 187 s-process candidates identified in LAMOST.
+Although the [Ba/Sr] ratio is quite noisy ($\sim$0.2\,dex) the overall metallicity [Fe/H] is quite precise (0.1\,dex).
+The final surface s-process index [Ba/Sr] seen in Figure \ref{fig:figure3} represents degree of the s-process pollution and is an indication of the binary AGB companion's mass.
+The [Ba/Sr] yields for our s-process candidates follow similar trends to previous studies \citep{fishlock2014,cristallo2015,karakas_lugaro2016}.
+This suggests that the main neutron source for s-process enhancement in our sample is the $C^{13}(\alpha,n)O^{16}$ reaction chain.
+Theoretical models show that this source is dominant in low-mass AGB stars and it follows, that most of the progenitors for s-process enhancement in our sample are low-mass AGB stars between $1 - 3\,M_{\odot}$.
+However our results do not indicate when the mass transfer occurred, and our candidates fitting these theoretical yields may not have the correlating binary companion masses.
+Mass transfer may have occurred early on in the AGB S binary companion star's lifespan.
+The resulting [Ba/Sr] abundance present in our s-process candidates and those not approximated by theoretical curves may reflect pollution from a lower AGB S star mass.
+Our s-process candidates that deviate from this relationship may also represent the possibly more massive and exceptionally rarer AGB S stars within our sample.
 
@@
 
-The majority of our sample showed pro-grade orbits that were consistent with membership in the Milky Way disk, indicating they do not originate from an unusual stellar event.
-Figures \ref{fig:figure4} and \ref{fig:figure5} illustrate the galactic distribution of each class of s-process enhanced star investigated.
-For our entire 898 sample, Figure \ref{fig:figure4} shows 97\% reside within the galactic disk (81\% thin disk and 16\% thick disk), and 3\% within the halo.
-Our results show similar trends to the literature, samples from \cite{gomez1997} and \cite{mennessier1997} present populations of 75\% contained within the disk, and 25\% within the halo.
-\cite{pereira2011}’s entire sample resides within the disk, and \cite{decastro2016} states their sample contains 90\% thin disk stars.
-Although, excluding the candidate sample presented by \cite{decastro2016}, it is important to note previous studies contain limited stellar populations ranging from 4 to 12 stars, and cannot be representative of the overall galactic distribution of s-process enhanced stars.
-\cite{jorissen1993} attributes the galactic position of s-process enhanced stars as dependent on their intrinsic or extrinsic nature, given our sample is entirely extrinsic we cannot comment on the comparison between the two enhancement sources.
-However, given our extrinsically s-process enhanced sample concentrates towards the galactic plane, we can propose the sample in \cite{jorissen1993} was not sufficiently large enough to represent the overarching galactic distribution of extrinsic S stars.
+The majority of our sample show pro-grade orbits that were consistent with membership in the Milky Way disk.
+Figures \ref{fig:figure4} and \ref{fig:figure5} illustrate the galactic position of each class of s-process enhanced star investigated.
+For our entire 898 sample, Figure \ref{fig:figure4} shows 97\% reside within the galactic disk  and 3\% with velocity consistent to the halo.
+Our results show similar trends to the literature, samples from \cite{gomez1997} and \cite{mennessier1997} present populations of 75\% contained within the disk and 25\% within the halo.
+\cite{pereira2011}’s entire sample resides within the disk.
+Although, these studies contain limited populations ranging from 4 to 12 stars, and cannot be representative of the overall galactic distribution of s-process enhanced stars.
+\cite{decastro2016} contains a more extensive sample and has similar trends to our findings with a 90\% thin disk membership.
+\cite{jorissen1993} attributes the galactic position of s-process enhanced stars as dependent on their intrinsic or extrinsic nature, concluding intrinsic s-process candidates are more concentrated towards the galactic plane.
+Since our sample is entirely extrinsic we cannot comment on the comparison between the two enhancement sources.
+However given our extrinsically s-process enhanced sample concentrates towards the galactic plane, we can propose the sample in \cite{jorissen1993} was not sufficiently large enough to represent the overarching galactic distribution of extrinsic S stars.
+Or this may be the result of our sample being bias towards finding extrinsic s-process candidates since we were limited mainly to RGB stars.
 
@@
 We conducted the largest ever search for s-process enhanced stars using the LAMOST second data release.
-From 454,180 giant stars, we identify 895 s-process candidates including: 187 stars with significant enhancements in barium and strontium (so-called `barium stars'), 49 stars exhibiting exclusively barium enhancement, and 659 exhibiting exclusively strontium enhancement.
-This sample size is the greatest total number of barium stars known, and represents the largest sample of s-process enhanced stars to date.
-Our kinematical analysis revealed our stellar sample contains 97\% disk stars (81\% thin and 16\% thick), and 3\% halo stars, indicating our barium stars were not produced through an unusual galactic event.
+From 454,180 giant stars, we identify 895 s-process enhanced stars including; 187 s-process candidates, 49 barium enriched stars, and 659 stars with strontium enrichment.
+This sample size is the greatest total number of s-process candidates known, and represents the largest sample of s-process enhanced stars to date.
+We found our sample contains 97\% disk star membership and 3\% with velocity consistent to the halo.
 
-We find 178/257 barium star candidates show carbon enhancement, consistent with the literature, and are possible CH stars.
-However, in contrast with previous works, we do not find barium stars to have significantly higher [Na/Fe] than Milky Way field giants.
-Only 5/257 of our barium stars show enhancement in Na, and the flux residuals in three of those are likely due to interstellar dust.
+We find the majority (178/257) of our s-process candidates show carbon enhancement in agreement with the literature and are classically defined CH stars.
+However contrary to previous works we do not find our s-process candidates to have significantly higher [Na/Fe] than Milky Way field giants.
+Only 5/257 of our s-process candidates show enhancement in Na, and the flux residuals in three of those are likely due to interstellar dust.
 We suggest that biases between literature sources and systematic effects in measuring [Na/Fe] from stars with low $\log{g}$ contributed to this effect.
 
-Despite our noisy estimates of [Ba/Fe] and [Sr/Fe] from LAMOST spectra, comparisons with AGB yields indicate the main neutron source responsible for the Ba and Sr enhancements, the $C^{13}(\alpha,n)O^{16}$ reaction chain, and theoretical yields suggest the progenitors of our s-process enhanced sample are low-mass AGB stars, between $1 - 3\,M_{\odot}$.
-We encourage follow-up observations with high-resolution spectrographs in order to precisely measure a full suite of neutron-capture abundances.
-This data would permit the most detailed comparisons with AGB star yields ever considered.
+Despite our noisy estimates of [Ba/Fe] and [Sr/Fe] from LAMOST spectra, comparisons with AGB yields indicate the main neutron source responsible for s-process enhancement is the $C^{13}(\alpha,n)O^{16}$ reaction chain.
+Theoretical yields suggest the progenitors of our s-process enhanced sample are low-mass AGB stars between $1 - 3\,M_{\odot}$.
+We encourage follow-up observations with high-resolution spectrographs in order to precisely measure a full suite of neutron-capture abundances and perform a comprehensive comparison of AGB star models.
 

### 2018-09-08 article/galactic_hist.py

@@ -1,0 +1,49 @@
+import numpy as np
+import matplotlib.pyplot as plt
+from astropy.table import Table
+from matplotlib import (colors, cm, ticker)
+
+from mpl_utils import mpl_style
+
+plt.style.use(mpl_style)
+
+stars = Table.read("dynamics_complete_test.csv")
+lamosts = Table.read("lamost_gaia_result.fits")
+
+
+s = stars['GAL_LAT']
+l = lamosts['GAL_LAT']
+
+b = np.absolute(s)
+b_l = np.absolute(l)
+s_h, bin_edges = np.histogram(b, 89)
+l_h, bin_edges = np.histogram(b_l, 89)
+div = np.divide(s_h, l_h)
+#sl_h = div
+#sl_h = np.transpose(sl_h)
+
+#grid_slm = np.ma.masked_where(grid_sl < 0.001, grid_sl)
+
+fig, axes = plt.subplots(2, 1)
+axes[0].bar(bin_edges[:-1], s_h, width = 1, facecolor='#FF9309', alpha=0.5)
+axes[0].set_xlim(min(bin_edges), max(bin_edges))
+axes[0].set_xlabel(r'$|b|$ $[^\circ]$')
+axes[0].set_ylabel(r'Number of candidates', 
+	                rotation=90)
+
+axes[1].bar(bin_edges[:-1], div, width = 1, facecolor='#FF9309', alpha=0.5)
+axes[1].set_xlim(min(bin_edges), max(bin_edges))
+axes[1].set_xlabel(r'$|b|$ $[^\circ]$')
+axes[1].set_ylabel(r'Fraction of candidates relative to LAMOST',
+	                 rotation=90)
+
+for ax in axes:
+    ax.xaxis.set_major_locator(ticker.MaxNLocator(6))
+    ax.yaxis.set_major_locator(ticker.MaxNLocator(6))
+
+fig.tight_layout()
+plt.show()
+'''
+fig.savefig('DynamicFigures/'+'histogram'+'.png')
+fig.savefig("DynamicFigures/histogram.pdf", dpi=150)
+'''

### 2018-09-09 article/ms.tex
paper adjustments

@@
 \\
-$^{6}$Carnegie Observatories
+$^{6}$The Observatories of the Carnegie Institution of Washington, 813 Santa Barbara St., Pasadena, CA 91101, USA
 }
@@
 The [Ba/Sr] yields for our s-process candidates follow similar trends to previous studies \citep{fishlock2014,cristallo2015,karakas_lugaro2016}.
-This suggests that the main neutron source for s-process enhancement in our sample is the $C^{13}(\alpha,n)O^{16}$ reaction chain.
+This suggests that the main neutron source for s-process enhancement in our sample is the $\text{C}^{13}$(\textrm{$\alpha$},n)$\text{O}^{16}$ reaction chain.
 Theoretical models show that this source is dominant in low-mass AGB stars and it follows, that most of the progenitors for s-process enhancement in our sample are low-mass AGB stars between $1 - 3\,M_{\odot}$.
@@
 For our entire 898 sample, Figure \ref{fig:figure4} shows 97\% reside within the galactic disk  and 3\% with velocity consistent to the halo.
-Our results show similar trends to the literature, samples from \cite{gomez1997} and \cite{mennessier1997} present populations of 75\% contained within the disk and 25\% within the halo.
-\cite{pereira2011}’s entire sample resides within the disk.
-Although, these studies contain limited populations ranging from 4 to 12 stars, and cannot be representative of the overall galactic distribution of s-process enhanced stars.
-\cite{decastro2016} contains a more extensive sample and has similar trends to our findings with a 90\% thin disk membership.
+Our results show similar trends to the literature, samples from \cite{gomez1997} and
+\cite{decastro2016} present populations with $\sim$90\% thin disk membership.
+\cite{pereira2011}’s limited sample (12 stars) entirely resides within the disk.
 \cite{jorissen1993} attributes the galactic position of s-process enhanced stars as dependent on their intrinsic or extrinsic nature, concluding intrinsic s-process candidates are more concentrated towards the galactic plane.
 Since our sample is entirely extrinsic we cannot comment on the comparison between the two enhancement sources.
-However given our extrinsically s-process enhanced sample concentrates towards the galactic plane, we can propose the sample in \cite{jorissen1993} was not sufficiently large enough to represent the overarching galactic distribution of extrinsic S stars.
-Or this may be the result of our sample being bias towards finding extrinsic s-process candidates since we were limited mainly to RGB stars.
+However as shown in Figure \ref{fig:figure4} our extrinsically s-process enhanced sample concentrates towards the galactic plane.
+We can propose that the sample in \cite{jorissen1993} was not sufficiently large enough to represent the overarching galactic distribution of extrinsic S stars.
+On the contrary, our findings may be reflective of our sample's bias towards finding extrinsic s-process candidates since we were limited mainly to RGB stars.
+It may not be representative of the overall galactic position of enhanced s-process stars.
 
@@
 \begin{figure}
-	\includegraphics[width=0.5\textwidth]{contour.pdf}
-	\caption{Galactic longitude ([$l^{\circ}$]; x-axis) and galactic latitude ([$b^{\circ}$]; y-axis) shown for: number of s-process enhanced candidates matched with Gaia DR2, the LAMOST sample matched with Gaia DR2, and a density contour between the latter two}
+	\includegraphics[width=0.5\textwidth]{histogram.pdf}
+	\caption{Galactic latitude ([$|b^{\circ}|$]; x-axis) shown for: number of s-process enhanced candidates matched with Gaia DR2, and s-process candidates as a fraction of the LAMOST sample matched with Gaia DR2}
 	\label{fig:figure5}
@@
 
-We find the majority (178/257) of our s-process candidates show carbon enhancement in agreement with the literature and are classically defined CH stars.
+We find the majority (178/187) of our s-process candidates show carbon enhancement in agreement with the literature and are classically defined CH stars.
 However contrary to previous works we do not find our s-process candidates to have significantly higher [Na/Fe] than Milky Way field giants.
@@
 
-Despite our noisy estimates of [Ba/Fe] and [Sr/Fe] from LAMOST spectra, comparisons with AGB yields indicate the main neutron source responsible for s-process enhancement is the $C^{13}(\alpha,n)O^{16}$ reaction chain.
+Despite our noisy estimates of [Ba/Fe] and [Sr/Fe] from LAMOST spectra, comparisons with AGB yields indicate the main neutron source responsible for s-process enhancement is the $\text{C}^{13}$(\textrm{$\alpha$},n)$\text{O}^{16}$ reaction chain.
 Theoretical yields suggest the progenitors of our s-process enhanced sample are low-mass AGB stars between $1 - 3\,M_{\odot}$.

### 2018-09-13 article/ms.tex
paper progress

@@
 
-Here we present the discovery of 895 stars enriched in s-process elements from the LAMOST spectra using a data-driven approach.
+Here we present the discovery of 895 s-process candidates from 454,180 giant stars observed by LAMOST using a data-driven approach.
 This sample constitutes the largest number of s-process enhanced stars ever discovered.
 Our sample includes; 187 s-process candidates that are enhanced in both barium and strontium, 49 stars with significant barium enhancement only, and 659 stars that show only strontium enhancement.
-Our entire s-process candidate sample exists within temperature and luminosity ranges not enveloped by the AGB?, which may indicate a recent ($<1\,\textrm{Myr}$) mass accretion event from an AGB companion.
-The majority of our barium stars ($95\%$) show strong carbon enhancements yet, only 5 candidates ($<3$\,\%) show evidence of sodium enhancement, in tension with previous observations of enhanced Na among s-process candidates.
-We argue this may have been a selection bias?
-in previous studies.
+Most of our sample are within temperature and log g ranges consistent with RGB populations, this is consistent with our selection bias towards finding RGB stars.
+The majority of our s-process candidates ($95\%$) show strong carbon enhancements yet, only 5 candidates ($<3$\,\%) show evidence of sodium enhancement, in tension with previous observations of enhanced Na among s-process candidates.
+We argue this may have been a systematic bias in previous studies.
 Our kinematical analysis reveals our sample is composed of 97\% disk stars, and 3\% with velocity consistent to the halo.
@@
 
-The abundance of elements created through the slow neutron-capture process (s-process), is a measure of the nucleosynthetic reactions that occur primarily in Asymptotic Giant Branch (AGB) stars.
+The abundance of elements created through the slow neutron-capture process (s-process) is a measure of the nucleosynthetic reactions that occur primarily in Asymptotic Giant Branch (AGB) stars.
 Due to their associated enrichment of the s-process element barium, stars with peculiar enhancements of carbon, and heavy elements (Z > 30) are commonly referred to as 'barium stars' \citep{Bidelman1951}.
@@
 These energy bursts drive a convective zone that sweeps almost the entire region lying between the core and the He-shell, mixing the products of nucleosynthesis within these regions.
-While simultaneously, forcing the star to expand and pushing the H-shell out to cooler regions \citep{karakas2002}.
+While simultaneously forcing the star to expand and pushing the H-shell out to cooler regions \citep{karakas2002}.
 The convective envelope will then move inwards towards regions previously mixed by the thermal pulse driven convective zones.
@@
 During the TP-AGB phase, the TDU is responsible for the surface enrichment in $^{12}$C and heavy elements produced by the s-process \citep[e.g.,][]{busso2001}.
-Post dredge up the star contracts, reigniting the H-shell, and producing the majority of the surface luminosity for the next interpulse period.
+Post dredge up the star contracts, reigniting the H-shell and producing the majority of the surface luminosity for the next interpulse period.
 The interpulse, thermal pulse, and dredge up cycle may occur numerous times and the frequency depends on the initial mass, composition, and mass-loss rate of the star.
 
-S-process candidate can form within a metallicity-dependent initial mass range of approximately $0.8 - 8\,M_{\odot}$ \citep{karakas2016cp}.
+S-process candidates can form within a metallicity-dependent initial mass range of approximately $0.8 - 8\,M_{\odot}$ \citep{karakas2016cp}.
 The minimum mass is defined by the onset of core helium burning, and the maximum by core carbon burning.
@@
 Less massive metal-rich stars may reach ages of $\approx$ 100Myr, this includes stars that are at the core carbon burning limit or very close to it \citep[e.g.,][]{whitelock2013}.
-The majority s-process candidates are observed to be members of the disk \citep{jorissen1993,gomez1997,mennessier1997}.
+The majority of s-process candidates are observed to be members of the disk \citep{jorissen1993,gomez1997,mennessier1997}.
 In \citet{pereira2011}, it is shown that metal-rich s-process candidates share similar kinematics to other metal-rich and super metal-rich stars already analysed, suggesting that they do not belong to the bulge population.
 \cite{jorissen1993} relates galactic position to the extrinsic or intrinsic nature of the s-process candidate.
-They show that intrinsically enhanced stars are more concentrated towards the galactic plane than extrinsic enhanced stars.
+They determine the scale height for their intrinsic candidates and state they are concentrated towards the galactic plane whilst their extrinsic s-process candidates are uniformly distributed.
 
@@
 Stellar parameters ($T_{\rm eff}$, $\log{g}$, [M/H], [$\alpha$/M]) were derived by \citep{ho2017} using a \emph{The Cannon} \citet{ness2016}, with labels for 9,952 giant stars in common between LAMOST and the APOGEE survey.
-We note that this sample is limited to giant stars, implying that we would not identify dwarf s-process enhanced stars.
+Our sample is limited entirely to giants implying that we would not identify dwarf s-process enhanced stars.
 Cross-validation tests shows that the typical uncertainties are approximately 70\,K in effective temperature $\rm T_{\rm eff}$, 0.1\,dex in surface gravity $\log{g}$, 0.1\,dex in metallicity [M/H], and 0.04\,dex in the $\alpha$-element abundance relative to overall metallicity [$\alpha$/M].
@@
 This sample consists of; 187 s-process candidates, 49 barium enriched stars, and 659 stars with strontium enrichment.
-It is the largest collection of s-process enhanced stars ever discovered, with the next sample of significant size containing 182 s-process candidates \citep[e.g.,][]{decastro2016}.
+It is the largest collection of s-process enhanced stars ever discovered.
 
@@
 Enhancements in sodium, technetium, and carbon are useful indicators when determining whether a sample is populated by intrinsically enhanced AGB S stars, or polluted extrinsic barium stars.
-We?
-performed an identical analysis to the process described in Section \ref{sec:cand} in order to identify sodium, technetium, or carbon enhancement in our sample of 187 s-process candidates.
+We performed an identical analysis to the process described in Section \ref{sec:cand} in order to identify negative flux residuals for enhancement in sodium, technetium, or carbon.
 For sodium enrichment, we required significant absorption in the doublet lines at 5889\,\AA\ and 5895\,\AA\.
@@
 The abundance ratios we estimate from high-resolution spectra are in excellent agreement with our estimates from LAMOST spectra, all agreeing within the joint $1.2\sigma$.
-Specifically, for J09162834+0259348 from high- and low-resolution spectra, respectively, we find $[{\rm Sr/Fe}] = 0.76 \pm 0.10$ and $0.85 \pm 0.21$, and $[{\rm Ba/Fe}] = 0.92 \pm 0.10$ and $0.77 \pm 0.21$.
+For J09162834+0259348 from high- and low-resolution spectra, respectively, we find $[{\rm Sr/Fe}] = 0.76 \pm 0.10$ and $0.85 \pm 0.21$, and $[{\rm Ba/Fe}] = 0.92 \pm 0.10$ and $0.77 \pm 0.21$.
 The biggest discrepancy we find between high- and low-resolution spectra is [Sr/Fe] for J09162834+0259348, where we find $[{\rm Sr/Fe}] = 0.62 \pm 0.07$ from our Magellan/MIKE spectra, and $0.90 \pm 0.22$ from LAMOST.
-Finally, for J09162834+0259348 we find $[{\rm Ba/Fe}] = 0.94 \pm 0.12$ from high-resolution spectra and $[{\rm Ba/Fe}] = 0.80 \pm 0.26$ from low-resolution spectra.
+For J08351472-0548480 we find $[{\rm Ba/Fe}] = 0.94 \pm 0.12$ from high-resolution spectra and $[{\rm Ba/Fe}] = 0.80 \pm 0.26$ from low-resolution spectra.
 Uncertainties on abundances derived from high-resolution spectra are taken as the standard deviation of multiple line measurements.
@@
 Intrinsically enhanced s-process candidates must be massive enough to reach the TP-AGB phase, and extrinsic s-process candidates must be in a binary with a previously polluting TP-AGB star companion (AGB S star).
-Previous literature \citep{van2017} states only 33\% of their sample are post-main-sequence s-process candidates (extrinsic).
-In comparison, Figure \ref{fig:figure2} shows that the majority of our sample have temperatures and luminosity not covered by the AGB.
+Previous literature \citep{van2017} \hspace{0.3mm} states only 33\% of their sample are post-main-sequence s-process candidates (extrinsic).
+In comparison, Figure \ref{fig:figure2} shows that the majority of our sample are within temperature and log g ranges consistent with RGB populations.
 This highlights that our sample does not contain stars evolved enough to reach the TP-AGB phase and therefore, must be extrinsic s-process candidates.
-This is in agreement with our sample selection given we were predominantly restricted to RGB stars.
-However stars with temperatures below 3800K in Figure \ref{fig:figure2} are consistent with being AGB stars, and their intrinsic or extrinsic nature is not certain.
+This is in agreement with our sample selection bias given we were predominantly restricted to RGB stars.
+However stars with temperatures below 3800K in Figure \ref{fig:figure2} are possible AGB candidates, and their intrinsic or extrinsic nature is not certain.
 
@@
 Sodium is transported to the surface via mixing during the first dredge-up and stars with masses more than $1.5\,M_\odot$ can show enhanced sodium abundances \citep{denissenkov1987,smiljanic2012}.
-\citet{antipova2004} reported  enhanced sodium in 3 of their 16 barium star candidates.
-They relate this to the dredge-up of nuclear-burning material produced by convection during the red-giant phase and suggest that [Na/Fe] ratios are systematically higher for giants with lower $\log{g}$ values.
+\citet{antipova2004} reported  enhanced sodium in 3 of their 16 s-process candidates.
+They relate this to the dredge-up of nuclear-burning material produced by convection during the red-giant phase, and suggest that [Na/Fe] ratios are systematically higher for giants with lower $\log{g}$ values.
 Similarly, \citet{decastro2016} proposes a possible weak anti-correlation between [Na/Fe] ratio and $\log{g}$, and highlights that this trend is present in previous studies \citep[e.g.,][]{boyarchuk2002,mishenina2006,luck2007,takeda2008}.
@@
 Our analysis searches for flux residuals around the Tc enhancement lines 4049\,\AA, 4238\,\AA, 4262\,\AA, 4297\,\AA, and 5924\,\AA.
-We found 51/187 of our s-process candidates to show enhanced Tc at the single line 4238,\AA.
+We found 51/187 of our s-process candidates to show enhanced Tc at exclusively 4238,\AA.
 The majority (46/51) have $\log{g} > 2$ suggesting they cannot be AGB S stars and may indicate a recent ($<1\,\textrm{Myr}$) mass accretion event.
-However we caution that Tc enhancement is usually a very weak signature and would require multiple lines of enhancement.
-Since all 51 matches were at single lines we concluded Tc enhanced candidates are more likely a result of data artefacts.
-Also, it is universally known that numerous Tc lines are considerably blended by other s-process enhancement lines \citep[e.g.,][]{van1999}.
-We therefore conclude our analysis finds no enhanced Tc s-process candidates and is in agreement with previous findings \citep[e.g.,][]{little1987,smith1984,smith1983}.
-The absence of Tc indicates our s-process candidates are not massive enough to produce the element, and suggests that our sample is populated solely by extrinsic s-process candidates.
+However we caution that Tc enhancement is usually a very weak signature, would require multiple lines of enhancement, and is considerably blended by other s-process enhancement lines \citep[e.g.,][]{van1999}.
+Since all 51 matches were at a single line we surmise Tc enhanced candidates are more likely a result of data artefacts.
+We therefore conclude our analysis finds no Tc enhanced candidates and is in agreement with previous findings \citep[e.g.,][]{little1987,smith1984,smith1983}.
+The absence of Tc indicates our sample is populated solely by extrinsic s-process candidates and a recent mass transfer event is not the source of our s-process enhancement.
 
@@
 Giants and supergiants become enhanced in carbon through TDU process discussed in Section \ref{sec:intro}, and extrinsic carbon enhancement occurs via mass transfer from a binary AGB star.
-Our analysis identifies carbon enhanced candidates by searching for flux residuals in the CH and G band regions at lines 4050\,\AA\hspace{0.5mm} and 4550\,\AA.
+Our analysis identifies carbon enhanced candidates by searching for flux residuals in the CH and G band regions near 4300\,\AA.
 We found 178/187 of our s-process candidates to have carbon enrichment (i.e., $[\textrm{C/Fe}] \gtrsim 0.5$).
-These 178 stars have in a metallicities ranging of 0 to -1.2, and are classically referred to as CH stars \citep[e.g.][]{luck1991, mcclure1997}, we simply define them as metal poor s-process candidates.
+These 178 stars have metallicities ranging of 0 to -1.2 and are classically referred to as CH stars \citep[e.g.][]{luck1991, mcclure1997}.
+We simply define them as metal poor s-process candidates.
 
@@
 Although the [Ba/Sr] ratio is quite noisy ($\sim$0.2\,dex) the overall metallicity [Fe/H] is quite precise (0.1\,dex).
-The final surface s-process index [Ba/Sr] seen in Figure \ref{fig:figure3} represents degree of the s-process pollution and is an indication of the binary AGB companion's mass.
+The final surface s-process index [Ba/Sr] seen in Figure \ref{fig:figure3} represents degree of the s-process element pollution, and is an indication of the binary AGB companion's mass.
 The [Ba/Sr] yields for our s-process candidates follow similar trends to previous studies \citep{fishlock2014,cristallo2015,karakas_lugaro2016}.
@@
 The majority of our sample show pro-grade orbits that were consistent with membership in the Milky Way disk.
-Figures \ref{fig:figure4} and \ref{fig:figure5} illustrate the galactic position of each class of s-process enhanced star investigated.
+Figures \ref{fig:figure4} and \ref{fig:figure5} illustrate the galactic position for each class of s-process enhanced star investigated.
 For our entire 898 sample, Figure \ref{fig:figure4} shows 97\% reside within the galactic disk and 3\% with velocity consistent to the halo.
@@
 \cite{decastro2016} present populations with $\sim$90\% thin disk membership.
-\cite{pereira2011}’s limited sample (12 stars) entirely resides within the disk.
-\cite{jorissen1993} attributes the galactic position of s-process enhanced stars as dependent on their intrinsic or extrinsic nature, concluding intrinsic s-process candidates are more concentrated towards the galactic plane.
-Since our sample is entirely extrinsic we cannot comment on the comparison between the two enhancement sources.
-However as shown in Figure \ref{fig:figure4} our extrinsically s-process enhanced sample concentrates towards the galactic plane.
-We can propose that the sample in \cite{jorissen1993} was not sufficiently large enough to represent the overarching galactic distribution of extrinsic S stars.
-On the contrary, our findings may be reflective of our sample's bias towards finding extrinsic s-process candidates since we were limited mainly to RGB stars.
-It may not be representative of the overall galactic position of enhanced s-process stars.
+\cite{pereira2011}'s limited sample (12 stars) entirely resides within the disk.
+\cite{jorissen1993} attributes the galactic position of s-process enhanced stars as dependent on their intrinsic or extrinsic nature (see their Sect.
+4.2).
+They determine the scale height for their intrinsic candidates and state they are concentrated towards the galactic plane whilst their extrinsic s-process candidates are uniformly distributed.
+Figure \ref{fig:figure5} illustrates all absolute galactic latitudes for our sample, after correcting for the LAMOST selection factor we see a uniform galactic distribution for all our extrinsic s-process candidates in-agreement with \citet{jorissen1993}.
+Since our sample is uniformly distributed we cannot comment on the scale height of our s-process candidates.
 
@@
 	\includegraphics[width=0.5\textwidth]{histogram.pdf}
-	\caption{Galactic latitude ([$|b^{\circ}|$]; x-axis) shown for: number of s-process enhanced candidates matched with Gaia DR2, and s-process candidates as a fraction of the LAMOST sample matched with Gaia DR2}
+	\caption{Absolute galactic latitude ([$|b^{\circ}|$]; x-axis) and the number of corresponding stars ([$N$] and [$N\mathbin{/}N_{LAMOST}$]; y-axis) shown for: s-process enhanced candidates matched with Gaia DR2, and the s-process candidates as a fraction of the LAMOST sample matched with Gaia DR2 }
 	\label{fig:figure5}
@@
 We found our sample contains 97\% disk star membership and 3\% with velocity consistent to the halo.
+We corrected for the LAMOST selection factor and discovered our sample is uniformly distributed across the galactic plane.
 
-We find the majority (178/187) of our s-process candidates show carbon enhancement in agreement with the literature and are classically defined CH stars.
+We find the majority (95\%) of our s-process candidates show carbon enhancement in agreement with the literature and are classically defined CH stars.
 However contrary to previous works we do not find our s-process candidates to have significantly higher [Na/Fe] than Milky Way field giants.
-Only 5/257 of our s-process candidates show enhancement in Na, and the flux residuals in three of those are likely due to interstellar dust.
-We suggest that biases between literature sources and systematic effects in measuring [Na/Fe] from stars with low $\log{g}$ contributed to this effect.
+Only 5 (< 3\%) of our s-process candidates show enhancement in Na, and the flux residuals in three of those are likely due to interstellar dust.
+We suggest that systematic effects in measuring [Na/Fe] from stars with low $\log{g}$ in previous works contributed to the
+discrepancy with our results.
 

### 2018-09-13 article/galactic_hist.py

@@ -19,23 +19,21 @@ b_l = np.absolute(l)
 s_h, bin_edges = np.histogram(b, 89)
 l_h, bin_edges = np.histogram(b_l, 89)
 div = np.divide(s_h, l_h)
-#sl_h = div
-#sl_h = np.transpose(sl_h)
+menStd = np.sqrt(s_h)
+menStd_f = ((s_h + np.sqrt(s_h))/(l_h + np.sqrt(l_h))) - (s_h/l_h)
 
-#grid_slm = np.ma.masked_where(grid_sl < 0.001, grid_sl)
-
-fig, axes = plt.subplots(2, 1)
-axes[0].bar(bin_edges[:-1], s_h, width = 1, facecolor='#FF9309', alpha=0.5)
+fig, axes = plt.subplots(2, 1, figsize=(8, 12))
+axes[0].bar(bin_edges[:-1], s_h, width = 1, facecolor='#FF9309', alpha=0.5,
+	                               yerr=menStd)
 axes[0].set_xlim(min(bin_edges), max(bin_edges))
 axes[0].set_xlabel(r'$|b|$ $[^\circ]$')
-axes[0].set_ylabel(r'Number of candidates', 
-	                rotation=90)
+axes[0].set_ylabel(r'$N$')
 
-axes[1].bar(bin_edges[:-1], div, width = 1, facecolor='#FF9309', alpha=0.5)
+axes[1].bar(bin_edges[:-1], div, width = 1, facecolor='#FF9309', alpha=0.5,
+	                               yerr=menStd_f)
 axes[1].set_xlim(min(bin_edges), max(bin_edges))
 axes[1].set_xlabel(r'$|b|$ $[^\circ]$')
-axes[1].set_ylabel(r'Fraction of candidates relative to LAMOST',
-	                 rotation=90)
+axes[1].set_ylabel(r'$N/N$ $_{LAMOST}$')
 
 for ax in axes:
     ax.xaxis.set_major_locator(ticker.MaxNLocator(6))
@@ -43,7 +41,7 @@ for ax in axes:
 
 fig.tight_layout()
 plt.show()
-'''
+
 fig.savefig('DynamicFigures/'+'histogram'+'.png')
 fig.savefig("DynamicFigures/histogram.pdf", dpi=150)
-'''
+plt.close()

### 2018-09-21 article/ms.tex
abstract update

@@
 Our sample includes; 187 s-process candidates that are enhanced in both barium and strontium, 49 stars with significant barium enhancement only, and 659 stars that show only strontium enhancement.
-Most of our sample are within temperature and log g ranges consistent with RGB populations, this is consistent with our selection bias towards finding RGB stars.
+Most of our sample are within temperature and log g ranges typical of RGB populations, this is consistent with our selection bias towards finding RGB stars.
 The majority of our s-process candidates ($95\%$) show strong carbon enhancements yet, only 5 candidates ($<3$\,\%) show evidence of sodium enhancement, in tension with previous observations of enhanced Na among s-process candidates.

### 2018-10-01 article/ms.tex
changes

@@
 
-The abundance of elements created through the slow neutron-capture process (s-process) is a measure of the nucleosynthetic reactions that occur primarily in Asymptotic Giant Branch (AGB) stars.
+The abundance of elements created through the slow neutron-capture process (s-process) is primarily a measure of the nucleosynthetic reactions that occur primarily in Asymptotic Giant Branch (AGB) stars.
 Due to their associated enrichment of the s-process element barium, stars with peculiar enhancements of carbon, and heavy elements (Z > 30) are commonly referred to as 'barium stars' \citep{Bidelman1951}.
-The naming convention associated with 'barium stars' is historical, for the purposes of this paper it is necessary to classify definitions used for subsequent discussions.
-Stars with Ba and Sr enrichment will be refereed to as s-process candidates, and singular enhancement samples will be named according to their respective element.
+The naming convention associated with 'barium stars' is historical, and for the purposes of this paper it is necessary to classify definitions used for subsequent discussions.
+Throughout this work we will refer to `s-process candidates' as stars with both Ba and Sr enrichment, and stars with just strong Sr enrichment or strong Ba enrichment will be referred to as Sr-rich or Ba-rich candidates.
 Metallicity-dependent classifications also exist in the literature.
-Metal-poor stars ([Fe/H] $\approx$ [0,-1.2]) enriched by s-process elements are classically refereed to as CH stars, we will simply define them as metal poor s-process candidates.
-An abundance criteria may also be used to define s-process enrichment, this is typically taken as threshold of $\rm[Ba/Fe]\geq +0.3$ \citep{malaney1988}.
+Metal-poor stars ([Fe/H] $\approx$ [0,-1.2]) enriched by s-process elements are classically refereed to as CH stars, whereas here we will simply define them as metal-poor s-process candidates.
+%An abundance criteria is also commonly used to define s-process enrichment, typically taken as a threshold of $\rm[Ba/Fe]\geq +0.3$ \citep{malaney1988}.
 For the purposes of this paper, s-process enrichment will be determined solely on the presence significant flux residuals as described in Section \ref{sec:cand}.
-S-process candidates can be classified as either extrinsic or intrinsic objects.
-Extrinsic s-process stars are stellar phenomena exhibiting an enhancement as the result of some polluting process.
+
+Extrinsic or intrinsic mechanisms can be invoked to explain s-process enrichment in a given star.
+%S-process candidates can be classified as either extrinsic or intrinsic objects. 
+This refers to the source of the enrichment, either a mechanism intrinsic to the star, or an extrinsic process (e.g., pollution) that resulted in an over-abundance of s-process elements.
+%Extrinsic s-process stars are stellar phenomena exhibiting an enhancement as the result of some polluting process.
 Stars intrinsically enhanced in s-process elements are known as AGB S stars.
-These stars are in the TP-AGB (thermally pulsing-asymptotic giant branch) phase.
-During this stage of nucleosynthesis, the s-process produces an over-abundance of both carbon and heavy elements.
-The thermal pulsing cycle transports these elements to surface of TP-AGB stars.
+These stars are in the thermally pulsing asymptotic giant branch (TP-AGB) phase.
+During this stage of nucleosynthesis, the slow neutron capture process produces an over-abundance of both carbon and heavy elements, and the thermal pulsing cycle transports these elements to surface of the star.
 According to the mass-transfer hypothesis, extrinsic s-process stars are a consequence of stellar wind accretion \citep{boffin1988,jorissen1992} or Roche-lobe overflow \citep{webbink1986}.
@@
 In fact, \citet{mcclure1983} determined 85\% of all s-process candidates are in binary systems.
-They further claimed that stars which appeared to be singular are actually pole-on, or highly eccentric binaries with significant radial velocity variations only occurring in a small ranges \citep{pourbaix2004}.
+They further claimed that stars which appeared to be singular stars are actually pole-on, or highly eccentric binaries with significant radial velocity variations only occurring in a small range \todo{of inclination angles?} \citep{pourbaix2004}.
 For these reasons, the properties and occurrence rate of s-process candidates are informative of the binary star fraction as a function of metallicity, the mass ratio of binary stars, as well as AGB yields across different masses and metallicities.
@@
 
-Occurring in the interior of AGB stars, the s-process synthesises roughly half of all elements heavier than iron \citep[e.g.,][]{busso1999,travaglio2001,herwig2005,bisterzo2014,karakas2014}.
-During the subsequent TP-AGB phase, thermal instabilities occur in the He shell every $10^5$ years or so, depending on the mass of the H-exhausted core.
+The s-process synthesises roughly half of all elements heavier than iron \citep[e.g.,][]{busso1999,travaglio2001,herwig2005,bisterzo2014,karakas2014}.
+During the thermal pulsing phase of AGB stars, thermal instabilities occur in the He shell every $10^5$ years or so, depending on the mass of the H-exhausted core.
 These energy bursts drive a convective zone that sweeps almost the entire region lying between the core and the He-shell, mixing the products of nucleosynthesis within these regions.
-While simultaneously forcing the star to expand and pushing the H-shell out to cooler regions \citep{karakas2002}.
-The convective envelope will then move inwards towards regions previously mixed by the thermal pulse driven convective zones.
+\todo{While simultaneously forcing the star to expand and pushing the H-shell out to cooler regions \citep{karakas2002}.} The convective envelope will then move inwards towards regions previously mixed by the thermal pulse driven convective zones.
 This phase of expansion and resulting inward movement is defined as the third dredge up (TDU), and is theorised to occur after each thermal pulse.
@@
 S-process candidates can form within a metallicity-dependent initial mass range of approximately $0.8 - 8\,M_{\odot}$ \citep{karakas2016cp}.
-The minimum mass is defined by the onset of core helium burning, and the maximum by core carbon burning.
+The minimum mass is defined by the onset of core helium burning, and the maximum is set by core carbon burning.
 The age of these stars varies considerably, with some reaching ages $\approx$ 12\,Gyr in metal-poor globular clusters.
-Less massive metal-rich stars may reach ages of $\approx$ 100Myr, this includes stars that are at the core carbon burning limit or very close to it \citep[e.g.,][]{whitelock2013}.
+Less massive metal-rich stars may reach ages of $\approx$ 100Myr, including  stars that are at the core carbon burning limit or very close to it \citep[e.g.,][]{whitelock2013}.
 The majority of s-process candidates are observed to be members of the disk \citep{jorissen1993,gomez1997,mennessier1997}.
-In \citet{pereira2011}, it is shown that metal-rich s-process candidates share similar kinematics to other metal-rich and super metal-rich stars already analysed, suggesting that they do not belong to the bulge population.
-\cite{jorissen1993} relates galactic position to the extrinsic or intrinsic nature of the s-process candidate.
-They determine the scale height for their intrinsic candidates and state they are concentrated towards the galactic plane whilst their extrinsic s-process candidates are uniformly distributed.
+In \citet{pereira2011}, it was shown that metal-rich s-process candidates share similar kinematics to other metal-rich and super metal-rich stars already known, suggesting that they do not belong exclusively to the bulge.
+\cite{jorissen1993} relates galactic position to the extrinsic or intrinsic nature of their s-process candidates.
+They determine the scale height for their intrinsic candidates and demonstrate they are concentrated towards the galactic plane, whilst their extrinsic s-process candidates are uniformly distributed in absolute galactic latitude.
+\todo{OK,..
+so maybe a comment on why that is scientifically important?
+what insight does that give?}
 
-In this paper we analyse 454,180 giant stars from the second LAMOST data release \citep{luo2015} and identify 895 s-process candidates.
+In this paper we analyse 454,180 giant stars from the second LAMOST data release \citep{luo2015}, and identify 895 s-process candidates using a data-driven approach.
 In Section \ref{sec:methods} we describe the observations and candidate selection.
@@
 Stellar parameters ($T_{\rm eff}$, $\log{g}$, [M/H], [$\alpha$/M]) were derived by \citep{ho2017} using a \emph{The Cannon} \citet{ness2016}, with labels for 9,952 giant stars in common between LAMOST and the APOGEE survey.
-Our sample is limited entirely to giants implying that we would not identify dwarf s-process enhanced stars.
+Our sample is limited entirely to giant stars, implying that we would not identify dwarf s-process enhanced stars.
 Cross-validation tests shows that the typical uncertainties are approximately 70\,K in effective temperature $\rm T_{\rm eff}$, 0.1\,dex in surface gravity $\log{g}$, 0.1\,dex in metallicity [M/H], and 0.04\,dex in the $\alpha$-element abundance relative to overall metallicity [$\alpha$/M].
@@
 The s-process candidates in this work were identified by filtering for significant flux residuals.
-We fit a Gaussian distribution with amplitude A to the flux residuals at each s-process element absorption line.
-These included; 4554\,\AA\ (\ion{Ba}{II}) and 4077\,\AA\ (\ion{Sr}{II}) wavelengths for s-process candidates, 4554\,\AA\ (\ion{Ba}{II}) and 4934\,\AA\ (\ion{Ba}{II}) wavelengths for barium enriched candidates, and wavelengths at 4077\,\AA\ (\ion{Sr}{II}) and 4215\,\AA\ (\ion{Sr}{II}) for strontium enriched candidates.
+We fit a Gaussian function with amplitude A to the flux residuals at each s-process element absorption line.
+This includes; 4554\,\AA\ (\ion{Ba}{II}) and 4077\,\AA\ (\ion{Sr}{II}) wavelengths for s-process candidates, 4554\,\AA\ (\ion{Ba}{II}) and 4934\,\AA\ (\ion{Ba}{II}) wavelengths for barium enriched candidates, and wavelengths at 4077\,\AA\ (\ion{Sr}{II}) and 4215\,\AA\ (\ion{Sr}{II}) for strontium enriched candidates.
 The amplitude of each Gaussian fit at each wavelength is analogous to the depth of each absorption line.
 The discrepancy is then measured as the difference between the normalised LAMOST flux and the data driven model.
-A negative residual indicates enrichment, this is shown for a randomly chosen s-process candidate in Figure \ref{fig:figure1}.
+A negative residual indicates enrichment, which is shown for a randomly chosen s-process candidate in Figure \ref{fig:figure1}.
 We used five filters for each spectrum and subsequent set of absorption lines in order to identify s-process enrichment, these included:
@@
 \end{enumerate}
-We use visual inspection with all candidates to exclude any results containing false positives: candidates with data reduction issues; apparent absorption finer then the spectral resolution; or overly noisy normalised LAMOST spectra.
-This approach discovers 895 s-process rich candidates which are provided in Table 1.
-This sample consists of; 187 s-process candidates, 49 barium enriched stars, and 659 stars with strontium enrichment.
-It is the largest collection of s-process enhanced stars ever discovered.
+In addition to requiring matches at two wavelengths (e.g., both 4934\,\AA\ and 4554\,\AA\ for barium enriched candidates), we visually inspected all candidates to exclude any  obvious false positives: candidates with data reduction issues; apparent absorption finer then the spectral resolution; or overly noisy spectra.
+This approach yielded 895 candidates, the details of which are tabulated in Table 1, and includes 187 s-process candidates, 49 barium enriched stars, and 659 stars with just strontium enrichment.
+This constitutes the largest collection of s-process enhanced stars ever discovered.
+\todo{what is the next biggest sample?}
 
@@
 We found that 51 s-process candidates exhibited some level of significant enhancement at the single absorption line 4238\,\AA.
-Single line enrichment discovered by our data driven approach are very likely attributed to data reduction/calibration artefacts present.
-These artefacts exist within in our data as a result of fitting a model to the LAMOST spectral data.
-As such, the 51 stars enhanced in a single Tc line can be ruled out as false positives.
-For carbon enhancement we searched for significant deviations at the CH and G band near 4300\,\AA, of which 178/187 s-process candidates exhibited significant carbon enhancement (i.e., $[\textrm{C/Fe}] \gtrsim 0.5$).
+However, single line enrichment discovered by our data driven approach are very likely attributed to data reduction/calibration artefacts present, and none of these candidates exhibited Tc enrichment at any other absorption line.
+As such, we discard these 51 stars with enhancement at a single Tc absorption line as false positives.
+For carbon enhancement we searched for significant deviations at the CH and G band near 4300\,\AA, of which 178/187 s-process candidates exhibited significant carbon enhancement.% (i.e., $[\textrm{C/Fe}] \gtrsim 0.5$).
 
@@
 \subsubsection{Abundances estimated from LAMOST spectra}
-We estimated [Ba/Fe] and [Sr/Fe] abundance ratios for all s-process enhanced candidates by synthesising spectra.
-We assumed that absorption due to metals is captured by \emph{The Cannon} model, and deviations in flux at the 4554\,\AA\ \ion{Ba}{II} line and the 4077\,\AA\ \ion{Sr}{II} transition are solely due to enhancements in Ba and Sr, respectively.
-We used an extensive grid of model
-atmospheres developed by the MARCS program \citep{marcs}, determined stellar parameters using the SME code\citep{sme},?
-
-In analyses of stellar spectra and colours, and for the analysis of integrated light from galaxies, a homogeneous grid of model
-atmospheres of late-type stars and corresponding flux spectra is needed
-We construct an extensive grid of spherically-symmetric models (supplemented with plane-parallel ones for the highest surface
-gravities), built on up-to-date atomic and molecular data, and make it available for public use.
-
-\citep{marcs,sme,vald,ispec}.
+We estimated [Ba/Fe] and [Sr/Fe] abundance ratios for all s-process enhanced candidates by spectrum synthesis.
+We assumed that absorption due to most metal lines is captured by \emph{The Cannon} model, and deviations in flux at the 4554\,\AA\ \ion{Ba}{II} line and the 4077\,\AA\ \ion{Sr}{II} transition are solely due to enhancements in Ba and Sr, respectively.
+We used the grid of MARCS model atmospheres \citep{marcs}, atomic transitions from VALD \citep{vald}, and the SME code \citep{sme,ispec} to synthesise spectra of each star, and varied the Ba and Sr abundances until they matched the flux deviations away from our data-driven model.
 We adopted the stellar parameters ($T_{\rm eff}$, $\log{g}$, [Fe/H]) from \citet{ho2017}, and assume a microturbulence of $v_{mic} = 2\,{\rm km\,s}^{-1}$.
@@
 
-Our analysis shows 186/187 of our s-process candidates exhibit enhancement at the BaII resonance line 4554 with a $\rm[Ba/Fe] \geq +0.3$, and a average abundance error of 0.1.
-Previous studies \citet{malaney1988} have defined s-process candidates through an abundance criteria of $\rm[Ba/Fe]\geq +0.3$.
+Previous studies have used a $\textrm{[Ba/Fe]} > +0.3$ threshold to define a star being a s-process candidate \citep{malaney1988}.
+Our abundance analysis shows 186/187 of our s-process candidates -- identified from flux residuals alone -- meet this criteria based on spectrum synthesis of the 4554\,\AA\ transition.
 Using this measure, only one star ($\rm J092155.95+265253.4$) from our sample exhibits a lower [Ba/Fe] of 0.12.
@@
 $\rm J092155.95+265253.4$ shows both a negative residual at 4554\,\AA\ and carbon enrichment, we therefore conclude that this single deviant case can be classified as a s-process candidate.
-This additionally applies to candidates that fall under $\rm[Ba/Fe]\geq +0.3$ due to the average abundance error.
+%This additionally applies to candidates that fall under $\rm[Ba/Fe]\geq +0.3$ due to the average abundance error.
 
 \subsection{Dynamics}
-We integrated the galactic orbits using recent astrometry from Gaia \citep{gaia2016,gaia2018b, cropper2018, katz2018, lindegren2018, sartoretti2018} for 871/895 s-process enhanced stars with parallax > 0 and parallax/parallax error > 5 selection filters.
-We integrated each star backwards for $0.5\,\textrm{Gyr}$ using the \texttt{gala} Python package \citep{price2017} in a Milky Way-like potential \citep{mwpotential2014} that consists of four components: a \citet{hernquist1990} bulge and nucleus, a \citet{miyamoto1975} disk, and a \citet{nfw1997} halo.
+We integrated the galactic orbits using recent astrometry from the second Gaia data release \citep{gaia2016,gaia2018b, cropper2018, katz2018, lindegren2018, sartoretti2018} for 871/895 s-process enhanced stars with positive parallaxes ($\varpi > 0$) and parallax S/N of five or above ($\varpi/\sigma_\varpi > 5$).
+We integrated each star backwards for $0.5\,\textrm{Gyr}$ using the \texttt{gala} Python package \citep{price2017} in a Milky Way-like potential \citep{mwpotential2014} that consists of three components: a \citet{hernquist1990} bulge and nucleus, a \citet{miyamoto1975} disk, and a \citet{nfw1997} halo.
 We computed spatial velocities relative to the local standard of rest, where $U_{LSR}$ is positive towards the Galactic centre, $V_{LSR}$ is positive in the direction of Galactic rotation ($l=90^{\circ}, b=0^{\circ}$), and $W_{LSR}$ is positive towards the north galactic pole ($b=90^{\circ}$).
@@
 On 07 January 2018 we acquired a high-resolution spectrum of two s-process candidates (J09162834+0259348 and J08351472-0548480) using the MIKE (Magellan Inamori Kyocera Echelle) \citep{bernstein2003} spectrograph on the Magellan Clay telescope \citep{schectman2003} at Las Campanas Observatory, Chile.
-These two candidates were observed as part of another program not a detailed follow-up campaign.
-They were selected based on observability constraints and ranked by their apparent visual magnitude, with both candidates having $V \approx 12$.
+These two candidates were observed as part of another program, and do not represent a comprehensive follow-up observational campaign.
+These targets were selected based on observability constraints and ranked by their apparent visual magnitude, with both candidates having $V \approx 12$.
 We observed both stars in good seeing using the 0.7 arcsecond slit and 2x2 spatial on-chip binning, providing a spectral resolution of $\mathcal{R} \approx 28,000$.
@@
 \subsection{Extrinsic or intrinsic}
-S-process enrichment can be explained by intrinsic or extrinsic phenomena.
+S-process enrichment can be explained by intrinsic or extrinsic mechanisms.
 Intrinsically enhanced s-process candidates must be massive enough to reach the TP-AGB phase, and extrinsic s-process candidates must be in a binary with a previously polluting TP-AGB star companion (AGB S star).
-Previous literature \citep{van2017} \hspace{0.3mm} states only 33\% of their sample are post-main-sequence s-process candidates (extrinsic).
-In comparison, Figure \ref{fig:figure2} shows that the majority of our sample are within temperature and log g ranges consistent with RGB populations.
-This highlights that our sample does not contain stars evolved enough to reach the TP-AGB phase and therefore, must be extrinsic s-process candidates.
-This is in agreement with our sample selection bias given we were predominantly restricted to RGB stars.
+\citet{van2017} found that only 33\% of their sample are post-main-sequence s-process candidates (extrinsic).
+In comparison, Figure \ref{fig:figure2} shows that the majority of our sample are within temperature and surface gravity ranges consistent with the first ascent giant branch.
+This highlights that our sample does not appear to contain many stars evolved enough to reach the TP-AGB phase and therefore, must be extrinsic s-process candidates.
+However stars with $\log{g} \lesssim 2$ in Figure \ref{fig:figure2} are possible AGB star candidates, and their intrinsic or extrinsic nature is not certain.
+
+%This is in agreement with our sample selection bias given we were predominantly restricted to RGB stars.
 However stars with temperatures below 3800K in Figure \ref{fig:figure2} are possible AGB candidates, and their intrinsic or extrinsic nature is not certain.
@@
 %however, these [Na/Fe] ratios do not exhibit variations in metallicity
-We find that less than $3$\,\% of our s-process candidates show enhanced sodium all of which have values of $\log{g} \approx 3$.
-It is possible our 5/187 enhanced sodium candidates are false-positives resulting from interstellar dust absorption.
-Using the IRSA's all-sky dust map \citep{schlafly2011}, we find that 2/5 of these candidates have E(B-V)$\approx$ 0.35 confirming that the flux residuals around the Na doublet are due to interstellar absorption.
-However 3/5 candidates exhibit low ($\approx$0.045) E(B-V) values indicating the enhancement is more likely due to stellar absorption.
+We find that only 5/187 s-process candidates ($<3$\,\%) show enhanced sodium, and all 5 have  $\log{g} \approx 3$.
+Moreover, it is likely that some of these stars appear to have high sodium due to interstellar dust lines of Na being misinterpreted as stellar absorption.
+Using the IRSA's all-sky dust map \citep{schlafly2011}, we find that 2/5 of these candidates have E(B-V)$\approx$ 0.35, suggestive that the flux residuals around the Na doublet are due to interstellar absorption.
+However 3/5 candidates exhibit low ($\approx$0.045) E(B-V) values, indicating the enhancement is more likely due to stellar absorption.
 These results suggest that sodium-rich material from a companion TP-AGB star has polluted these 3 s-process candidates.
 It also highlights sodium enhancement is by no means ubiquitous in s-process candidates.
-Yet, low resolution spectra can imitate Na line saturation and limits flux enhancement even if an abundance enhancement is present.
+%Yet, low resolution spectra can imitate Na line saturation and limits flux enhancement even if an abundance enhancement is present.
 %Previous studies \citep[e.g.,][]{decastro2016} suggest lower $\log{g}$ values systematically contribute to higher [Na/Fe] abundance ratios.
 
-The data that led \citet{decastro2016} to conclude that s-process candidates have higher [Na/Fe] ratios is subject to systematic differences (biases) between Milky Way studies of normal FGK-type stars, and those focussed on s-process candidates.
-This has the potential to contain unresolved differences in the reported [Na/Fe] abundance ratio.
+The data that led \citet{decastro2016} to conclude that s-process candidates have higher [Na/Fe] ratios is subject to systematic differences (biases) between Milky Way studies of normal FGK-type stars, and those focused on s-process candidates.
+Specifically, the  comparisons made by \citet{decastro2016} included  [Na/Fe] abundance ratios that were derived from different stellar populations, using different abundance analysis techniques.
+This has the potential to amplify systematic differences in the reported [Na/Fe] abundance ratio.
 These systematic effects would also contribute to the observed correlation between [Na/Fe] and $\log{g}$, since intrinsic s-process candidates (by definition) have low $\log{g}$ values.
@@
 \subsection{Carbon bands}
-During the AGB phase of a star, carbon abundance is a product of helium fusion via the triple-alpha process.
+During the AGB phase of a star, carbon is produced through helium fusion during the triple-alpha process.
 Giants and supergiants become enhanced in carbon through TDU process discussed in Section \ref{sec:intro}, and extrinsic carbon enhancement occurs via mass transfer from a binary AGB star.
 Our analysis identifies carbon enhanced candidates by searching for flux residuals in the CH and G band regions near 4300\,\AA.
-We found 178/187 of our s-process candidates to have carbon enrichment (i.e., $[\textrm{C/Fe}] \gtrsim 0.5$).
-These 178 stars have metallicities ranging of 0 to -1.2 and are classically referred to as CH stars \citep[e.g.][]{luck1991, mcclure1997}.
+We found 178/187 of our s-process candidates to have carbon enrichment.
+These 178 stars have metallicities ranging from [Fe/H] = $-1.2$ to [Fe/H] $= 0$ and would classically be described in the literature as CH stars \citep[e.g.][]{luck1991, mcclure1997}.
 We simply define them as metal poor s-process candidates.
@@
 In Figure \ref{fig:figure3} we show the heavy-to-light s-process abundance ratio (taken as [Ba/Sr]) for all 187 s-process candidates identified in LAMOST.
-Although the [Ba/Sr] ratio is quite noisy ($\sim$0.2\,dex) the overall metallicity [Fe/H] is quite precise (0.1\,dex).
+Although the [Ba/Sr] ratio is quite noisy ($\sim$0.2\,dex) the overall metallicity [Fe/H] is quite precise (0.1\,dex or better).
 The final surface s-process index [Ba/Sr] seen in Figure \ref{fig:figure3} represents degree of the s-process element pollution, and is an indication of the binary AGB companion's mass.
@@
 Theoretical models show that this source is dominant in low-mass AGB stars and it follows, that most of the progenitors for s-process enhancement in our sample are low-mass AGB stars between $1 - 3\,M_{\odot}$.
-However our results do not indicate when the mass transfer occurred, and our candidates fitting these theoretical yields may not have the correlating binary companion masses.
+However our results do not indicate when the mass transfer occurred, and our candidates fitting these theoretical yields may not have the corresponding binary companion masses.
 Mass transfer may have occurred early on in the AGB S binary companion star's lifespan.
@@
 
-The majority of our sample show pro-grade orbits that were consistent with membership in the Milky Way disk.
-Figures \ref{fig:figure4} and \ref{fig:figure5} illustrate the galactic position for each class of s-process enhanced star investigated.
-For our entire 898 sample, Figure \ref{fig:figure4} shows 97\% reside within the galactic disk and 3\% with velocity consistent to the halo.
-Our results show similar trends to the literature, samples from \cite{gomez1997} and
-\cite{decastro2016} present populations with $\sim$90\% thin disk membership.
-\cite{pereira2011}'s limited sample (12 stars) entirely resides within the disk.
+The majority of our sample show prograde orbits that are consistent with membership in the Milky Way disk.
+Figures \ref{fig:figure4} and \ref{fig:figure5} illustrate the galactic velocities for all s-process candidates in this work.
+For our entire sample, Figure \ref{fig:figure4} shows that 97\% have velocities that are consistent with the disk, and just 3\% with velocities that are more consistent with the halo.
+Our results show similar trends to the literature, where \citet{gomez1997} and
+\citet{decastro2016} present samples with $\sim$90\% thin disk membership.
+\cite{pereira2011} sample of 12 s-process stars are fully consistent with disk membership.
 \cite{jorissen1993} attributes the galactic position of s-process enhanced stars as dependent on their intrinsic or extrinsic nature (see their Sect.
 4.2).
-They determine the scale height for their intrinsic candidates and state they are concentrated towards the galactic plane whilst their extrinsic s-process candidates are uniformly distributed.
-Figure \ref{fig:figure5} illustrates all absolute galactic latitudes for our sample, after correcting for the LAMOST selection factor we see a uniform galactic distribution for all our extrinsic s-process candidates in-agreement with \citet{jorissen1993}.
-Since our sample is uniformly distributed we cannot comment on the scale height of our s-process candidates.
+They estimate the scale height for their intrinsic candidates, and find that they are concentrated towards the galactic plane whilst their extrinsic s-process candidates are uniformly distributed in absolute galactic latitude.
+Figure \ref{fig:figure5} shows all absolute galactic latitudes for our sample.
+After coarsely correcting for the LAMOST selection function we find that our extrinsic s-process candidates show a near uniform distribution in absolute galactic latitude, in agreement with \citet{jorissen1993}.
+Since our sample is primarily extrinsic s-process stars -- and these are uniformly distributed with absolute galactic latitude -- we cannot comment on the scale height of our s-process candidates.
 
@@
 	\includegraphics[width=0.5\textwidth]{toomre.pdf}
-	\caption{Galactic distribution represented by a Toomre diagram, spatial velocities ([V (km/s)]; x-axis) and ([$\sqrt{U^2+W^2}$ (km/s)]; y-axis) for number of s-process enhanced candidates matched with Gaia DR2.
+	\caption{Galactic distribution represented by a Toomre diagram, spatial velocities (V km\,s$^{-1}$; x-axis) and ($\sqrt{U^2+W^2}$ km\,s$^{-1}$; y-axis) for number of s-process enhanced candidates matched with Gaia DR2.
 Coloured markers red, blue, and purple highlight barium, strontium, and both barium and strontium enhancement respectively.}
@@
 	\includegraphics[width=0.5\textwidth]{histogram.pdf}
-	\caption{Absolute galactic latitude ([$|b^{\circ}|$]; x-axis) and the number of corresponding stars ([$N$] and [$N\mathbin{/}N_{LAMOST}$]; y-axis) shown for: s-process enhanced candidates matched with Gaia DR2, and the s-process candidates as a fraction of the LAMOST sample matched with Gaia DR2 }
+	\caption{Absolute galactic latitude ($|b^{\circ}|$; x-axis) and the number of corresponding stars ($N$ and $N\mathbin{/}N_{LAMOST}$; y-axis) shown for: s-process enhanced candidates matched with Gaia DR2, and the s-process candidates as a fraction of the LAMOST sample matched with Gaia DR2 }
 	\label{fig:figure5}
@@
 From 454,180 giant stars, we identify 895 s-process enhanced stars including; 187 s-process candidates, 49 barium enriched stars, and 659 stars with strontium enrichment.
-This sample size is the greatest total number of s-process candidates known, and represents the largest sample of s-process enhanced stars to date.
-We found our sample contains 97\% disk star membership and 3\% with velocity consistent to the halo.
-We corrected for the LAMOST selection factor and discovered our sample is uniformly distributed across the galactic plane.
+This sample size is the greatest number of s-process candidates known.
+We found 97\% of our sample to have velocities that are consistent with disk membership, and just 3\% with velocities more consistent with the halo.
+We find our sample is nearly uniformly distributed in absolute galactic latitudes.%We corrected for the LAMOST selection factor and discovered our sample is uniformly distributed across the galactic plane.
 
-We find the majority (95\%) of our s-process candidates show carbon enhancement in agreement with the literature and are classically defined CH stars.
-However contrary to previous works we do not find our s-process candidates to have significantly higher [Na/Fe] than Milky Way field giants.
-Only 5 (< 3\%) of our s-process candidates show enhancement in Na, and the flux residuals in three of those are likely due to interstellar dust.
+We find the majority (95\%) of our s-process candidates show carbon enhancement.
+However contrary to previous works we do not find s-process candidates to have significantly higher [Na/Fe] than Milky Way field giants.
+Only 5 ($<$3\%) of our s-process candidates show enhancement in Na, and the flux residuals in three of those are likely due to interstellar dust.
 We suggest that systematic effects in measuring [Na/Fe] from stars with low $\log{g}$ in previous works contributed to the
-discrepancy with our results.
+discrepancy with our results, as well as comparisons between studies that make use of different abundance analysis techniques.
 
